### 2019-09-17 rainbowCAM.tex
First commit

 \documentclass[preprint,showpacs,preprintnumbers,amssymb,superscriptaddress,aps,prd,nofootinbib,11pt]{revtex4-1}
\linespread{1.2}

\usepackage{graphicx, epsfig, amssymb} 
\usepackage{amsmath, amsfonts}
\usepackage{bm} 
\usepackage{enumitem}
\usepackage[usenames]{color}
\definecolor{navyblue}{rgb}{0.0, 0.0, 0.5}
\usepackage[linktocpage,colorlinks=true,allcolors=navyblue]{hyperref}
\usepackage[caption=false]{subfig}
\usepackage[utf8]{inputenc}
\usepackage{tensor}
\usepackage{soul}
%\usepackage{enumerate}
\usepackage{pict2e}
\usepackage{diagbox}
\usepackage{empheq}

%\usepackage[margin=1in]{geometry}
\usepackage{float}
%\usepackage{subfig}
\usepackage{comment}
\usepackage{array}
%\usepackage{varioref}
%\usepackage[hidelinks]{hyperref}
%\usepackage{cleveref}
%\usepackage[numbers]{natbib}
\usepackage{units}
\usepackage{wasysym}
%\usepackage{caption}
%\usepackage{subcaption}

\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
\newcommand{\ff}{\hat{f}}

\def\l{\left}
\def\r{\right}
\def\p{\partial}

\newcommand{\angarg}{(\theta,\phi)}
\newcommand{\dth}{\frac{d}{d \theta}}
\newcommand{\sh}{ {}_{-s} S_{\ell m}^{a \omega}}
\newcommand{\zh}{ {}_{-s} Z_{\ell m}^{a \omega}}
\newcommand{\syjm}{  {}_{-s}Y_{jm} }
\newcommand{\sylm}{  {}_{-s} Y_{\ell m} }
\newcommand{\sumjm}{\sum_{j=s}^{\infty} \sum_{m=-j}^{j}}
\newcommand{\sumjms}{\sum_{j,m}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\lmws}{{\ell m \omega s}}
\newcommand{\nn}{\nonumber}

\newcommand*\widefbox[1]{\fbox{\rule[-2cm]{0pt}{4cm}\hspace{2em}#1\hspace{2em}}}

\newcommand{\sam}[1]{\textcolor{red}{(Sam: #1)}}
\newcommand{\tom}[1]{\textcolor{blue}{(Tom: #1)}}
\newcommand{\mo}[1]{\textcolor{green}{(Mohamed: #1)}}

\begin{document}

%\title{Off-axis plane wave scattering on rotating black holes}
\title{Scattering from compact objects: Regge poles and complex angular momentum}

\author{Mohamed Ould Elhadj}\email{m.ouldelhadj@sheffield.ac.uk}
\affiliation{Consortium for Fundamental Physics,  School of Mathematics and Statistics,
University of Sheffield, Hicks Building, Hounsfield Road, Sheffield S3 7RH, United Kingdom \looseness=-1}
%
\author{Tom Stratton}\email{tstratton1@sheffield.ac.uk}
\affiliation{Consortium for Fundamental Physics,  School of Mathematics and Statistics,
University of Sheffield, Hicks Building, Hounsfield Road, Sheffield S3 7RH, United Kingdom \looseness=-1}
%
\author{Sam R. Dolan}\email{s.dolan@sheffield.ac.uk}
\affiliation{Consortium for Fundamental Physics,  School of Mathematics and Statistics,
University of Sheffield, Hicks Building, Hounsfield Road, Sheffield S3 7RH, United Kingdom \looseness=-1}
%
\begin{abstract}
To be written
\end{abstract}

\date{\today}

\maketitle

\section{Introduction}
 The topic of time-independent scattering has been studied in detail since the 1960s \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970}, and there now exists a substantial literature \cite{Mashhoon:1973zz,Chrzanowski:1976jb,DeLogi:1977dp,Sanchez:1977vz,MatznerRyan1978,Handler:1980un,Matzner:1985rjn,Futterman:1988ni,Andersson:1995vi,Glampedakis:2001cx,Dolan:2006vj,Dolan:2007ut,Dolan:2008kf,Crispino:2009xt,Cotaescu:2014jca,Sorge:2015yoa,Gussmann:2016mkp,Leite:2017zyb,Nambu:2019sqn, Folacci:2019vtt,Leite:2019eis}.

\acknowledgments
T.S.~acknowledges financial support from EPSRC. S.R.D.~acknowledges financial support from the European Union's Horizon 2020 research and innovation programme under the H2020-MSCA-RISE-2017 Grant No.~FunFiCO-777740, and from the Science and Technology Facilities Council (STFC) under Grant No.~ST/P000800/1.

\bibliography{rainbowCAM}
\bibliographystyle{apsrev4-1}

\end{document}

### 2019-09-17 rainbowCAM.tex
blah

@@
 
-%\title{Off-axis plane wave scattering on rotating black holes}
-\title{Scattering from compact objects: Regge poles and complex angular momentum}
+\title{Scattering from compact objects, Regge poles \\ and the Complex Angular Momentum method}
 
@@
 \section{Introduction}
+Blah.
+
  The topic of time-independent scattering has been studied in detail since the 1960s \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970}, and there now exists a substantial literature \cite{Mashhoon:1973zz,Chrzanowski:1976jb,DeLogi:1977dp,Sanchez:1977vz,MatznerRyan1978,Handler:1980un,Matzner:1985rjn,Futterman:1988ni,Andersson:1995vi,Glampedakis:2001cx,Dolan:2006vj,Dolan:2007ut,Dolan:2008kf,Crispino:2009xt,Cotaescu:2014jca,Sorge:2015yoa,Gussmann:2016mkp,Leite:2017zyb,Nambu:2019sqn, Folacci:2019vtt,Leite:2019eis}.

### 2019-10-01 rainbowCAM.tex
minor change
hello
added section on classification of QNMs

@@
 \section{Introduction}
-Blah.
+Blah. hello. some more text.
 
  The topic of time-independent scattering has been studied in detail since the 1960s \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970}, and there now exists a substantial literature \cite{Mashhoon:1973zz,Chrzanowski:1976jb,DeLogi:1977dp,Sanchez:1977vz,MatznerRyan1978,Handler:1980un,Matzner:1985rjn,Futterman:1988ni,Andersson:1995vi,Glampedakis:2001cx,Dolan:2006vj,Dolan:2007ut,Dolan:2008kf,Crispino:2009xt,Cotaescu:2014jca,Sorge:2015yoa,Gussmann:2016mkp,Leite:2017zyb,Nambu:2019sqn, Folacci:2019vtt,Leite:2019eis}.
+
+\section{Classification of quasinormal modes}
+
+The study of stellar quasinormal modes began with a general relativistic extension of the Newtonian treatment of fluid pulsations of stars.
+Newly formed neutron stars, the remnants of supernovae collapse, are predicted to pulsate with a large initial energy \cite{thorne1967non}.
+It was and still is of interest to study how these pulsations lose energy in the form of gravitational waves.
+Recently, the gravitational waves from a neutron star merger were detected...
+In particular the emitted radiation should cary a signature of the modes of oscillation allowed inside the star.
+These fluid modes can be classified in analogy to their real Newtonian counterparts, with an additional damping time due to emission of GWs.
+Later, Kokkotas and Schutz showed that an additional family of modes existed \cite{Kokkotas:1986gd,Kokkotas:1992ka}, dubbed $\omega$-modes.
+These modes are characterised by a negligible excitation of fluid motion (and in the axial sector no fluid motion).
+They're highly damped and correspond to excitations of the dynamical perturbed space-time.
+For an excellent review of (gravitational) quasinormal modes in relativistic stars and black holes see \cite{Kokkotas:1999bd}.
+
+We consider the scalar field, with modes that obeys an equation of motion very similar to the axial gravitational wave modes.
+Accordingly, a similar spectrum for scalar modes can be expected (with no fluid excitation).
+Whilst these are arguably of less astrophysical interest, they are nonetheless a good model for axial GWs and allow us to make a first step towards a CAM approach for perturbed relativistic stars.
+We will classify the scalar $\omega$-modes as the axial GW modes have been, we have
+
+	\begin{enumerate}
+		\item Curvature modes: These modes exist for all relativistic stars. They are rapidly damped, and the damping is larger for less compact bodies. 
+		\item Trapped modes: These are the scalar analogue of the axial trapped modes considered by Chandrasekhar and Ferrari \cite{Chandrasekhar449}.
+They exist for bodies with $R/M < 3$.
+These models have an effective radial potential with a local minimum somewhere inside the star, and local maximum at the photon sphere $r=3M$.
+The trapped modes are essentially the first few curvature modes with energy less than the potential barrier.
+There are a finite number of them, and the number increases with the depth of the potential well.
+		\item Interface modes: also known as $\omega_{\text{II}}$-modes, these were discovered by Leins \textit{et al.} \cite{Leins:1993zz}.
+They used a generalisation of Leaver's continued fraction  method as well as a `Wronskain method' that allowed them to accurately compute these modes which are characterised by very rapid damping (large imaginary part).
+This second branch of modes is the most similar to the Schwarzschild black hole quasinormal modes.
+We have taken their continued fraction method one step further (see section...) in order to be confident with our results.
+	\end{enumerate}
 

### 2019-10-02 rainbowCAM.tex
added some references

@@
 
-We consider the scalar field, with modes that obeys an equation of motion very similar to the axial gravitational wave modes.
+We consider the massless scalar field which only couples to the body via gravitation.
+The scalar modes obey an equation of motion very similar to the axial gravitational wave sector.
 Accordingly, a similar spectrum for scalar modes can be expected (with no fluid excitation).

### 2019-10-13 rainbowCAM.tex
Minor tinkering
Add files via upload

@@
- \documentclass[preprint,showpacs,preprintnumbers,amssymb,superscriptaddress,aps,prd,nofootinbib,11pt]{revtex4-1}
+\documentclass[aps,prd,longbibliography,reprint,twocolumn,amsmath,amssymb,amsfonts,showpacs,superscriptaddress]{revtex4-1}%reprint
+
 \linespread{1.2}
@@
 \newcommand{\nn}{\nonumber}
+\newcommand{\be}{\begin{equation}}
+\newcommand{\ee}{\end{equation}}
 
@@
 
+\renewcommand{\arraystretch}{1.3} % espace entre les lignes de la table
+%\setlength{\tabcolsep}{.3cm} % espace entre les colonnes de la table
+
+\usepackage{footnote}
+\usepackage{tablefootnote}
+
+\usepackage{threeparttable}
+
 \begin{document}
@@
 
-\author{Mohamed Ould Elhadj}\email{m.ouldelhadj@sheffield.ac.uk}
+\author{Mohamed \surname{Ould~El~Hadj}}
+\email{m.ouldelhadj@sheffield.ac.uk}
+
+\affiliation{Equipe Physique
+Th\'eorique, SPE, UMR 6134 du CNRS
+et de l'Universit\'e de Corse,\\
+Universit\'e de Corse, Facult\'e des Sciences, BP 52, F-20250 Corte,
+France}
+
 \affiliation{Consortium for Fundamental Physics,  School of Mathematics and Statistics,
@@
  The topic of time-independent scattering has been studied in detail since the 1960s \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970}, and there now exists a substantial literature \cite{Mashhoon:1973zz,Chrzanowski:1976jb,DeLogi:1977dp,Sanchez:1977vz,MatznerRyan1978,Handler:1980un,Matzner:1985rjn,Futterman:1988ni,Andersson:1995vi,Glampedakis:2001cx,Dolan:2006vj,Dolan:2007ut,Dolan:2008kf,Crispino:2009xt,Cotaescu:2014jca,Sorge:2015yoa,Gussmann:2016mkp,Leite:2017zyb,Nambu:2019sqn, Folacci:2019vtt,Leite:2019eis}.
+
+\section{Differential scattering cross sections for scalar waves, their CAM representation and their Regge pole approximations}
+\label{SecII}
+
+In this section, we describe our compact objets model and we recall the partial wave expansions of the differential scattering cross section for plane monochromatic scalar waves impinging upon a compact body and we apply the CAM-approach developed in \cite{Folacci:2019cmc} and \cite{Folacci:2019vtt}
+
+\subsection{Our model}
+\label{SecIIa}
+
+  We consider that the gravitating source a spherically symmetric incompressible perfect fluid ball of uniform
+density (see Ref~\cite{Dolan:2017rtj} and reference therein) in a coordinate system $\{t,r,\theta,\varphi\}$ and is defined by the metric
+\begin{equation}\label{Line_elem}
+  ds^2= -f(r) dt^2+h(r)^{-1}dr^2+r^2d\sigma_2^2
+\end{equation}
+where $d\sigma_2^2$ denotes the metric on the unit 2-sphere $S^2$.
+Here, the radial function $h(r)$ is continuous but not differentiable across the surface of the star $r=R$ and the function $f(r)$ is one, but not twice, differentiable.
+We recall that, in the exterior of the star (i.e., $r>R$), we have $f(r)=h(r)=a-2M/r$ by Birkhoff's~\cite{VojeJohansen:2005nd}.
+In the interior of the star (i.e.
+$r<R$), we have the Schwarzschild solution for an incompressible fluid~\cite{Shapiro1983}
+
+\begin{subequations}\label{Interior_Solution}
+\begin{align}\label{Interior_Solution_f}
+    f(r) =\frac{1}{4}\left(1-\frac{2 M r^2}{R^3}\right)+\frac{9}{4}\left(1-\frac{2M}{R}\right) \nonumber\\ -\frac{3}{2}
+                \sqrt{\left(1-\frac{2M}{R}\right)\left(1-\frac{2 M r^2}{R^3}\right)}
+\end{align}
+\begin{equation}\label{Interior_Solution_h}
+ h(r) =1-\frac{2 M r^2}{R^3}
+\end{equation}
+\end{subequations}
+
+\subsection{Partial wave expansions of differential scattering cross sections}
+\label{SecIIb}
+
+We recall that, for the scalar field, the differential scattering cross section is given by (see, e.g.,\cite{Dolan:2017rtj} and references therein)
+\begin{equation}\label{Scalar_Scattering_diff}
+  \frac{d\sigma}{d\Omega} = |\hat{f}(\omega,\theta)|^2
+\end{equation}
+where
+\begin{equation}\label{Scalar_Scattering_amp}
+ \hat{f}(\omega,\theta) = \frac{1}{2 i \omega} \sum_{\ell = 0}^{\infty} (2\ell+1)[S_{\ell}(\omega)-1]P_{\ell}(\cos\theta)
+\end{equation}
+denotes the scattering amplitude.
+In Eqs.~(\ref{Scalar_Scattering_amp}), the functions $P_{\ell}(\cos\theta)$ are the Legendre polynomials \cite{AS65}.
+We also recall that the $S$-matrix elements $S_{\ell}(\omega)$ appearing in Eqs.~(\ref{Scalar_Scattering_amp}) can be defined from the modes $\phi_{\omega \ell}^{in}$ solutions of the homogenous radial equation
+\begin{equation}
+\label{H_Radial_equation}
+\left[\frac{d^{2}}{dr_{\ast}^{2}}+\omega^{2}-V_{\ell}(r)\right]\phi_{\omega\ell}= 0
+\end{equation}
+here $dr/dr^\ast =\sqrt{f(r)h(r)}$ denotes the tortoise coordinate, where
+\begin{equation}\label{Inside_Potentiel}
+  V_{\ell}(r) =f(r)\left[\frac{\ell(\ell+1)}{r^2}+\frac{h(r)}{2r}\left(\frac{f'(r)}{f(r)}+\frac{h'(r)}{h(r)}\right)\right]
+\end{equation}
+the potential inside the star ($r<R$) and  $V_{\ell}(r)$ reduces to the Regge-Wheeler potential outside the star ($r>R$)
+\begin{equation}\label{RW_Potentiel}
+  V_{\ell}(r) =\left(1-\frac{2M}{r}\right)\left(\frac{\ell(\ell+1)}{r^2}+\frac{2M}{r^3}\right)
+\end{equation}
+and the tortoise coordinates $r^\ast$ reduces to $r^\ast = r+ 2M \ln [r/(2M) -1]+\mathrm{const}$.
+
+It is important to recall that the modes $\phi_{\omega \ell}^{in}$ have a regular behavior at the origin $r \to 0$  
+\begin{equation}\label{bc_1_in}
+\phi^\mathrm{in}_{\omega  \ell}(r) \scriptstyle{\underset{r \to 0}{\sim}}
+\displaystyle{r^{\ell}}.
+\end{equation}
+of the compact body and an asymptotic behavior at spatial infinity $r \to +\infty$ (i.e., for $r_\ast \to +\infty$) of the form
+\begin{equation}\label{bc_2_in}
+\phi^\mathrm{in}_{\omega  \ell}(r) \scriptstyle{\underset{r_\ast \to +\infty}{\sim}}
+\displaystyle{ A^{(-)}_\ell (\omega) e^{-i\omega r_\ast} + A^{(+)}_\ell (\omega) e^{+i\omega r_\ast}}.
+\end{equation}
+In this last equation, the coefficients $A^{(-)}_\ell (\omega)$ and  $A^{(+)}_\ell (\omega)$ are complex amplitudes and we have
+\begin{equation}\label{Matrix_S}
+  S_{\ell}(\omega) =  e^{i(\ell+1)\pi} \, \frac{A_{\ell}^{(+)}(\omega)}{A_{\ell}^{(-)}(\omega)}.
+\end{equation}
+
+\subsection{CAM representation of the scattering amplitude}
+\label{SecIIc}
+
+To construct the CAM representation, we follow the steps in section~II of the Ref~\cite{Folacci:2019cmc} and recall the main results.
+
+By using the Sommerfeld-Watson transformation \cite{Watson18,Sommerfeld49,Newton:1982qc} which permits us to write
+\begin{equation}\label{SWT_gen}
+\sum_{\ell=0}^{+\infty} (-1)^\ell F(\ell)= \frac{i}{2} \int_{\cal C} d\lambda \, \frac{F(\lambda -1/2)}{\cos (\pi \lambda)}
+\end{equation}
+with a function $F$ without any singularities on the real $\lambda$ axis,we replace in Eq.~(\ref{Scalar_Scattering_amp}) the discrete sum over the ordinary angular momentum $\ell$ by a contour integral in the complex $\lambda$ plane (i.e., in the complex $\ell$ plane with $\lambda = \ell +1/2$).
+By noting that $P_\ell (\cos \theta)=(-1)^\ell P_\ell (-\cos \theta)$, we obtain
+\begin{eqnarray}\label{SW_Scalar_Scattering_amp}
+& & \hat{f}(\omega,\theta) = \frac{1}{2 \omega}  \int_{\cal C} d\lambda \, \frac{\lambda}{\cos (\pi \lambda)} \nonumber \\
+&&  \qquad\qquad   \times \left[ S_{\lambda -1/2} (\omega) -1 \right]P_{\lambda -1/2} (-\cos \theta).
+\end{eqnarray}
+In Eqs.~(\ref{SWT_gen}) and (\ref{SW_Scalar_Scattering_amp}), the integration contour encircles counterclockwise the positive real axis of the complex $\lambda$ plane, i.e., we take ${\cal C}=]+\infty +i\epsilon,+i\epsilon] \cup
+[+i\epsilon,-i\epsilon] \cup [-i\epsilon, +\infty -i\epsilon[$ with $\epsilon \to 0_+$ (see Fig.1 Ref~\cite{Folacci:2019cmc}).
+
+Here, we note that, the Legendre function of first kind $P_{\lambda -1/2} (z)$ denotes the analytic extension of the Legendre polynomials $P_\ell (z)$.
+It is defined in terms of hypergeometric functions by \cite{AS65}
+\begin{equation}\label{Def_ext_LegendreP}
+P_{\lambda -1/2} (z) = F[1/2-\lambda,1/2+\lambda;1;(1-z)/2].
+\end{equation}
+In Eq.~(\ref{SW_Scalar_Scattering_amp}), $S_{\lambda -1/2} (\omega)$ denotes ``the'' analytic extension of $S_\ell (\omega)$. It is given by [see Eq.~(\ref{Matrix_S})]
+\begin{equation}\label{Matrix_S_CAM}
+  S_{\lambda -1/2}(\omega) =  e^{i(\lambda + 1/2)\pi} \, \frac{A_{\lambda -1/2}^{(+)}(\omega)}{A_{\lambda -1/2}^{(-)}(\omega)}
+\end{equation}
+where the complex amplitudes $A^{(-)}_{\lambda -1/2} (\omega)$ and  $A^{(+)}_{\lambda -1/2} (\omega)$ are defined from the analytic extension of the modes $\phi_{\omega \ell}^{in}$, i.e., from the function $\phi_{\omega ,\lambda -1/2}^{in}$.
+
+It is important to note that the poles of  $S_{\lambda -1/2} (\omega)$ in the complex $\lambda$ plan (i.e., the Regge poles) are defined  as  the zeros $\lambda_n(\omega)$ with $n=1,2,3,\ldots$ of the coefficient  $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~(\ref{Matrix_S_CAM})]
+\begin{equation}\label{PR_def_Am}
+A^{(-)}_{\lambda_n(\omega)-1/2} (\omega)=0.
+\end{equation}
+and the associated residues will play a central role.
+We note that the residue of the matrix $S_{\lambda-1/2}(\omega)$ at the pole $\lambda=\lambda_n(\omega)$ is defined by [see Eq.~(\ref{Matrix_S_CAM})]
+\begin{equation}\label{residues_RP}
+r_n(\omega)=e^{i\pi [\lambda_n(\omega)+1/2]} \left[ \frac{A_{\lambda -1/2}^{(+)}(\omega)}{\frac{d}{d \lambda}A_{\lambda -1/2}^{(-)}(\omega)}\right]_{\lambda=\lambda_n(\omega)}.
+\end{equation}
+
+Now, we ``deform'' the contour ${\cal C}$ in Eq.~(\ref{SW_Scalar_Scattering_amp}) in order to collect, by using the Cauchy's theorem, the Regge poles contributions.
+This achieved by following, \textit{mutatis mutandis}, the approach developed in Ref~\cite{Folacci:2019cmc} (see more particularly Sec.
+IIB~3 and Fig.~1).
+We obtain
+
+\begin{equation}\label{CAM_Scalar_Scattering_amp_tot}
+\hat{f} (\omega, \theta) =  \hat{f}^\text{\tiny{B}} (\omega, \theta) +  \hat{f}^\text{\tiny{RP}} (\omega, \theta)
+\end{equation}
+where
+\begin{subequations}\label{CAM_Scalar_Scattering_amp_decomp}
+\begin{equation}\label{CAM_Scalar_Scattering_amp_decomp_Background}
+\hat{f}^\text{\tiny{B}} (\omega, \theta) = \hat{f}^\text{\tiny{B},\tiny{Re}} (\omega, \theta)+ \hat{f}^\text{\tiny{B},\tiny{Im}} (\omega, \theta)
+\end{equation}
+with
+\begin{equation}\label{CAM_Scalar_Scattering_amp_decomp_Background_a}
+\hat{f}^\text{\tiny{B},\tiny{Re}} (\omega, \theta) = \frac{1}{\pi \omega} \int_{{\cal C}_{-}} d\lambda \, \lambda S_{\lambda -1/2}(\omega) Q_{\lambda -1/2}(\cos \theta +i0)
+\end{equation}
+and
+\begin{eqnarray}\label{CAM_Scalar_Scattering_amp_decomp_Background_b}
+\hat{f}^\text{\tiny{B},\tiny{Im}} && (\omega, \theta) = \frac{1}{2 \omega}\left(\int_{+i\infty}^{0} d\lambda \, \left[S_{\lambda -1/2}(\omega) P_{\lambda_n(\omega) -1/2} (-\cos \theta) \right.
+\right.\nonumber \\
+&& -\left. \left. S_{-\lambda -1/2}(\omega) e^{i \pi \left(\lambda+1/2\right)}P_{\lambda_n(\omega) -1/2} (\cos \theta) \right]\lambda\right)
+\end{eqnarray}
+\end{subequations}
+is a background integral contribution and where
+\begin{eqnarray}\label{CAM_Scalar_Scattering_amp_decomp_RP}
+& & \hat{f}^\text{\tiny{RP}} (\omega, \theta) = -\frac{i \pi}{\omega}    \sum_{n=1}^{+\infty}   \frac{ \lambda_n(\omega) r_n(\omega)}{\cos[\pi \lambda_n(\omega)]}  \nonumber \\
+&&  \qquad\qquad \qquad\qquad \times  P_{\lambda_n(\omega) -1/2} (-\cos \theta)
+\end{eqnarray}
+is a sum over the Regge poles lying in the first quadrant of the CAM plane.
+Of course, Eqs.~(\ref{CAM_Scalar_Scattering_amp_tot}), (\ref{CAM_Scalar_Scattering_amp_decomp}) and (\ref{CAM_Scalar_Scattering_amp_decomp_RP}) provide an exact representation of the scattering amplitude $\hat{f} (\omega, \theta)$ for the scalar field, equivalent to the initial partial wave expansion (\ref{Scalar_Scattering_amp}).
+From this CAM representation, we can extract the contribution $\hat{f}^\text{\tiny{RP}} (\omega, \theta)$ given by (\ref{CAM_Scalar_Scattering_amp_decomp_RP}) which, as a sum over Regge poles, is only an approximation of $\hat{f} (\omega, \theta)$, and which provides us with an approximation of the differential scattering cross section (\ref{Scalar_Scattering_diff}).
+
+\section{Reconstruction of differential scattering cross sections from Regge pole sums}
+\label{SecIII}
+
+In this section,  we compare CAM representations or, more precisely, their Regge pole approximations with their partial wave expansions of the differential scattering cross sections.
+
+\subsection{Computational methods}
+\label{SecIIIa}
+
+To construct the scattering amplitude \eqref{Scalar_Scattering_amp}, the back ground integrals~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} and~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_b} as well as the Regge pole contribution~\eqref{CAM_Scalar_Scattering_amp_decomp_RP}, we use, \textit{mutatis mutandis} the computational methods that have permitted us, in the Refs~\cite{Folacci:2019cmc,Folacci:2019vtt}, to reconsider the CAM representation for scattering of the scalar, electromagnetic and gravitational waves by Schwarzschild BH (see also Ref~\cite{Dolan:2017rtj}).
+It is important to remark that, duo to the long rang nature of the field propagating on the Schwarzschild BH (outside the compact body), the scattering amplitude~\eqref{Scalar_Scattering_amp} and the background integral~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} suffer a lack of convergence and to overcome this problem, i.e., to accelerate the convergence of these sum and integral, we have used the method described int the Appendix of Ref~\cite{Folacci:2019cmc}.
+It should be noted that we have performed all the numerical calculations by using {\it Mathematica} \cite{Mathematica}.
+
+\subsection{Results and comments}
+\label{SecIIIb}
+
+ \begin{figure}[htb]
+\centering
+ \includegraphics[scale=0.50]{RP_R_6_2Mw_3_16}
+\caption{\label{RP_approx_2Mw_3_6_s_1} The Regge poles $\lambda_n(\omega)$ for the scalar field. We assume $2M =1$}
+\end{figure}
+
+ \begin{figure}[htb]
+\centering
+ \includegraphics[scale=0.50]{RP_R_2_dot_26_2Mw_3_6}
+\caption{\label{RP_approx_2Mw_3_6_s_1} The Regge poles $\lambda_n(\omega)$ for the scalar field. We assume $2M =1$}
+\end{figure}
+
+\begin{figure*}%[h!]
+ \includegraphics[scale=0.50]{Scattering_Cross_Section_R_6_2Mw_3}
+\caption{\label{S_0_2Mw_01_Exact_vs_CAM} The scalar cross section of a compact bodies for $2M\omega=3$ and $R=6M$, its Regge pole approximation and the background integral contribution.}
+\end{figure*}
+
+\begin{figure*}%[h!]
+ \includegraphics[scale=0.50]{Scattering_Cross_Section_R_6_2Mw_16}
+\caption{\label{S_0_2Mw_01_Exact_vs_CAM} The scalar cross section of a compact bodies for $2M\omega=16$ and $R=6M$, its Regge pole approximation and the background integral contribution.}
+\end{figure*}
+
+\begin{figure*}%[h!]
+\centering
+ \includegraphics[scale=0.50]{Scattering_Cross_Section_R_2-dot-26_2Mw_3}
+\caption{\label{S_0_2Mw_06_Exact_vs_CAM} The scalar cross section of a very compact bodies for $2M\omega=3$ and $R=2.26M$ and its Regge pole approximation.}
+\end{figure*}
+
+\begin{figure*}%[h!]
+\centering
+ \includegraphics[scale=0.50]{Scattering_Cross_Section_R_2-dot-26_2Mw_6}
+\caption{\label{S_0_2Mw_06_Exact_vs_CAM} The scalar cross section of a very compact bodies for $2M\omega=6$ and $R=2.26M$ and its Regge pole approximation.}
+\end{figure*}
+
+\begin{figure}%[h!]
+\centering
+ \includegraphics[scale=0.50]{Rainbow_Cross_Section_R_6_2Mw_16}
+\caption{\label{S_0_2Mw_06_Exact_vs_CAM} Rainbow scattering for compact bodies for $2M\omega=16$ and $R=6M$, its Regge pole approximation and different contributions of the sum over Regge poles.}
+\end{figure}
+
+\begin{figure}%[h!]
+\centering
+ \includegraphics[scale=0.50]{Diff_Contribution_Cross_Section_R_2-dot-26_2Mw_6}
+\caption{\label{S_0_2Mw_06_Exact_vs_CAM} Rainbow scattering for compact bodies for $2M\omega=16$ and $R=2.26M$, its Regge pole approximation and different contributions of the sum over Regge poles.}
+\end{figure}
+
+\begingroup
+\begin{table*}[htp]
+\begin{threeparttable}[htp]
+%\captionsetup{font=small}
+\caption{\label{tab:table2} The lowest Regge poles $\lambda_{n}(\omega)$ for the scalar field and the associated residues $r_{n}(\omega)$.
+The radius of the compact bodies is $R = 6M$ and we assume $2M=1$.}
+\smallskip
+\centering
+\begin{ruledtabular}
+\begin{tabular}{cccccc}
+ $n$ & $\omega$  & $\lambda^{\text{(S-W)\tnote{1}}}_n(\omega)$ & $\lambda^{\text{(B-R)\tnote{2}}}_n(\omega)$ & $r^{\text{(S-W)}}_{n}(\omega)$ & $r^{\text{(B-R)}}_{n}(\omega)$
+ \\ \hline
+$1$  & $3$  & $ 9.14850+2.76784 i$  & $1.06219+2.33072 i$  & $-12.41483-0.10424 i$  & $ -0.184457+0.480330 i$    \\
+     & $16$  & $55.50945+5.71038 i$  & $ 0.12529+3.27098 i$  & $-447.5395+25.2912 i$  & $-0.322061-0.088002 i $  \\
+
+$2$  & $3$  & $ 10.21986+5.16209 i $  & $3.31484+2.48159 i$  & $13.8486+24.3824 i$  & $0.290952+1.043116 i$    \\
+     & $16$  & $ 57.94656+9.18793 i$  & $2.14868+3.31439 i$  & $5188.750-859.909 i$  & $ -0.381581-0.077583 i$    \\
+
+$3$  & $3$  & $11.12296+7.17454 i$  & $ 5.85675+2.64104 i$  & $39.4189-12.3554 i$ & $2.83038-0.28686 i$    \\
+     & $16$  & $59.70374+12.14965 i$  & $4.20011+3.35821 i$  & $-29331.71-18578.38 i$  & $-0.456423-0.021249 i$ \\
+
+$4$  & $3$  & $ 11.9297+8.9960 i$  & $/$  & $ 12.7301-50.8802 i$ & $/$    \\
+     & $16$  & $ 61.17700+14.84728 i $  & $6.28093+3.40257 i$  & $-15868.9+161199.9 i$  & $-0.528929+0.106794 i$ \\
+
+$5$  & $3$  & $12.6734+10.6929 i$  & $/$  & $-33.7366-51.7404 i$ & $/$     \\
+     & $16$  & $62.48626+17.37165 i$  & $8.39270+3.44762 i$  & $589920.5-79507.8 i$  & $-0.550038+0.330275 i$    \\
+
+$6$  & $3$  & $13.3709+12.2989 i$  & $/$   & $-66.4436-20.7767 i$ & $/$    \\
+     & $16$  & $ 63.68605+19.76911 i$  & $10.53720+3.49356 i$  & $-360464.-1.797518\times 10^6 i$  & $ -0.426365+0.639191 i$    \\
+
+$7$  & $3$  & $14.0322+13.8342 i$  & $/$   & $-73.0825+21.9088 i$ & $/$     \\
+     & $16$  & $64.80640+22.06743 i$  & $12.71653+3.54058 i$  & $-4.880638\times 10^6+646112. i$  & $-0.038292+0.926498 i$    \\
+
+$8$  & $3$  & $14.6640+15.3122 i$  & $/$   & $-56.3641+59.6187 i$ & $/$     \\
+     & $16$  & $65.86581+24.28491 i$  & $14.9331+3.5889 i$  & $-479098.+1.1836070\times 10^7 i$  & $0.652285+0.920876 i$    \\
+
+$9$  & $3$  & $15.2709+16.7425 i$  & $/$   & $-25.0183+83.3731 i$ & $/$     \\
+     & $16$  & $66.87659+26.43447 i$  & $17.1898+3.6390 i$  & $2.487209\times 10^7+7.72797\times 10^6 i$  & $1.363464+0.248276 i$    \\
+
+$10$  & $3$  & $15.8565+18.1321 i$  & $/$   & $11.7631+90.6815 i$ & $/$     \\
+     & $16$  & $67.84738+28.52564 i $  & $19.4900+3.6910 i$  & $3.163822\times 10^7-4.265475\times 10^7 i$  & $1.29469-1.13096 i$    \\
+\end{tabular}
+\end{ruledtabular}
+\begin{tablenotes}
+     \item[1] Surface waves
+     \item[2] Boarder resonances
+   \end{tablenotes}
+\end{threeparttable}
+\end{table*}
+\endgroup
+
+\begingroup
+\squeezetable
+\begin{table*}[htp]
+\begin{threeparttable}[htp]
+%\captionsetup{font=small}
+\caption{\label{tab:table2} The lowest Regge poles $\lambda_{n}(\omega)$ for the scalar field and the associated residues $r_{n}(\omega)$.
+The radius of the compact bodies is $R = 2.26M$ and we assume $2M=1$.}
+\smallskip
+\centering
+\begin{ruledtabular}
+\begin{tabular}{cccccccc}
+ $n$ & $\omega$  & $\lambda^{\text{(S-W)\tnote{1}}}_n(\omega)$  & $\lambda^{\text{(B-R)\tnote{2}}}_n(\omega)$ & $\lambda^{\text{(N-R)\tnote{3}}}_n(\omega)$ & $r^{\text{(S-W)}}_{n}(\omega)$ & $r^{\text{(B-R)}}_{n}(\omega)$ & $r^{\text{(N-R)}}_{n}(\omega)$
+ \\ \hline
+$1$  & $3$  & $5.371590+1.553799 i$  & $1.23455+1.64951 i  $  & $ 5.98474+0.68765 i $  & $-179.7945+131.4187 i $ & $ -1.52081-2.30968 i$ & $-2.5672-15.3797 i $  \\
+     & $6$  & $12.491923+1.754967 i $  & $ 1.39664+2.13696 i  $  & $ 12.84118+1.13496 i $  & $4356.193+647.790 i $ & $  -0.66176-1.31963 i$ & $  -390.218+379.906 i $  \\
+
+$2$  & $3$  & $5.278805+3.228990 i  $  & $ 2.98084+1.45765 i$  & $  6.75606+0.24457 i$  & $428.6893-235.0321 i $ & $16.2123+5.2371 i $ & $ -0.272250-1.150335 i$  \\
+     & $6$  & $12.205495+3.383881 i $  & $ 3.24238+2.01309 i $  & $13.68757+0.68182 i $  & $-35075.99-9772.94 i $ & $-2.93679+4.83548 i $ & $ -11.3519+34.5571 i $  \\
+
+$3$  & $3$  & $ 5.424546+4.705899 i $  & $  4.60229+1.29099 i$  & $ 7.45763+0.01764 i$  & $-404.6185-390.8531 i$ & $ 70.4849+54.1888 i  $ & $ -0.0370202-0.0048174 i $  \\
+     & $6$  & $12.096259+4.982661 i $  & $  4.99829+1.89576 i $  & $14.4017+0.2912 i $  & $82360.19+81990.53 i$ & $ 6.7872-16.9564 i$ & $0.27028+2.27905 i  $  \\
+
+$4$  & $3$  & $ 5.644986+6.043188 i $  & $ /$  & $/ $  & $ -471.5443+314.3116 i  $ & $ /$ & $/ $  \\
+     & $6$  & $ 12.114598+6.503749 i  $  & $ 6.67509+1.78279 i $  & $15.0621+0.0422 i  $  & $39281.5-229393.2 i  $ & $39.6176+33.5152 i  $ & $0.1011154+0.0020569 i $  \\
+
+$5$  & $3$  & $5.898427+7.281723 i $  & $ /$  & $/ $  & $37.8777+546.8945 i $ & $ /$ & $/ $  \\
+     & $6$  & $  12.21646+7.95208 i $  & $ 8.28112+1.67243 i  $  & $ /$  & $ -356055.5+34945.9 i$ & $ 2.1175+134.5962 i $ & $/ $  \\
+
+$6$  & $3$  & $ 6.166837+8.447532 i $  & $/ $  & $ /$  & $418.7890+315.4209 i$ & $/ $ & $/ $  \\
+     & $6$  & $ 12.37420+9.33552 i $  & $ 9.82300+1.56317 i$  & $/ $  & $45934.6+468157.5 i $ & $ 66.944+324.598 i$ & $/ $  \\
+
+$7$  & $3$  & $ 6.441642+9.557619 i $  & $ /$  & $/ $  & $499.2703-37.6476 i $ & $ /$ & $ /$  \\
+     & $6$  & $12.56993+10.66226 i $  & $ 11.30630+1.45720 i  $  & $ /$  & $558619.4+61956.5 i $ & $ 833.855+78.332 i $ & $/ $  \\
+
+$8$  & $3$  & $6.718463+10.623548 i $  & $ /$  & $/ $  & $ 367.2578-307.7533 i  $ & $ /$ & $/ $  \\
+     & $6$  & $12.79184+11.93979 i $  & $/ $  & $/ $  & $ 293571.8-559756.8 i $ & $/ $ & $/ $  \\
+
+$9$  & $3$  & $ 6.994953+11.653498 i $  & $/ $  & $/ $  & $147.3038-435.8160 i  $ & $ /$ & $/ $  \\
+     & $6$  & $ 13.03197+13.17461 i  $  & $/ $  & $/ $  & $ -376511.5-570254.0 i  $ & $/$ & $ /$  \\
+
+$10$ & $3$  & $7.26982+12.65345 i $  & $/ $  & $/ $  & $-71.8294-437.3469 i  $ & $/ $ & $ /$  \\
+     & $6$  & $ 13.28485+14.37216 i$  & $ /$  & $/ $  & $ -719306.1-20011.7 i $ & $ /$ & $/ $  \\
+
+\end{tabular}
+\end{ruledtabular}
+\begin{tablenotes}
+     \item[1] Surface waves
+     \item[2] Boarder resonances
+     \item[3] Narrow  resonances
+   \end{tablenotes}
+\end{threeparttable}
+\end{table*}
+\endgroup
+
+\be
+\cos \left( \tfrac{1}{2} \theta_R \right) = \frac{1}{n^2} \left[ \frac{4 - n^2}{3} \right]^{3/2}
+\ee
+(Huygens 1652).
 
@@
 	\end{enumerate}
+>>>>>>> 8b666c5c215fddaf7f72884caa26962c43500921
 
 \acknowledgments
+M.
+O.
+E.
+H.
+wish to thank Antoine Folacci for various discussions concerning this work.
 T.S.~acknowledges financial support from EPSRC.

### 2019-10-19 rainbowCAM.tex
Esthetiques
Correction of condition at the origin
Change Boarder to Broad in some plots
Changing in table l to lambda
WKB for lowest Broad Regge Poles ?!

@@
 \newcommand{\nn}{\nonumber}
-\newcommand{\be}{\begin{equation}}
-\newcommand{\ee}{\end{equation}}
 
@@
 \phi^\mathrm{in}_{\omega  \ell}(r) \scriptstyle{\underset{r \to 0}{\sim}}
-\displaystyle{r^{\ell}}.
+\displaystyle{r^{\ell+1}}.
 \end{equation}
@@
 \begingroup
+\squeezetable
 \begin{table*}[htp]
@@
  \\ \hline
-$1$  & $3$  & $ 9.14850+2.76784 i$  & $1.06219+2.33072 i$  & $-12.41483-0.10424 i$  & $ -0.184457+0.480330 i$    \\
-     & $16$  & $55.50945+5.71038 i$  & $ 0.12529+3.27098 i$  & $-447.5395+25.2912 i$  & $-0.322061-0.088002 i $  \\
+$1$  & $3$  & $ 9.64850+2.76784 i$  & $1.56219+2.33072 i$  & $-12.41483-0.10424 i$  & $ -0.184457+0.480330 i$    \\
+     & $16$  & $56.00945+5.71038 i$  & $ 0.62529+3.27098 i$  & $-447.5395+25.2912 i$  & $-0.322061-0.088002 i $  \\
 
-$2$  & $3$  & $ 10.21986+5.16209 i $  & $3.31484+2.48159 i$  & $13.8486+24.3824 i$  & $0.290952+1.043116 i$    \\
-     & $16$  & $ 57.94656+9.18793 i$  & $2.14868+3.31439 i$  & $5188.750-859.909 i$  & $ -0.381581-0.077583 i$    \\
+$2$  & $3$  & $ 10.71986+5.16209 i $  & $3.81484+2.48159 i$  & $13.8486+24.3824 i$  & $0.290952+1.043116 i$    \\
+     & $16$  & $ 58.442656+9.18793 i$  & $3.14868+3.31439 i$  & $5188.750-859.909 i$  & $ -0.381581-0.077583 i$    \\
 
-$3$  & $3$  & $11.12296+7.17454 i$  & $ 5.85675+2.64104 i$  & $39.4189-12.3554 i$ & $2.83038-0.28686 i$    \\
-     & $16$  & $59.70374+12.14965 i$  & $4.20011+3.35821 i$  & $-29331.71-18578.38 i$  & $-0.456423-0.021249 i$ \\
+$3$  & $3$  & $11.62296+7.17454 i$  & $ 6.35675+2.64104 i$  & $39.4189-12.3554 i$ & $2.83038-0.28686 i$    \\
+     & $16$  & $60.20374+12.14965 i$  & $4.70011+3.35821 i$  & $-29331.71-18578.38 i$  & $-0.456423-0.021249 i$ \\
 
-$4$  & $3$  & $ 11.9297+8.9960 i$  & $/$  & $ 12.7301-50.8802 i$ & $/$    \\
-     & $16$  & $ 61.17700+14.84728 i $  & $6.28093+3.40257 i$  & $-15868.9+161199.9 i$  & $-0.528929+0.106794 i$ \\
+$4$  & $3$  & $ 12.4297+8.9960 i$  & $/$  & $ 13.2301-50.8802 i$ & $/$    \\
+     & $16$  & $ 61.67700+14.84728 i $  & $6.78093+3.40257 i$  & $-15868.9+161199.9 i$  & $-0.528929+0.106794 i$ \\
 
-$5$  & $3$  & $12.6734+10.6929 i$  & $/$  & $-33.7366-51.7404 i$ & $/$     \\
-     & $16$  & $62.48626+17.37165 i$  & $8.39270+3.44762 i$  & $589920.5-79507.8 i$  & $-0.550038+0.330275 i$    \\
+$5$  & $3$  & $13.1734+10.6929 i$  & $/$  & $-33.7366-51.7404 i$ & $/$     \\
+     & $16$  & $62.98626+17.37165 i$  & $8.89270+3.44762 i$  & $589920.5-79507.8 i$  & $-0.550038+0.330275 i$    \\
 
-$6$  & $3$  & $13.3709+12.2989 i$  & $/$   & $-66.4436-20.7767 i$ & $/$    \\
-     & $16$  & $ 63.68605+19.76911 i$  & $10.53720+3.49356 i$  & $-360464.-1.797518\times 10^6 i$  & $ -0.426365+0.639191 i$    \\
+$6$  & $3$  & $13.8709+12.2989 i$  & $/$   & $-66.4436-20.7767 i$ & $/$    \\
+     & $16$  & $ 64.18605+19.76911 i$  & $11.03720+3.49356 i$  & $-360464.-1.797518\times 10^6 i$  & $ -0.426365+0.639191 i$    \\
 
-$7$  & $3$  & $14.0322+13.8342 i$  & $/$   & $-73.0825+21.9088 i$ & $/$     \\
-     & $16$  & $64.80640+22.06743 i$  & $12.71653+3.54058 i$  & $-4.880638\times 10^6+646112. i$  & $-0.038292+0.926498 i$    \\
+$7$  & $3$  & $14.5322+13.8342 i$  & $/$   & $-73.0825+21.9088 i$ & $/$     \\
+     & $16$  & $65.30640+22.06743 i$  & $13.21653+3.54058 i$  & $-4.880638\times 10^6+646112. i$  & $-0.038292+0.926498 i$    \\
 
-$8$  & $3$  & $14.6640+15.3122 i$  & $/$   & $-56.3641+59.6187 i$ & $/$     \\
-     & $16$  & $65.86581+24.28491 i$  & $14.9331+3.5889 i$  & $-479098.+1.1836070\times 10^7 i$  & $0.652285+0.920876 i$    \\
+$8$  & $3$  & $15.1640+15.3122 i$  & $/$   & $-56.3641+59.6187 i$ & $/$     \\
+     & $16$  & $66.36581+24.28491 i$  & $15.4331+3.5889 i$  & $-479098.+1.1836070\times 10^7 i$  & $0.652285+0.920876 i$    \\
 
-$9$  & $3$  & $15.2709+16.7425 i$  & $/$   & $-25.0183+83.3731 i$ & $/$     \\
-     & $16$  & $66.87659+26.43447 i$  & $17.1898+3.6390 i$  & $2.487209\times 10^7+7.72797\times 10^6 i$  & $1.363464+0.248276 i$    \\
+$9$  & $3$  & $15.7709+16.7425 i$  & $/$   & $-25.0183+83.3731 i$ & $/$     \\
+     & $16$  & $67.37659+26.43447 i$  & $17.6898+3.6390 i$  & $2.487209\times 10^7+7.72797\times 10^6 i$  & $1.363464+0.248276 i$    \\
 
-$10$  & $3$  & $15.8565+18.1321 i$  & $/$   & $11.7631+90.6815 i$ & $/$     \\
-     & $16$  & $67.84738+28.52564 i $  & $19.4900+3.6910 i$  & $3.163822\times 10^7-4.265475\times 10^7 i$  & $1.29469-1.13096 i$    \\
+$10$  & $3$  & $16.3565+18.1321 i$  & $/$   & $11.7631+90.6815 i$ & $/$     \\
+     & $16$  & $68.34738+28.52564 i $  & $19.9900+3.6910 i$  & $3.163822\times 10^7-4.265475\times 10^7 i$  & $1.29469-1.13096 i$    \\
 \end{tabular}
@@
      \item[1] Surface waves
-     \item[2] Boarder resonances
+     \item[2] Broad resonances
    \end{tablenotes}
@@
  \\ \hline
-$1$  & $3$  & $5.371590+1.553799 i$  & $1.23455+1.64951 i  $  & $ 5.98474+0.68765 i $  & $-179.7945+131.4187 i $ & $ -1.52081-2.30968 i$ & $-2.5672-15.3797 i $  \\
-     & $6$  & $12.491923+1.754967 i $  & $ 1.39664+2.13696 i  $  & $ 12.84118+1.13496 i $  & $4356.193+647.790 i $ & $  -0.66176-1.31963 i$ & $  -390.218+379.906 i $  \\
+$1$  & $3$  & $5.871590+1.553799 i$  & $1.73455+1.64951 i  $  & $ 6.48474+0.68765 i $  & $-179.7945+131.4187 i $ & $ -1.52081-2.30968 i$ & $-2.5672-15.3797 i $  \\
+     & $6$  & $12.991923+1.754967 i $  & $ 1.89664+2.13696 i  $  & $ 13.34118+1.13496 i $  & $4356.193+647.790 i $ & $  -0.66176-1.31963 i$ & $  -390.218+379.906 i $  \\
 
-$2$  & $3$  & $5.278805+3.228990 i  $  & $ 2.98084+1.45765 i$  & $  6.75606+0.24457 i$  & $428.6893-235.0321 i $ & $16.2123+5.2371 i $ & $ -0.272250-1.150335 i$  \\
-     & $6$  & $12.205495+3.383881 i $  & $ 3.24238+2.01309 i $  & $13.68757+0.68182 i $  & $-35075.99-9772.94 i $ & $-2.93679+4.83548 i $ & $ -11.3519+34.5571 i $  \\
+$2$  & $3$  & $5.778805+3.228990 i  $  & $ 3.48084+1.45765 i$  & $  7.25606+0.24457 i$  & $428.6893-235.0321 i $ & $16.2123+5.2371 i $ & $ -0.272250-1.150335 i$  \\
+     & $6$  & $12.705495+3.383881 i $  & $ 3.74238+2.01309 i $  & $14.18757+0.68182 i $  & $-35075.99-9772.94 i $ & $-2.93679+4.83548 i $ & $ -11.3519+34.5571 i $  \\
 
-$3$  & $3$  & $ 5.424546+4.705899 i $  & $  4.60229+1.29099 i$  & $ 7.45763+0.01764 i$  & $-404.6185-390.8531 i$ & $ 70.4849+54.1888 i  $ & $ -0.0370202-0.0048174 i $  \\
-     & $6$  & $12.096259+4.982661 i $  & $  4.99829+1.89576 i $  & $14.4017+0.2912 i $  & $82360.19+81990.53 i$ & $ 6.7872-16.9564 i$ & $0.27028+2.27905 i  $  \\
+$3$  & $3$  & $ 5.924546+4.705899 i $  & $  5.10229+1.29099 i$  & $ 7.95763+0.01764 i$  & $-404.6185-390.8531 i$ & $ 70.4849+54.1888 i  $ & $ -0.0370202-0.0048174 i $  \\
+     & $6$  & $12.596259+4.982661 i $  & $  5.49829+1.89576 i $  & $14.9017+0.2912 i $  & $82360.19+81990.53 i$ & $ 6.7872-16.9564 i$ & $0.27028+2.27905 i  $  \\
 
-$4$  & $3$  & $ 5.644986+6.043188 i $  & $ /$  & $/ $  & $ -471.5443+314.3116 i  $ & $ /$ & $/ $  \\
-     & $6$  & $ 12.114598+6.503749 i  $  & $ 6.67509+1.78279 i $  & $15.0621+0.0422 i  $  & $39281.5-229393.2 i  $ & $39.6176+33.5152 i  $ & $0.1011154+0.0020569 i $  \\
+$4$  & $3$  & $ 6.144986+6.043188 i $  & $ /$  & $/ $  & $ -471.5443+314.3116 i  $ & $ /$ & $/ $  \\
+     & $6$  & $ 12.614598+6.503749 i  $  & $ 7.17509+1.78279 i $  & $15.5621+0.0422 i  $  & $39281.5-229393.2 i  $ & $39.6176+33.5152 i  $ & $0.1011154+0.0020569 i $  \\
 
-$5$  & $3$  & $5.898427+7.281723 i $  & $ /$  & $/ $  & $37.8777+546.8945 i $ & $ /$ & $/ $  \\
-     & $6$  & $  12.21646+7.95208 i $  & $ 8.28112+1.67243 i  $  & $ /$  & $ -356055.5+34945.9 i$ & $ 2.1175+134.5962 i $ & $/ $  \\
+$5$  & $3$  & $6.398427+7.281723 i $  & $ /$  & $/ $  & $37.8777+546.8945 i $ & $ /$ & $/ $  \\
+     & $6$  & $  12.71646+7.95208 i $  & $ 8.78112+1.67243 i  $  & $ /$  & $ -356055.5+34945.9 i$ & $ 2.1175+134.5962 i $ & $/ $  \\
 
-$6$  & $3$  & $ 6.166837+8.447532 i $  & $/ $  & $ /$  & $418.7890+315.4209 i$ & $/ $ & $/ $  \\
-     & $6$  & $ 12.37420+9.33552 i $  & $ 9.82300+1.56317 i$  & $/ $  & $45934.6+468157.5 i $ & $ 66.944+324.598 i$ & $/ $  \\
+$6$  & $3$  & $ 6.666837+8.447532 i $  & $/ $  & $ /$  & $418.7890+315.4209 i$ & $/ $ & $/ $  \\
+     & $6$  & $ 12.87420+9.33552 i $  & $ 10.32300+1.56317 i$  & $/ $  & $45934.6+468157.5 i $ & $ 66.944+324.598 i$ & $/ $  \\
 
-$7$  & $3$  & $ 6.441642+9.557619 i $  & $ /$  & $/ $  & $499.2703-37.6476 i $ & $ /$ & $ /$  \\
-     & $6$  & $12.56993+10.66226 i $  & $ 11.30630+1.45720 i  $  & $ /$  & $558619.4+61956.5 i $ & $ 833.855+78.332 i $ & $/ $  \\
+$7$  & $3$  & $ 6.941642+9.557619 i $  & $ /$  & $/ $  & $499.2703-37.6476 i $ & $ /$ & $ /$  \\
+     & $6$  & $13.06993+10.66226 i $  & $ 11.80630+1.45720 i  $  & $ /$  & $558619.4+61956.5 i $ & $ 833.855+78.332 i $ & $/ $  \\
 
-$8$  & $3$  & $6.718463+10.623548 i $  & $ /$  & $/ $  & $ 367.2578-307.7533 i  $ & $ /$ & $/ $  \\
-     & $6$  & $12.79184+11.93979 i $  & $/ $  & $/ $  & $ 293571.8-559756.8 i $ & $/ $ & $/ $  \\
+$8$  & $3$  & $7.218463+10.623548 i $  & $ /$  & $/ $  & $ 367.2578-307.7533 i  $ & $ /$ & $/ $  \\
+     & $6$  & $13.29184+11.93979 i $  & $/ $  & $/ $  & $ 293571.8-559756.8 i $ & $/ $ & $/ $  \\
 
-$9$  & $3$  & $ 6.994953+11.653498 i $  & $/ $  & $/ $  & $147.3038-435.8160 i  $ & $ /$ & $/ $  \\
-     & $6$  & $ 13.03197+13.17461 i  $  & $/ $  & $/ $  & $ -376511.5-570254.0 i  $ & $/$ & $ /$  \\
+$9$  & $3$  & $ 7.494953+11.653498 i $  & $/ $  & $/ $  & $147.3038-435.8160 i  $ & $ /$ & $/ $  \\
+     & $6$  & $ 13.53197+13.17461 i  $  & $/ $  & $/ $  & $ -376511.5-570254.0 i  $ & $/$ & $ /$  \\
 
-$10$ & $3$  & $7.26982+12.65345 i $  & $/ $  & $/ $  & $-71.8294-437.3469 i  $ & $/ $ & $ /$  \\
-     & $6$  & $ 13.28485+14.37216 i$  & $ /$  & $/ $  & $ -719306.1-20011.7 i $ & $ /$ & $/ $  \\
+$10$ & $3$  & $7.76982+12.65345 i $  & $/ $  & $/ $  & $-71.8294-437.3469 i  $ & $/ $ & $ /$  \\
+     & $6$  & $ 13.78485+14.37216 i$  & $ /$  & $/ $  & $ -719306.1-20011.7 i $ & $ /$ & $/ $  \\
 
@@
      \item[1] Surface waves
-     \item[2] Boarder resonances
+     \item[2] Broad resonances
      \item[3] Narrow  resonances
@@
 
-\be
-\cos \left( \tfrac{1}{2} \theta_R \right) = \frac{1}{n^2} \left[ \frac{4 - n^2}{3} \right]^{3/2}
-\ee
-(Huygens 1652).
+\section{WKB ?}
+\label{SecIII}
+
+The WKB approach developed in the context of the determination of the QNMs by Zhang, Wu and Leung~\cite{Zhang:2011pq} can be adapted in order to obtain analytical approximations for the ``Broad Regge poles''.
+Indeed, Regge modes and QNMs both satisfy the same wave equation and the same boundary conditions but with different interpretations for the angular momentum index and the frequency.
+By using WKB approximation for the Regge modes, we can find that the Regge pole $\lambda$ are the complex solutions  of the equation
+\begin{equation}\label{WKB_1}
+  e^{-2 i R_*\omega} = a \omega^{-2} e^{-i \pi (\lambda+1/2)}
+\end{equation}
+with 
+\begin{equation}\label{Def_a}
+  a= \frac{3M \left(R-2M\right)^2}{4 R^5\omega}
+\end{equation}
+and
+\begin{equation}\label{R_star}
+  R_*=\int_{0}^{R}\, dr\,\frac{1}{\sqrt{f(r)h(r)}}
+\end{equation}
+We then solve Eq.~\eqref{WKB_1} and we obtain for the lowest ``Broad Regge poles''  
+\begin{equation}\label{lambda_Approx} 
+  \lambda_n \approx \frac{2 \omega R_*}{\pi}+ 2 \left(n-\frac{1}{4}\right)+ 2\left\lfloor \ \frac{1}{2} - \frac{\text{Im}[2 i\omega R_*]}{2\pi} \right\rfloor - \frac{i}{\pi} \ln\left(\frac{a}{\omega^2}\right)
+\end{equation}
+
+%\begin{eqnarray}\label{lambda_Approx}
+%% \nonumber % Remove numbering (before each equation)
+%  \lambda_n \approx & & \frac{2 \omega R_*}{\pi}+ 2 \left(n-\frac{1}{4}\right)+ 2\left\lfloor \ \frac{1}{2} - \frac{\Im [2 i\omega R_*]}{2\pi} \right\rfloor\nonumber\\
+%   &-& \frac{i}{\pi} \ln\left(\frac{a}{\omega^2}\right)
+%\end{eqnarray}
 
@@
 	\end{enumerate}
->>>>>>> 8b666c5c215fddaf7f72884caa26962c43500921
 

### 2019-10-21 rainbowCAM.tex
WKB some adding

@@
 In Eqs.~(\ref{Scalar_Scattering_amp}), the functions $P_{\ell}(\cos\theta)$ are the Legendre polynomials \cite{AS65}.
-We also recall that the $S$-matrix elements $S_{\ell}(\omega)$ appearing in Eqs.~(\ref{Scalar_Scattering_amp}) can be defined from the modes $\phi_{\omega \ell}^{in}$ solutions of the homogenous radial equation
+We also recall that the $S$-matrix elements $S_{\ell}(\omega)$ appearing in Eqs.~(\ref{Scalar_Scattering_amp}) can be defined from the modes $\phi_{\omega \ell}$ solutions of the homogenous radial equation
 \begin{equation}
@@
 
-It is important to recall that the modes $\phi_{\omega \ell}^{in}$ have a regular behavior at the origin $r \to 0$
+It is important to recall that the modes $\phi_{\omega \ell}$ have a regular behavior at the origin $r \to 0$
 \begin{equation}\label{bc_1_in}
-\phi^\mathrm{in}_{\omega  \ell}(r) \scriptstyle{\underset{r \to 0}{\sim}}
+\phi_{\omega  \ell}(r) \scriptstyle{\underset{r \to 0}{\sim}}
 \displaystyle{r^{\ell+1}}.
@@
 \begin{equation}\label{bc_2_in}
-\phi^\mathrm{in}_{\omega  \ell}(r) \scriptstyle{\underset{r_\ast \to +\infty}{\sim}}
+\phi_{\omega  \ell}(r) \scriptstyle{\underset{r_\ast \to +\infty}{\sim}}
 \displaystyle{ A^{(-)}_\ell (\omega) e^{-i\omega r_\ast} + A^{(+)}_\ell (\omega) e^{+i\omega r_\ast}}.
@@
 \end{equation}
-where the complex amplitudes $A^{(-)}_{\lambda -1/2} (\omega)$ and  $A^{(+)}_{\lambda -1/2} (\omega)$ are defined from the analytic extension of the modes $\phi_{\omega \ell}^{in}$, i.e., from the function $\phi_{\omega ,\lambda -1/2}^{in}$.
+where the complex amplitudes $A^{(-)}_{\lambda -1/2} (\omega)$ and  $A^{(+)}_{\lambda -1/2} (\omega)$ are defined from the analytic extension of the modes $\phi_{\omega \ell}$, i.e., from the function $\phi_{\omega ,\lambda -1/2}$.
 
@@
 
-The WKB approach developed in the context of the determination of the QNMs by Zhang, Wu and Leung~\cite{Zhang:2011pq} can be adapted in order to obtain analytical approximations for the ``Broad Regge poles''.
+The WKB approach developed in the context of the determination of the \textit{w}-modes QNMs by Zhang, Wu and Leung~\cite{Zhang:2011pq} can be adapted in order to obtain analytical approximations for the ``broad Regge poles''.
 Indeed, Regge modes and QNMs both satisfy the same wave equation and the same boundary conditions but with different interpretations for the angular momentum index and the frequency.
-By using WKB approximation for the Regge modes, we can find that the Regge pole $\lambda$ are the complex solutions  of the equation
-\begin{equation}\label{WKB_1}
-  e^{-2 i R_*\omega} = a \omega^{-2} e^{-i \pi (\lambda+1/2)}
+Indeed, they satisfy the regularity condition at the origin~\eqref{bc_1_in} and the condition~\eqref{bc_2_in} at the spatial infinity, thus, the Regge poles are solutions of Eq.~\eqref{H_Radial_equation} for which the  Wronskian of $\phi^{(r_*\to 0)}_{\omega\ell}$ and $\phi^{(r_*\to \infty)}_{\omega\ell}$ vanishes (\textit{i.e.}, $A^{(-)}_{\lambda_n(\omega)-1/2} (\omega)=0$)
+\begin{equation}\label{Wronskian}
+  W[\phi^{(r_*\to 0)}_{\omega\ell},\phi^{(r_*\to \infty)}_{\omega\ell}]= 0
 \end{equation} 
-with 
-\begin{equation}\label{Def_a}
-  a= \frac{3M \left(R-2M\right)^2}{4 R^5\omega}
+It has been shown that, the asymptotic expressions of $\phi^{(r_*\to 0)}_{\omega\ell}$ and $\phi^{(r_*\to \infty)}_{\omega\ell}$ can be derived, buy using the standard WKB approximation, in the high-frequency domain and we have (see Refs \ldots)
+\begin{equation}\label{Approx_origin}
+  \phi^{(r_* \to 0)}_{\omega\ell} \underset{\omega \to \infty}{=} \omega r_* j_\ell(\omega r_*) \quad\quad 0\leq r_*\leq R_*
 \end{equation}
 and 
+\begin{equation}
+\label{Approx_infinity}
+\phi^{(r_* \to \infty)}_{\omega\ell}\scriptstyle{\underset{\omega \to \infty}{=}}
+\left\{
+\begin{aligned}
+&e^{i\omega(r_*-R_*)}+\mathcal{R} e^{-i\omega (r_*-R_*)}& \scriptstyle{1/\omega\leq r_{*} < R_*,}\\
+&\left(1+\mathcal{R}\right) e^{i\omega(r_*-R_*)}        & \scriptstyle{R_*\leq r_{*}<\infty.}
+\end{aligned}
+\right.
+\end{equation}
+Here 
 \begin{equation}\label{R_star}
@@
 \end{equation}
-We then solve Eq.~\eqref{WKB_1} and we obtain for the lowest ``Broad Regge poles''  
-\begin{equation}\label{lambda_Approx} 
-  \lambda_n \approx \frac{2 \omega R_*}{\pi}+ 2 \left(n-\frac{1}{4}\right)+ 2\left\lfloor \ \frac{1}{2} - \frac{\text{Im}[2 i\omega R_*]}{2\pi} \right\rfloor - \frac{i}{\pi} \ln\left(\frac{a}{\omega^2}\right)
+where $\mathcal{R}$ is the standard reflection coefficient as defined in (Ref\ldots)
+Because the potential has a direct discontinuity at the surface of the compact body (see. Refs \ldots for more details), we have for our model (\textit{i.e.}, compact body with a constant density)
+\begin{equation}\label{R_reflection_1}
+  \mathcal{R} = a \omega^{-2}
+\end{equation}
+with 
+\begin{equation}\label{a_def}
+a= \frac{3M \left(R-2M\right)^2}{4 R^5}
+\end{equation}
+Now, by inserting~\eqref{Approx_origin}, or more precisely his expansion series when $\omega \to \infty$, \textit{i.e.},
+\begin{equation}\label{Approx_origin_bis}
+  \phi^{(r_* \to 0)}_{\omega\lambda-1/2} \underset{\omega \to \infty}{\approx} - \sin(\frac{\left(\lambda-1/2\right)\pi}{2}-\omega r_*)\quad\quad 0\leq r_*\leq R_*
+\end{equation}
+and \eqref{Approx_infinity} into  \eqref{Wronskian}, we obtain
+
+\begin{equation}\label{WKB_1}
+   e^{\frac{i\pi}{2}(\lambda-1/2)-i \omega R_*}=-\mathcal{R} e^{-\frac{i\pi}{2}(\lambda-1/2)-i \omega R_*}
 \end{equation}
 
-%\begin{eqnarray}\label{lambda_Approx}
-%% \nonumber % Remove numbering (before each equation)
-%  \lambda_n \approx & & \frac{2 \omega R_*}{\pi}+ 2 \left(n-\frac{1}{4}\right)+ 2\left\lfloor \ \frac{1}{2} - \frac{\Im [2 i\omega R_*]}{2\pi} \right\rfloor\nonumber\\
-%   &-& \frac{i}{\pi} \ln\left(\frac{a}{\omega^2}\right)
-%\end{eqnarray}
+We then solve Eq.~\eqref{WKB_1} and we obtain for the lowest ``Broad Regge poles''
+
+\begin{equation}\label{lambda_Approx}
+  \lambda_n \approx \frac{2 \omega R_*}{\pi}-\left(2n+\frac{1}{2}\right)-\frac{i}{\pi} \ln\left(\mathcal{R}\right)
+\end{equation}
+
+%\begin{equation}\label{lambda_Approx}
+%  \lambda_n \approx \frac{2 \omega R_*}{\pi}+ 2 \left(n-\frac{1}{4}\right)+ 2\left\lfloor \ \frac{1}{2} - \frac{\text{Im}[2 i\omega R_*]}{2\pi} \right\rfloor - \frac{i}{\pi} \ln\left(\frac{a}{\omega^2}\right)
+%\end{equation}
 

### 2019-10-21 rainbowCAM.tex
about WKB of  broad resonances

@@
 \begin{equation}\label{Approx_origin_bis}
-  \phi^{(r_* \to 0)}_{\omega\lambda-1/2} \underset{\omega \to \infty}{\approx} - \sin(\frac{\left(\lambda-1/2\right)\pi}{2}-\omega r_*)\quad\quad 0\leq r_*\leq R_*
+  \phi^{(r_* \to 0)}_{\omega\lambda-1/2} \underset{\omega \to \infty}{\approx} - \sin\left(\frac{\left(\lambda-1/2\right)\pi}{2}-\omega r_*\right)\quad\quad 0\leq r_*\leq R_*
 \end{equation}
 and \eqref{Approx_infinity} into  \eqref{Wronskian}, we obtain
-
 \begin{equation}\label{WKB_1}
-   e^{\frac{i\pi}{2}(\lambda-1/2)-i \omega R_*}=-\mathcal{R} e^{-\frac{i\pi}{2}(\lambda-1/2)-i \omega R_*}
+   e^{\frac{i\pi}{2}(\lambda-1/2)-i \omega R_*}=-\mathcal{R}\, e^{-\frac{i\pi}{2}(\lambda-1/2)-i \omega R_*}
 \end{equation}
-
-We then solve Eq.~\eqref{WKB_1} and we obtain for the lowest ``Broad Regge poles''
-
+We then solve Eq.~\eqref{WKB_1} and we obtain
 \begin{equation}\label{lambda_Approx}
-  \lambda_n \approx \frac{2 \omega R_*}{\pi}-\left(2n+\frac{1}{2}\right)-\frac{i}{\pi} \ln\left(\mathcal{R}\right)
+  \lambda_n \approx \frac{2 \omega R_*}{\pi}-\left(2n+\frac{1}{2}\right)+\frac{i}{\pi} \ln\left(\frac{1}{\mathcal{R}}\right)
 \end{equation}
+This corresponds to the series of Regge poles with spacing $|\Delta \lambda_n|\approx 2$ with the almost constant  imaginary part.
+Of course, they lies in the first quadrant of the CAM plan with a positive real part
+\begin{equation}\label{Real_Part}
+  \frac{2 \omega R_*}{\pi}-\left(2n+\frac{1}{2}\right)>0
+\end{equation}
+where $n =1,2,\ldots$ correspond to the overtones and has an upper limit
+\begin{equation}\label{Limit_Broad_RP}
+n < \left\lfloor \frac{\omega R_*}{\pi} - \frac{1}{4}\right\rfloor
+\end{equation} 
+This is means, in other words, that there is a finite number of the ``broad Regge poles''. These poles are associated with the broad resonances above the top of the centrifugal barrier!
 

### 2019-10-24 rainbowCAM.tex
few typos corrected
Checking some resulats
some minor rewording

--- 2019-10-21 rainbowCAM.tex
@@
 \definecolor{navyblue}{rgb}{0.0, 0.0, 0.5}
-\usepackage[linktocpage,colorlinks=true,allcolors=navyblue]{hyperref}
+\usepackage[pdftex]{hyperref}
+\hypersetup
+	{
+		colorlinks,%
+		citecolor=blue,%
+		linkcolor=red,%
+		urlcolor=blue,%
+	}
+
+%\usepackage[linktocpage,colorlinks=true,linkcolor=red]{hyperref}
 \usepackage[caption=false]{subfig}
@@
 
+\tableofcontents
+
 \section{Introduction}
-Blah. hello. some more text.
 
@@
 
-In this section, we describe our compact objets model and we recall the partial wave expansions of the differential scattering cross section for plane monochromatic scalar waves impinging upon a compact body and we apply the CAM-approach developed in \cite{Folacci:2019cmc} and \cite{Folacci:2019vtt}
+In this section we describe the model for our compact object.
+Then we recall the partial wave expansions of the differential scattering cross section for plane monochromatic scalar waves impinging upon a compact body.
+Finally we apply the CAM-approach developed for black-hole scattering in \cite{Folacci:2019cmc} and \cite{Folacci:2019vtt}.
 
@@
 
-  We consider that the gravitating source a spherically symmetric incompressible perfect fluid ball of uniform
-density (see Ref~\cite{Dolan:2017rtj} and reference therein) in a coordinate system $\{t,r,\theta,\varphi\}$ and is defined by the metric
+  We consider that the gravitating source is a spherically symmetric incompressible perfect fluid ball of uniform
+density (see Ref~\cite{Dolan:2017rtj} and references therein). In a coordinate system $\{t,r,\theta,\varphi\}$, the object is described by the metric
 \begin{equation}\label{Line_elem}
@@
 Here, the radial function $h(r)$ is continuous but not differentiable across the surface of the star $r=R$ and the function $f(r)$ is one, but not twice, differentiable.
-We recall that, in the exterior of the star (i.e., $r>R$), we have $f(r)=h(r)=a-2M/r$ by Birkhoff's~\cite{VojeJohansen:2005nd}.
+We recall that, in the exterior of the star (i.e., $r>R$), we have $f(r)=h(r)=a-2M/r$ by Birkhoff's theorem~\cite{VojeJohansen:2005nd}.
 In the interior of the star (i.e.
-$r<R$), we have the Schwarzschild solution for an incompressible fluid~\cite{Shapiro1983}
+$r<R$), we use the Schwarzschild solution for an incompressible fluid~\cite{Shapiro1983}
 
@@
     f(r) =\frac{1}{4}\left(1-\frac{2 M r^2}{R^3}\right)+\frac{9}{4}\left(1-\frac{2M}{R}\right) \nonumber\\ -\frac{3}{2}
-                \sqrt{\left(1-\frac{2M}{R}\right)\left(1-\frac{2 M r^2}{R^3}\right)}
+                \sqrt{\left(1-\frac{2M}{R}\right)\left(1-\frac{2 M r^2}{R^3}\right)},
 \end{align}
@@
 denotes the scattering amplitude.
-In Eqs.~(\ref{Scalar_Scattering_amp}), the functions $P_{\ell}(\cos\theta)$ are the Legendre polynomials \cite{AS65}.
-We also recall that the $S$-matrix elements $S_{\ell}(\omega)$ appearing in Eqs.~(\ref{Scalar_Scattering_amp}) can be defined from the modes $\phi_{\omega \ell}$ solutions of the homogenous radial equation
+In Eq.~(\ref{Scalar_Scattering_amp}), the functions $P_{\ell}(\cos\theta)$ are the Legendre polynomials \cite{AS65}.
+We also recall that the $S$-matrix elements $S_{\ell}(\omega)$ appearing in Eq.~(\ref{Scalar_Scattering_amp}) can be defined from the modes $\phi_{\omega \ell}$ that solve the homogenous radial equation
 \begin{equation}
 \label{H_Radial_equation}
-\left[\frac{d^{2}}{dr_{\ast}^{2}}+\omega^{2}-V_{\ell}(r)\right]\phi_{\omega\ell}= 0
+\left[\frac{d^{2}}{dr_{\ast}^{2}}+\omega^{2}-V_{\ell}(r)\right]\phi_{\omega\ell}= 0,
 \end{equation}
-here $dr/dr^\ast =\sqrt{f(r)h(r)}$ denotes the tortoise coordinate, where
+where $r^\ast$ denotes the tortoise coordinate defined by  $dr/dr^\ast =\sqrt{f(r)h(r)}$, and
 \begin{equation}\label{Inside_Potentiel}
@@
 \end{equation}
-the potential inside the star ($r<R$) and  $V_{\ell}(r)$ reduces to the Regge-Wheeler potential outside the star ($r>R$)
+is the effective potential. Outside the star ($r>R$), $V_{\ell}(r)$ reduces to the Regge-Wheeler potential 
 \begin{equation}\label{RW_Potentiel}
@@
 
-It is important to recall that the modes $\phi_{\omega \ell}$ have a regular behavior at the origin $r \to 0$
+It is important to recall that the modes $\phi_{\omega \ell}$ should have a regular behaviour at the origin $r \to 0$
 \begin{equation}\label{bc_1_in}
-\phi_{\omega  \ell}(r) \scriptstyle{\underset{r \to 0}{\sim}}
+\phi_{\omega  \ell}(r) \scriptstyle{\underset{r \to 0}{\sim}}.
 \displaystyle{r^{\ell+1}}.
 \end{equation}
-of the compact body and an asymptotic behavior at spatial infinity $r \to +\infty$ (i.e., for $r_\ast \to +\infty$) of the form
+The asymptotic behaviour of the modes at spatial infinity $r \to +\infty$ (i.e., for $r_\ast \to +\infty$) is 
 \begin{equation}\label{bc_2_in}
@@
 \end{equation}
-with a function $F$ without any singularities on the real $\lambda$ axis,we replace in Eq.~(\ref{Scalar_Scattering_amp}) the discrete sum over the ordinary angular momentum $\ell$ by a contour integral in the complex $\lambda$ plane (i.e., in the complex $\ell$ plane with $\lambda = \ell +1/2$).
+with a function $F$ without any singularities on the real $\lambda$ axis, we replace the discrete sum over the ordinary angular momentum $\ell$ in Eq.~(\ref{Scalar_Scattering_amp}) by a contour integral in the complex $\lambda$ plane (i.e., in the complex $\ell$ plane with $\lambda = \ell +1/2$).
 By noting that $P_\ell (\cos \theta)=(-1)^\ell P_\ell (-\cos \theta)$, we obtain
@@
 
-Here, we note that, the Legendre function of first kind $P_{\lambda -1/2} (z)$ denotes the analytic extension of the Legendre polynomials $P_\ell (z)$.
-It is defined in terms of hypergeometric functions by \cite{AS65}
+The Legendre function of first kind $P_{\lambda -1/2} (z)$ denotes the analytic extension of the Legendre polynomials $P_\ell (z)$. It is defined in terms of hypergeometric functions by \cite{AS65}
 \begin{equation}\label{Def_ext_LegendreP}
@@
 \end{equation}
-and the associated residues will play a central role.
-We note that the residue of the matrix $S_{\lambda-1/2}(\omega)$ at the pole $\lambda=\lambda_n(\omega)$ is defined by [see Eq.~(\ref{Matrix_S_CAM})]
+The residue of the matrix $S_{\lambda-1/2}(\omega)$ at the pole $\lambda=\lambda_n(\omega)$ is defined by [see Eq.~(\ref{Matrix_S_CAM})]
 \begin{equation}\label{residues_RP}
@@
 \end{equation}
+These residues play a central role in the complex angular momentum paradigm.
 
-Now, we ``deform'' the contour ${\cal C}$ in Eq.~(\ref{SW_Scalar_Scattering_amp}) in order to collect, by using the Cauchy's theorem, the Regge poles contributions.
-This achieved by following, \textit{mutatis mutandis}, the approach developed in Ref~\cite{Folacci:2019cmc} (see more particularly Sec.
+Now, we ``deform'' the contour ${\cal C}$ in Eq.~(\ref{SW_Scalar_Scattering_amp}) in order to collect, by using Cauchy's theorem, the Regge poles contributions.
+This is achieved by following, \textit{mutatis mutandis}, the approach developed in Ref~\cite{Folacci:2019cmc} (see more particularly Sec.
 IIB~3 and Fig.~1).
@@
 \end{equation}
-with
+is a background integral contribution with
 \begin{equation}\label{CAM_Scalar_Scattering_amp_decomp_Background_a}
@@
 \end{subequations}
-is a background integral contribution and where
+The second term in Eq.~(\ref{CAM_Scalar_Scattering_amp_tot}) ,
 \begin{eqnarray}\label{CAM_Scalar_Scattering_amp_decomp_RP}
 & & \hat{f}^\text{\tiny{RP}} (\omega, \theta) = -\frac{i \pi}{\omega}    \sum_{n=1}^{+\infty}   \frac{ \lambda_n(\omega) r_n(\omega)}{\cos[\pi \lambda_n(\omega)]}  \nonumber \\
-&&  \qquad\qquad \qquad\qquad \times  P_{\lambda_n(\omega) -1/2} (-\cos \theta)
+&&  \qquad\qquad \qquad\qquad \times  P_{\lambda_n(\omega) -1/2} (-\cos \theta),
 \end{eqnarray}
@@
 
-In this section,  we compare CAM representations or, more precisely, their Regge pole approximations with their partial wave expansions of the differential scattering cross sections.
+In this section,  we compare the partial wave expansions of the differential scattering cross sections with their equivalent CAM representations or, more precisely, their Regge pole approximations.
 
@@
 
-To construct the scattering amplitude \eqref{Scalar_Scattering_amp}, the back ground integrals~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} and~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_b} as well as the Regge pole contribution~\eqref{CAM_Scalar_Scattering_amp_decomp_RP}, we use, \textit{mutatis mutandis} the computational methods that have permitted us, in the Refs~\cite{Folacci:2019cmc,Folacci:2019vtt}, to reconsider the CAM representation for scattering of the scalar, electromagnetic and gravitational waves by Schwarzschild BH (see also Ref~\cite{Dolan:2017rtj}).
-It is important to remark that, duo to the long rang nature of the field propagating on the Schwarzschild BH (outside the compact body), the scattering amplitude~\eqref{Scalar_Scattering_amp} and the background integral~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} suffer a lack of convergence and to overcome this problem, i.e., to accelerate the convergence of these sum and integral, we have used the method described int the Appendix of Ref~\cite{Folacci:2019cmc}.
-It should be noted that we have performed all the numerical calculations by using {\it Mathematica} \cite{Mathematica}.
+To construct the scattering amplitude \eqref{Scalar_Scattering_amp}, the back ground integrals~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} and~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_b} as well as the Regge pole contribution~\eqref{CAM_Scalar_Scattering_amp_decomp_RP}, we use, \textit{mutatis mutandis} the computational methods that permitted one of us, in Refs~\cite{Folacci:2019cmc,Folacci:2019vtt} to consider the CAM representation for scattering of the scalar, electromagnetic and gravitational waves by Schwarzschild BH (see also Ref~\cite{Dolan:2017rtj}).
+It is important to remark that, duo to the long rang nature of the field propagating on the Schwarzschild BH (outside the compact body), the scattering amplitude~\eqref{Scalar_Scattering_amp} and the background integral~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} suffer a lack of convergence and to overcome this problem, i.e., to accelerate the convergence of this sum and integral, we have used the method described in the Appendix of Ref~\cite{Folacci:2019cmc}.
+We have performed all the numerical calculations by using {\it Mathematica} \cite{Mathematica}.
 
@@
 
-The WKB approach developed in the context of the determination of the \textit{w}-modes QNMs by Zhang, Wu and Leung~\cite{Zhang:2011pq} can be adapted in order to obtain analytical approximations for the ``broad Regge poles''.
-Indeed, Regge modes and QNMs both satisfy the same wave equation and the same boundary conditions but with different interpretations for the angular momentum index and the frequency.
+The WKB approach developed by Zhang, Wu and Leung~\cite{Zhang:2011pq} to determine the \textit{w}-modes of a variety of stellar models can be adapted in order to obtain analytical approximations for the ``broad Regge poles''.
+Indeed, Regge poles and quasinormal modes for relativistic stellar models (of which \textit{w}-modes are a sub-category) both satisfy the same wave equation and the same boundary conditions but with different interpretations for the angular momentum index and the frequency.
 Indeed, they satisfy the regularity condition at the origin~\eqref{bc_1_in} and the condition~\eqref{bc_2_in} at the spatial infinity, thus, the Regge poles are solutions of Eq.~\eqref{H_Radial_equation} for which the  Wronskian of $\phi^{(r_*\to 0)}_{\omega\ell}$ and $\phi^{(r_*\to \infty)}_{\omega\ell}$ vanishes (\textit{i.e.}, $A^{(-)}_{\lambda_n(\omega)-1/2} (\omega)=0$)
@@
 \begin{equation}\label{Approx_origin_bis}
-  \phi^{(r_* \to 0)}_{\omega\lambda-1/2} \underset{\omega \to \infty}{\approx} - \sin(\frac{\left(\lambda-1/2\right)\pi}{2}-\omega r_*)\quad\quad 0\leq r_*\leq R_*
+  \phi^{(r_* \to 0)}_{\omega\lambda-1/2} \underset{\omega \to \infty}{\approx} - \sin\left(\frac{\left(\lambda-1/2\right)\pi}{2}-\omega r_*\right)\quad\quad 0\leq r_*\leq R_*
 \end{equation}
 and \eqref{Approx_infinity} into  \eqref{Wronskian}, we obtain
+\begin{equation}\label{WKB_1}
+   e^{\frac{i\pi}{2}(\lambda-1/2)-i \omega R_*}=-\mathcal{R}\, e^{-\left(\frac{i\pi}{2}(\lambda-1/2)-i \omega R_*\right)}
+\end{equation}
+We then solve Eq.~\eqref{WKB_1} and we obtain \dots
 
-\begin{equation}\label{WKB_1}
-   e^{\frac{i\pi}{2}(\lambda-1/2)-i \omega R_*}=-\mathcal{R} e^{-\frac{i\pi}{2}(\lambda-1/2)-i \omega R_*}
-\end{equation}
-
-We then solve Eq.~\eqref{WKB_1} and we obtain for the lowest ``Broad Regge poles''
-
-\begin{equation}\label{lambda_Approx}
-  \lambda_n \approx \frac{2 \omega R_*}{\pi}-\left(2n+\frac{1}{2}\right)-\frac{i}{\pi} \ln\left(\mathcal{R}\right)
-\end{equation}
-
-%\begin{equation}\label{lambda_Approx}
-%  \lambda_n \approx \frac{2 \omega R_*}{\pi}+ 2 \left(n-\frac{1}{4}\right)+ 2\left\lfloor \ \frac{1}{2} - \frac{\text{Im}[2 i\omega R_*]}{2\pi} \right\rfloor - \frac{i}{\pi} \ln\left(\frac{a}{\omega^2}\right)
-%\end{equation}
+To be completed after checking
 

### 2019-10-24 rainbowCAM.tex
some rewording and work on WKB section

@@
 
-The WKB approach developed by Zhang, Wu and Leung~\cite{Zhang:2011pq} to determine the \textit{w}-modes of a variety of stellar models can be adapted in order to obtain analytical approximations for the ``broad Regge poles''.
-Indeed, Regge poles and quasinormal modes for relativistic stellar models (of which \textit{w}-modes are a sub-category) both satisfy the same wave equation and the same boundary conditions but with different interpretations for the angular momentum index and the frequency.
-Indeed, they satisfy the regularity condition at the origin~\eqref{bc_1_in} and the condition~\eqref{bc_2_in} at the spatial infinity, thus, the Regge poles are solutions of Eq.~\eqref{H_Radial_equation} for which the  Wronskian of $\phi^{(r_*\to 0)}_{\omega\ell}$ and $\phi^{(r_*\to \infty)}_{\omega\ell}$ vanishes (\textit{i.e.}, $A^{(-)}_{\lambda_n(\omega)-1/2} (\omega)=0$)
+The WKB approach developed by Zhang, Wu and Leung~\cite{Zhang:2011pq} to determine the axial \textit{w}-modes of a variety of stellar models can be adapted in order to obtain analytical approximations for the ``broad Regge poles'' for a scalar wave on a stellar background.
+The radial equation for axial gravitational perturbations is identical to Eq.~(\ref{H_Radial_equation}) but with the potential replaced by $V_{\ell}(r) \rightarrow V_{\ell}^{\text{ax}}$ where
+\begin{eqnarray}\label{RW_Potentiel_axialGW}
+V_{\ell}^{\text{ax}} = f(r)\bigg[\frac{\ell(\ell+1)}{r^2}  +\dfrac{h(r)}{2r}\left(\dfrac{f'(r)}{f(r)}+\dfrac{h'(r)}{h(r)}\right) & \nonumber \\
+	 + 8 \pi (p - \rho) & \bigg] .
+\end{eqnarray}
+%
+We can expect then that Regge poles for axial gravitational perturbations are qualitatively the same as for scalar perturbations, and the methods discussed can be easily adapted to deal with either case.
+
+\newcommand{\phiout}{\phi^{\text{out}}_{\omega\ell}}
+Regge poles and quasinormal modes for relativistic stellar models (of which \textit{w}-modes are a sub-category for gravitational perturbations) both satisfy the same wave equation and the same boundary conditions but with different interpretations for the angular momentum index and the frequency.
+Both types of pole satisfy the regularity condition at the origin~\eqref{bc_1_in} and the condition of a purely outgoing wave in the far field
+%
+\begin{equation}\label{bc_pole_inf}
+\phiout (r) \scriptstyle{\underset{r_\ast \to +\infty}{\sim}}
+\displaystyle{  A^{(+)}_\ell (\omega) e^{+i\omega r_\ast}}.
+\end{equation}
+%
+Thus, the Regge poles are solutions of Eq.~\eqref{H_Radial_equation} for which the  Wronskian of $\phi_{\omega\ell}$ and $\phiout$ vanishes (\textit{i.e.}, $A^{(-)}_{\lambda_n(\omega)-1/2} (\omega)=0$)
 \begin{equation}\label{Wronskian}
-  W[\phi^{(r_*\to 0)}_{\omega\ell},\phi^{(r_*\to \infty)}_{\omega\ell}]= 0
+  W[\phi^{}_{\omega\ell}, \phiout ]= 0
 \end{equation}
-It has been shown that, the asymptotic expressions of $\phi^{(r_*\to 0)}_{\omega\ell}$ and $\phi^{(r_*\to \infty)}_{\omega\ell}$ can be derived, buy using the standard WKB approximation, in the high-frequency domain and we have (see Refs \ldots)
+It has been shown that, the asymptotic expressions of $\phi_{\omega\ell}$ and $\phiout$ can be derived in certain regions, buy using the standard WKB approximation.
+In the high-frequency domain and we have (see Refs \ldots)
 \begin{equation}\label{Approx_origin}
-  \phi^{(r_* \to 0)}_{\omega\ell} \underset{\omega \to \infty}{=} \omega r_* j_\ell(\omega r_*) \quad\quad 0\leq r_*\leq R_*
+  \phi_{\omega\ell} \underset{\omega \to \infty}{=} \omega r_* j_\ell(\omega r_*) \quad\quad 0\leq r_*\leq R_*
 \end{equation}
@@
 \label{Approx_infinity}
-\phi^{(r_* \to \infty)}_{\omega\ell}\scriptstyle{\underset{\omega \to \infty}{=}}
+\phiout  \scriptstyle{\underset{\omega \to \infty}{=}}
 \left\{
@@
 \end{equation}
-where $\mathcal{R}$ is the standard reflection coefficient as defined in (Ref\ldots)
+and calligraphic $\mathcal{R}$ is a reflection coefficient as defined in (Ref\ldots)
 Because the potential has a direct discontinuity at the surface of the compact body (see. Refs \ldots for more details), we have for our model (\textit{i.e.}, compact body with a constant density)
@@
 \begin{equation}\label{a_def}
-a= \frac{3M \left(R-2M\right)^2}{4 R^5}
+a= \frac{3M \left(R-2M\right)^2}{4 R^5}.
 \end{equation}
-Now, by inserting~\eqref{Approx_origin}, or more precisely his expansion series when $\omega \to \infty$, \textit{i.e.},
+Now, by inserting the high frequency approximation for Eq.~\eqref{Approx_origin},
 \begin{equation}\label{Approx_origin_bis}
-  \phi^{(r_* \to 0)}_{\omega\lambda-1/2} \underset{\omega \to \infty}{\approx} - \sin\left(\frac{\left(\lambda-1/2\right)\pi}{2}-\omega r_*\right)\quad\quad 0\leq r_*\leq R_*
+  \phi^{}_{\omega,\lambda-1/2} \underset{\omega \to \infty}{\approx} - \sin\left(\frac{\left(\lambda-1/2\right)\pi}{2}-\omega r_*\right)\quad\quad 0\leq r_*\leq R_*
 \end{equation}
-and \eqref{Approx_infinity} into  \eqref{Wronskian}, we obtain
+and Eq. \eqref{Approx_infinity} into the condition  \eqref{Wronskian}, we obtain
 \begin{equation}\label{WKB_1}
-   e^{\frac{i\pi}{2}(\lambda-1/2)-i \omega R_*}=-\mathcal{R}\, e^{-\left(\frac{i\pi}{2}(\lambda-1/2)-i \omega R_*\right)}
+   e^{\frac{i\pi}{2}(\lambda-1/2)-i \omega R_*}=-\mathcal{R}\, e^{-\left(\frac{i\pi}{2}(\lambda-1/2)-i \omega R_*\right)}.
 \end{equation}

### 2019-10-24 rainbowCAM.tex
more work on WKB section

@@
 \definecolor{navyblue}{rgb}{0.0, 0.0, 0.5}
-\usepackage[pdftex]{hyperref}
+\usepackage{hyperref}
 \hypersetup
@@
 \begin{equation}\label{bc_1_in}
-\phi_{\omega  \ell}(r) \scriptstyle{\underset{r \to 0}{\sim}}.
+\phi_{\omega  \ell}(r) \scriptstyle{\underset{r \to 0}{\sim}}
 \displaystyle{r^{\ell+1}}.
@@
 
-The Legendre function of first kind $P_{\lambda -1/2} (z)$ denotes the analytic extension of the Legendre polynomials $P_\ell (z)$. It is defined in terms of hypergeometric functions by \cite{AS65}
+The Legendre function of the first kind $P_{\lambda -1/2} (z)$ denotes the analytic extension of the Legendre polynomials $P_\ell (z)$.
+It is defined in terms of hypergeometric functions by \cite{AS65}
 \begin{equation}\label{Def_ext_LegendreP}
@@
 \right.\nonumber \\
-&& -\left. \left. S_{-\lambda -1/2}(\omega) e^{i \pi \left(\lambda+1/2\right)}P_{\lambda_n(\omega) -1/2} (\cos \theta) \right]\lambda\right)
+&& -\left. \left. S_{-\lambda -1/2}(\omega) e^{i \pi \left(\lambda+1/2\right)}P_{\lambda_n(\omega) -1/2} (\cos \theta) \right]\lambda\right).
 \end{eqnarray}
@@
 The WKB approach developed by Zhang, Wu and Leung~\cite{Zhang:2011pq} to determine the axial \textit{w}-modes of a variety of stellar models can be adapted in order to obtain analytical approximations for the ``broad Regge poles'' for a scalar wave on a stellar background.
-The radial equation for axial gravitational perturbations is identical to Eq.~(\ref{H_Radial_equation}) but with the potential replaced by $V_{\ell}(r) \rightarrow V_{\ell}^{\text{ax}}$ where
+The radial equation for axial gravitational perturbations is identical to Eq.~(\ref{H_Radial_equation}) but with the potential replaced by $V_{\ell} \rightarrow V_{\ell}^{\text{ax}}$ where \cite{Cardoso:2014sna}
 \begin{eqnarray}\label{RW_Potentiel_axialGW}
-V_{\ell}^{\text{ax}} = f(r)\bigg[\frac{\ell(\ell+1)}{r^2}  +\dfrac{h(r)}{2r}\left(\dfrac{f'(r)}{f(r)}+\dfrac{h'(r)}{h(r)}\right) & \nonumber \\
+V_{\ell}^{\text{ax}}(r) = f(r)\bigg[\frac{\ell(\ell+1)}{r^2}  - \dfrac{3 h(r)}{2r}\left(\dfrac{f'(r)}{f(r)}+\dfrac{h'(r)}{h(r)}\right) & \nonumber \\
 	 + 8 \pi (p - \rho) & \bigg] .
@@
 
-\newcommand{\phiout}{\phi^{\text{out}}_{\omega\ell}}
+\newcommand{\phiout}{\phi^{\text{out}}_{\omega, \lambda-1/2}}
+\newcommand{\phireg}{\phi^{}_{\omega, \lambda-1/2}}
+
 Regge poles and quasinormal modes for relativistic stellar models (of which \textit{w}-modes are a sub-category for gravitational perturbations) both satisfy the same wave equation and the same boundary conditions but with different interpretations for the angular momentum index and the frequency.
@@
 \phiout (r) \scriptstyle{\underset{r_\ast \to +\infty}{\sim}}
-\displaystyle{  A^{(+)}_\ell (\omega) e^{+i\omega r_\ast}}.
+\displaystyle{  A^{(+)}_{\lambda-1/2} (\omega) e^{+i\omega r_\ast}}.
 \end{equation}
 %
-Thus, the Regge poles are solutions of Eq.~\eqref{H_Radial_equation} for which the  Wronskian of $\phi_{\omega\ell}$ and $\phiout$ vanishes (\textit{i.e.}, $A^{(-)}_{\lambda_n(\omega)-1/2} (\omega)=0$)
+Thus, the Regge poles are solutions of Eq.~\eqref{H_Radial_equation} for which the  Wronskian of $\phireg$ and $\phiout$ vanishes (\textit{i.e.}, $A^{(-)}_{\lambda_n(\omega)-1/2} (\omega)=0$)
 \begin{equation}\label{Wronskian}
-  W[\phi^{}_{\omega\ell}, \phiout ]= 0
+  W[\phireg, \phiout ]= 0
 \end{equation}
-It has been shown that, the asymptotic expressions of $\phi_{\omega\ell}$ and $\phiout$ can be derived in certain regions, buy using the standard WKB approximation.
-In the high-frequency domain and we have (see Refs \ldots)
+It has been shown that, the asymptotic expressions of $\phireg$ and $\phiout$ can be derived in certain regions, buy using the standard WKB approximation.
+In the high-frequency domain we have (see Refs \ldots)
 \begin{equation}\label{Approx_origin}
-  \phi_{\omega\ell} \underset{\omega \to \infty}{=} \omega r_* j_\ell(\omega r_*) \quad\quad 0\leq r_*\leq R_*
+  \phireg \underset{\omega \to \infty}{=} \omega r_* j_{\lambda-1/2} (\omega r_*) \quad\quad 0\leq r_*\leq R_*
 \end{equation}
-and
+where $j_{\lambda-1/2}$ is the spherical Bessel function of the first kind and
 \begin{equation}
@@
 \end{equation}
-and calligraphic $\mathcal{R}$ is a reflection coefficient as defined in (Ref\ldots)
-Because the potential has a direct discontinuity at the surface of the compact body (see. Refs \ldots for more details), we have for our model (\textit{i.e.}, compact body with a constant density)
+and $\mathcal{R}$ is a reflection coefficient with the defintion given in Ref.~\cite{Berry_1982}.
+Because the potential has a direct discontinuity at the surface of the compact body (see.
+Refs \cite{Zhang:2011pq,Berry_1982} for more details), we have for our model (\textit{i.e.}, compact body with a constant density)
 \begin{equation}\label{R_reflection_1}
@@
 \end{equation}
-Now, by inserting the high frequency approximation for Eq.~\eqref{Approx_origin},
+Now, by inserting the high frequency approximation for $j_{\lambda-1/2} (\omega r_*)$ into Eq.~\eqref{Approx_origin} \cite{nist},
 \begin{equation}\label{Approx_origin_bis}
@@
 \begin{equation}\label{WKB_1}
-   e^{\frac{i\pi}{2}(\lambda-1/2)-i \omega R_*}=-\mathcal{R}\, e^{-\left(\frac{i\pi}{2}(\lambda-1/2)-i \omega R_*\right)}.
+   e^{ i\pi (\lambda-1/2)- 2 i \omega R_*}=-\mathcal{R}.
 \end{equation}
-We then solve Eq.~\eqref{WKB_1} and we obtain \dots
+%
+We then solve Eq.~\eqref{WKB_1} and we obtain
+\begin{equation}\label{lambda_Approx}
+  \lambda_n \approx \frac{2 \omega R_*}{\pi}-\left(2n+\frac{1}{2}\right)+\frac{i}{\pi} \ln\left(\frac{1}{\mathcal{R}}\right)
+\end{equation}
+This corresponds to the series of Regge poles with spacing $|\Delta \lambda_n|\approx 2$ with the almost constant  imaginary part.
+Of course, they lie in the first quadrant of the CAM plan with a positive real part
+%
+\begin{equation}\label{Real_Part}
+  \frac{2 \omega R_*}{\pi}-\left(2n+\frac{1}{2}\right)>0.
+\end{equation}
+%
+The overtones are labelled by $n =1,2,\ldots$ and $n$ has an upper limit
+%
+\begin{equation}\label{Limit_Broad_RP}
+n < \left\lfloor \frac{\omega R_*}{\pi} - \frac{1}{4}\right\rfloor.
+\end{equation}
+%
+In other words, there is a finite number of the ``broad Regge poles''.
 
-To be completed after checking
+%\begin{equation}\label{lambda_Approx}
+
+%  \lambda_n \approx \frac{2 \omega R_*}{\pi}+ 2 \left(n-\frac{1}{4}\right)+ 2\left\lfloor \ \frac{1}{2} - \frac{\text{Im}[2 i\omega R_*]}{2\pi} \right\rfloor - \frac{i}{\pi} \ln\left(\frac{a}{\omega^2}\right)
+
+%\end{equation}
 

### 2019-11-03 rainbowCAM.tex
Adding in WKB section
Table WKB vs Exact
Adding in WKB

@@
 $2$  & $3$  & $ 10.71986+5.16209 i $  & $3.81484+2.48159 i$  & $13.8486+24.3824 i$  & $0.290952+1.043116 i$    \\
-     & $16$  & $ 58.442656+9.18793 i$  & $3.14868+3.31439 i$  & $5188.750-859.909 i$  & $ -0.381581-0.077583 i$    \\
+     & $16$  & $ 58.442656+9.18793 i$ & $2.64868+3.31439 i$  & $5188.750-859.909 i$  & $ -0.381581-0.077583 i$    \\
 
@@
 $8$  & $3$  & $15.1640+15.3122 i$  & $/$   & $-56.3641+59.6187 i$ & $/$     \\
-     & $16$  & $66.36581+24.28491 i$  & $15.4331+3.5889 i$  & $-479098.+1.1836070\times 10^7 i$  & $0.652285+0.920876 i$    \\
+     & $16$  & $66.36581+24.28491 i$  & $15.43310+3.5889 i$  & $-479098.+1.1836070\times 10^7 i$  & $0.652285+0.920876 i$    \\
 
@@
 with
-\begin{equation}\label{a_def}
-a= \frac{3M \left(R-2M\right)^2}{4 R^5}.
-\end{equation}
+\begin{eqnarray}
+% \nonumber % Remove numbering (before each equation)
+  a &=& -\left(\frac{i}{2}\right)^2 \lim_{\epsilon\to 0^{+}} \left[V_{\lambda-1/2}(r)\Bigg{|}_{r=R+\epsilon}-V_{\lambda-1/2}(r)\Bigg{|}_{r=R-\epsilon}\right] \nonumber\\
+   &=& \frac{3M(R-2M)}{4 R^4}
+\end{eqnarray}
+
+%\begin{equation}\label{a_def}
+%a= \frac{3M \left(R-2M\right)^2}{4 R^5}.
+%\end{equation}
 Now, by inserting the high frequency approximation for $j_{\lambda-1/2} (\omega r_*)$ into Eq.~\eqref{Approx_origin} \cite{nist},
@@
 \begin{equation}\label{Limit_Broad_RP}
-n < \left\lfloor \frac{\omega R_*}{\pi} - \frac{1}{4}\right\rfloor.
+n \leq \left\lfloor \frac{\omega R_*}{\pi} - \frac{1}{4}\right\rfloor.
 \end{equation}
@@
 %\begin{equation}\label{lambda_Approx}
+%  \lambda_n \approx \frac{2 \omega R_*}{\pi}+ 2 \left(n-\frac{1}{4}\right)+ 2\left\lfloor \ \frac{1}{2} - \frac{\text{Im}[2 i\omega R_*]}{2\pi} \right\rfloor - \frac{i}{\pi} \ln\left(\frac{a}{\omega^2}\right)
+%\end{equation}
 
-%  \lambda_n \approx \frac{2 \omega R_*}{\pi}+ 2 \left(n-\frac{1}{4}\right)+ 2\left\lfloor \ \frac{1}{2} - \frac{\text{Im}[2 i\omega R_*]}{2\pi} \right\rfloor - \frac{i}{\pi} \ln\left(\frac{a}{\omega^2}\right)
+\begingroup
+\squeezetable
+\begin{table}[htp]
+\caption{\label{tab:table3} The lowest Regge poles $\lambda_{n}(\omega)$ for the scalar field versus WBK results given by Eq.~\eqref{lambda_Approx}.
+The radius of the compact bodies is $R = 6M$ and we assume $2M=1$.}
+\smallskip
+\centering
+\begin{ruledtabular}
+\begin{tabular}{cccc}
+ $n$ & $\omega$  & $\lambda^{\text{(B-R)}}_n(\omega)$ & $\lambda^{\text{(B-R, WKB)}}_n(\omega)$
+ \\ \hline
+$1$  & $3$  & $1.56219+2.33072 i$  & $1.592793+2.189767i$   \\
+     & $16$ & $ 0.62529+3.27098 i$ & $0.661564+3.255453i $   \\
 
-%\end{equation}
+$2$  & $3$  & $3.81484+2.48159 i$  & $3.592793+2.189767i $    \\
+     & $16$ & $2.64868+3.31439 i$  & $2.661564+3.255453i $    \\
+
+$3$  & $3$  & $6.35675+2.64104 i$ & $5.592793+2.189767i $    \\
+     & $16$ & $4.70011+3.35821 i$  & $4.661564+3.255453i $    \\
+
+$4$  & $3$  & $/$  & $ / $   \\
+     & $16$ & $6.78093+3.40257 i$  & $6.661564+3.255453i $  \\
+
+$5$  & $3$  & $/$  & $/$     \\
+     & $16$ & $8.89270+3.44762 i$  & $8.661564+3.255453i $   \\
+
+$6$  & $3$  & $/$  & $/$    \\
+     & $16$ & $11.03720+3.49356 i$ & $10.661564+3.255453i $ \\
+
+$7$  & $3$  & $/$ & $/$     \\
+     & $16$ & $13.21653+3.54058 i$  & $12.661564+3.255453i$ \\
+
+$8$  & $3$ & $/$   & $/$     \\
+     & $16$ & $15.4331+3.5889 i$  & $14.661564+3.255453i $  \\
+
+$9$  & $3$ & $/$   & $/$   \\
+     & $16$ & $17.6898+3.6390 i$  & $16.661564+3.384517i $   \\
+
+$10$  & $3$  & $/$  & $/$   \\
+     & $16$  & $19.9900+3.6910 i$  & $18.661564+3.255453i $  \\
+\end{tabular}
+\end{ruledtabular}
+\end{table}
+\endgroup
 
@@
 \bibliography{rainbowCAM}
-\bibliographystyle{apsrev4-1}
+%\bibliographystyle{apsrev4-1}
 

### 2019-11-08 rainbowCAM.tex

@@
 
- The topic of time-independent scattering has been studied in detail since the 1960s \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970}, and there now exists a substantial literature \cite{Mashhoon:1973zz,Chrzanowski:1976jb,DeLogi:1977dp,Sanchez:1977vz,MatznerRyan1978,Handler:1980un,Matzner:1985rjn,Futterman:1988ni,Andersson:1995vi,Glampedakis:2001cx,Dolan:2006vj,Dolan:2007ut,Dolan:2008kf,Crispino:2009xt,Cotaescu:2014jca,Sorge:2015yoa,Gussmann:2016mkp,Leite:2017zyb,Nambu:2019sqn, Folacci:2019vtt,Leite:2019eis}.
+ The topic of time-independent scattering by compact bodies in the gravitational context has been studied in detail since the 1960s \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970}, and there now exists a substantial literature exploring the scattering of scalar, spinor, electromagnetic and gravitational waves \cite{Mashhoon:1973zz,Chrzanowski:1976jb,DeLogi:1977dp,Sanchez:1977vz,MatznerRyan1978,Handler:1980un,Matzner:1985rjn,Futterman:1988ni,Andersson:1995vi,Glampedakis:2001cx,Dolan:2006vj,Dolan:2007ut,Dolan:2008kf,Crispino:2009xt,Cotaescu:2014jca,Sorge:2015yoa,Gussmann:2016mkp,Leite:2017zyb,Nambu:2019sqn, Folacci:2019vtt,Leite:2019eis}.
 

### 2019-11-08 rainbowCAM.tex
Started work on the Introduction.

--- 2019-11-03 rainbowCAM.tex
@@
 
- The topic of time-independent scattering has been studied in detail since the 1960s \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970}, and there now exists a substantial literature \cite{Mashhoon:1973zz,Chrzanowski:1976jb,DeLogi:1977dp,Sanchez:1977vz,MatznerRyan1978,Handler:1980un,Matzner:1985rjn,Futterman:1988ni,Andersson:1995vi,Glampedakis:2001cx,Dolan:2006vj,Dolan:2007ut,Dolan:2008kf,Crispino:2009xt,Cotaescu:2014jca,Sorge:2015yoa,Gussmann:2016mkp,Leite:2017zyb,Nambu:2019sqn, Folacci:2019vtt,Leite:2019eis}.
+The time-independent scattering of planar waves in the gravitational field of a compact body has been studied in some detail since the 1960s \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970}.
+A substantial literature has developed on \emph{black hole scattering}, focussing on the canonical scenario of a planar wave of frequency $\omega$ and spin $s$ \cite{Chrzanowski:1976jb} impinging upon a black hole of mass $M$ in vacuum \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970, Mashhoon:1973zz,Fabbri:1975,Sanchez:1977vz,MatznerRyan1978,Handler:1980un,Matzner:1985rjn,Futterman:1988ni,Andersson:1995vi,Glampedakis:2001cx,Dolan:2006vj,Dolan:2007ut,Dolan:2008kf,Crispino:2009xt,Cotaescu:2014jca,Gussmann:2016mkp}.
+A dimensionless parameter,
+\begin{equation}
+M \omega = \pi \frac{r_g}{\lambda}, 
+\end{equation}
+encapsulates the ratio of the gravitational radius $r_g = 2GM/c^2$ to the wavelength $\lambda$ (here we adopt geometric units such that $G=c=1$).
+The long wavelength ($M \omega \ll 1$), short wavelength ($M \omega \gg 1$) and intermediate regimes have been studied with a combination of perturbative \cite{DeLogi:1977dp,Dolan:2007ut,Guadagnini:2008ha,Sorge:2015yoa}, semi-classical \cite{Matzner:1985rjn, Anninos:1992ih} and numerical methods.
+The $s = 0$ (scalar) \cite{Matzner:1968,Sanchez:1977vz,Andersson:1995vi,Glampedakis:2001cx,Leite:2019eis}, $s=1/2$ (fermion) \cite{Dolan:2006vj,Cotaescu:2014jca}, $s=1$ (electromagnetic) \cite{Fabbri:1975, Crispino:2009xt, Crispino:2015gua} and $s=2$ (gravitational) cases \cite{MatznerRyan1978,Handler:1980un,Dolan:2008kf} have all been covered.
+
+Time-independent scattering by a compact body with a regular centre, such as a neutron star or white dwarf, has received comparatively less attention.
+In such a scenario, an electromagnetic wave will not penetrate inside the compact body; on the other hand, a gravitational wave will pass through the body without impediment from the matter distribution.
+Similarly, a neutron star is expected to be substantially transparent to neutrinos.
+In these cases, the body scatters the wave indirectly, through its influence on the spacetime curvature.
+Recent work \cite{Dolan:2017rtj, Stratton:2019deq} has explored the \emph{rainbow scattering} phenomenon that arises at short wavelengths, due to a stationary point in the geodesic deflection function associated with a ray that passes somewhat inside the body.
+In principle, the rainbow angle is a diagnostic of the matter distribution of the body, and thus its nuclear equation of state.
+\cite{Nambu:2019sqn}
+
+Now describe the application of CAM methods to black holes, and its successes ... The aim of this work is to extend the methods to compact bodies.
+
+Describe QNMs - resonances in the time domain: \cite{Detweiler:1985zz, Kokkotas:1986gd, Chandrasekhar449, Kokkotas:1992ka, Leins:1993zz, Andersson:1995ez, Andersson1996} Review of QNMs: \cite{Kokkotas:1999bd}.
+Now describe how these are connected to Regge poles.
+
+Finally a paragraph on the connections to Mie scattering by a transparent sphere.
+
+\cite{Leite:2017zyb,Nambu:2019sqn, Folacci:2019vtt,}.
 

### 2019-11-08 rainbowCAM.tex
Started to rearrange the sections.

@@
 
-\section{Differential scattering cross sections for scalar waves, their CAM representation and their Regge pole approximations}
+%\section{Differential scattering cross sections for scalar waves, their CAM representation and their Regge pole approximations}
+\section{The Regge pole spectrum of a compact body}
 \label{SecII}
@@
 
-\subsection{Our model}
+\subsection{The model}
 \label{SecIIa}
 
-  We consider that the gravitating source is a spherically symmetric incompressible perfect fluid ball of uniform
-density (see Ref~\cite{Dolan:2017rtj} and references therein). In a coordinate system $\{t,r,\theta,\varphi\}$, the object is described by the metric
+The gravitating source is assumed to be spherically-symmetric, such that in a coordinate system $\{t,r,\theta,\varphi\}$, the object is described by a diagonal metric $g_{\mu \nu}$ and the line element
 \begin{equation}\label{Line_elem}
-  ds^2= -f(r) dt^2+h(r)^{-1}dr^2+r^2d\sigma_2^2
+ ds^2 = g_{\mu \nu} dx^\mu dx^\nu = -f(r) dt^2+h(r)^{-1}dr^2+r^2d\sigma_2^2
 \end{equation}
 where $d\sigma_2^2$ denotes the metric on the unit 2-sphere $S^2$.
-Here, the radial function $h(r)$ is continuous but not differentiable across the surface of the star $r=R$ and the function $f(r)$ is one, but not twice, differentiable.
-We recall that, in the exterior of the star (i.e., $r>R$), we have $f(r)=h(r)=a-2M/r$ by Birkhoff's theorem~\cite{VojeJohansen:2005nd}.
-In the interior of the star (i.e.
-$r<R$), we use the Schwarzschild solution for an incompressible fluid~\cite{Shapiro1983}
+In the vacuum exterior of the star (i.e., $r>R$), the radial functions $f(r)$ and $h(r)$ depend only on $M$, the total mass of body: $f(r)=h(r)=1-2M/r$ by Birkhoff's theorem~\cite{VojeJohansen:2005nd}.
+In the interior, $f(r)$ and $h(r)$ depend on the matter distribution and equation of state (EoS).
 
+A widely-studied model is that of a polytropic star, with an EoS $p(\rho) = \kappa \rho^{1+1/n}$, where $n$ is the polytropic index (see e.g.~\cite{Stratton:2019deq}).
+Here we shall consider an incompressible perfect fluid ball of uniform density described by Schwarzschild's interior solution for an incompressible fluid \cite{Shapiro1983}, with
+\begin{subequations}
+\begin{align}
+\rho &= \frac{M}{\frac{4}{3} \pi R^3} , \\
+p &= \rho \frac{\beta(R) - \beta(r)}{ \beta(r) - 3 \beta(R)} , \\
+\beta(x) &= \sqrt{3 - 8 \pi \rho x^2}
+\end{align}
+\end{subequations}
+and
+%
 \begin{subequations}\label{Interior_Solution}
 \begin{align}\label{Interior_Solution_f}
-    f(r) =\frac{1}{4}\left(1-\frac{2 M r^2}{R^3}\right)+\frac{9}{4}\left(1-\frac{2M}{R}\right) \nonumber\\ -\frac{3}{2}
-                \sqrt{\left(1-\frac{2M}{R}\right)\left(1-\frac{2 M r^2}{R^3}\right)},
+ f(r) &= \frac{1}{4}\left(1-\frac{2 M r^2}{R^3}\right)+\frac{9}{4}\left(1-\frac{2M}{R}\right) \nn \\ 
+       & \quad -\frac{3}{2} \sqrt{\left(1-\frac{2M}{R}\right)\left(1-\frac{2 M r^2}{R^3}\right)}, \\
+ h(r) &= 1-\frac{2 M r^2}{R^3} . \label{Interior_Solution_h}
 \end{align}
-\begin{equation}\label{Interior_Solution_h}
- h(r) =1-\frac{2 M r^2}{R^3}
+\end{subequations}
+The constant-density model can be thought of as representing the $n=0$ limit of the polytropes. 
+The radial function $h(r)$ is $C^0$ (i.e.~continuous but not differentiable) at the surface of the star $r=R$, and the radial function $f(r)$ is $C^1$ there (i.e.~once but not twice differentiable).
+In the polytropic cases $n > 0$, the functions are more regular at the surface, but not $C^\infty$ (i.e.~not smooth).
+As we shall see, the breakdown of smoothness leads to consequences for the Regge pole spectrum.
+
+We shall consider a scalar wave $\Phi(x)$ on the compact body spacetime governed by the Klein-Gordon equation
+\begin{equation}
+\Box \Phi \equiv \frac{1}{\sqrt{-g}} \partial_{\mu} \left( \sqrt{-g} g^{\mu \nu} \partial_{\nu} \Phi \right) = 0
 \end{equation}
-\end{subequations}
-
-\subsection{Partial wave expansions of differential scattering cross sections}
-\label{SecIIb}
-
-We recall that, for the scalar field, the differential scattering cross section is given by (see, e.g.,\cite{Dolan:2017rtj} and references therein)
-\begin{equation}\label{Scalar_Scattering_diff}
-  \frac{d\sigma}{d\Omega} = |\hat{f}(\omega,\theta)|^2
+where $g^{\mu \nu}$ is the inverse metric 
+$
+g = - f(r) h^{-1}(r) r^4 \sin^2 \theta
+$
+and is the metric determinant. Performing a standard separation of variables,
+\begin{equation}
+\Phi = \frac{1}{r} \sum_{\omega \ell m} \phi_{\omega \ell}(r)  Y_{lm}(\theta, \phi) e^{-i \omega t} ,
 \end{equation}
-where
-\begin{equation}\label{Scalar_Scattering_amp}
- \hat{f}(\omega,\theta) = \frac{1}{2 i \omega} \sum_{\ell = 0}^{\infty} (2\ell+1)[S_{\ell}(\omega)-1]P_{\ell}(\cos\theta)
-\end{equation}
-denotes the scattering amplitude.
-In Eq.~(\ref{Scalar_Scattering_amp}), the functions $P_{\ell}(\cos\theta)$ are the Legendre polynomials \cite{AS65}.
-We also recall that the $S$-matrix elements $S_{\ell}(\omega)$ appearing in Eq.~(\ref{Scalar_Scattering_amp}) can be defined from the modes $\phi_{\omega \ell}$ that solve the homogenous radial equation
+leads to a radial equation of the form
 \begin{equation}
@@
 \end{equation}
-where $r^\ast$ denotes the tortoise coordinate defined by  $dr/dr^\ast =\sqrt{f(r)h(r)}$, and
+where $r^\ast$ denotes the \emph{tortoise coordinate} defined by  $dr/dr^\ast =\sqrt{f(r)h(r)}$, and $V_{\ell}(r)$
+is the effective potential.
+
+\subsection{Effective potentials}
+The effective potential for the scalar field is $V_{\ell}(r) = V_{\ell}^{(s=0)}(r)$, where
 \begin{equation}\label{Inside_Potentiel}
-  V_{\ell}(r) =f(r)\left[\frac{\ell(\ell+1)}{r^2}+\frac{h(r)}{2r}\left(\frac{f'(r)}{f(r)}+\frac{h'(r)}{h(r)}\right)\right]
+  V_{\ell}^{(s)}(r) \equiv f(r)\left[\frac{\ell(\ell+1)}{r^2}+\frac{(1-s^2) h(r)}{2r}\left(\frac{f'(r)}{f(r)}+\frac{h'(r)}{h(r)}\right)\right]
 \end{equation}
-is the effective potential. Outside the star ($r>R$), $V_{\ell}(r)$ reduces to the Regge-Wheeler potential
+Remarkably, the radial equation for axial gravitational perturbations is identical to Eq.~(\ref{H_Radial_equation}) but with the potential replaced by $V_{\ell}(r) \rightarrow V_{\ell}^{\text{ax}}(r)$ where \cite{Cardoso:2014sna}
+\begin{eqnarray}\label{RW_Potentiel_axialGW}
+V_{\ell}^{\text{ax}}(r) = V_{\ell}^{(s=2)} + 8 \pi f(r) (p - \rho)  .
+\end{eqnarray}
+%
+Outside the star in the vacuum region ($r>R$), $V_{\ell}(r)$ reduces to the Regge-Wheeler potential ,
 \begin{equation}\label{RW_Potentiel}
-  V_{\ell}(r) =\left(1-\frac{2M}{r}\right)\left(\frac{\ell(\ell+1)}{r^2}+\frac{2M}{r^3}\right)
+  V_{\ell}(r) =\left(1-\frac{2M}{r}\right)\left(\frac{\ell(\ell+1)}{r^2}+\frac{2M(1-s^2)}{r^3}\right)
 \end{equation}
-and the tortoise coordinates $r^\ast$ reduces to $r^\ast = r+ 2M \ln [r/(2M) -1]+\mathrm{const}$.
+with $s=0$ in the scalar-field case, and $s=2$ in the axial gravitational-wave case. In the exterior, the tortoise coordinates $r^\ast$ reduces to $r^\ast = r+ 2M \ln [r/(2M) -1]+\mathrm{const}$.
 
+Effective potentials for the incompressible model are shown in Fig.~\ref{}, for two cases: (i) a neutron-star model with $R = 6M$, and (ii) a ultra-compact object with $R = 2.26M$ (i.e.~close to the Buchdahl bound).
+In both cases we observe a discontinuity in $V_{\ell}(r)$ across the star's surface, due to the $C^0$ behaviour of $h(r)$.
+The jump in the potential takes opposite signs in the scalar-field and gravitational-wave cases, with
+\begin{subequations}
+\begin{align}
+\Delta V^{(s=0)} &= + \frac{3Mf(R)}{R^3} , \\
+\Delta V^{(ax)} &= - \frac{3Mf(R)}{R^3} , 
+\end{align}
+\end{subequations}
+where
+\begin{equation}
+\Delta V \equiv \lim_{\epsilon \rightarrow 0} \left\{ V(R + \epsilon) - V(R - \epsilon) \right\} . 
+\end{equation}
+
+\subsection{Boundary conditions}
 It is important to recall that the modes $\phi_{\omega \ell}$ should have a regular behaviour at the origin $r \to 0$
@@
 \end{equation}
+
+We can expect then that Regge poles for axial gravitational perturbations are qualitatively the same as for scalar perturbations, and the methods discussed can be easily adapted to deal with either case.
+
+\subsection{Partial wave expansions of differential scattering cross sections}
+\label{SecIIb}
+
+\subsection{Scattering theory}
+We recall that, for the scalar field, the differential scattering cross section is given by (see, e.g.,\cite{Dolan:2017rtj} and references therein)
+\begin{equation}\label{Scalar_Scattering_diff}
+  \frac{d\sigma}{d\Omega} = |\hat{f}(\omega,\theta)|^2
+\end{equation}
+where
+\begin{equation}\label{Scalar_Scattering_amp}
+ \hat{f}(\omega,\theta) = \frac{1}{2 i \omega} \sum_{\ell = 0}^{\infty} (2\ell+1)[S_{\ell}(\omega)-1]P_{\ell}(\cos\theta)
+\end{equation}
+denotes the scattering amplitude.
+In Eq.~(\ref{Scalar_Scattering_amp}), the functions $P_{\ell}(\cos\theta)$ are the Legendre polynomials \cite{AS65}.
+We also recall that the $S$-matrix elements $S_{\ell}(\omega)$ appearing in Eq.~(\ref{Scalar_Scattering_amp}) can be defined from the modes $\phi_{\omega \ell}$ that solve the homogenous radial equation
 
@@
 To construct the scattering amplitude \eqref{Scalar_Scattering_amp}, the back ground integrals~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} and~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_b} as well as the Regge pole contribution~\eqref{CAM_Scalar_Scattering_amp_decomp_RP}, we use, \textit{mutatis mutandis} the computational methods that permitted one of us, in Refs~\cite{Folacci:2019cmc,Folacci:2019vtt} to consider the CAM representation for scattering of the scalar, electromagnetic and gravitational waves by Schwarzschild BH (see also Ref~\cite{Dolan:2017rtj}).
-It is important to remark that, duo to the long rang nature of the field propagating on the Schwarzschild BH (outside the compact body), the scattering amplitude~\eqref{Scalar_Scattering_amp} and the background integral~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} suffer a lack of convergence and to overcome this problem, i.e., to accelerate the convergence of this sum and integral, we have used the method described in the Appendix of Ref~\cite{Folacci:2019cmc}.
+It is important to remark that, due to the long rang nature of the field propagating on the Schwarzschild BH (outside the compact body), the scattering amplitude~\eqref{Scalar_Scattering_amp} and the background integral~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} suffer a lack of convergence and to overcome this problem, i.e., to accelerate the convergence of this sum and integral, we have used the method described in the Appendix of Ref~\cite{Folacci:2019cmc}.
 We have performed all the numerical calculations by using {\it Mathematica} \cite{Mathematica}.

### 2019-11-11 rainbowCAM.tex
Added a figure showing the effective potential (thanks Tom!)

@@
 \end{equation}
-where $r^\ast$ denotes the \emph{tortoise coordinate} defined by  $dr/dr^\ast =\sqrt{f(r)h(r)}$, and $V_{\ell}(r)$
-is the effective potential.
+where $V_{\ell}(r)$ is the effective potential, and $r^\ast$ denotes the \emph{tortoise coordinate} defined by  
+\begin{equation}
+dr/dr^\ast =\sqrt{f(r)h(r)} .  \label{eq:tortoise}
+\end{equation}
 
@@
 
-Effective potentials for the incompressible model are shown in Fig.~\ref{}, for two cases: (i) a neutron-star model with $R = 6M$, and (ii) a ultra-compact object with $R = 2.26M$ (i.e.~close to the Buchdahl bound).
+Effective potentials for the incompressible model are shown in Fig.~\ref{fig:Veff}, for two cases: (i) a neutron-star model with $R = 6M$, and (ii) a ultra-compact object with $R = 2.26M$ (i.e.~close to the Buchdahl bound).
 In both cases we observe a discontinuity in $V_{\ell}(r)$ across the star's surface, due to the $C^0$ behaviour of $h(r)$.
@@
 \end{equation}
+
+ \begin{figure}[htb]
+\centering
+ \includegraphics[scale=0.50]{potentials_s02_CD_R6L2_v2} \\ \vspace{0.2cm}
+ \includegraphics[scale=0.50]{potentials_s02_CD_R2p26L2}
+\caption{\label{RP_approx_2Mw_3_6_s_1} The effective potential $V_\ell$ for a quadrupole ($\ell =2$) perturbation of a compact body of constant density and tenuity $R/M = 6$ (upper) and $R /M = 2.26$ (lower).
+The scalar field and axial gravitational-wave potentials are indicated as solid/black lines and dotted/red lines, respectively.
+The horizontal axis is the tortoise coordinate $r_\ast$ defined in Eq.~(\ref{eq:tortoise}).}
+\label{fig:Veff}
+\end{figure}
 

### 2019-11-13 rainbowCAM.tex
re scaled potential figures
Moved things around a bit.

@@
 
-\title{Scattering from compact objects, Regge poles \\ and the Complex Angular Momentum method}
+\title{Scattering from compact objects: Regge poles \\ and the Complex Angular Momentum method}
 
@@
 %\section{Differential scattering cross sections for scalar waves, their CAM representation and their Regge pole approximations}
-\section{The Regge pole spectrum of a compact body}
+\section{Waves on a compact-body spacetime}
 \label{SecII}
 
-In this section we describe the model for our compact object.
+In this section we describe the model for the compact object.
 Then we recall the partial wave expansions of the differential scattering cross section for plane monochromatic scalar waves impinging upon a compact body.
@@
 \end{equation}
-where $d\sigma_2^2$ denotes the metric on the unit 2-sphere $S^2$.
-In the vacuum exterior of the star (i.e., $r>R$), the radial functions $f(r)$ and $h(r)$ depend only on $M$, the total mass of body: $f(r)=h(r)=1-2M/r$ by Birkhoff's theorem~\cite{VojeJohansen:2005nd}.
+where $d\sigma_2^2 = d\theta^2 + \sin^2 \theta d\varphi^2$ denotes the metric on the unit 2-sphere $S^2$.
+In the vacuum exterior of the star ($r>R$), the radial functions $f(r)$ and $h(r)$ depend only on $M$, the total mass of body: $f(r)=h(r)=1-2M/r$ by Birkhoff's theorem~\cite{VojeJohansen:2005nd}.
 In the interior, $f(r)$ and $h(r)$ depend on the matter distribution and equation of state (EoS).
@@
 A widely-studied model is that of a polytropic star, with an EoS $p(\rho) = \kappa \rho^{1+1/n}$, where $n$ is the polytropic index (see e.g.~\cite{Stratton:2019deq}).
-Here we shall consider an incompressible perfect fluid ball of uniform density described by Schwarzschild's interior solution for an incompressible fluid \cite{Shapiro1983}, with
+Here we shall consider a special case: an incompressible perfect fluid ball of uniform density described by Schwarzschild's interior solution for an incompressible fluid \cite{Shapiro1983}, with
 \begin{subequations}
@@
 \end{subequations}
-and
+and metric functions
 %
@@
 \end{subequations}
-The constant-density model can be thought of as representing the $n=0$ limit of the polytropes. 
-The radial function $h(r)$ is $C^0$ (i.e.~continuous but not differentiable) at the surface of the star $r=R$, and the radial function $f(r)$ is $C^1$ there (i.e.~once but not twice differentiable).
-In the polytropic cases $n > 0$, the functions are more regular at the surface, but not $C^\infty$ (i.e.~not smooth).
+The constant-density model can be thought of as representing the $n=0$ limit of the family of polytropes. 
+The radial function $h(r)$ is $C^0$ (i.e.~continuous but not differentiable) at the surface of the star $r=R$, and the radial function $f(r)$ is $C^1$ there (i.e.~once-differentiable).
+In the polytropic cases $n > 0$, the functions are more regular \sam{can we make a precise statement?} at the surface, but not $C^\infty$ (i.e.~not smooth).
 As we shall see, the breakdown of smoothness leads to consequences for the Regge pole spectrum.
 
-We shall consider a scalar wave $\Phi(x)$ on the compact body spacetime governed by the Klein-Gordon equation
+We shall consider a scalar wave $\Phi(x)$ propagating on the compact body spacetime, governed by the Klein-Gordon equation
 \begin{equation} 
@@
 \end{equation}
-where $g^{\mu \nu}$ is the inverse metric 
+where $g^{\mu \nu}$ is the inverse metric and 
 $
-g = - f(r) h^{-1}(r) r^4 \sin^2 \theta
+g % = - f(r) h^{-1}(r) r^4 \sin^2 \theta
 $
-and is the metric determinant. Performing a standard separation of variables,
+ is the metric determinant. Performing a standard separation of variables,
 \begin{equation}
@@
 \begin{equation}
-dr/dr^\ast =\sqrt{f(r)h(r)} .  \label{eq:tortoise}
+\frac{dr}{dr^\ast} =\sqrt{f(r)h(r)} .  \label{eq:tortoise}
 \end{equation}
@@
 \subsection{Effective potentials}
-The effective potential for the scalar field is $V_{\ell}(r) = V_{\ell}^{(s=0)}(r)$, where
+The effective potential for the scalar field in Eq.~(\ref{H_Radial_equation}) is $V_{\ell}(r) = V_{\ell}^{(s=0)}(r)$, where we define
 \begin{equation}\label{Inside_Potentiel}
@@
 \end{equation}
-Remarkably, the radial equation for axial gravitational perturbations is identical to Eq.~(\ref{H_Radial_equation}) but with the potential replaced by $V_{\ell}(r) \rightarrow V_{\ell}^{\text{ax}}(r)$ where \cite{Cardoso:2014sna}
+Remarkably, the radial equation for axial gravitational perturbations is identical to Eq.~(\ref{H_Radial_equation}) but with an effective potential $V_{\ell}^{\text{ax}}(r)$ where \cite{Cardoso:2014sna}
 \begin{eqnarray}\label{RW_Potentiel_axialGW}
@@
 %
-Outside the star in the vacuum region ($r>R$), $V_{\ell}(r)$ reduces to the Regge-Wheeler potential ,
+Outside the star in the vacuum region ($r>R$), the effective potentials reduce to the Regge-Wheeler potential,
 \begin{equation}\label{RW_Potentiel}
-  V_{\ell}(r) =\left(1-\frac{2M}{r}\right)\left(\frac{\ell(\ell+1)}{r^2}+\frac{2M(1-s^2)}{r^3}\right)
+V^{(s)}_{\ell}(r) =\left(1-\frac{2M}{r}\right)\left(\frac{\ell(\ell+1)}{r^2}+\frac{2M(1-s^2)}{r^3}\right)
 \end{equation}
-with $s=0$ in the scalar-field case, and $s=2$ in the axial gravitational-wave case. In the exterior, the tortoise coordinates $r^\ast$ reduces to $r^\ast = r+ 2M \ln [r/(2M) -1]+\mathrm{const}$.
+with $s=0$ in the scalar-field case, and $s=2$ in the axial gravitational-wave case.
+In the exterior, the tortoise coordinates $r^\ast$ reduces to $r^\ast = r+ 2M \ln [r/(2M) -1]+k$, where $k$ is a constant that is chosen such that $r_\ast(r=0) = 0$ and $r_\ast(r)$ is a continuous function.
 
-Effective potentials for the incompressible model are shown in Fig.~\ref{fig:Veff}, for two cases: (i) a neutron-star model with $R = 6M$, and (ii) a ultra-compact object with $R = 2.26M$ (i.e.~close to the Buchdahl bound).
-In both cases we observe a discontinuity in $V_{\ell}(r)$ across the star's surface, due to the $C^0$ behaviour of $h(r)$.
+Effective potentials for the incompressible model are shown in Fig.~\ref{fig:Veff}, for two cases: (i) a neutron-star model with $R = 6M$, and (ii) a ultra-compact object (UCO \cite{Macedo:2018yoi}) with $R = 2.26M$.
+% (i.e.~close to the Buchdahl bound of $R/M = 9/4$).
+In both cases we observe a discontinuity in $V_{\ell}(r)$ across the star's surface, due to the $C^0$ property of $h(r)$.
 The jump in the potential takes opposite signs in the scalar-field and gravitational-wave cases, with
@@
 \begin{align}
-\Delta V^{(s=0)} &= + \frac{3Mf(R)}{R^3} , \\
-\Delta V^{(ax)} &= - \frac{3Mf(R)}{R^3} , 
+\Delta V_{\ell}^{(s=0)} &= + \frac{3Mf(R)}{R^3} , \\
+\Delta V_{\ell}^{(ax)} &= - \frac{3Mf(R)}{R^3} , 
 \end{align}
@@
 \begin{equation}
-\Delta V \equiv \lim_{\epsilon \rightarrow 0} \left\{ V(R + \epsilon) - V(R - \epsilon) \right\} . 
+\Delta V_{\ell} \equiv \lim_{\epsilon \rightarrow 0} \left\{ V_{\ell}(R + \epsilon) - V_{\ell}(R - \epsilon) \right\} . 
 \end{equation}
@@
 
-\subsection{Boundary conditions}
-It is important to recall that the modes $\phi_{\omega \ell}$ should have a regular behaviour at the origin $r \to 0$
+In the UCO case ($R < 3M$), the effective potential has a maximum near the light-ring at $r=3M$, and there is a trapping region, as shown in Fig.~\ref{fig:Veff}.
+
+\subsection{Boundary conditions and scattering}
+The modes $\phi_{\omega \ell}$ should have a regular behaviour at the centre of the object ($r = 0$), and inspection of the radial equation (\ref{H_Radial_equation}) shows that
 \begin{equation}\label{bc_1_in}
-\phi_{\omega  \ell}(r) \scriptstyle{\underset{r \to 0}{\sim}}
+\phi_{\omega  \ell}(r) \, \scriptstyle{\underset{r \to 0}{\sim}} \,
 \displaystyle{r^{\ell+1}}.
 \end{equation}
-The asymptotic behaviour of the modes at spatial infinity $r \to +\infty$ (i.e., for $r_\ast \to +\infty$) is
+The asymptotic behaviour of the modes far from the body ($r \to +\infty$, or equivalently $r_\ast \to +\infty$) is
 \begin{equation}\label{bc_2_in}
@@
 \end{equation}
-In this last equation, the coefficients $A^{(-)}_\ell (\omega)$ and  $A^{(+)}_\ell (\omega)$ are complex amplitudes and we have
+With the complex coefficients $A^{(\pm)}_\ell (\omega)$ we then define the \emph{S-matrix elements}, 
 \begin{equation}\label{Matrix_S}
@@
 
-We can expect then that Regge poles for axial gravitational perturbations are qualitatively the same as for scalar perturbations, and the methods discussed can be easily adapted to deal with either case.
+%We can expect then that Regge poles for axial gravitational perturbations are qualitatively the same as for scalar perturbations, and the methods discussed can be easily adapted to deal with either case.
 
-\subsection{Partial wave expansions of differential scattering cross sections}
-\label{SecIIb}
+\section{The Regge pole spectrum}
 
-\subsection{Scattering theory}
-We recall that, for the scalar field, the differential scattering cross section is given by (see, e.g.,\cite{Dolan:2017rtj} and references therein)
-\begin{equation}\label{Scalar_Scattering_diff}
-  \frac{d\sigma}{d\Omega} = |\hat{f}(\omega,\theta)|^2
-\end{equation}
-where
-\begin{equation}\label{Scalar_Scattering_amp}
- \hat{f}(\omega,\theta) = \frac{1}{2 i \omega} \sum_{\ell = 0}^{\infty} (2\ell+1)[S_{\ell}(\omega)-1]P_{\ell}(\cos\theta)
-\end{equation}
-denotes the scattering amplitude.
-In Eq.~(\ref{Scalar_Scattering_amp}), the functions $P_{\ell}(\cos\theta)$ are the Legendre polynomials \cite{AS65}.
-We also recall that the $S$-matrix elements $S_{\ell}(\omega)$ appearing in Eq.~(\ref{Scalar_Scattering_amp}) can be defined from the modes $\phi_{\omega \ell}$ that solve the homogenous radial equation
+ \subsection{Regge poles and quasinormal modes}
 
-\subsection{CAM representation of the scattering amplitude}
-\label{SecIIc}
+ \subsection{Numerical method}
 
-To construct the CAM representation, we follow the steps in section~II of the Ref~\cite{Folacci:2019cmc} and recall the main results.
-
-By using the Sommerfeld-Watson transformation \cite{Watson18,Sommerfeld49,Newton:1982qc} which permits us to write
-\begin{equation}\label{SWT_gen}
-\sum_{\ell=0}^{+\infty} (-1)^\ell F(\ell)= \frac{i}{2} \int_{\cal C} d\lambda \, \frac{F(\lambda -1/2)}{\cos (\pi \lambda)}
-\end{equation}
-with a function $F$ without any singularities on the real $\lambda$ axis, we replace the discrete sum over the ordinary angular momentum $\ell$ in Eq.~(\ref{Scalar_Scattering_amp}) by a contour integral in the complex $\lambda$ plane (i.e., in the complex $\ell$ plane with $\lambda = \ell +1/2$).
-By noting that $P_\ell (\cos \theta)=(-1)^\ell P_\ell (-\cos \theta)$, we obtain
-\begin{eqnarray}\label{SW_Scalar_Scattering_amp}
-& & \hat{f}(\omega,\theta) = \frac{1}{2 \omega}  \int_{\cal C} d\lambda \, \frac{\lambda}{\cos (\pi \lambda)} \nonumber \\
-&&  \qquad\qquad   \times \left[ S_{\lambda -1/2} (\omega) -1 \right]P_{\lambda -1/2} (-\cos \theta).
-\end{eqnarray}
-In Eqs.~(\ref{SWT_gen}) and (\ref{SW_Scalar_Scattering_amp}), the integration contour encircles counterclockwise the positive real axis of the complex $\lambda$ plane, i.e., we take ${\cal C}=]+\infty +i\epsilon,+i\epsilon] \cup
-[+i\epsilon,-i\epsilon] \cup [-i\epsilon, +\infty -i\epsilon[$ with $\epsilon \to 0_+$ (see Fig.1 Ref~\cite{Folacci:2019cmc}).
-
-The Legendre function of the first kind $P_{\lambda -1/2} (z)$ denotes the analytic extension of the Legendre polynomials $P_\ell (z)$.
-It is defined in terms of hypergeometric functions by \cite{AS65}
-\begin{equation}\label{Def_ext_LegendreP}
-P_{\lambda -1/2} (z) = F[1/2-\lambda,1/2+\lambda;1;(1-z)/2].
-\end{equation}
-In Eq.~(\ref{SW_Scalar_Scattering_amp}), $S_{\lambda -1/2} (\omega)$ denotes ``the'' analytic extension of $S_\ell (\omega)$. It is given by [see Eq.~(\ref{Matrix_S})]
-\begin{equation}\label{Matrix_S_CAM}
-  S_{\lambda -1/2}(\omega) =  e^{i(\lambda + 1/2)\pi} \, \frac{A_{\lambda -1/2}^{(+)}(\omega)}{A_{\lambda -1/2}^{(-)}(\omega)}
-\end{equation}
-where the complex amplitudes $A^{(-)}_{\lambda -1/2} (\omega)$ and  $A^{(+)}_{\lambda -1/2} (\omega)$ are defined from the analytic extension of the modes $\phi_{\omega \ell}$, i.e., from the function $\phi_{\omega ,\lambda -1/2}$.
-
-It is important to note that the poles of  $S_{\lambda -1/2} (\omega)$ in the complex $\lambda$ plan (i.e., the Regge poles) are defined  as  the zeros $\lambda_n(\omega)$ with $n=1,2,3,\ldots$ of the coefficient  $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~(\ref{Matrix_S_CAM})]
-\begin{equation}\label{PR_def_Am}
-A^{(-)}_{\lambda_n(\omega)-1/2} (\omega)=0.
-\end{equation}
-The residue of the matrix $S_{\lambda-1/2}(\omega)$ at the pole $\lambda=\lambda_n(\omega)$ is defined by [see Eq.~(\ref{Matrix_S_CAM})]
-\begin{equation}\label{residues_RP}
-r_n(\omega)=e^{i\pi [\lambda_n(\omega)+1/2]} \left[ \frac{A_{\lambda -1/2}^{(+)}(\omega)}{\frac{d}{d \lambda}A_{\lambda -1/2}^{(-)}(\omega)}\right]_{\lambda=\lambda_n(\omega)}.
-\end{equation}
-These residues play a central role in the complex angular momentum paradigm.
-
-Now, we ``deform'' the contour ${\cal C}$ in Eq.~(\ref{SW_Scalar_Scattering_amp}) in order to collect, by using Cauchy's theorem, the Regge poles contributions.
-This is achieved by following, \textit{mutatis mutandis}, the approach developed in Ref~\cite{Folacci:2019cmc} (see more particularly Sec.
-IIB~3 and Fig.~1).
-We obtain
-
-\begin{equation}\label{CAM_Scalar_Scattering_amp_tot}
-\hat{f} (\omega, \theta) =  \hat{f}^\text{\tiny{B}} (\omega, \theta) +  \hat{f}^\text{\tiny{RP}} (\omega, \theta)
-\end{equation}
-where
-\begin{subequations}\label{CAM_Scalar_Scattering_amp_decomp}
-\begin{equation}\label{CAM_Scalar_Scattering_amp_decomp_Background}
-\hat{f}^\text{\tiny{B}} (\omega, \theta) = \hat{f}^\text{\tiny{B},\tiny{Re}} (\omega, \theta)+ \hat{f}^\text{\tiny{B},\tiny{Im}} (\omega, \theta)
-\end{equation}
-is a background integral contribution with
-\begin{equation}\label{CAM_Scalar_Scattering_amp_decomp_Background_a}
-\hat{f}^\text{\tiny{B},\tiny{Re}} (\omega, \theta) = \frac{1}{\pi \omega} \int_{{\cal C}_{-}} d\lambda \, \lambda S_{\lambda -1/2}(\omega) Q_{\lambda -1/2}(\cos \theta +i0)
-\end{equation}
-and
-\begin{eqnarray}\label{CAM_Scalar_Scattering_amp_decomp_Background_b}
-\hat{f}^\text{\tiny{B},\tiny{Im}} && (\omega, \theta) = \frac{1}{2 \omega}\left(\int_{+i\infty}^{0} d\lambda \, \left[S_{\lambda -1/2}(\omega) P_{\lambda_n(\omega) -1/2} (-\cos \theta) \right.
-\right.\nonumber \\
-&& -\left. \left. S_{-\lambda -1/2}(\omega) e^{i \pi \left(\lambda+1/2\right)}P_{\lambda_n(\omega) -1/2} (\cos \theta) \right]\lambda\right).
-\end{eqnarray}
-\end{subequations}
-The second term in Eq.~(\ref{CAM_Scalar_Scattering_amp_tot}) ,
-\begin{eqnarray}\label{CAM_Scalar_Scattering_amp_decomp_RP}
-& & \hat{f}^\text{\tiny{RP}} (\omega, \theta) = -\frac{i \pi}{\omega}    \sum_{n=1}^{+\infty}   \frac{ \lambda_n(\omega) r_n(\omega)}{\cos[\pi \lambda_n(\omega)]}  \nonumber \\
-&&  \qquad\qquad \qquad\qquad \times  P_{\lambda_n(\omega) -1/2} (-\cos \theta),
-\end{eqnarray}
-is a sum over the Regge poles lying in the first quadrant of the CAM plane.
-Of course, Eqs.~(\ref{CAM_Scalar_Scattering_amp_tot}), (\ref{CAM_Scalar_Scattering_amp_decomp}) and (\ref{CAM_Scalar_Scattering_amp_decomp_RP}) provide an exact representation of the scattering amplitude $\hat{f} (\omega, \theta)$ for the scalar field, equivalent to the initial partial wave expansion (\ref{Scalar_Scattering_amp}).
-From this CAM representation, we can extract the contribution $\hat{f}^\text{\tiny{RP}} (\omega, \theta)$ given by (\ref{CAM_Scalar_Scattering_amp_decomp_RP}) which, as a sum over Regge poles, is only an approximation of $\hat{f} (\omega, \theta)$, and which provides us with an approximation of the differential scattering cross section (\ref{Scalar_Scattering_diff}).
-
-\section{Reconstruction of differential scattering cross sections from Regge pole sums}
-\label{SecIII}
-
-In this section,  we compare the partial wave expansions of the differential scattering cross sections with their equivalent CAM representations or, more precisely, their Regge pole approximations.
-
-\subsection{Computational methods}
-\label{SecIIIa}
-
-To construct the scattering amplitude \eqref{Scalar_Scattering_amp}, the back ground integrals~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} and~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_b} as well as the Regge pole contribution~\eqref{CAM_Scalar_Scattering_amp_decomp_RP}, we use, \textit{mutatis mutandis} the computational methods that permitted one of us, in Refs~\cite{Folacci:2019cmc,Folacci:2019vtt} to consider the CAM representation for scattering of the scalar, electromagnetic and gravitational waves by Schwarzschild BH (see also Ref~\cite{Dolan:2017rtj}).
-It is important to remark that, due to the long rang nature of the field propagating on the Schwarzschild BH (outside the compact body), the scattering amplitude~\eqref{Scalar_Scattering_amp} and the background integral~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} suffer a lack of convergence and to overcome this problem, i.e., to accelerate the convergence of this sum and integral, we have used the method described in the Appendix of Ref~\cite{Folacci:2019cmc}.
-We have performed all the numerical calculations by using {\it Mathematica} \cite{Mathematica}.
-
-\subsection{Results and comments}
-\label{SecIIIb}
+ \subsection{Results}
 
@@
 \caption{\label{RP_approx_2Mw_3_6_s_1} The Regge poles $\lambda_n(\omega)$ for the scalar field. We assume $2M =1$}
-\end{figure}
-
-\begin{figure*}%[h!]
- \includegraphics[scale=0.50]{Scattering_Cross_Section_R_6_2Mw_3}
-\caption{\label{S_0_2Mw_01_Exact_vs_CAM} The scalar cross section of a compact bodies for $2M\omega=3$ and $R=6M$, its Regge pole approximation and the background integral contribution.}
-\end{figure*}
-
-\begin{figure*}%[h!]
- \includegraphics[scale=0.50]{Scattering_Cross_Section_R_6_2Mw_16}
-\caption{\label{S_0_2Mw_01_Exact_vs_CAM} The scalar cross section of a compact bodies for $2M\omega=16$ and $R=6M$, its Regge pole approximation and the background integral contribution.}
-\end{figure*}
-
-\begin{figure*}%[h!]
-\centering
- \includegraphics[scale=0.50]{Scattering_Cross_Section_R_2-dot-26_2Mw_3}
-\caption{\label{S_0_2Mw_06_Exact_vs_CAM} The scalar cross section of a very compact bodies for $2M\omega=3$ and $R=2.26M$ and its Regge pole approximation.}
-\end{figure*}
-
-\begin{figure*}%[h!]
-\centering
- \includegraphics[scale=0.50]{Scattering_Cross_Section_R_2-dot-26_2Mw_6}
-\caption{\label{S_0_2Mw_06_Exact_vs_CAM} The scalar cross section of a very compact bodies for $2M\omega=6$ and $R=2.26M$ and its Regge pole approximation.}
-\end{figure*}
-
-\begin{figure}%[h!]
-\centering
- \includegraphics[scale=0.50]{Rainbow_Cross_Section_R_6_2Mw_16}
-\caption{\label{S_0_2Mw_06_Exact_vs_CAM} Rainbow scattering for compact bodies for $2M\omega=16$ and $R=6M$, its Regge pole approximation and different contributions of the sum over Regge poles.}
-\end{figure}
-
-\begin{figure}%[h!]
-\centering
- \includegraphics[scale=0.50]{Diff_Contribution_Cross_Section_R_2-dot-26_2Mw_6}
-\caption{\label{S_0_2Mw_06_Exact_vs_CAM} Rainbow scattering for compact bodies for $2M\omega=16$ and $R=2.26M$, its Regge pole approximation and different contributions of the sum over Regge poles.}
 \end{figure}
@@
 
-\section{WKB ?}
-\label{SecIII}
+ \subsection{Classification of quasinormal modes}
+
+The study of stellar quasinormal modes began with a general relativistic extension of the Newtonian treatment of fluid pulsations of stars.
+Newly formed neutron stars, the remnants of supernovae collapse, are predicted to pulsate with a large initial energy \cite{thorne1967non}.
+It was and still is of interest to study how these pulsations lose energy in the form of gravitational waves.
+Recently, the gravitational waves from a neutron star merger were detected...
+In particular the emitted radiation should cary a signature of the modes of oscillation allowed inside the star.
+These fluid modes can be classified in analogy to their real Newtonian counterparts, with an additional damping time due to emission of GWs.
+Later, Kokkotas and Schutz showed that an additional family of modes existed \cite{Kokkotas:1986gd,Kokkotas:1992ka}, dubbed $\omega$-modes.
+These modes are characterised by a negligible excitation of fluid motion (and in the axial sector no fluid motion).
+They're highly damped and correspond to excitations of the dynamical perturbed space-time.
+For an excellent review of (gravitational) quasinormal modes in relativistic stars and black holes see \cite{Kokkotas:1999bd}.
+
+We consider the massless scalar field which only couples to the body via gravitation.
+The scalar modes obey an equation of motion very similar to the axial gravitational wave sector.
+Accordingly, a similar spectrum for scalar modes can be expected (with no fluid excitation).
+Whilst these are arguably of less astrophysical interest, they are nonetheless a good model for axial GWs and allow us to make a first step towards a CAM approach for perturbed relativistic stars.
+We will classify the scalar $\omega$-modes as the axial GW modes have been, we have
+
+	\begin{enumerate}
+		\item Curvature modes: These modes exist for all relativistic stars. They are rapidly damped, and the damping is larger for less compact bodies.
+		\item Trapped modes: These are the scalar analogue of the axial trapped modes considered by Chandrasekhar and Ferrari \cite{Chandrasekhar449}.
+They exist for bodies with $R/M < 3$.
+These models have an effective radial potential with a local minimum somewhere inside the star, and local maximum at the photon sphere $r=3M$.
+The trapped modes are essentially the first few curvature modes with energy less than the potential barrier.
+There are a finite number of them, and the number increases with the depth of the potential well.
+		\item Interface modes: also known as $\omega_{\text{II}}$-modes, these were discovered by Leins \textit{et al.} \cite{Leins:1993zz}.
+They used a generalisation of Leaver's continued fraction  method as well as a `Wronskain method' that allowed them to accurately compute these modes which are characterised by very rapid damping (large imaginary part).
+This second branch of modes is the most similar to the Schwarzschild black hole quasinormal modes.
+We have taken their continued fraction method one step further (see section...) in order to be confident with our results.
+	\end{enumerate}
+
+ \subsection{The WKB approximation}
 
@@
 
-\section{Classification of quasinormal modes}
+\section{Scattering and CAM theory}
 
-The study of stellar quasinormal modes began with a general relativistic extension of the Newtonian treatment of fluid pulsations of stars.
-Newly formed neutron stars, the remnants of supernovae collapse, are predicted to pulsate with a large initial energy \cite{thorne1967non}.
-It was and still is of interest to study how these pulsations lose energy in the form of gravitational waves.
-Recently, the gravitational waves from a neutron star merger were detected...
-In particular the emitted radiation should cary a signature of the modes of oscillation allowed inside the star.
-These fluid modes can be classified in analogy to their real Newtonian counterparts, with an additional damping time due to emission of GWs.
-Later, Kokkotas and Schutz showed that an additional family of modes existed \cite{Kokkotas:1986gd,Kokkotas:1992ka}, dubbed $\omega$-modes.
-These modes are characterised by a negligible excitation of fluid motion (and in the axial sector no fluid motion).
-They're highly damped and correspond to excitations of the dynamical perturbed space-time.
-For an excellent review of (gravitational) quasinormal modes in relativistic stars and black holes see \cite{Kokkotas:1999bd}.
+\subsection{The partial wave expansion}
 
-We consider the massless scalar field which only couples to the body via gravitation.
-The scalar modes obey an equation of motion very similar to the axial gravitational wave sector.
-Accordingly, a similar spectrum for scalar modes can be expected (with no fluid excitation).
-Whilst these are arguably of less astrophysical interest, they are nonetheless a good model for axial GWs and allow us to make a first step towards a CAM approach for perturbed relativistic stars.
-We will classify the scalar $\omega$-modes as the axial GW modes have been, we have
+We recall that, for the scalar field, the differential scattering cross section is given by (see, e.g.,\cite{Dolan:2017rtj} and references therein)
+\begin{equation}\label{Scalar_Scattering_diff}
+  \frac{d\sigma}{d\Omega} = |\hat{f}(\omega,\theta)|^2
+\end{equation}
+where
+\begin{equation}\label{Scalar_Scattering_amp}
+ \hat{f}(\omega,\theta) = \frac{1}{2 i \omega} \sum_{\ell = 0}^{\infty} (2\ell+1)[S_{\ell}(\omega)-1]P_{\ell}(\cos\theta)
+\end{equation}
+denotes the scattering amplitude.
+In Eq.~(\ref{Scalar_Scattering_amp}), the functions $P_{\ell}(\cos\theta)$ are the Legendre polynomials \cite{AS65}.
+We also recall that the $S$-matrix elements $S_{\ell}(\omega)$ appearing in Eq.~(\ref{Scalar_Scattering_amp}) can be defined from the modes $\phi_{\omega \ell}$ that solve the homogenous radial equation
 
-	\begin{enumerate}
-		\item Curvature modes: These modes exist for all relativistic stars. They are rapidly damped, and the damping is larger for less compact bodies.
-		\item Trapped modes: These are the scalar analogue of the axial trapped modes considered by Chandrasekhar and Ferrari \cite{Chandrasekhar449}.
-They exist for bodies with $R/M < 3$.
-These models have an effective radial potential with a local minimum somewhere inside the star, and local maximum at the photon sphere $r=3M$.
-The trapped modes are essentially the first few curvature modes with energy less than the potential barrier.
-There are a finite number of them, and the number increases with the depth of the potential well.
-		\item Interface modes: also known as $\omega_{\text{II}}$-modes, these were discovered by Leins \textit{et al.} \cite{Leins:1993zz}.
-They used a generalisation of Leaver's continued fraction  method as well as a `Wronskain method' that allowed them to accurately compute these modes which are characterised by very rapid damping (large imaginary part).
-This second branch of modes is the most similar to the Schwarzschild black hole quasinormal modes.
-We have taken their continued fraction method one step further (see section...) in order to be confident with our results.
-	\end{enumerate}
+\subsection{CAM representation of the scattering amplitude}
+\label{SecIIc}
+
+To construct the CAM representation, we follow the steps in section~II of the Ref~\cite{Folacci:2019cmc} and recall the main results.
+
+By using the Sommerfeld-Watson transformation \cite{Watson18,Sommerfeld49,Newton:1982qc} which permits us to write
+\begin{equation}\label{SWT_gen}
+\sum_{\ell=0}^{+\infty} (-1)^\ell F(\ell)= \frac{i}{2} \int_{\cal C} d\lambda \, \frac{F(\lambda -1/2)}{\cos (\pi \lambda)}
+\end{equation}
+with a function $F$ without any singularities on the real $\lambda$ axis, we replace the discrete sum over the ordinary angular momentum $\ell$ in Eq.~(\ref{Scalar_Scattering_amp}) by a contour integral in the complex $\lambda$ plane (i.e., in the complex $\ell$ plane with $\lambda = \ell +1/2$).
+By noting that $P_\ell (\cos \theta)=(-1)^\ell P_\ell (-\cos \theta)$, we obtain
+\begin{eqnarray}\label{SW_Scalar_Scattering_amp}
+& & \hat{f}(\omega,\theta) = \frac{1}{2 \omega}  \int_{\cal C} d\lambda \, \frac{\lambda}{\cos (\pi \lambda)} \nonumber \\
+&&  \qquad\qquad   \times \left[ S_{\lambda -1/2} (\omega) -1 \right]P_{\lambda -1/2} (-\cos \theta).
+\end{eqnarray}
+In Eqs.~(\ref{SWT_gen}) and (\ref{SW_Scalar_Scattering_amp}), the integration contour encircles counterclockwise the positive real axis of the complex $\lambda$ plane, i.e., we take ${\cal C}=]+\infty +i\epsilon,+i\epsilon] \cup
+[+i\epsilon,-i\epsilon] \cup [-i\epsilon, +\infty -i\epsilon[$ with $\epsilon \to 0_+$ (see Fig.1 Ref~\cite{Folacci:2019cmc}).
+
+The Legendre function of the first kind $P_{\lambda -1/2} (z)$ denotes the analytic extension of the Legendre polynomials $P_\ell (z)$.
+It is defined in terms of hypergeometric functions by \cite{AS65}
+\begin{equation}\label{Def_ext_LegendreP}
+P_{\lambda -1/2} (z) = F[1/2-\lambda,1/2+\lambda;1;(1-z)/2].
+\end{equation}
+In Eq.~(\ref{SW_Scalar_Scattering_amp}), $S_{\lambda -1/2} (\omega)$ denotes ``the'' analytic extension of $S_\ell (\omega)$. It is given by [see Eq.~(\ref{Matrix_S})]
+\begin{equation}\label{Matrix_S_CAM}
+  S_{\lambda -1/2}(\omega) =  e^{i(\lambda + 1/2)\pi} \, \frac{A_{\lambda -1/2}^{(+)}(\omega)}{A_{\lambda -1/2}^{(-)}(\omega)}
+\end{equation}
+where the complex amplitudes $A^{(-)}_{\lambda -1/2} (\omega)$ and  $A^{(+)}_{\lambda -1/2} (\omega)$ are defined from the analytic extension of the modes $\phi_{\omega \ell}$, i.e., from the function $\phi_{\omega ,\lambda -1/2}$.
+
+It is important to note that the poles of  $S_{\lambda -1/2} (\omega)$ in the complex $\lambda$ plan (i.e., the Regge poles) are defined  as  the zeros $\lambda_n(\omega)$ with $n=1,2,3,\ldots$ of the coefficient  $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~(\ref{Matrix_S_CAM})]
+\begin{equation}\label{PR_def_Am}
+A^{(-)}_{\lambda_n(\omega)-1/2} (\omega)=0.
+\end{equation}
+The residue of the matrix $S_{\lambda-1/2}(\omega)$ at the pole $\lambda=\lambda_n(\omega)$ is defined by [see Eq.~(\ref{Matrix_S_CAM})]
+\begin{equation}\label{residues_RP}
+r_n(\omega)=e^{i\pi [\lambda_n(\omega)+1/2]} \left[ \frac{A_{\lambda -1/2}^{(+)}(\omega)}{\frac{d}{d \lambda}A_{\lambda -1/2}^{(-)}(\omega)}\right]_{\lambda=\lambda_n(\omega)}.
+\end{equation}
+These residues play a central role in the complex angular momentum paradigm.
+
+Now, we ``deform'' the contour ${\cal C}$ in Eq.~(\ref{SW_Scalar_Scattering_amp}) in order to collect, by using Cauchy's theorem, the Regge poles contributions.
+This is achieved by following, \textit{mutatis mutandis}, the approach developed in Ref~\cite{Folacci:2019cmc} (see more particularly Sec.
+IIB~3 and Fig.~1).
+We obtain
+
+\begin{equation}\label{CAM_Scalar_Scattering_amp_tot}
+\hat{f} (\omega, \theta) =  \hat{f}^\text{\tiny{B}} (\omega, \theta) +  \hat{f}^\text{\tiny{RP}} (\omega, \theta)
+\end{equation}
+where
+\begin{subequations}\label{CAM_Scalar_Scattering_amp_decomp}
+\begin{equation}\label{CAM_Scalar_Scattering_amp_decomp_Background}
+\hat{f}^\text{\tiny{B}} (\omega, \theta) = \hat{f}^\text{\tiny{B},\tiny{Re}} (\omega, \theta)+ \hat{f}^\text{\tiny{B},\tiny{Im}} (\omega, \theta)
+\end{equation}
+is a background integral contribution with
+\begin{equation}\label{CAM_Scalar_Scattering_amp_decomp_Background_a}
+\hat{f}^\text{\tiny{B},\tiny{Re}} (\omega, \theta) = \frac{1}{\pi \omega} \int_{{\cal C}_{-}} d\lambda \, \lambda S_{\lambda -1/2}(\omega) Q_{\lambda -1/2}(\cos \theta +i0)
+\end{equation}
+and
+\begin{eqnarray}\label{CAM_Scalar_Scattering_amp_decomp_Background_b}
+\hat{f}^\text{\tiny{B},\tiny{Im}} && (\omega, \theta) = \frac{1}{2 \omega}\left(\int_{+i\infty}^{0} d\lambda \, \left[S_{\lambda -1/2}(\omega) P_{\lambda_n(\omega) -1/2} (-\cos \theta) \right.
+\right.\nonumber \\
+&& -\left. \left. S_{-\lambda -1/2}(\omega) e^{i \pi \left(\lambda+1/2\right)}P_{\lambda_n(\omega) -1/2} (\cos \theta) \right]\lambda\right).
+\end{eqnarray}
+\end{subequations}
+The second term in Eq.~(\ref{CAM_Scalar_Scattering_amp_tot}) ,
+\begin{eqnarray}\label{CAM_Scalar_Scattering_amp_decomp_RP}
+& & \hat{f}^\text{\tiny{RP}} (\omega, \theta) = -\frac{i \pi}{\omega}    \sum_{n=1}^{+\infty}   \frac{ \lambda_n(\omega) r_n(\omega)}{\cos[\pi \lambda_n(\omega)]}  \nonumber \\
+&&  \qquad\qquad \qquad\qquad \times  P_{\lambda_n(\omega) -1/2} (-\cos \theta),
+\end{eqnarray}
+is a sum over the Regge poles lying in the first quadrant of the CAM plane.
+Of course, Eqs.~(\ref{CAM_Scalar_Scattering_amp_tot}), (\ref{CAM_Scalar_Scattering_amp_decomp}) and (\ref{CAM_Scalar_Scattering_amp_decomp_RP}) provide an exact representation of the scattering amplitude $\hat{f} (\omega, \theta)$ for the scalar field, equivalent to the initial partial wave expansion (\ref{Scalar_Scattering_amp}).
+From this CAM representation, we can extract the contribution $\hat{f}^\text{\tiny{RP}} (\omega, \theta)$ given by (\ref{CAM_Scalar_Scattering_amp_decomp_RP}) which, as a sum over Regge poles, is only an approximation of $\hat{f} (\omega, \theta)$, and which provides us with an approximation of the differential scattering cross section (\ref{Scalar_Scattering_diff}).
+
+\section{Reconstruction of differential scattering cross sections from Regge pole sums}
+\label{SecIII}
+
+In this section,  we compare the partial wave expansions of the differential scattering cross sections with their equivalent CAM representations or, more precisely, their Regge pole approximations.
+
+\subsection{Computational methods}
+\label{SecIIIa}
+
+To construct the scattering amplitude \eqref{Scalar_Scattering_amp}, the back ground integrals~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} and~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_b} as well as the Regge pole contribution~\eqref{CAM_Scalar_Scattering_amp_decomp_RP}, we use, \textit{mutatis mutandis} the computational methods that permitted one of us, in Refs~\cite{Folacci:2019cmc,Folacci:2019vtt} to consider the CAM representation for scattering of the scalar, electromagnetic and gravitational waves by Schwarzschild BH (see also Ref~\cite{Dolan:2017rtj}).
+It is important to remark that, due to the long rang nature of the field propagating on the Schwarzschild BH (outside the compact body), the scattering amplitude~\eqref{Scalar_Scattering_amp} and the background integral~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} suffer a lack of convergence and to overcome this problem, i.e., to accelerate the convergence of this sum and integral, we have used the method described in the Appendix of Ref~\cite{Folacci:2019cmc}.
+We have performed all the numerical calculations by using {\it Mathematica} \cite{Mathematica}.
+
+\subsection{Results}
+\label{SecIIIb}
+
+\begin{figure*}%[h!]
+ \includegraphics[scale=0.50]{Scattering_Cross_Section_R_6_2Mw_3}
+\caption{\label{S_0_2Mw_01_Exact_vs_CAM} The scalar cross section of a compact bodies for $2M\omega=3$ and $R=6M$, its Regge pole approximation and the background integral contribution.}
+\end{figure*}
+
+\begin{figure*}%[h!]
+ \includegraphics[scale=0.50]{Scattering_Cross_Section_R_6_2Mw_16}
+\caption{\label{S_0_2Mw_01_Exact_vs_CAM} The scalar cross section of a compact bodies for $2M\omega=16$ and $R=6M$, its Regge pole approximation and the background integral contribution.}
+\end{figure*}
+
+\begin{figure*}%[h!]
+\centering
+ \includegraphics[scale=0.50]{Scattering_Cross_Section_R_2-dot-26_2Mw_3}
+\caption{\label{S_0_2Mw_06_Exact_vs_CAM} The scalar cross section of a very compact bodies for $2M\omega=3$ and $R=2.26M$ and its Regge pole approximation.}
+\end{figure*}
+
+\begin{figure*}%[h!]
+\centering
+ \includegraphics[scale=0.50]{Scattering_Cross_Section_R_2-dot-26_2Mw_6}
+\caption{\label{S_0_2Mw_06_Exact_vs_CAM} The scalar cross section of a very compact bodies for $2M\omega=6$ and $R=2.26M$ and its Regge pole approximation.}
+\end{figure*}
+
+\begin{figure}%[h!]
+\centering
+ \includegraphics[scale=0.50]{Rainbow_Cross_Section_R_6_2Mw_16}
+\caption{\label{S_0_2Mw_06_Exact_vs_CAM} Rainbow scattering for compact bodies for $2M\omega=16$ and $R=6M$, its Regge pole approximation and different contributions of the sum over Regge poles.}
+\end{figure}
+
+\begin{figure}%[h!]
+\centering
+ \includegraphics[scale=0.50]{Diff_Contribution_Cross_Section_R_2-dot-26_2Mw_6}
+\caption{\label{S_0_2Mw_06_Exact_vs_CAM} Rainbow scattering for compact bodies for $2M\omega=16$ and $R=2.26M$, its Regge pole approximation and different contributions of the sum over Regge poles.}
+\end{figure}
+
+\section{Discussion and conclusions\label{sec:conclusions}}
 

### 2019-11-14 rainbowCAM.tex
Adding the spin 2 spectrum

@@
 \centering
- \includegraphics[scale=0.50]{potentials_s02_CD_R6L2_v2} \\ \vspace{0.2cm}
- \includegraphics[scale=0.50]{potentials_s02_CD_R2p26L2}
+ \includegraphics[scale=0.50]{potentials_s02_CD_R6L2_v3} \\ \vspace{0.2cm}
+ \includegraphics[scale=0.50]{potentials_s02_CD_R2p26L2_v3}
 \caption{\label{RP_approx_2Mw_3_6_s_1} The effective potential $V_\ell$ for a quadrupole ($\ell =2$) perturbation of a compact body of constant density and tenuity $R/M = 6$ (upper) and $R /M = 2.26$ (lower).
 The scalar field and axial gravitational-wave potentials are indicated as solid/black lines and dotted/red lines, respectively.
-The horizontal axis is the tortoise coordinate $r_\ast$ defined in Eq.~(\ref{eq:tortoise}).}
+The horizontal axis is the tortoise coordinate $r_\ast/(2M)$ defined in Eq.~(\ref{eq:tortoise}).}
 \label{fig:Veff}
@@
 \centering
- \includegraphics[scale=0.50]{RP_R_6_2Mw_3_16}
-\caption{\label{RP_approx_2Mw_3_6_s_1} The Regge poles $\lambda_n(\omega)$ for the scalar field. We assume $2M =1$}
+ \includegraphics[scale=0.50]{RP_R_6_2Mw_3_16_s_0_s_2}
+\caption{\label{RP_approx_2Mw_3_6_s_1} The Regge poles $\lambda_n(\omega)$ for the scalar field (empty markers) and for the axial gravitational waves (filled markers). We assume $2M =1$}
 \end{figure}
@@
 \centering
- \includegraphics[scale=0.50]{RP_R_2_dot_26_2Mw_3_6}
-\caption{\label{RP_approx_2Mw_3_6_s_1} The Regge poles $\lambda_n(\omega)$ for the scalar field. We assume $2M =1$}
+ \includegraphics[scale=0.50]{RP_R_2_dot_26_2Mw_3_6_s_0_s_2}
+\caption{\label{RP_approx_2Mw_3_6_s_1}  The Regge poles $\lambda_n(\omega)$ for the scalar field (empty markers) and for the axial gravitational waves (filled markers). We assume $2M =1$}
 \end{figure}
@@
 \begin{tablenotes}
-     \item[1] Surface waves
-     \item[2] Broad resonances
+     \item[1] S-W : Surface waves
+     \item[2] B-R : Broad resonances
    \end{tablenotes}
@@
 \begin{tablenotes}
-     \item[1] Surface waves
-     \item[2] Broad resonances
-     \item[3] Narrow  resonances
+     \item[1] S-W : Surface waves
+     \item[2] B-R : Broad resonances
+     \item[3] N-R : Narrow  resonances
    \end{tablenotes}
@@
 \end{table*}
+\endgroup
+
+\begingroup
+\squeezetable
+\begin{table}[htp]
+\begin{threeparttable}[htp]
+%\captionsetup{font=small}
+\caption{\label{tab:table3} The lowest Regge poles $\lambda_{n}(\omega)$ for the axial gravitational waves. The radius of the compact bodies is $R = 6M$ and we assume $2M=1$.}
+\smallskip
+\centering
+\begin{ruledtabular}
+\begin{tabular}{cccc}
+ $n$ & $\omega$  & $\lambda^{\text{(S-W)\tnote{1}}}_n(\omega)$ & $\lambda^{\text{(B-R)\tnote{2}}}_n(\omega)$
+ \\ \hline
+$1$  & $3$  & $10.004639+2.935907 i$  & $0.461101+2.2269826 i $   \\
+     & $16$ & $56.179459+5.874240 i $ & $1.624880+3.2909174 i $
+ \\
+
+$2$  & $3$  & $11.205047+5.343083 i$  & $2.551455+2.401243 i $     \\
+     & $16$ & $58.717121+9.365689 i  $& $3.659398+3.336427 i $
+ \\
+
+$3$  & $3$  & $12.166772+7.344219 i $  & $4.790413+2.635624 i  $     \\
+     & $16$ & $60.528800+12.332399 i $ & $5.722341+3.384112 i $
+ \\
+
+$4$  & $3$  & $13.009174+9.155489 i  $  & $7.164229+2.930135 i $     \\
+     & $16$ & $62.040466+15.032415 i  $ & $7.815081+3.434319 i  $
+      \\
+
+$5$  & $3$  & $13.777754+10.843971 i $  & $/ $   \\
+     & $16$ & $63.379530+17.557778 i $  & $9.939189+3.487474 i $      \\
+
+$6$  & $3$  & $14.494020+12.442853 i $  & $/ $      \\
+     & $16$ & $64.603684+19.955393 i $  & $12.096463+3.544109 i  $
+   \\
+
+$7$  & $3$  & $15.170211+13.972029 i $  & $ /$       \\
+     & $16$ & $65.744593+22.253317 i $  & $14.288975+3.604892 i $
+         \\
+
+$8$  & $3$  & $15.814162+15.444717 i $  & $/ $        \\
+     & $16$ & $66.821746+24.470040 i $  & $16.519109+3.670678 i $
+         \\
+
+$9$  & $3$  & $16.431296+16.870298 i $  & $/ $      \\
+     & $16$ & $67.848089+26.618578 i $  & $18.789625+3.742581 i $
+         \\
+
+$10$  & $3$  & $17.025584+18.255740 i $  & $/ $     \\
+     & $16$  & $68.832711+28.708547 i  $  & $21.103712+3.822080 i $
+        \\
+\end{tabular}
+\end{ruledtabular}
+\begin{tablenotes}
+     \item[1] S-W : Surface waves
+     \item[2] B-R : Broad resonances
+   \end{tablenotes}
+\end{threeparttable}
+\end{table}
+\endgroup
+
+\begingroup
+\squeezetable
+\begin{table}[htp]
+\begin{threeparttable}[htp]
+%\captionsetup{font=small}
+\caption{\label{tab:table4} The lowest Regge poles $\lambda_{n}(\omega)$ for the axial gravitational waves. The radius of the compact bodies is $R = 2.26M$ and we assume $2M=1$.}
+\smallskip
+\centering
+\begin{ruledtabular}
+\begin{tabular}{ccccc}
+ $n$ & $\omega$  & $\lambda^{\text{(S-W)\tnote{1}}}_n(\omega)$  & $\lambda^{\text{(B-R)\tnote{2}}}_n(\omega)$ & $\lambda^{\text{(N-R)\tnote{3}}}_n(\omega)$
+ \\ \hline
+$1$  & $3$  & $5.884755+2.047850 i $  & $0.840822+1.728755 i   $  & $8.0740924+0.022432 i   $   \\
+     & $6$  & $12.796673+2.200987 i  $  & $0.959779+2.193488 i   $  & $14.247709+0.699340 i  $    \\
+
+$2$  & $3$  & $5.960332+3.632211 i   $  & $2.633309+1.559084 i   $  & $7.386249+0.264972 i   $  \\
+     & $6$  & $12.640961+3.871470 i  $  & $2.842316+2.075844 i  $  & $14.969378+0.297175 i  $  \\
+
+$3$  & $3$  & $6.153107+5.055691 i   $  & $4.262509+1.419601 i   $  & $6.662827+0.729518 i  $   \\
+     & $6$  & $ 12.628734+5.440977 i$  & $4.629152+1.973668 i  $  & $13.496329+1.146922 i  $  \\
+
+$4$  & $3$  & $6.403231+6.358703 i  $  & $ 5.746584+1.200761 i$  & $/ $   \\
+     & $6$  & $12.711478+6.932783 i  $  & $6.330877+1.883529 i  $  & $15.612017+0.049364 i  $   \\
+
+$5$  & $3$  & $6.678538+7.572564 i $  & $ /$  & $/ $   \\
+     & $6$  & $12.859039+8.354930 i   $  & $7.954922+1.803188 i    $  & $ /$  \\
+
+$6$  & $3$  & $6.964301+8.719285 i  $  & $/ $  & $ /$  \\
+     & $6$  & $13.050962+9.715667 i  $  & $9.505808+1.730884 i  $  & $/ $   \\
+
+$7$  & $3$  & $7.253473+9.813908 i   $  & $ /$  & $/ $  \\
+     & $6$  & $13.273382+11.022841 i  $  & $10.985288+1.664216 i   $  & $ /$   \\
+
+$8$  & $3$  & $7.542524+10.866909 i $  & $ /$  & $/ $   \\
+     & $6$  & $13.516855+12.283449 i $  & $12.423672+1.572865 i $  & $/ $   \\
+
+$9$  & $3$  & $7.829631+11.885800 i   $  & $/ $  & $/ $   \\
+     & $6$  & $13.774891+13.503511 i  $  & $/ $  & $/ $   \\
+
+$10$ & $3$  & $8.113848+12.876130 i $  & $/ $  & $/ $    \\
+     & $6$  & $14.042970+14.688113 i $  & $ /$  & $/ $   \\
+\end{tabular}
+\end{ruledtabular}
+\begin{tablenotes}
+     \item[1] S-W : Surface waves
+     \item[2] B-R : Broad resonances
+     \item[3] N-R : Narrow  resonances
+   \end{tablenotes}
+\end{threeparttable}
+\end{table}
 \endgroup

### 2019-11-25 rainbowCAM.tex
Numerical method for PR

@@
  \subsection{Numerical method}
+
+In order to determine the Regge poles we use the method described in sec.~4 of ref.~\cite{Benhar:1998au}.
+In fact, they had adapted the \textit{continued fraction method}, developed by Leaver in the case of BH-QNM frequencies~\cite{Leaver:1985ax}, to determine the axial QNM frequencies of a compact bodies.
+Though they used their method to find the QNM frequencies, their method is equally valid, \textit{mutatis mutandis}, for finding the Regge poles.
+We have implemented numerically this method by using the Hill determinant approach of Majumdar and Panchapakesan~\cite{mp}, or more precisely, by modifying their method and adapting it to our problem, \textit{i.e.}, using it for a 4-term recurrence relation.
 

### 2019-12-02 rainbowCAM.tex
Moved and shortened the section on classification of QNMs. Other small improvements throughout. Started on writing the results section.

--- 2019-11-14 rainbowCAM.tex
@@
 \end{equation}
-encapsulates the ratio of the gravitational radius $r_g = 2GM/c^2$ to the wavelength $\lambda$ (here we adopt geometric units such that $G=c=1$).
+encapsulates the ratio of the gravitational radius $r_g = 2GM/c^2$ to the wavelength $\lambda$ (henceforth we adopt geometric units such that $G=c=1$).
 The long wavelength ($M \omega \ll 1$), short wavelength ($M \omega \gg 1$) and intermediate regimes have been studied with a combination of perturbative \cite{DeLogi:1977dp,Dolan:2007ut,Guadagnini:2008ha,Sorge:2015yoa}, semi-classical \cite{Matzner:1985rjn, Anninos:1992ih} and numerical methods.
@@
 Time-independent scattering by a compact body with a regular centre, such as a neutron star or white dwarf, has received comparatively less attention.
-In such a scenario, an electromagnetic wave will not penetrate inside the compact body; on the other hand, a gravitational wave will pass through the body without impediment from the matter distribution.
+In such a scenario, an electromagnetic wave will not penetrate inside the compact body; but on the other hand, a gravitational wave will pass through the body without impediment from the matter distribution.
 Similarly, a neutron star is expected to be substantially transparent to neutrinos.
-In these cases, the body scatters the wave indirectly, through its influence on the spacetime curvature.
+Though the coupling to matter is weak, the incident wave is still strongly scattered due to the influence on the spacetime curvature.
 Recent work \cite{Dolan:2017rtj, Stratton:2019deq} has explored the \emph{rainbow scattering} phenomenon that arises at short wavelengths, due to a stationary point in the geodesic deflection function associated with a ray that passes somewhat inside the body.
@@
 
-In this section we describe the model for the compact object.
-Then we recall the partial wave expansions of the differential scattering cross section for plane monochromatic scalar waves impinging upon a compact body.
-Finally we apply the CAM-approach developed for black-hole scattering in \cite{Folacci:2019cmc} and \cite{Folacci:2019vtt}.
+In this section we describe the model for the compact object (\ref{SecIIa}); we introduce the effective potentials for scalar field and axial gravitational waves (\ref{subsec:Potentials}); and we define the physical boundary conditions and the S-matrix (\ref{subsec:bc}).
+
+%Finally we apply the CAM-approach developed for black-hole scattering in \cite{Folacci:2019cmc} and \cite{Folacci:2019vtt}.
 
@@
 \end{subequations}
-The constant-density model can be thought of as representing the $n=0$ limit of the family of polytropes.
-The radial function $h(r)$ is $C^0$ (i.e.~continuous but not differentiable) at the surface of the star $r=R$, and the radial function $f(r)$ is $C^1$ there (i.e.~once-differentiable).
+The constant-density model can be thought of as representing the $n \rightarrow 0$ limit of the family of polytropes.
+The radial function $h(r)$ is $C^0$ at the surface of the star $r=R$ (i.e.~continuous but not differentiable), and the radial function $f(r)$ is $C^1$ there (i.e.~once-differentiable).
 In the polytropic cases $n > 0$, the functions are more regular \sam{can we make a precise statement?} at the surface, but not $C^\infty$ (i.e.~not smooth).
@@
 \Phi = \frac{1}{r} \sum_{\omega \ell m} \phi_{\omega \ell}(r)  Y_{lm}(\theta, \phi) e^{-i \omega t} ,
+\label{eq:sepvariables}
 \end{equation}
@@
 
-\subsection{Effective potentials}
+\subsection{Effective potentials}\label{subsec:Potentials}
 The effective potential for the scalar field in Eq.~(\ref{H_Radial_equation}) is $V_{\ell}(r) = V_{\ell}^{(s=0)}(r)$, where we define
 \begin{equation}\label{Inside_Potentiel}
-  V_{\ell}^{(s)}(r) \equiv f(r)\left[\frac{\ell(\ell+1)}{r^2}+\frac{(1-s^2) h(r)}{2r}\left(\frac{f'(r)}{f(r)}+\frac{h'(r)}{h(r)}\right)\right]
+  V_{\ell}^{(s)}(r) \equiv f(r)\left[\frac{\ell(\ell+1)}{r^2}+\frac{\beta_s \, h(r)}{2r}\left(\frac{f'(r)}{f(r)}+\frac{h'(r)}{h(r)}\right)\right] ,
 \end{equation}
+where $\beta_s \equiv 1-s^2$. 
 Remarkably, the radial equation for axial gravitational perturbations is identical to Eq.~(\ref{H_Radial_equation}) but with an effective potential $V_{\ell}^{\text{ax}}(r)$ where \cite{Cardoso:2014sna}
@@
 \begin{equation}\label{RW_Potentiel}
-V^{(s)}_{\ell}(r) =\left(1-\frac{2M}{r}\right)\left(\frac{\ell(\ell+1)}{r^2}+\frac{2M(1-s^2)}{r^3}\right)
+V^{(s)}_{\ell}(r) =\left(1-\frac{2M}{r}\right)\left(\frac{\ell(\ell+1)}{r^2}+\frac{2M \beta_s}{r^3}\right)
 \end{equation}
@@
 \Delta V_{\ell}^{(s=0)} &= + \frac{3Mf(R)}{R^3} , \\
-\Delta V_{\ell}^{(ax)} &= - \frac{3Mf(R)}{R^3} ,
+\Delta V_{\ell}^{\text{ax}} &= - \frac{3Mf(R)}{R^3} ,
 \end{align}
@@
 \caption{\label{RP_approx_2Mw_3_6_s_1} The effective potential $V_\ell$ for a quadrupole ($\ell =2$) perturbation of a compact body of constant density and tenuity $R/M = 6$ (upper) and $R /M = 2.26$ (lower).
-The scalar field and axial gravitational-wave potentials are indicated as solid/black lines and dotted/red lines, respectively.
+The scalar field potential (\ref{Inside_Potentiel}) and axial gravitational-wave potential (\ref{RW_Potentiel_axialGW}) are indicated as solid/black lines and dotted/red lines, respectively.
 The horizontal axis is the tortoise coordinate $r_\ast/(2M)$ defined in Eq.~(\ref{eq:tortoise}).}
@@
 
-\subsection{Boundary conditions and scattering}
-The modes $\phi_{\omega \ell}$ should have a regular behaviour at the centre of the object ($r = 0$), and inspection of the radial equation (\ref{H_Radial_equation}) shows that
+\subsection{Boundary conditions and scattering}\label{subsec:bc}
+The modes $\phi_{\omega \ell}$ in Eq.~(\ref{eq:sepvariables}) should have a regular behaviour at the centre of the object ($r = 0$), and inspection of the radial equation (\ref{H_Radial_equation}) shows that
 \begin{equation}\label{bc_1_in}
@@
 \end{equation}
+At the boundary of the compact object, the potential is $C^0$ and thus the mode is $C^2$. 
 The asymptotic behaviour of the modes far from the body ($r \to +\infty$, or equivalently $r_\ast \to +\infty$) is
@@
 \end{equation}
+We now consider the poles of $S_{\ell}(\omega)$ in the complex plane.
 
@@
 
- \subsection{Regge poles and quasinormal modes}
+ \subsection{Quasinormal modes and Regge poles}
+ Mathematically, there is a close relationship between quasinormal modes and Regge poles; both are sets of poles of the scattering matrix.
+Physically, quasinormal modes are most relevant in time-dependent scattering scenarios, and Regge poles in time-independent scattering scenarios.
 
- \subsection{Numerical method}
+The \emph{quasinormal mode spectrum} is the set of frequencies $\{ \omega_{\ell \hat{n}} \}$ in the complex-$\omega$ plane at which the scattering matrix $ S_{\ell}(\omega)$ has a simple pole, for a real value of $\ell$; that is, $\ell \in \mathbb{R}$ and $\omega_{\ell \hat{n}} \in \mathbb{C}$.
 
- \subsection{Results}
+The \emph{Regge pole spectrum} is the set of angular momenta $\lambda_{\omega \hat{n}} = \ell_{\hat{n}}(\omega) + 1/2$ in the complex-$\lambda$ plane at which the scattering matrix has a simple pole for real $\omega$; that is, $\omega \in \mathbb{R}$ and $\lambda_{\hat{n}}(\omega) \in \mathbb{C}$.
+Here $\hat{n}$ is an index for enumerating the poles (see below).
+In all cases considered in this work, the simple poles arise as simple zeros of $A_{\ell}^{(-)}(\omega)$.
+
+The quasinormal mode spectrum of spherically-symmetric compact objects has been studied in some detail in \cite{Kokkotas:1986gd,Kokkotas:1992ka,Andersson:1997eq,Kokkotas:1999bd,Leins:1993zz}. 
+Newly-formed neutron stars, the remnants of supernovae collapse, are predicted to pulsate with a large initial energy \cite{thorne1967non}, and fluid pulsations will surely generate gravitational waves.
+In 1967, Thorne and Campolattaro \cite{thorne1967non} classified the fluid modes of a relativistic body by analogy with fluid modes in a Newtonian body, with the addition of a damping time due to the emission of GWs.
+Two decades later, Kokkotas and Schutz showed that an additional family of modes existed \cite{Kokkotas:1986gd,Kokkotas:1992ka}, dubbed $w$-modes.
+These modes are characterised by a negligible excitation of fluid motion, and in the axial sector, by no fluid motion.
+They are highly damped and correspond to excitations of the dynamical perturbed space-time.
+For a review of (gravitational) quasinormal modes in relativistic stars and black holes see \cite{Kokkotas:1999bd}.
+
+The $w$-modes (quasinormal modes) may be divided into three branches:
+	\begin{enumerate}
+   \item Curvature modes, oscillations whose damping is larger for less compact bodies.
+   \item Interface modes ($\omega_{\text{II}}$-modes \cite{Leins:1993zz}), characterised by very rapid damping (i.e.~large negative imaginary part of $\omega_{\ell \hat{n}}$).
+This branch of modes is most similar to the Schwarzschild black hole quasinormal modes.
+   \item Trapped modes \cite{Chandrasekhar449}: These modes exist for UCOs with $R/M < 3$, as the effective radial potential has a local minimum inside the star, and local maximum near the photon sphere $r=3M$.
+%The trapped modes are essentially the first few curvature modes with energy less than the potential barrier.
+   The number of trapped modes increases with the depth of the potential well, and the damping rate decreases. 
+	\end{enumerate}
+For more details on quasinormal modes see \sam{Appropriate reference needed.}
+
+We now turn our attention to calculating the Regge pole spectrum for compact bodies.
+
+ \subsection{Numerical method}\label{subsec:method}
+
+In order to determine the Regge poles we adapt the method of Benhar, Berti and Ferrari (BBF), described in Sec.~4 of Ref.~\cite{Benhar:1998au}, who used it to determine the axial QNM frequencies of compact bodies.
+In turn, the BBF method is an adaptation of the \textit{continued fraction method} developed by Leaver in the case of black hole-quasinormal mode frequencies~\cite{Leaver:1985ax}.
+Though BBF used their method to find the QNM frequencies, their method is equally valid, \textit{mutatis mutandis}, for finding the Regge poles.
+We have implemented numerically this method by using the Hill determinant approach of Majumdar and Panchapakesan~\cite{mp}, or more precisely, by modifying their method and adapting it to our problem, \textit{i.e.}, using it for a 4-term recurrence relation.
+
+\sam{I think we need a little bit more detail here -- how does the four-term recurrence relation arise, and where can it be found specifically?}
+
+ \subsection{Numerical results}\label{subsec:results}
+In this section we present numerical results for the Regge pole spectrum of a compact body, in two cases: (i) a neutron-star-like body with tenuity $R / M = 6$, and (ii) a UCO with a tenuity just above the Buchdahl bound, $R / M = 2.26$.
+Results for the frequencies $M \omega = 3/2$ and $M \omega = 8$ are compared, for the scalar-field ($s=0$) and axial GW ($s=2$) cases.
 
@@
  \includegraphics[scale=0.50]{RP_R_6_2Mw_3_16_s_0_s_2}
-\caption{\label{RP_approx_2Mw_3_6_s_1} The Regge poles $\lambda_n(\omega)$ for the scalar field (empty markers) and for the axial gravitational waves (filled markers). We assume $2M =1$}
+\caption{\label{RP_approx_2Mw_3_6_s_1} The Regge poles $\lambda_n(\omega)$ for the scalar field (empty markers) and for the axial gravitational waves (filled markers). %We assume $2M =1$.
+}
 \end{figure}
@@
  \includegraphics[scale=0.50]{RP_R_2_dot_26_2Mw_3_6_s_0_s_2}
-\caption{\label{RP_approx_2Mw_3_6_s_1}  The Regge poles $\lambda_n(\omega)$ for the scalar field (empty markers) and for the axial gravitational waves (filled markers). We assume $2M =1$}
+\caption{\label{RP_approx_2Mw_3_6_s_1}  The Regge poles $\lambda_n(\omega)$ for the scalar field (empty markers) and for the axial gravitational waves (filled markers). %We assume $2M =1$.
+}
 \end{figure}
@@
 \endgroup
-
-\subsection{Classification of quasinormal modes}
-
-The study of stellar quasinormal modes began with a general relativistic extension of the Newtonian treatment of fluid pulsations of stars.
-Newly formed neutron stars, the remnants of supernovae collapse, are predicted to pulsate with a large initial energy \cite{thorne1967non}.
-It was and still is of interest to study how these pulsations lose energy in the form of gravitational waves.
-Recently, the gravitational waves from a neutron star merger were detected...
-In particular the emitted radiation should cary a signature of the modes of oscillation allowed inside the star.
-These fluid modes can be classified in analogy to their real Newtonian counterparts, with an additional damping time due to emission of GWs.
-Later, Kokkotas and Schutz showed that an additional family of modes existed \cite{Kokkotas:1986gd,Kokkotas:1992ka}, dubbed $\omega$-modes.
-These modes are characterised by a negligible excitation of fluid motion (and in the axial sector no fluid motion).
-They're highly damped and correspond to excitations of the dynamical perturbed space-time.
-For an excellent review of (gravitational) quasinormal modes in relativistic stars and black holes see \cite{Kokkotas:1999bd}.
-
-We consider the massless scalar field which only couples to the body via gravitation.
-The scalar modes obey an equation of motion very similar to the axial gravitational wave sector.
-Accordingly, a similar spectrum for scalar modes can be expected (with no fluid excitation).
-Whilst these are arguably of less astrophysical interest, they are nonetheless a good model for axial GWs and allow us to make a first step towards a CAM approach for perturbed relativistic stars.
-We will classify the scalar $\omega$-modes as the axial GW modes have been, we have
-
-	\begin{enumerate}
-		\item Curvature modes: These modes exist for all relativistic stars. They are rapidly damped, and the damping is larger for less compact bodies.
-		\item Trapped modes: These are the scalar analogue of the axial trapped modes considered by Chandrasekhar and Ferrari \cite{Chandrasekhar449}.
-They exist for bodies with $R/M < 3$.
-These models have an effective radial potential with a local minimum somewhere inside the star, and local maximum at the photon sphere $r=3M$.
-The trapped modes are essentially the first few curvature modes with energy less than the potential barrier.
-There are a finite number of them, and the number increases with the depth of the potential well.
-		\item Interface modes: also known as $\omega_{\text{II}}$-modes, these were discovered by Leins \textit{et al.} \cite{Leins:1993zz}.
-They used a generalisation of Leaver's continued fraction  method as well as a `Wronskain method' that allowed them to accurately compute these modes which are characterised by very rapid damping (large imaginary part).
-This second branch of modes is the most similar to the Schwarzschild black hole quasinormal modes.
-We have taken their continued fraction method one step further (see section...) in order to be confident with our results.
-	\end{enumerate}
 

### 2019-12-02 rainbowCAM.tex
Finished describing the results for Regge poles, moved on to start on the WKB section.

@@
 
-Time-independent scattering by a compact body with a regular centre, such as a neutron star or white dwarf, has received comparatively less attention.
+Time-independent scattering by a compact body of radius $R$ with a regular centre, such as a neutron star or white dwarf, has received comparatively less attention.
 In such a scenario, an electromagnetic wave will not penetrate inside the compact body; but on the other hand, a gravitational wave will pass through the body without impediment from the matter distribution.
@@
 In principle, the rainbow angle is a diagnostic of the matter distribution of the body, and thus its nuclear equation of state.
-\cite{Nambu:2019sqn}
+
+The tenuity (inverse compactness) .
+
+find room for \cite{Nambu:2019sqn}
 
@@
 
-A widely-studied model is that of a polytropic star, with an EoS $p(\rho) = \kappa \rho^{1+1/n}$, where $n$ is the polytropic index (see e.g.~\cite{Stratton:2019deq}).
+A widely-studied model is that of a polytropic star, with an EoS $p(\rho) = \kappa \rho^{1+1/\hat{n}}$, where $\hat{n}$ is the polytropic index (see e.g.~\cite{Stratton:2019deq}).
 Here we shall consider a special case: an incompressible perfect fluid ball of uniform density described by Schwarzschild's interior solution for an incompressible fluid \cite{Shapiro1983}, with
@@
 \end{subequations}
-The constant-density model can be thought of as representing the $n \rightarrow 0$ limit of the family of polytropes.
+The constant-density model can be thought of as representing the $\hat{n} \rightarrow 0$ limit of the family of polytropes.
 The radial function $h(r)$ is $C^0$ at the surface of the star $r=R$ (i.e.~continuous but not differentiable), and the radial function $f(r)$ is $C^1$ there (i.e.~once-differentiable).
@@
  \subsection{Quasinormal modes and Regge poles}
- Mathematically, there is a close relationship between quasinormal modes and Regge poles; both are sets of poles of the scattering matrix.
-Physically, quasinormal modes are most relevant in time-dependent scattering scenarios, and Regge poles in time-independent scattering scenarios.
+ Mathematically, there is a close relationship between quasinormal modes and Regge poles; they are both sets of poles of the scattering matrix.
+Physically, quasinormal modes are most relevant to time-dependent scattering scenarios, and Regge poles to time-independent scattering scenarios.
 
-The \emph{quasinormal mode spectrum} is the set of frequencies $\{ \omega_{\ell \hat{n}} \}$ in the complex-$\omega$ plane at which the scattering matrix $ S_{\ell}(\omega)$ has a simple pole, for a real value of $\ell$; that is, $\ell \in \mathbb{R}$ and $\omega_{\ell \hat{n}} \in \mathbb{C}$.
+The \emph{quasinormal mode spectrum} is the set of frequencies $\{ \omega_{\ell n} \}$ in the complex-$\omega$ plane at which the scattering matrix $ S_{\ell}(\omega)$ has a simple pole for a integer value of $\ell$ (so $\ell \in \mathbb{N}$ and $\omega_{\ell n} \in \mathbb{C}$).
 
-The \emph{Regge pole spectrum} is the set of angular momenta $\lambda_{\omega \hat{n}} = \ell_{\hat{n}}(\omega) + 1/2$ in the complex-$\lambda$ plane at which the scattering matrix has a simple pole for real $\omega$; that is, $\omega \in \mathbb{R}$ and $\lambda_{\hat{n}}(\omega) \in \mathbb{C}$.
-Here $\hat{n}$ is an index for enumerating the poles (see below).
-In all cases considered in this work, the simple poles arise as simple zeros of $A_{\ell}^{(-)}(\omega)$.
+The \emph{Regge pole spectrum} is the set of angular momenta $\lambda_{\omega n} = \ell_{n}(\omega) + 1/2$ in the complex-$\lambda$ plane at which the scattering matrix has a simple pole for a real value of $\omega$ (so $\omega \in \mathbb{R}$ and $\lambda_{n}(\omega) \in \mathbb{C}$).
+Here $n$ is an index for enumerating the discrete spectrum of poles.
+In all cases considered in this work, the simple poles of $S_{\ell}(\omega)$ arise as simple zeros of $A_{\ell}^{(-)}(\omega)$.
 
-The quasinormal mode spectrum of spherically-symmetric compact objects has been studied in some detail in \cite{Kokkotas:1986gd,Kokkotas:1992ka,Andersson:1997eq,Kokkotas:1999bd,Leins:1993zz}. 
-Newly-formed neutron stars, the remnants of supernovae collapse, are predicted to pulsate with a large initial energy \cite{thorne1967non}, and fluid pulsations will surely generate gravitational waves.
-In 1967, Thorne and Campolattaro \cite{thorne1967non} classified the fluid modes of a relativistic body by analogy with fluid modes in a Newtonian body, with the addition of a damping time due to the emission of GWs.
-Two decades later, Kokkotas and Schutz showed that an additional family of modes existed \cite{Kokkotas:1986gd,Kokkotas:1992ka}, dubbed $w$-modes.
-These modes are characterised by a negligible excitation of fluid motion, and in the axial sector, by no fluid motion.
+The quasinormal mode spectrum of spherically-symmetric compact objects has been studied in some detail in Refs.~\cite{Kokkotas:1986gd,Kokkotas:1992ka,Andersson:1997eq,Kokkotas:1999bd,Leins:1993zz}. 
+Newly-formed neutron stars, the remnants of supernovae collapse, are predicted to pulsate with a large initial energy, and fluid pulsations will generate gravitational waves.
+In 1967, Thorne and Campolattaro \cite{thorne1967non} classified the fluid modes of a relativistic compact body by analogy with the fluid modes of a Newtonian body, with the addition of a damping time due to the emission of GWs.
+Two decades later, the subject was examined again \cite{Detweiler:1985zz,Kokkotas:1986gd}, and Kokkotas and Schutz \cite{Kokkotas:1992ka} showed the existence of an additional family of modes, dubbed $w$-modes.
+These modes are characterised by a negligible excitation of fluid motion, and in the axial sector, by no fluid motion at all.
 They are highly damped and correspond to excitations of the dynamical perturbed space-time.
-For a review of (gravitational) quasinormal modes in relativistic stars and black holes see \cite{Kokkotas:1999bd}.
+For a review of (gravitational) quasinormal modes in relativistic stars and black holes see Ref.~\cite{Kokkotas:1999bd}.
 
@@
 	\begin{enumerate}
-   \item Curvature modes, oscillations whose damping is larger for less compact bodies.
-   \item Interface modes ($\omega_{\text{II}}$-modes \cite{Leins:1993zz}), characterised by very rapid damping (i.e.~large negative imaginary part of $\omega_{\ell \hat{n}}$).
+   \item Curvature modes, oscillations whose damping is larger for less compact bodies. \sam{Anything else to say on curvature modes?}
+   \item Interface modes ($\omega_{\text{II}}$-modes \cite{Leins:1993zz}), characterised by very rapid damping (i.e.~large negative imaginary part of $\omega_{\ell n}$).
 This branch of modes is most similar to the Schwarzschild black hole quasinormal modes.
-   \item Trapped modes \cite{Chandrasekhar449}: These modes exist for UCOs with $R/M < 3$, as the effective radial potential has a local minimum inside the star, and local maximum near the photon sphere $r=3M$.
+   \item Trapped modes \cite{Chandrasekhar449}: These modes exist for UCOs with $R/M < 3$, because the effective radial potential has a local minimum inside the star, and local maximum near the photon sphere $r=3M$.
 %The trapped modes are essentially the first few curvature modes with energy less than the potential barrier.
@@
 
-In order to determine the Regge poles we adapt the method of Benhar, Berti and Ferrari (BBF), described in Sec.~4 of Ref.~\cite{Benhar:1998au}, who used it to determine the axial QNM frequencies of compact bodies.
+In order to determine the Regge poles we adapt the method of Benhar, Berti and Ferrari (BBF), described in Sec.~4 of Ref.~\cite{Benhar:1998au}.
 In turn, the BBF method is an adaptation of the \textit{continued fraction method} developed by Leaver in the case of black hole-quasinormal mode frequencies~\cite{Leaver:1985ax}.
-Though BBF used their method to find the QNM frequencies, their method is equally valid, \textit{mutatis mutandis}, for finding the Regge poles.
+Though BBF used the method to find axial QNM frequencies, their method is equally valid, \textit{mutatis mutandis}, for finding the Regge poles.
 We have implemented numerically this method by using the Hill determinant approach of Majumdar and Panchapakesan~\cite{mp}, or more precisely, by modifying their method and adapting it to our problem, \textit{i.e.}, using it for a 4-term recurrence relation.
+We implemented the method with  \emph{Mathematica}.
 
@@
  \subsection{Numerical results}\label{subsec:results}
-In this section we present numerical results for the Regge pole spectrum of a compact body, in two cases: (i) a neutron-star-like body with tenuity $R / M = 6$, and (ii) a UCO with a tenuity just above the Buchdahl bound, $R / M = 2.26$.
+In this section we show numerical results for the Regge pole spectrum of a compact body, in two particular cases: (i) a neutron-star-like body with tenuity $R / M = 6$, and (ii) a UCO with tenuity $R / M = 2.26$ close to the Buchdahl bound.
 Results for the frequencies $M \omega = 3/2$ and $M \omega = 8$ are compared, for the scalar-field ($s=0$) and axial GW ($s=2$) cases.
+
+Figure \ref{fig:rp1} shows the Regge pole spectrum for a neutron-star-like body ($R/M = 6$).
+We see that there are two branches of Regge poles in the first quadrant, which meet at $\text{Re}( \lambda_n(\omega) ) \sim \omega b_0$, where $b_0$ is the impact parameter for the null ray which grazes the surface of the compact body.
+The axial GW $s=2$ modes (filled markers) are typically close to their scalar-field $s=0$ counterparts (unfilled markers), as might be anticipated from the similarities in the effective potentials for the two cases (see Fig.~\ref{fig:Veff}).
 
@@
 }
+\label{fig:rp1}
 \end{figure}
+
+Figure \ref{fig:rp2} shows the spectrum for a UCO with $R/M = 2.26$.
+These plots show evidence for an additional branch of modes that emerges from the point where the first two branches meet.
+The number of modes in this branch increases as the radius of the body approaches the Buchdahl limit $R \rightarrow \tfrac{9}{4}M$.
 
@@
 }
+\label{fig:rp2}
 \end{figure}
+
+The Regge pole spectrum for a compact body is qualitatively similar to the Regge pole spectrum found in Mie scattering of electromagnetic waves by a transparent droplet of refractive index $\tilde{n}$.
+This has been studied since the 1960s; see for example Fig.~9.2 in Ref.~\cite{Nussenzveig:2006}.
+% In the latter case, the poles are given by the zeros of a combination of special functions.
+Henceforth we shall adopt the terminology of Nussenzveig \cite{Nussenzveig:2006}, in which the three branches are labelled as:
+\begin{enumerate}
+ \item \emph{Broad resonances}: approximately uniformly-spaced poles above the real axis with approximately constant imaginary part; somewhat sensitive to internal structure ($r < R$);
+ \item \emph{Surface waves}: highly-damped modes that are relatively insensitive to the internal structure and which depend chiefly on the surface geometry. 
+ \item \emph{Narrow resonances}: modes approaching the real axis corresponding to trapped modes which only appear in the UCO case ($R < 3M$). 
+\end{enumerate}
+In Figs.~\ref{fig:rp1} and \ref{fig:rp2} the broad resonances, surface waves and narrow resonances are indicated by red squares, blue circles and purple triangles, respectively; and black diamonds indicate the black hole RPs.
+Whereas there exists an infinite number of poles of the surface-wave branch, in principle, there are no narrow-resonance poles at all in the $R/M = 6$ case, and just $\le 4$ narrow-resonance poles in the $R/M = 2.26$ case.
+The narrow-resonance branch is observed to end close to the start of the black-hole branch.
+
+Data for Regge poles $\lambda_n(\omega)$ is listed in Table \ref{tab:table1} (scalar field, $R/M=6$), Table \ref{tab:table2} (scalar field, $R/M = 2.26$), Table \ref{tab:table3} (axial $s=2$, $R/M = 6$) and Table \ref{tab:table4} (axial $s=2$, $R/M = 2.26$).
+The values are labelled by branch (broad; surface; narrow).
+For the scalar field, the associated residues (see Sec.~) are also presented in Tables \ref{tab:table1} and Table \ref{tab:table2}.
 
@@
 %\captionsetup{font=small}
-\caption{\label{tab:table2} The lowest Regge poles $\lambda_{n}(\omega)$ for the scalar field and the associated residues $r_{n}(\omega)$.
-The radius of the compact bodies is $R = 6M$ and we assume $2M=1$.}
+\caption{\label{tab:table1} The lowest Regge poles $\lambda_{n}(\omega)$ for the scalar field and the associated residues $r_{n}(\omega)$.
+The radius of the compact bodies is $R = 6M$ and we set $2M=1$.}
 \smallskip
@@
 \begin{tabular}{cccccc}
- $n$ & $\omega$  & $\lambda^{\text{(S-W)\tnote{1}}}_n(\omega)$ & $\lambda^{\text{(B-R)\tnote{2}}}_n(\omega)$ & $r^{\text{(S-W)}}_{n}(\omega)$ & $r^{\text{(B-R)}}_{n}(\omega)$
+ $n$ & $2 M \omega$  & $\lambda^{\text{(S-W)\tnote{1}}}_n(\omega)$ & $\lambda^{\text{(B-R)\tnote{2}}}_n(\omega)$ & $r^{\text{(S-W)}}_{n}(\omega)$ & $r^{\text{(B-R)}}_{n}(\omega)$
  \\ \hline
@@
 \caption{\label{tab:table2} The lowest Regge poles $\lambda_{n}(\omega)$ for the scalar field and the associated residues $r_{n}(\omega)$.
-The radius of the compact bodies is $R = 2.26M$ and we assume $2M=1$.}
+The radius of the compact bodies is $R = 2.26M$ and we set $2M=1$.}
 \smallskip
@@
 \begin{tabular}{cccccccc}
- $n$ & $\omega$  & $\lambda^{\text{(S-W)\tnote{1}}}_n(\omega)$  & $\lambda^{\text{(B-R)\tnote{2}}}_n(\omega)$ & $\lambda^{\text{(N-R)\tnote{3}}}_n(\omega)$ & $r^{\text{(S-W)}}_{n}(\omega)$ & $r^{\text{(B-R)}}_{n}(\omega)$ & $r^{\text{(N-R)}}_{n}(\omega)$
+ $n$ & $2M\omega$  & $\lambda^{\text{(S-W)\tnote{1}}}_n(\omega)$  & $\lambda^{\text{(B-R)\tnote{2}}}_n(\omega)$ & $\lambda^{\text{(N-R)\tnote{3}}}_n(\omega)$ & $r^{\text{(S-W)}}_{n}(\omega)$ & $r^{\text{(B-R)}}_{n}(\omega)$ & $r^{\text{(N-R)}}_{n}(\omega)$
  \\ \hline
@@
 %\captionsetup{font=small}
-\caption{\label{tab:table3} The lowest Regge poles $\lambda_{n}(\omega)$ for the axial gravitational waves. The radius of the compact bodies is $R = 6M$ and we assume $2M=1$.}
+\caption{\label{tab:table3} The lowest Regge poles $\lambda_{n}(\omega)$ for the axial gravitational waves. The radius of the compact bodies is $R = 6M$ and we set $2M=1$.}
 \smallskip
@@
 \begin{tabular}{cccc}
- $n$ & $\omega$  & $\lambda^{\text{(S-W)\tnote{1}}}_n(\omega)$ & $\lambda^{\text{(B-R)\tnote{2}}}_n(\omega)$
+ $n$ & $2M\omega$  & $\lambda^{\text{(S-W)\tnote{1}}}_n(\omega)$ & $\lambda^{\text{(B-R)\tnote{2}}}_n(\omega)$
  \\ \hline
@@
 %\captionsetup{font=small}
-\caption{\label{tab:table4} The lowest Regge poles $\lambda_{n}(\omega)$ for the axial gravitational waves. The radius of the compact bodies is $R = 2.26M$ and we assume $2M=1$.}
+\caption{\label{tab:table4} The lowest Regge poles $\lambda_{n}(\omega)$ for the axial gravitational waves. The radius of the compact bodies is $R = 2.26M$ and we set $2M=1$.}
 \smallskip
@@
 \begin{tabular}{ccccc}
- $n$ & $\omega$  & $\lambda^{\text{(S-W)\tnote{1}}}_n(\omega)$  & $\lambda^{\text{(B-R)\tnote{2}}}_n(\omega)$ & $\lambda^{\text{(N-R)\tnote{3}}}_n(\omega)$
+ $n$ & $2M\omega$  & $\lambda^{\text{(S-W)\tnote{1}}}_n(\omega)$  & $\lambda^{\text{(B-R)\tnote{2}}}_n(\omega)$ & $\lambda^{\text{(N-R)\tnote{3}}}_n(\omega)$
  \\ \hline
@@
  \subsection{The WKB approximation}
+To investigate the relationship between the qualitative features of the effective potential (Fig.~\ref{fig:Veff}) and the three branches of Regge poles revealed in Sec.~\ref{subsec:results}, we now employ the WKB method, with a view of obtain an approximation that is valid at high frequencies ($M\omega \rightarrow \infty$).
 
@@
 \begin{table}[htp]
-\caption{\label{tab:table3} The lowest Regge poles $\lambda_{n}(\omega)$ for the scalar field versus WBK results given by Eq.~\eqref{lambda_Approx}.
+\caption{\label{tab:table3} The lowest Regge poles $\lambda_{n}(\omega)$ for the scalar field versus WKB results given by Eq.~\eqref{lambda_Approx}.
 The radius of the compact bodies is $R = 6M$ and we assume $2M=1$.}

### 2019-12-02 rainbowCAM.tex
Wrote some text for the Results (2) section.

@@
 
+\newcommand{\phiout}{\phi^{\text{out}}_{\omega, \lambda-1/2}}
+\newcommand{\phireg}{\phi^{}_{\omega, \lambda-1/2}}
+
 \renewcommand{\arraystretch}{1.3} % espace entre les lignes de la table
@@
 
-\title{Scattering from compact objects: Regge poles \\ and the Complex Angular Momentum method}
+\title{Scattering from compact objects: \\ Regge poles and the Complex Angular Momentum method}
 
@@
 \begin{equation}
-M \omega = \pi \frac{r_g}{\lambda},
+M \omega = \frac{\pi r_g}{\lambda},
 \end{equation}
@@
 \begin{equation}
-\Delta V_{\ell} \equiv \lim_{\epsilon \rightarrow 0} \left\{ V_{\ell}(R + \epsilon) - V_{\ell}(R - \epsilon) \right\} .
+\Delta V_{\ell} \equiv \lim_{\epsilon \rightarrow 0} \left\{ V_{\ell}(R + \epsilon) - V_{\ell}(R - \epsilon) \right\} . \label{def:DeltaV}
 \end{equation}
@@
 
- \subsection{Numerical results}\label{subsec:results}
+ \subsection{Numerical results: the spectrum}\label{subsec:results1}
 In this section we show numerical results for the Regge pole spectrum of a compact body, in two particular cases: (i) a neutron-star-like body with tenuity $R / M = 6$, and (ii) a UCO with tenuity $R / M = 2.26$ close to the Buchdahl bound.
@@
 
-The WKB approach developed by Zhang, Wu and Leung~\cite{Zhang:2011pq} to determine the axial \textit{w}-modes of a variety of stellar models can be adapted in order to obtain analytical approximations for the ``broad Regge poles'' for a scalar wave on a stellar background.
-The radial equation for axial gravitational perturbations is identical to Eq.~(\ref{H_Radial_equation}) but with the potential replaced by $V_{\ell} \rightarrow V_{\ell}^{\text{ax}}$ where \cite{Cardoso:2014sna}
-\begin{eqnarray}\label{RW_Potentiel_axialGW}
-V_{\ell}^{\text{ax}}(r) = f(r)\bigg[\frac{\ell(\ell+1)}{r^2}  - \dfrac{3 h(r)}{2r}\left(\dfrac{f'(r)}{f(r)}+\dfrac{h'(r)}{h(r)}\right) & \nonumber \\
-	 + 8 \pi (p - \rho) & \bigg] .
-\end{eqnarray}
-%
-We can expect then that Regge poles for axial gravitational perturbations are qualitatively the same as for scalar perturbations, and the methods discussed can be easily adapted to deal with either case.
-
-\newcommand{\phiout}{\phi^{\text{out}}_{\omega, \lambda-1/2}}
-\newcommand{\phireg}{\phi^{}_{\omega, \lambda-1/2}}
+Here we follow the approach of Zhang, Wu and Leung~\cite{Zhang:2011pq}, who applied the WKB method to determine the axial \textit{w}-modes of a variety of stellar models.
+Here, we adapt the method to obtain analytical approximations for the ``broad resonances'' for waves on a stellar background.
+The starting point is with the radial equation (\ref{H_Radial_equation}) with either the effective potential for the scalar field (\ref{Inside_Potentiel}), or for axial gravitational perturbations (\ref{RW_Potentiel_axialGW}).
 
@@
 %
-Thus, the Regge poles are solutions of Eq.~\eqref{H_Radial_equation} for which the  Wronskian of $\phireg$ and $\phiout$ vanishes (\textit{i.e.}, $A^{(-)}_{\lambda_n(\omega)-1/2} (\omega)=0$)
+Thus, the Regge poles are solutions of Eq.~\eqref{H_Radial_equation} for which the  Wronskian of $\phireg$ and $\phiout$ vanishes (\textit{i.e.}, $A^{(-)}_{\lambda_n(\omega)-1/2} (\omega)=0$), viz.,
 \begin{equation}\label{Wronskian}
-  W[\phireg, \phiout ]= 0
+  W[\phireg, \phiout ]= 0 .
 \end{equation}
-It has been shown that, the asymptotic expressions of $\phireg$ and $\phiout$ can be derived in certain regions, buy using the standard WKB approximation.
-In the high-frequency domain we have (see Refs \ldots)
+It has been shown \cite{Zhang:2011pq} that the asymptotic expressions of $\phireg$ and $\phiout$ can be derived in asymptotic regions, by using the standard WKB approximation.
+In the high-frequency limit, the interior solution of Eq.~(\ref{H_Radial_equation}) is (see Refs \ldots \sam{Please fill this in})
 \begin{equation}\label{Approx_origin}
-  \phireg \underset{\omega \to \infty}{=} \omega r_* j_{\lambda-1/2} (\omega r_*) \quad\quad 0\leq r_*\leq R_*
+  \phireg \underset{\omega \to \infty}{=} \omega r_* j_{\lambda-1/2} (\omega r_*),  \quad\quad 0\leq r_*\leq R_* ,
 \end{equation}
-where $j_{\lambda-1/2}$ is the spherical Bessel function of the first kind and
+where $j_{\lambda-1/2}(\cdot)$ is the spherical Bessel function of the first kind and
 \begin{equation}
@@
 \end{equation}
-Here
+Here $R_*$ is the tortoise coordinate at the surface of the body, 
 \begin{equation}\label{R_star}
@@
 \end{equation}
-and $\mathcal{R}$ is a reflection coefficient with the defintion given in Ref.~\cite{Berry_1982}.
+and $\mathcal{R}$ is a reflection coefficient with the definition given in Ref.~\cite{Berry_1982}.
 Because the potential has a direct discontinuity at the surface of the compact body (see.
-Refs \cite{Zhang:2011pq,Berry_1982} for more details), we have for our model (\textit{i.e.}, compact body with a constant density)
+Refs \cite{Zhang:2011pq,Berry_1982} for more details), we have for our model (\textit{i.e.}, a compact body with a constant density)
 \begin{equation}\label{R_reflection_1}
-  \mathcal{R} = a \omega^{-2}
+  \mathcal{R} = \alpha \omega^{-2}
 \end{equation}
@@
 % \nonumber % Remove numbering (before each equation)
-  a &=& -\left(\frac{i}{2}\right)^2 \lim_{\epsilon\to 0^{+}} \left[V_{\lambda-1/2}(r)\Bigg{|}_{r=R+\epsilon}-V_{\lambda-1/2}(r)\Bigg{|}_{r=R-\epsilon}\right] \nonumber\\
-   &=& \frac{3M(R-2M)}{4 R^4}
+  \alpha &=& \frac{1}{4} \Delta V(R) = \pm \frac{3M(R-2M)}{4 R^4} ,
 \end{eqnarray}
+where $\Delta V$ is the discontinuity in the effective potential at the surface, defined in Eq.~(\ref{def:DeltaV}), and the $+$ ($-$) sign is chosen for scalar field (axial gravitational wave) cases.
 
@@
 %
-We then solve Eq.~\eqref{WKB_1} and we obtain
+We then solve Eq.~\eqref{WKB_1} to obtain
 \begin{equation}\label{lambda_Approx}
-  \lambda_n \approx \frac{2 \omega R_*}{\pi}-\left(2n+\frac{1}{2}\right)+\frac{i}{\pi} \ln\left(\frac{1}{\mathcal{R}}\right)
+  \lambda_n \approx \frac{2 \omega R_*}{\pi}-\left(2n \pm \frac{1}{2}\right)+\frac{i}{\pi} \ln\left(\frac{2 R^2 \omega}{\sqrt{3M (R-2M)}}\right) .
 \end{equation}
-This corresponds to the series of Regge poles with spacing $|\Delta \lambda_n|\approx 2$ with the almost constant  imaginary part.
-Of course, they lie in the first quadrant of the CAM plan with a positive real part
-%
-\begin{equation}\label{Real_Part}
-  \frac{2 \omega R_*}{\pi}-\left(2n+\frac{1}{2}\right)>0.
+\sam{Please double-check this formula is correct for both scalar (+) and axial GW (-) cases.}
+This corresponds to a series of Regge poles with spacing $|\Delta \lambda_n|\approx 2$ with the almost-constant imaginary part; these are the broad resonances shown in Figs.~\ref{fig:rp1} and \ref{fig:rp2}.
+The formula also correctly accounts for the alternating sequence of the scalar-field and axial-GW modes.
+ %Of course, they lie in the first quadrant of the CAM plan with a positive real part
+
+The overtones are labelled by $n =1,2,\ldots$ and the condition $\text{Re} \, \lambda_n > 0$ leads to an upper limit for $n$ of %
+\begin{equation}\label{Limit_Broad_RP}
+n \leq \left\lfloor \frac{\omega R_*}{\pi} \mp \frac{1}{4}\right\rfloor.
 \end{equation}
 %
-The overtones are labelled by $n =1,2,\ldots$ and $n$ has an upper limit
-%
-\begin{equation}\label{Limit_Broad_RP}
-n \leq \left\lfloor \frac{\omega R_*}{\pi} - \frac{1}{4}\right\rfloor.
-\end{equation}
-%
-In other words, there is a finite number of the ``broad Regge poles''.
+In other words, there are a finite number of the broad resonances in the first quadrant.
+
+Table \ref{tab:table5} compares the numerically-determined Regge poles with the WKB approximation in Eq.~(\ref{lambda_Approx}),  for the scalar-field case.
+The data shows that, while the leading-order WKB approximation captures the essential features of the broad resonance branch, it is not particularly accurate.
+Higher-order extensions are possible, but not pursued here.
 
@@
 \begin{table}[htp]
-\caption{\label{tab:table3} The lowest Regge poles $\lambda_{n}(\omega)$ for the scalar field versus WKB results given by Eq.~\eqref{lambda_Approx}.
-The radius of the compact bodies is $R = 6M$ and we assume $2M=1$.}
+\caption{\label{tab:table5} The lowest Regge poles $\lambda_{n}(\omega)$ for the scalar field versus WKB results given by Eq.~\eqref{lambda_Approx}.
+The radius of the compact bodies is $R = 6M$ and we set $2M=1$.}
 \smallskip
@@
 \begin{tabular}{cccc}
- $n$ & $\omega$  & $\lambda^{\text{(B-R)}}_n(\omega)$ & $\lambda^{\text{(B-R, WKB)}}_n(\omega)$
+ $n$ & $2 M \omega$  & $\lambda^{\text{(B-R)}}_n(\omega)$ & $\lambda^{\text{(B-R, WKB)}}_n(\omega)$
  \\ \hline
@@
 \section{Scattering and CAM theory}
+In this section we calculate the scattering cross section $d\sigma / d\Omega$ by means of the Complex Angular Momentum (CAM) method, and we compare with results obtained in the standard way from a partial-wave series \cite{Dolan:2017rtj}.
 
@@
 
-We recall that, for the scalar field, the differential scattering cross section is given by (see, e.g.,\cite{Dolan:2017rtj} and references therein)
+For a scalar field, the differential scattering cross section is given by
 \begin{equation}\label{Scalar_Scattering_diff}
@@
 \end{equation}
-denotes the scattering amplitude.
-In Eq.~(\ref{Scalar_Scattering_amp}), the functions $P_{\ell}(\cos\theta)$ are the Legendre polynomials \cite{AS65}.
-We also recall that the $S$-matrix elements $S_{\ell}(\omega)$ appearing in Eq.~(\ref{Scalar_Scattering_amp}) can be defined from the modes $\phi_{\omega \ell}$ that solve the homogenous radial equation
+is the scattering amplitude (for details see e.g.~\cite{Dolan:2017rtj} and references therein).
+In Eq.~(\ref{Scalar_Scattering_amp}), the functions $P_{\ell}(\cos\theta)$ are the Legendre polynomials \cite{AS65}, and the $S$-matrix elements $S_{\ell}(\omega)$ appearing in Eq.~(\ref{Scalar_Scattering_amp}) were defined in Eq.~(\ref{Matrix_S}).
 
@@
 
-To construct the CAM representation, we follow the steps in section~II of the Ref~\cite{Folacci:2019cmc} and recall the main results.
+To construct the CAM representation of $\hat{f}(\theta)$, we follow the steps in section~II of Ref.~\cite{Folacci:2019cmc} and recall the main results below.
 
-By using the Sommerfeld-Watson transformation \cite{Watson18,Sommerfeld49,Newton:1982qc} which permits us to write
+The Sommerfeld-Watson transformation \cite{Watson18,Sommerfeld49,Newton:1982qc} permits us to replace a sum with an integral, viz.,
 \begin{equation}\label{SWT_gen}
-\sum_{\ell=0}^{+\infty} (-1)^\ell F(\ell)= \frac{i}{2} \int_{\cal C} d\lambda \, \frac{F(\lambda -1/2)}{\cos (\pi \lambda)}
+\sum_{\ell=0}^{+\infty} (-1)^\ell F(\ell)= \frac{i}{2} \int_{\cal C} d\lambda \, \frac{F(\lambda -1/2)}{\cos (\pi \lambda)} ,
 \end{equation}
-with a function $F$ without any singularities on the real $\lambda$ axis, we replace the discrete sum over the ordinary angular momentum $\ell$ in Eq.~(\ref{Scalar_Scattering_amp}) by a contour integral in the complex $\lambda$ plane (i.e., in the complex $\ell$ plane with $\lambda = \ell +1/2$).
+where $F(\cdot)$ is any function without singularities on the real $\lambda$ axis.
+Applying this to Eq.~(\ref{Scalar_Scattering_amp}) allows us to replace the discrete sum over the ordinary angular momentum $\ell$ with a contour integral in the complex $\lambda$ plane (that is, in the complex $\ell$ plane with $\lambda = \ell +1/2$).
 By noting that $P_\ell (\cos \theta)=(-1)^\ell P_\ell (-\cos \theta)$, we obtain
@@
 In Eqs.~(\ref{SWT_gen}) and (\ref{SW_Scalar_Scattering_amp}), the integration contour encircles counterclockwise the positive real axis of the complex $\lambda$ plane, i.e., we take ${\cal C}=]+\infty +i\epsilon,+i\epsilon] \cup
-[+i\epsilon,-i\epsilon] \cup [-i\epsilon, +\infty -i\epsilon[$ with $\epsilon \to 0_+$ (see Fig.1 Ref~\cite{Folacci:2019cmc}).
+[+i\epsilon,-i\epsilon] \cup [-i\epsilon, +\infty -i\epsilon[$ with $\epsilon \to 0_+$ (see Fig.~1 in Ref~\cite{Folacci:2019cmc}).
 
@@
 
-It is important to note that the poles of  $S_{\lambda -1/2} (\omega)$ in the complex $\lambda$ plan (i.e., the Regge poles) are defined  as  the zeros $\lambda_n(\omega)$ with $n=1,2,3,\ldots$ of the coefficient  $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~(\ref{Matrix_S_CAM})]
+It is important to note that the poles of  $S_{\lambda -1/2} (\omega)$ in the complex $\lambda$ plan (i.e., the Regge poles) are defined  as  the zeros of the coefficient  $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~(\ref{Matrix_S_CAM})], i.e., the values $\lambda_n(\omega)$ such that
 \begin{equation}\label{PR_def_Am}
-A^{(-)}_{\lambda_n(\omega)-1/2} (\omega)=0.
+A^{(-)}_{\lambda_n(\omega)-1/2} (\omega)=0,
 \end{equation}
+with $n=1,2,3,\ldots$
 The residue of the matrix $S_{\lambda-1/2}(\omega)$ at the pole $\lambda=\lambda_n(\omega)$ is defined by [see Eq.~(\ref{Matrix_S_CAM})]
@@
 We obtain
-
+%
 \begin{equation}\label{CAM_Scalar_Scattering_amp_tot}
@@
 Of course, Eqs.~(\ref{CAM_Scalar_Scattering_amp_tot}), (\ref{CAM_Scalar_Scattering_amp_decomp}) and (\ref{CAM_Scalar_Scattering_amp_decomp_RP}) provide an exact representation of the scattering amplitude $\hat{f} (\omega, \theta)$ for the scalar field, equivalent to the initial partial wave expansion (\ref{Scalar_Scattering_amp}).
-From this CAM representation, we can extract the contribution $\hat{f}^\text{\tiny{RP}} (\omega, \theta)$ given by (\ref{CAM_Scalar_Scattering_amp_decomp_RP}) which, as a sum over Regge poles, is only an approximation of $\hat{f} (\omega, \theta)$, and which provides us with an approximation of the differential scattering cross section (\ref{Scalar_Scattering_diff}).
-
-\section{Reconstruction of differential scattering cross sections from Regge pole sums}
-\label{SecIII}
-
-In this section,  we compare the partial wave expansions of the differential scattering cross sections with their equivalent CAM representations or, more precisely, their Regge pole approximations.
+From this CAM representation, we can extract the contribution $\hat{f}^\text{\tiny{RP}} (\omega, \theta)$ given by (\ref{CAM_Scalar_Scattering_amp_decomp_RP}) which, as a sum over Regge poles, is only an approximation of $\hat{f} (\omega, \theta)$, and which provides us with a corresponding approximation of the differential scattering cross section via (\ref{Scalar_Scattering_diff}).
 
@@
 
-To construct the scattering amplitude \eqref{Scalar_Scattering_amp}, the back ground integrals~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} and~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_b} as well as the Regge pole contribution~\eqref{CAM_Scalar_Scattering_amp_decomp_RP}, we use, \textit{mutatis mutandis} the computational methods that permitted one of us, in Refs~\cite{Folacci:2019cmc,Folacci:2019vtt} to consider the CAM representation for scattering of the scalar, electromagnetic and gravitational waves by Schwarzschild BH (see also Ref~\cite{Dolan:2017rtj}).
-It is important to remark that, due to the long rang nature of the field propagating on the Schwarzschild BH (outside the compact body), the scattering amplitude~\eqref{Scalar_Scattering_amp} and the background integral~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} suffer a lack of convergence and to overcome this problem, i.e., to accelerate the convergence of this sum and integral, we have used the method described in the Appendix of Ref~\cite{Folacci:2019cmc}.
-We have performed all the numerical calculations by using {\it Mathematica} \cite{Mathematica}.
+To construct the scattering amplitude \eqref{Scalar_Scattering_amp}, the background integrals~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} and~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_b}, and the Regge pole amplitude~\eqref{CAM_Scalar_Scattering_amp_decomp_RP}, we use, \textit{mutatis mutandis}, the computational methods of Refs~\cite{Folacci:2019cmc,Folacci:2019vtt}.
+In these works the authors calculated the CAM representation of scattering amplitudes for scalar, electromagnetic and gravitational waves by Schwarzschild BH (see also Ref~\cite{Dolan:2017rtj}).
 
-\subsection{Results}
-\label{SecIIIb}
+Due to the long rang nature of the field propagating on the Schwarzschild BH (outside the compact body), the scattering amplitude~\eqref{Scalar_Scattering_amp} and the background integral~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} both suffer a lack of convergence.
+To overcome this problem, i.e., to accelerate the convergence of this sum and integral, we have used the method described in the Appendix of Ref~\cite{Folacci:2019cmc}.
+We have performed all the numerical calculations by using {\it Mathematica}.
+% \cite{Mathematica}.
+
+\subsection{Numerical results: scattering cross sections}
+\label{subsec:results2}
+
+Figures \ref{S_0_R_6_2Mw_3_Exact_vs_CAM}, \ref{S_0_R_6_2Mw_16_Exact_vs_CAM}, \ref{S_0_R_2-dot-26_2Mw_3_Exact_vs_CAM}, \ref{S_0_R_2-dot-26_2Mw_6_Exact_vs_CAM}, \ref{Rainbow_Cross_Section_R_6_2Mw_16}, and \ref{Diff_Contribution_Cross_Section_R_2-dot-26_2Mw_6} show a selection of results for the scattering cross section $d\sigma / d\Omega$ computed with the CAM method, and compared with results from the standard partial-wave method.
+As in Sec.~\ref{subsec:results1}, we focus on two cases: a neutron-star-like object with $R/M = 6$, and an Ultra-Compact Object with $R/M = 2.26$.
+
+Figure \ref{S_0_R_6_2Mw_3_Exact_vs_CAM} demonstrates that the CAM cross section approaches the partial-wave cross section as (i) successively more Regge poles are included in the sum (\ref{CAM_Scalar_Scattering_amp_decomp_RP}), and (ii) the background-integral contributions (\ref{CAM_Scalar_Scattering_amp_decomp_Background}) are included.
+The first plot shows that, at a `low' frequency of $M \omega = 3/2$ for the neutron star model ($R/M = 6$), taking a sum over just \emph{two} Regge poles in Eq.~(\ref{CAM_Scalar_Scattering_amp_decomp_RP}) captures the crude features of the cross section.
+The final plot shows that a cross section calculated from a sum of $15$ Regge poles and the background integral is indistinguishable (on the plot) from the partial-wave sum.
 
@@
  \includegraphics[scale=0.50]{Scattering_Cross_Section_R_6_2Mw_3}
-\caption{\label{S_0_2Mw_01_Exact_vs_CAM} The scalar cross section of a compact bodies for $2M\omega=3$ and $R=6M$, its Regge pole approximation and the background integral contribution.}
+\caption{\label{S_0_R_6_2Mw_3_Exact_vs_CAM} The scalar cross section of a compact bodies for $2M\omega=3$ and $R=6M$, its Regge pole approximation and the background integral contribution.
+The plots show the effect of including successively more Regge poles (plots 1--3).
+In the final plot, the background integral is added, giving a cross section which agrees well with the (regularized) partial-wave sum.}
 \end{figure*}
+
+Figure \ref{S_0_R_6_2Mw_16_Exact_vs_CAM} shows the neutron star model ($R/M = 6$) at the higher frequency of $M \omega = 8$.
+The first plot shows that, in this case, including just two Regge poles is yields a poor approximation.
+With 20 Regge poles, the primary peak of the rainbow, the first supernumerary, and the shadow region are well captured, but at smaller angles ($\theta  \lesssim 40^\circ$) there is no agreement.
+With 42 Regge poles, but no background integral, the agreement is excellent for $\theta \gtrsim 30^\circ$.
+Finally, with 81 Regge poles and the background integral included, the CAM result is again indistinguishable from the partial-wave result on the plot.
 
@@
  \includegraphics[scale=0.50]{Scattering_Cross_Section_R_6_2Mw_16}
-\caption{\label{S_0_2Mw_01_Exact_vs_CAM} The scalar cross section of a compact bodies for $2M\omega=16$ and $R=6M$, its Regge pole approximation and the background integral contribution.}
+\caption{\label{S_0_R_6_2Mw_16_Exact_vs_CAM} The scalar cross section of a compact bodies for $2M\omega=16$ and $R=6M$, its Regge pole approximation and the background integral contribution.}
 \end{figure*}
+
+Figure \ref{S_0_R_6_2Mw_16_Exact_vs_CAM} shows the cross section for an Ultra Compact Object with $R/M = 2.26$ at the `low' frequency of $M \omega = 3/2$.
+In this case, the rainbow angle exceeds $180^\circ$, and there is both a light-ring and a trapping region (see Fig.~\ref{fig:Veff}).
+The cross section exhibits regular orbiting oscillations with angle $\theta$.
+The angular width is consistent with generation by the light-ring (i.e.~ the peak in the potential barrier).
+The second plot shows that including just 3 modes from each of the three branches leads to a good description of scattering at large angles $\theta \gtrsim 100^\circ$.
+As there is no shadow region in this case, the cross section at large angles in non-negligible.
+For $R/M = 2.26$, the cross section at the antipodal point ($\theta = 180^\circ$) is a factor of $> 10^6$ larger than in the $R/M = 6$ case.
+The final plot shows that excellent agreement with the partial-wave results is obtained, for $\theta \gtrsim 20^\circ$, by summing over $27$ poles.
 
@@
  \includegraphics[scale=0.50]{Scattering_Cross_Section_R_2-dot-26_2Mw_3}
-\caption{\label{S_0_2Mw_06_Exact_vs_CAM} The scalar cross section of a very compact bodies for $2M\omega=3$ and $R=2.26M$ and its Regge pole approximation.}
+\caption{\label{S_0_R_2-dot-26_2Mw_3_Exact_vs_CAM} The scalar cross section of a very compact bodies for $2M\omega=3$ and $R=2.26M$ and its Regge pole approximation.}
 \end{figure*}
+
+Figure \ref{S_0_R_2-dot-26_2Mw_6_Exact_vs_CAM} shows the cross section for an UCO at the higher frequency of $M \omega = 8$.
+In this case, the cross section is non-negligible at all angles, and there is evidence for interference between oscillations of comparable amplitudes and widths.
+Summing 31 Regge poles leads to good agreement for the cross section for angles $\theta \gtrsim 35^\circ$.
+As before, it is necessary to include the background integral as well to obtain agreement at smaller angles.
 
@@
  \includegraphics[scale=0.50]{Scattering_Cross_Section_R_2-dot-26_2Mw_6}
-\caption{\label{S_0_2Mw_06_Exact_vs_CAM} The scalar cross section of a very compact bodies for $2M\omega=6$ and $R=2.26M$ and its Regge pole approximation.}
+\caption{\label{S_0_R_2-dot-26_2Mw_6_Exact_vs_CAM} The scalar cross section of a very compact bodies for $2M\omega=6$ and $R=2.26M$ and its Regge pole approximation.}
 \end{figure*}
+
+Figures \ref{Rainbow_Cross_Section_R_6_2Mw_16} and \ref{Diff_Contribution_Cross_Section_R_2-dot-26_2Mw_6} show the relative magnitudes of the contributions from the different branches of Regge poles.
+For $R/M = 6$ (Fig.~ \ref{Rainbow_Cross_Section_R_6_2Mw_16}) the surface-wave and broad-resonance amplitudes are similar in magnitude, and similar in magnitude to their sum.
+There is a difference in phase between these amplitudes which generates the peaks and troughs of the rainbow-scattering pattern.
 
@@
  \includegraphics[scale=0.50]{Rainbow_Cross_Section_R_6_2Mw_16}
-\caption{\label{S_0_2Mw_06_Exact_vs_CAM} Rainbow scattering for compact bodies for $2M\omega=16$ and $R=6M$, its Regge pole approximation and different contributions of the sum over Regge poles.}
+\caption{\label{Rainbow_Cross_Section_R_6_2Mw_16} Rainbow scattering for compact bodies for $2M\omega=16$ and $R=6M$, its Regge pole approximation and different contributions of the sum over Regge poles.}
 \end{figure}
+
+For $R/M = 2.26$ (Fig.~\ref{Diff_Contribution_Cross_Section_R_2-dot-26_2Mw_6}), however, the amplitudes  from the three branches are comparable in magnitude, but their sum is several orders-of-magnitude smaller.
+In other words, there is some delicate cancellation occurring between the contributions from the branches, suggesting that the CAM approach used here is not an efficient method for computing the cross section in this case.
 
@@
  \includegraphics[scale=0.50]{Diff_Contribution_Cross_Section_R_2-dot-26_2Mw_6}
-\caption{\label{S_0_2Mw_06_Exact_vs_CAM} Rainbow scattering for compact bodies for $2M\omega=16$ and $R=2.26M$, its Regge pole approximation and different contributions of the sum over Regge poles.}
+\caption{\label{Diff_Contribution_Cross_Section_R_2-dot-26_2Mw_6} Rainbow scattering for compact bodies for $2M\omega=16$ and $R=2.26M$, its Regge pole approximation and different contributions of the sum over Regge poles.}
 \end{figure}
@@
 \bibliography{rainbowCAM}
-%\bibliographystyle{apsrev4-1}
+\bibliographystyle{apsrev4-1}
 

### 2019-12-06 rainbowCAM.tex
Small changes to intro, added one reference.

@@
 The time-independent scattering of planar waves in the gravitational field of a compact body has been studied in some detail since the 1960s \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970}.
-A substantial literature has developed on \emph{black hole scattering}, focussing on the canonical scenario of a planar wave of frequency $\omega$ and spin $s$ \cite{Chrzanowski:1976jb} impinging upon a black hole of mass $M$ in vacuum \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970, Mashhoon:1973zz,Fabbri:1975,Sanchez:1977vz,MatznerRyan1978,Handler:1980un,Matzner:1985rjn,Futterman:1988ni,Andersson:1995vi,Glampedakis:2001cx,Dolan:2006vj,Dolan:2007ut,Dolan:2008kf,Crispino:2009xt,Cotaescu:2014jca,Gussmann:2016mkp}.
-A dimensionless parameter,
-\begin{equation}
-M \omega = \frac{\pi r_g}{\lambda},
-\end{equation}
-encapsulates the ratio of the gravitational radius $r_g = 2GM/c^2$ to the wavelength $\lambda$ (henceforth we adopt geometric units such that $G=c=1$).
+A substantial literature has developed on \emph{black hole scattering}, focussing on the canonical scenario of a planar wave of circular frequency $\omega$ and spin $s$ \cite{Chrzanowski:1976jb} impinging upon a black hole of mass $M$ in vacuum \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970, Mashhoon:1973zz,Fabbri:1975,Sanchez:1977vz,MatznerRyan1978,Handler:1980un,Matzner:1985rjn,Futterman:1988ni,Andersson:1995vi,Glampedakis:2001cx,Dolan:2006vj,Dolan:2007ut,Dolan:2008kf,Crispino:2009xt,Cotaescu:2014jca,Gussmann:2016mkp}.
+The dimensionless parameter
+$
+M \omega = \pi r_g / \lambda
+$
+encapsulates the ratio of the gravitational radius $r_g = 2GM/c^2$ to the wavelength $\lambda$ (we adopt geometric units such that $G=c=1$).
 The long wavelength ($M \omega \ll 1$), short wavelength ($M \omega \gg 1$) and intermediate regimes have been studied with a combination of perturbative \cite{DeLogi:1977dp,Dolan:2007ut,Guadagnini:2008ha,Sorge:2015yoa}, semi-classical \cite{Matzner:1985rjn, Anninos:1992ih} and numerical methods.
-The $s = 0$ (scalar) \cite{Matzner:1968,Sanchez:1977vz,Andersson:1995vi,Glampedakis:2001cx,Leite:2019eis}, $s=1/2$ (fermion) \cite{Dolan:2006vj,Cotaescu:2014jca}, $s=1$ (electromagnetic) \cite{Fabbri:1975, Crispino:2009xt, Crispino:2015gua} and $s=2$ (gravitational) cases \cite{MatznerRyan1978,Handler:1980un,Dolan:2008kf} have all been covered.
+The $s = 0$ (scalar) \cite{Matzner:1968,Sanchez:1977vz,Andersson:1995vi,Glampedakis:2001cx,Leite:2019eis}, $s=1/2$ (fermion) \cite{Dolan:2006vj,Cotaescu:2014jca}, $s=1$ (electromagnetic) \cite{Fabbri:1975, Crispino:2009xt, Crispino:2015gua} and $s=2$ (gravitational) cases \cite{MatznerRyan1978,Handler:1980un,Dolan:2008kf} have all been addressed.
 
@@
 Similarly, a neutron star is expected to be substantially transparent to neutrinos.
-Though the coupling to matter is weak, the incident wave is still strongly scattered due to the influence on the spacetime curvature.
+However, even in cases where the coupling to matter is weak, the incident wave is still strongly scattered due to the influence of the spacetime curvature.
 Recent work \cite{Dolan:2017rtj, Stratton:2019deq} has explored the \emph{rainbow scattering} phenomenon that arises at short wavelengths, due to a stationary point in the geodesic deflection function associated with a ray that passes somewhat inside the body.
@@
 
+Other recent works have examined scattering from a compact object with an absorbing surface \cite{Nambu:2019sqn}; and scattering simulations using finite-element-method codes \cite{He:2019orl}.
+
 The tenuity (inverse compactness) .
-
-find room for \cite{Nambu:2019sqn}
 

### 2019-12-06 rainbowCAM.tex
blah

@@
 A substantial literature has developed on \emph{black hole scattering}, focussing on the canonical scenario of a planar wave of circular frequency $\omega$ and spin $s$ \cite{Chrzanowski:1976jb} impinging upon a black hole of mass $M$ in vacuum \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970, Mashhoon:1973zz,Fabbri:1975,Sanchez:1977vz,MatznerRyan1978,Handler:1980un,Matzner:1985rjn,Futterman:1988ni,Andersson:1995vi,Glampedakis:2001cx,Dolan:2006vj,Dolan:2007ut,Dolan:2008kf,Crispino:2009xt,Cotaescu:2014jca,Gussmann:2016mkp}.
-The dimensionless parameter
+A dimensionless parameter
 $
@@
 Similarly, a neutron star is expected to be substantially transparent to neutrinos.
-However, even in cases where the coupling to matter is weak, the incident wave is still strongly scattered due to the influence of the spacetime curvature.
-Recent work \cite{Dolan:2017rtj, Stratton:2019deq} has explored the \emph{rainbow scattering} phenomenon that arises at short wavelengths, due to a stationary point in the geodesic deflection function associated with a ray that passes somewhat inside the body.
+However, even in these cases where the coupling to matter is negligible, the incident wave is still scattered by the influence of the spacetime curvature.
+Recent work \cite{Dolan:2017rtj, Stratton:2019deq} explored the \emph{rainbow scattering} phenomenon that arises at short wavelengths, due to a stationary point in the geodesic deflection function associated with a ray that passes somewhat inside the body.
 In principle, the rainbow angle is a diagnostic of the matter distribution of the body, and thus its nuclear equation of state.
+Indeed, in the 1970s, experimental data on rainbows in nucleon-nucleon scattering experiments was used to constrain models of the nuclear potential.
 

### 2019-12-06 rainbowCAM.tex
work on classification of QNM section

--- 2019-12-02 rainbowCAM.tex
@@
 	\begin{enumerate}
-   \item Curvature modes, oscillations whose damping is larger for less compact bodies. \sam{Anything else to say on curvature modes?}
+   \item Curvature modes, the standard $w$-modes extant for all relativistic stars.
+The less compact the star the more rapid the damping (Im$\{\omega\}$ increases with $R/M$).
+\sam{Anything else to say on curvature modes?}
    \item Interface modes ($\omega_{\text{II}}$-modes \cite{Leins:1993zz}), characterised by very rapid damping (i.e.~large negative imaginary part of $\omega_{\ell n}$).
-This branch of modes is most similar to the Schwarzschild black hole quasinormal modes.
+This branch of modes is somewhat similar to modes for acoustic waves scattered of a hard sphere.
    \item Trapped modes \cite{Chandrasekhar449}: These modes exist for UCOs with $R/M < 3$, because the effective radial potential has a local minimum inside the star, and local maximum near the photon sphere $r=3M$.
@@
 	\end{enumerate}
+
 For more details on quasinormal modes see \sam{Appropriate reference needed.}
+
+As far as we know, the only study into Regge pole spectra for relativistic stellar models was done by Chandrasekhar and Ferrari in 1991 \cite{ChandrasekharIV:1992ey}.
+They used Regge pole theory to calculate the flow of gravitational energy through a star.
 

### 2019-12-06 rainbowCAM.tex
adding in Numerical section

--- 2019-12-06 rainbowCAM.tex
@@
 \end{equation}
-where $V_{\ell}(r)$ is the effective potential, and $r^\ast$ denotes the \emph{tortoise coordinate} defined by
+where $V_{\ell}(r)$ is the effective potential, and $r_\ast$ denotes the \emph{tortoise coordinate} defined by
 \begin{equation}
-\frac{dr}{dr^\ast} =\sqrt{f(r)h(r)} .  \label{eq:tortoise}
+\frac{dr}{dr_\ast} =\sqrt{f(r)h(r)} .  \label{eq:tortoise}
 \end{equation}
@@
 with $s=0$ in the scalar-field case, and $s=2$ in the axial gravitational-wave case.
-In the exterior, the tortoise coordinates $r^\ast$ reduces to $r^\ast = r+ 2M \ln [r/(2M) -1]+k$, where $k$ is a constant that is chosen such that $r_\ast(r=0) = 0$ and $r_\ast(r)$ is a continuous function.
+In the exterior, the tortoise coordinates $r_\ast$ reduces to $r_\ast = r+ 2M \ln [r/(2M) -1]+k$, where $k$ is a constant that is chosen such that $r_\ast(r=0) = 0$ and $r_\ast(r)$ is a continuous function.
 
@@
 
-The \emph{Regge pole spectrum} is the set of angular momenta $\lambda_{\omega n} = \ell_{n}(\omega) + 1/2$ in the complex-$\lambda$ plane at which the scattering matrix has a simple pole for a real value of $\omega$ (so $\omega \in \mathbb{R}$ and $\lambda_{n}(\omega) \in \mathbb{C}$).
+The \emph{Regge pole spectrum} is the set of angular momenta $\lambda_{n}(\omega) = \ell_{n}(\omega) + 1/2$ in the complex-$\lambda$ plane at which the scattering matrix has a simple pole for a real value of $\omega$ (so $\omega \in \mathbb{R}$ and $\lambda_{n}(\omega) \in \mathbb{C}$).
 Here $n$ is an index for enumerating the discrete spectrum of poles.
@@
 In turn, the BBF method is an adaptation of the \textit{continued fraction method} developed by Leaver in the case of black hole-quasinormal mode frequencies~\cite{Leaver:1985ax}.
-Though BBF used the method to find axial QNM frequencies, their method is equally valid, \textit{mutatis mutandis}, for finding the Regge poles.
-We have implemented numerically this method by using the Hill determinant approach of Majumdar and Panchapakesan~\cite{mp}, or more precisely, by modifying their method and adapting it to our problem, \textit{i.e.}, using it for a 4-term recurrence relation.
-We implemented the method with  \emph{Mathematica}.
+Though BBF used the method to find axial QNM frequencies, their method is equally valid, \textit{mutatis mutandis}, for finding the Regge poles $\{\lambda_n(\omega)= \ell_n +1/2\}$ of $ S_{\ell}(\omega)$.
+BBF write the solution of the Regge-Wheeler equation in a power-series form as follows:
+%\begin{equation}\label{Power_series}
+%  \phi_{\omega_\ell}(r) =\left(\frac{r}{2M}-2M\right)^{i 2M\omega} \,e^{i\omega r} \sum_{n,=0}^{+\infty}a_n\left(1-\frac{b}{r}\right)^n
+%\end{equation}
 
-\sam{I think we need a little bit more detail here -- how does the four-term recurrence relation arise, and where can it be found specifically?}
+\begin{eqnarray}\label{Power_series}
+% \nonumber % Remove numbering (before each equation)
+ \phi_{\omega_\ell}(r)&=&\left(\frac{r}{2M}-2M\right)^{i 2M\omega} \,e^{i\omega r} \sum_{n,=0}^{+\infty}a_n\left(1-\frac{b}{r}\right)^n \nonumber \\
+                      &=& e^{i\omega r_*(r)}\sum_{n,=0}^{+\infty}a_n\left(1-\frac{b}{r}\right)^n
+\end{eqnarray}
+where $r = b$ is some point outside the star. By substituting \eqref{Power_series} in the Regge-Wheeler equation, BBF found that the coefficients $a_n$ satisfy a four–term recurrence
+relation of the form:
+\begin{equation}\label{Recurrence_4_terms}
+\alpha_n a_{n+1} + \beta_n a_{n} +\gamma_{n} a_{n-1} +\delta_{n} a_{n-2}  = 0, \quad \forall n\geq 2
+\end{equation}
+where
+\begin{eqnarray}\label{Coeffs_3_termes}
+ && \alpha_n = n (n+1)\left(1-\frac{2M}{b}\right)   \\
+ && \beta_n  = 2i\omega b n + 3\left(\frac{2M}{b}\right)n^2-2n^2  \\
+ && \gamma_n = \left(1-\frac{6M}{b}\right)n(n-1)-\beta_s\left(\frac{2M}{b}\right)-\ell(\ell+1)  \\
+ && \delta_n = \left(\frac{2M}{b}\right)\left(n(n-2)+\beta_s\right)
+\end{eqnarray}
+To determine the initial conditions $a_0$ and $a_1$, we impose the continuity of $\phi_{\omega_\ell}(r)$ and its derivative in $r = b$, according to Eq~\eqref{Power_series}, we obtain:
+\begin{eqnarray}\label{Initial_Conds}
+ && a_0 = e^{i\omega r_*(b)\phi_{\omega_\ell}(b)}  \\
+ && a_1 = b e^{-i\omega r_*(b)}\left(\frac{-i\omega b}{b-2M}\phi_{\omega_\ell}(b)+ \frac{d}{dr}\phi_{\omega_\ell}(r)\Big{|}_{r=b}\right)
+\end{eqnarray}
+Here, to obtain $\phi_{\omega_\ell}(b)$ and its derivative in $r=b$, we need to solve numerically the Eq.~\eqref{H_Radial_equation} inside the star and to continue the solution outside, up to $r=b$, by solving the Regge-wheeler equation.
+
+It is important to note that, the \textit{continued fraction method} is applied to the three-term recurrence relation. To do this, BBF has used the method introduced by Leaver in
+the case of Reissner-Nordstöm   black hole \cite{Leaver:1990zz}, \textit{i.e.}, reducing the four-term recurrence relations \eqref{Recurrence_4_terms} to a three-term recurrence relation by using the gaussian elimination step.
+
+We have implemented numerically this method by using the \textit{Hill determinant approach} of Majumdar and Panchapakesan~\cite{mp} introduced in the case of Schwarzschild black hole.
+They gave an alternative condition and they suggested that the nontrivial solutions of \eqref{Recurrence_4_terms} exists  when the Hill determinant vanish:
+\begin{equation}
+\label{Determinant_Hill_4_termes}
+D   =  \begin{vmatrix}
+   \beta_0         &  \alpha_0    &        0             &       0                    &          0                &     \ldots          &     \ldots        &    \ldots \\
+   \gamma_1        &  \beta_1      &     \alpha_1     &       0                    &          0                &     \ldots          &     \ldots        &    \ldots  \\
+    \delta_2       &   \gamma_2     &    \beta_2       &   \alpha_2             &         0                &     \ldots           &    \ldots         &    \ldots  \\
+    \vdots         &      \ddots     &     \ddots       &    \ddots                &       \ddots          &     \ddots           &   \ldots          &    \ldots \\
+     \vdots        &     \vdots      &     \delta_{n-1}      &    \gamma_{n-1}      &     \beta_{n-1}     &      \alpha_{n-1} &    \ddots         &    \ldots  \\
+     \vdots        &  \vdots        &     \vdots        &     \delta_n                &    \gamma_{n}    &     \beta_{n}        &     \alpha_{n}  &    \ddots     \\
+     \vdots        &  \vdots        &     \vdots        &     \vdots                &    \ddots            &     \ddots            &     \ddots       &    \ddots
+                        \end{vmatrix}
+       = 0
+\end{equation}
 
@@
 \begin{eqnarray}\label{CAM_Scalar_Scattering_amp_decomp_Background_b}
-\hat{f}^\text{\tiny{B},\tiny{Im}} && (\omega, \theta) = \frac{1}{2 \omega}\left(\int_{+i\infty}^{0} d\lambda \, \left[S_{\lambda -1/2}(\omega) P_{\lambda_n(\omega) -1/2} (-\cos \theta) \right.
+\hat{f}^\text{\tiny{B},\tiny{Im}} && (\omega, \theta) = \frac{1}{2 \omega}\left(\int_{+i\infty}^{0} d\lambda \, \left[S_{\lambda -1/2}(\omega) P_{\lambda-1/2} (-\cos \theta) \right.
 \right.\nonumber \\
-&& -\left. \left. S_{-\lambda -1/2}(\omega) e^{i \pi \left(\lambda+1/2\right)}P_{\lambda_n(\omega) -1/2} (\cos \theta) \right]\lambda\right).
+&& -\left. \left. S_{-\lambda -1/2}(\omega) e^{i \pi \left(\lambda+1/2\right)}P_{\lambda-1/2} (\cos \theta) \right]\lambda\right).
 \end{eqnarray}

### 2019-12-06 rainbowCAM.tex
test
Some thoughts on topics for the discussion section.

--- 2019-12-06 rainbowCAM.tex
@@
 \section{Introduction}
+
+Change !
 
@@
 %\captionsetup{font=small}
-\caption{\label{tab:table1} The lowest Regge poles $\lambda_{n}(\omega)$ for the scalar field and the associated residues $r_{n}(\omega)$.
-The radius of the compact bodies is $R = 6M$ and we set $2M=1$.}
+\caption{\label{tab:table1} The lowest Regge poles $\lambda_{n}(\omega)$ for the scalar field and the associated residues $r_{n}(\omega)$. The radius of the compact bodies is $R = 6M$.}
 \smallskip
@@
 %\captionsetup{font=small}
-\caption{\label{tab:table2} The lowest Regge poles $\lambda_{n}(\omega)$ for the scalar field and the associated residues $r_{n}(\omega)$.
-The radius of the compact bodies is $R = 2.26M$ and we set $2M=1$.}
+\caption{\label{tab:table2} The lowest Regge poles $\lambda_{n}(\omega)$ for the scalar field and the associated residues $r_{n}(\omega)$. The radius of the compact bodies is $R = 2.26M$.}
 \smallskip
@@
 %\captionsetup{font=small}
-\caption{\label{tab:table3} The lowest Regge poles $\lambda_{n}(\omega)$ for the axial gravitational waves. The radius of the compact bodies is $R = 6M$ and we set $2M=1$.}
+\caption{\label{tab:table3} The lowest Regge poles $\lambda_{n}(\omega)$ for the axial gravitational waves. The radius of the compact bodies is $R = 6M$.}
 \smallskip
@@
 %\captionsetup{font=small}
-\caption{\label{tab:table4} The lowest Regge poles $\lambda_{n}(\omega)$ for the axial gravitational waves. The radius of the compact bodies is $R = 2.26M$ and we set $2M=1$.}
+\caption{\label{tab:table4} The lowest Regge poles $\lambda_{n}(\omega)$ for the axial gravitational waves. The radius of the compact bodies is $R = 2.26M$.}
 \smallskip
@@
 \begin{table}[htp]
-\caption{\label{tab:table5} The lowest Regge poles $\lambda_{n}(\omega)$ for the scalar field versus WKB results given by Eq.~\eqref{lambda_Approx}.
-The radius of the compact bodies is $R = 6M$ and we set $2M=1$.}
+\caption{\label{tab:table5} The lowest Regge poles $\lambda_{n}(\omega)$ for the scalar field versus WKB results given by Eq.~\eqref{lambda_Approx}. The radius of the compact bodies is $R = 6M$.}
 \smallskip
@@
 
+We have calculated the full spectrum of Regge poles for a compact body spacetime for the first time.
+
+We find 2 distinct branches - - in the case $R > 3M$, and a third branch of narrow resonances appears for UCO.
+
+Confident that there are no additional poles in the first quadrant with imaginary parts less than (blah), for two reasons.
+First, we have scanned across the domain using the scanning method.
+Second, we obtain an excellent agreement, which would not be the case if poles in this domain had been missed.
+
+Links between QNMs and Regge poles. Further examination.
+
+Through a WKB method, we have obtained qualitative understanding of the broad resonances, finding that the imaginary part is predicted, with a certain degree of accuracy, from the discontinuity in the potential at the surface of the body.
+Further work is need on modelling the surface-wave branch, the narrow resonances.
+Taking the WKB method to higher orders will presumably improve the accuracy.
+
+Complementary method.
+Not efficient method at present.
+Convergence of the sum is not as rapid as in the BH case, due to the branch of broad resonances close to the real axis.
+Neither have we obtained an approximation has powerful as that of Ould Elhadj and Folacci for describing the orbiting phenomenon.
+In the case of Mie scattering, a powerful resummation approach is that of Regge-Debye poles, reducing to one branch of poles of higher order.
+This is a possible direction for future work.
+
+We have examined the case of $R=2.26M$, which is above the Buchdahl bound but nevertheless below ... blah blah, work in Tom's text.
+
 \acknowledgments

### 2019-12-06 rainbowCAM.tex
work on Regge pole spectrum section and numerical method section

@@
 The less compact the star the more rapid the damping (Im$\{\omega\}$ increases with $R/M$).
-\sam{Anything else to say on curvature modes?}
+\sam{Anything else to say on curvature modes?} \tom{have added a little}
    \item Interface modes ($\omega_{\text{II}}$-modes \cite{Leins:1993zz}), characterised by very rapid damping (i.e.~large negative imaginary part of $\omega_{\ell n}$).
@@
 
-For more details on quasinormal modes see \sam{Appropriate reference needed.}
+For more details on quasinormal modes see \sam{Appropriate reference needed.} \tom{Can we just get rid of this sentence as have already referred to review by Kokkotas?}
 
-As far as we know, the only study into Regge pole spectra for relativistic stellar models was done by Chandrasekhar and Ferrari in 1991 \cite{ChandrasekharIV:1992ey}.
-They used Regge pole theory to calculate the flow of gravitational energy through a star.
-
-We now turn our attention to calculating the Regge pole spectrum for compact bodies.
+As far as we know, the only published study into Regge pole spectra for relativistic stellar models was that of Chandrasekhar and Ferrari in 1991 \cite{ChandrasekharIV:1992ey}.
+%They used Regge pole theory to calculate the flow of gravitational energy through a star.
+They restricted their attention to resonant modes, i.e.
+poles with small imaginary parts.
+For the axial sector these are only present for UCOs.
+For the polar sector the situation is more complicated, as there are long lived fluid pulsation modes.
+They considered resonant modes (poles with small imaginary parts corresponding to trapped $w$-modes or fluid modes), and used CAM theory to calculate the flow of gravitational energy through a star.
+More literature exists on Regge pole theory applied to black hole scattering, for example Andersson and Thylwe have described scattering of scalar waves by a Schwarzschild BH utilising CAM techniques \cite{Andersson:1994rk}.
+They associate the BH Regge poles with ``surface waves'' localised near the unstable light ring at $r=3M$.
+Later, Decanini and collaborators showed that the Schwarzschild BH QNMs are in fact Breit-Wigner type resonances generated by said surface waves.
+We see here that CAM theory is a powerful approach to BH physics, that provides a clear and robust physical picture.
+It seems reasonable to expect that CAM may also aid in our understanding of other compact objects such as UCOs and neutron stars.
+With this in mind, we now turn our attention to calculating the Regge pole spectrum for compact bodies.
+\tom{Some of this paragraph may be more suited to the introduction?}
 
@@
 
-In order to determine the Regge poles we adapt the method of Benhar, Berti and Ferrari (BBF), described in Sec.~4 of Ref.~\cite{Benhar:1998au}.
+%In order to determine the Regge poles we adapt the method of Benhar, Berti and Ferrari (BBF), described in Sec.~4 of Ref.~\cite{Benhar:1998au}.
 In turn, the BBF method is an adaptation of the \textit{continued fraction method} developed by Leaver in the case of black hole-quasinormal mode frequencies~\cite{Leaver:1985ax}.
@@
 
+Leins Nollert and Soffel \cite{Leins:1993zz} have developed a method for calculating the polar QNM frequencies of spherically symmetric spacetimes.
+Benhar, Berti and Ferarri (BBF) have extended this method to the axial sector.
+Here we shall present a generalisation the BBF method for axial \emph{and} scalar QNM frequencies ($s=2$ and $s=0$ respectively).
+The method is equally valid, \textit{mutatis mutandis}, for finding Regge poles $\{\lambda_n(\omega)= \ell_n +1/2\}$ of $ S_{\ell}(\omega)$.
+The solution of the Regge-Wheeler equation is written in a power-series form as follows:
+%
 \begin{eqnarray}\label{Power_series}
@@
 \end{eqnarray}
-where $r = b$ is some point outside the star. By substituting \eqref{Power_series} in the Regge-Wheeler equation, BBF found that the coefficients $a_n$ satisfy a four–term recurrence
-relation of the form:
+where $r = b$ is some point outside the star.
+By substituting \eqref{Power_series} in the Regge-Wheeler equation, it can be shown that the coefficients $a_n$ satisfy a four–term recurrence relation of the form:
 \begin{equation}\label{Recurrence_4_terms}
@@
 
-It is important to note that, the \textit{continued fraction method} is applied to the three-term recurrence relation. To do this, BBF has used the method introduced by Leaver in
-the case of Reissner-Nordstöm   black hole \cite{Leaver:1990zz}, \textit{i.e.}, reducing the four-term recurrence relations \eqref{Recurrence_4_terms} to a three-term recurrence relation by using the gaussian elimination step.
+It is important to note that, the \textit{continued fraction method} is applied to the three-term recurrence relation. To do this, Leins~\emph{et al.} and BBF use the method introduced by Leaver in
+the case of Reissner-Nordstöm black holes \cite{Leaver:1990zz}, \textit{i.e.}, reducing the four-term recurrence relations \eqref{Recurrence_4_terms} to a three-term recurrence relation by using the gaussian elimination step.
 
-We have implemented numerically this method by using the \textit{Hill determinant approach} of Majumdar and Panchapakesan~\cite{mp} introduced in the case of Schwarzschild black hole.
-They gave an alternative condition and they suggested that the nontrivial solutions of \eqref{Recurrence_4_terms} exists  when the Hill determinant vanish:
+We do not use the gaussian elimination step.
+Instead we find solutions of \eqref{Recurrence_4_terms} by adapting the \textit{Hill determinant approach} employed by Majumdar and Panchapakesan~\cite{mp} to solve the black hole recurrence formula of Leaver \cite{Leaver:1985ax}.
+The nontrivial solutions of \eqref{Recurrence_4_terms} exist when the Hill determinant vanishes:
 \begin{equation}
@@
                         \end{vmatrix}
-       = 0
+       = 0.
 \end{equation}
+%
+Letting $D_n$ be the determinant of the $n \times n$ sub matrix of $D$ (with diagonal $\{\beta_0,\beta_1,....\beta_n\}$), by \eqref{Recurrence_4_terms}
+%
+\begin{equation}
+D_n = \beta_n D_{n-1} - \alpha_{n-1} \gamma_n D_{n-2} + \alpha_{n-1} \alpha_{n-2} \delta_n D_{n-3}.
+\end{equation}
+%
+Regge poles (QNM frequencies) are found by fixing $\omega$ ($\lambda$) and numerically finding roots $\lambda_n$ ($\omega_n$) of $D_n$, i.e.~ $D_n(\lambda_n,\omega)=0$ ($D_n(\lambda,\omega_n)=0$). 
+%Regge poles $\lambda_n$ (QNM frequencies $\omega_n$) are roots of $D_n$
 

### 2019-12-06 rainbowCAM.tex
reference added for Decanini and initial conditions for Dn

@@
 %\usepackage{subcaption}
+\usepackage{xcolor}
 
@@
 \newcommand{\tom}[1]{\textcolor{blue}{(Tom: #1)}}
-\newcommand{\mo}[1]{\textcolor{green}{(Mohamed: #1)}}
+\newcommand{\moh}[1]{\textcolor{green}{(Mohamed: #1)}}
 
@@
 They associate the BH Regge poles with ``surface waves'' localised near the unstable light ring at $r=3M$.
-Later, Decanini and collaborators showed that the Schwarzschild BH QNMs are in fact Breit-Wigner type resonances generated by said surface waves.
+Later, Decanini, Folacci and Jensen showed that the Schwarzschild BH QNMs are in fact Breit-Wigner type resonances generated by said surface waves \cite{Decanini:2002ha}.
 We see here that CAM theory is a powerful approach to BH physics, that provides a clear and robust physical picture.
@@
 With this in mind, we now turn our attention to calculating the Regge pole spectrum for compact bodies.
-\tom{Some of this paragraph may be more suited to the introduction?}
-
+\tom{Some of this paragraph may be more suited to the introduction?}\\
+\moh{Reference Added for Decanini, Folacci and Jensen}.
  \subsection{Numerical method}\label{subsec:method}
@@
 
-Leins Nollert and Soffel \cite{Leins:1993zz} have developed a method for calculating the polar QNM frequencies of spherically symmetric spacetimes.
+Leins, Nollert and Soffel \cite{Leins:1993zz} have developed a method for calculating the polar QNM frequencies of spherically symmetric spacetimes.
 Benhar, Berti and Ferarri (BBF) have extended this method to the axial sector.
@@
 % \nonumber % Remove numbering (before each equation)
- \phi_{\omega_\ell}(r)&=&\left(\frac{r}{2M}-2M\right)^{i 2M\omega} \,e^{i\omega r} \sum_{n,=0}^{+\infty}a_n\left(1-\frac{b}{r}\right)^n \nonumber \\
+ \phi_{\omega_\ell}(r)&=&\left(\frac{r}{2M}-1\right)^{i 2M\omega} \,e^{i\omega r} \sum_{n,=0}^{+\infty}a_n\left(1-\frac{b}{r}\right)^n \nonumber \\
                       &=& e^{i\omega r_*(r)}\sum_{n,=0}^{+\infty}a_n\left(1-\frac{b}{r}\right)^n
@@
 \begin{equation}
-D_n = \beta_n D_{n-1} - \alpha_{n-1} \gamma_n D_{n-2} + \alpha_{n-1} \alpha_{n-2} \delta_n D_{n-3}.
+\label{derecurrence_4_termes}
+D_n=\beta_n D_{n-1} - \gamma_{n}\alpha_{n-1}D_{n-2} + \delta_n \alpha_{n-1} \alpha_{n-2} D_{n-3}
+\end{equation}
+%
+with the initial conditions
+ \begin{equation}
+ \label{Determinant_initial_conds}
+ \begin{split}
+    D_0 &=\beta_0, \\
+    D_1 &=\beta_1\beta_0-\gamma_1\alpha_0  \\
+    D_2 &=\beta_0(\beta_1 \beta_2 - \alpha_1 \gamma_2)- \alpha_0(\alpha_1 \delta_2 -\gamma_1 \beta_2)
+ \end{split}
  \end{equation}
@@
 %Regge poles $\lambda_n$ (QNM frequencies $\omega_n$) are roots of $D_n$
-
+\\
+\moh{initial conditions added for $D_n$}
  \subsection{Numerical results: the spectrum}\label{subsec:results1}

### 2019-12-09 rainbowCAM.tex
To do lists.

@@
 
+As far as we know, the only published study into Regge pole spectra for relativistic stellar models was that of Chandrasekhar and Ferrari in 1991 \cite{ChandrasekharIV:1992ey}.
+%They used Regge pole theory to calculate the flow of gravitational energy through a star.
+They restricted their attention to resonant modes, i.e.
+poles with small imaginary parts.
+For the axial sector these are only present for UCOs.
+For the polar sector the situation is more complicated, as there are long lived fluid pulsation modes.
+They considered resonant modes (poles with small imaginary parts corresponding to trapped $w$-modes or fluid modes), and used CAM theory to calculate the flow of gravitational energy through a star.
+More literature exists on Regge pole theory applied to black hole scattering, for example Andersson and Thylwe have described scattering of scalar waves by a Schwarzschild BH utilising CAM techniques \cite{Andersson:1994rk}.
+They associate the BH Regge poles with ``surface waves'' localised near the unstable light ring at $r=3M$.
+Later, Decanini, Folacci and Jensen showed that the Schwarzschild BH QNMs are in fact Breit-Wigner type resonances generated by said surface waves \cite{Decanini:2002ha}.
+We see here that CAM theory is a powerful approach to BH physics, that provides a clear and robust physical picture.
+It seems reasonable to expect that CAM may also aid in our understanding of other compact objects such as UCOs and neutron stars.
+With this in mind, we now turn our attention to calculating the Regge pole spectrum for compact bodies.
+
+\sam{Sam to finish}
+
 %\section{Differential scattering cross sections for scalar waves, their CAM representation and their Regge pole approximations}
@@
 The radial function $h(r)$ is $C^0$ at the surface of the star $r=R$ (i.e.~continuous but not differentiable), and the radial function $f(r)$ is $C^1$ there (i.e.~once-differentiable).
-In the polytropic cases $n > 0$, the functions are more regular \sam{can we make a precise statement?} at the surface, but not $C^\infty$ (i.e.~not smooth).
+In the polytropic cases $n > 0$, the functions are more regular \sam{can we make a precise statement?}\tom{I will write something here} at the surface, but not $C^\infty$ (i.e.~not smooth).
 As we shall see, the breakdown of smoothness leads to consequences for the Regge pole spectrum.
@@
 	\begin{enumerate}
-   \item Curvature modes, the standard $w$-modes extant for all relativistic stars.
-The less compact the star the more rapid the damping (Im$\{\omega\}$ increases with $R/M$).
-\sam{Anything else to say on curvature modes?} \tom{have added a little}
+   \item Curvature modes, the standard $w$-modes extant for all relativistic stars. The less compact the star the more rapid the damping (Im$\{\omega\}$ increases with $R/M$).
    \item Interface modes ($\omega_{\text{II}}$-modes \cite{Leins:1993zz}), characterised by very rapid damping (i.e.~large negative imaginary part of $\omega_{\ell n}$).
@@
 
-For more details on quasinormal modes see \sam{Appropriate reference needed.} \tom{Can we just get rid of this sentence as have already referred to review by Kokkotas?}
-
-As far as we know, the only published study into Regge pole spectra for relativistic stellar models was that of Chandrasekhar and Ferrari in 1991 \cite{ChandrasekharIV:1992ey}.
-%They used Regge pole theory to calculate the flow of gravitational energy through a star.
-They restricted their attention to resonant modes, i.e.
-poles with small imaginary parts.
-For the axial sector these are only present for UCOs.
-For the polar sector the situation is more complicated, as there are long lived fluid pulsation modes.
-They considered resonant modes (poles with small imaginary parts corresponding to trapped $w$-modes or fluid modes), and used CAM theory to calculate the flow of gravitational energy through a star.
-More literature exists on Regge pole theory applied to black hole scattering, for example Andersson and Thylwe have described scattering of scalar waves by a Schwarzschild BH utilising CAM techniques \cite{Andersson:1994rk}.
-They associate the BH Regge poles with ``surface waves'' localised near the unstable light ring at $r=3M$.
-Later, Decanini, Folacci and Jensen showed that the Schwarzschild BH QNMs are in fact Breit-Wigner type resonances generated by said surface waves \cite{Decanini:2002ha}.
-We see here that CAM theory is a powerful approach to BH physics, that provides a clear and robust physical picture.
-It seems reasonable to expect that CAM may also aid in our understanding of other compact objects such as UCOs and neutron stars.
-With this in mind, we now turn our attention to calculating the Regge pole spectrum for compact bodies.
-\tom{Some of this paragraph may be more suited to the introduction?}\\
-\moh{Reference Added for Decanini, Folacci and Jensen}.
+We now move on to consider the Regge poles of compact bodies, which have received comparatively less attention \cite{ChandrasekharIV:1992ey}.
+
  \subsection{Numerical method}\label{subsec:method}
@@
 where $r = b$ is some point outside the star.
-By substituting \eqref{Power_series} in the Regge-Wheeler equation, it can be shown that the coefficients $a_n$ satisfy a four–term recurrence relation of the form:
+By substituting \eqref{Power_series} in the Regge-Wheeler equation, it can be shown that the coefficients $a_n$ satisfy a four-term recurrence relation of the form:
 \begin{equation}\label{Recurrence_4_terms}
@@
 where
+\begin{subequations}
 \begin{eqnarray}\label{Coeffs_3_termes}
@@
  && \beta_n  = 2i\omega b n + 3\left(\frac{2M}{b}\right)n^2-2n^2  \\
- && \gamma_n = \left(1-\frac{6M}{b}\right)n(n-1)-\beta_s\left(\frac{2M}{b}\right)-\ell(\ell+1)  \\
+ && \gamma_n = \left(1-\frac{6M}{b}\right)n(n-1)-\frac{2M\beta_s}{b}-\ell(\ell+1)  \\
  && \delta_n = \left(\frac{2M}{b}\right)\left(n(n-2)+\beta_s\right)
 \end{eqnarray}
+\end{subequations}
 To determine the initial conditions $a_0$ and $a_1$, we impose the continuity of $\phi_{\omega_\ell}(r)$ and its derivative in $r = b$, according to Eq~\eqref{Power_series}, we obtain:
@@
 It is important to note that, the \textit{continued fraction method} is applied to the three-term recurrence relation. To do this, Leins~\emph{et al.} and BBF use the method introduced by Leaver in
-the case of Reissner-Nordstöm black holes \cite{Leaver:1990zz}, \textit{i.e.}, reducing the four-term recurrence relations \eqref{Recurrence_4_terms} to a three-term recurrence relation by using the gaussian elimination step.
+the case of Reissner-Nordst\"om black holes \cite{Leaver:1990zz}, \textit{i.e.}, reducing the four-term recurrence relations \eqref{Recurrence_4_terms} to a three-term recurrence relation by using the gaussian elimination step.
 
@@
 %Regge poles $\lambda_n$ (QNM frequencies $\omega_n$) are roots of $D_n$
-\\
-\moh{initial conditions added for $D_n$}
+
  \subsection{Numerical results: the spectrum}\label{subsec:results1}
@@
 The values are labelled by branch (broad; surface; narrow).
-For the scalar field, the associated residues (see Sec.~) are also presented in Tables \ref{tab:table1} and Table \ref{tab:table2}.
+For the scalar field, the associated residues (see Eq.~\eqref{residues_RP}) are also presented in Tables \ref{tab:table1} and Table \ref{tab:table2}.
 
@@
  \subsection{The WKB approximation}
+ \tom{Tom to review this section}
+
 To investigate the relationship between the qualitative features of the effective potential (Fig.~\ref{fig:Veff}) and the three branches of Regge poles revealed in Sec.~\ref{subsec:results}, we now employ the WKB method, with a view of obtain an approximation that is valid at high frequencies ($M\omega \rightarrow \infty$).
@@
 
+\sam{Sam to write this}
+
 We have calculated the full spectrum of Regge poles for a compact body spacetime for the first time.

### 2019-12-09 rainbowCAM.tex
mohamed email
added statement on smoothness of f and h and Mohamed has checked and corrected equation 33 and checked equation 34

@@
 \author{Mohamed \surname{Ould~El~Hadj}}
-\email{m.ouldelhadj@sheffield.ac.uk}
+\email{med.ouldelhadj@gmail.com}
 
@@
 The radial function $h(r)$ is $C^0$ at the surface of the star $r=R$ (i.e.~continuous but not differentiable), and the radial function $f(r)$ is $C^1$ there (i.e.~once-differentiable). 
-In the polytropic cases $n > 0$, the functions are more regular \sam{can we make a precise statement?}\tom{I will write something here} at the surface, but not $C^\infty$ (i.e.~not smooth).
+%In the polytropic cases $n > 0$, the functions are more regular \sam{can we make a precise statement?}\tom{I will write something here} at the surface, but not $C^\infty$ (i.e.~not smooth).
+As we shall see, the breakdown of smoothness leads to consequences for the Regge pole spectrum.
+For a general polytrope with $n>0$ and $m$ the smallest integer such that $m \geq n$, $h(r)$ is $C^m$ and $f(r)$ is $C^{m+1}$ at the surface. 
+%\tom{This can be seen from equations relating $(m,\rho,p,f,h)$ and by noting $\rho \sim a(R-r)^n$ at the surface \cite{Lindblom:1983ps} but we don't mention these.}
 As we shall see, the breakdown of smoothness leads to consequences for the Regge pole spectrum.
@@
 \begin{equation}\label{lambda_Approx}
-  \lambda_n \approx \frac{2 \omega R_*}{\pi}-\left(2n \pm \frac{1}{2}\right)+\frac{i}{\pi} \ln\left(\frac{2 R^2 \omega}{\sqrt{3M (R-2M)}}\right) .
-\end{equation}
-\sam{Please double-check this formula is correct for both scalar (+) and axial GW (-) cases.}
+  \lambda_n \approx \frac{2 \omega R_*}{\pi}-\left(2n \pm \frac{1}{2}\right)+\frac{2 i}{\pi} \ln\left(\frac{2 R^2 \omega}{\sqrt{3M (R-2M)}}\right) .
+\end{equation}
+%
 This corresponds to a series of Regge poles with spacing $|\Delta \lambda_n|\approx 2$ with the almost-constant imaginary part; these are the broad resonances shown in Figs.~\ref{fig:rp1} and \ref{fig:rp2}.

### 2019-12-09 rainbowCAM.tex
reviewed WKB section and made minor changes to wording and referencing

@@
 
- \subsection{Quasinormal modes and Regge poles}
+ \subsection{Quasinormal modes and Regge poles}\label{subsec:QNMs_RPs}
  Mathematically, there is a close relationship between quasinormal modes and Regge poles; they are both sets of poles of the scattering matrix.
@@
  \includegraphics[scale=0.50]{RP_R_6_2Mw_3_16_s_0_s_2}
-\caption{\label{RP_approx_2Mw_3_6_s_1} The Regge poles $\lambda_n(\omega)$ for the scalar field (empty markers) and for the axial gravitational waves (filled markers). %We assume $2M =1$.
+\caption{\label{RP_R6_approx_2Mw_3_6_s_1} The Regge poles $\lambda_n(\omega)$ for the scalar field (empty markers) and for the axial gravitational waves (filled markers). %We assume $2M =1$.
 }
@@
  \includegraphics[scale=0.50]{RP_R_2_dot_26_2Mw_3_6_s_0_s_2}
-\caption{\label{RP_approx_2Mw_3_6_s_1}  The Regge poles $\lambda_n(\omega)$ for the scalar field (empty markers) and for the axial gravitational waves (filled markers). %We assume $2M =1$.
+\caption{\label{RP_R226_approx_2Mw_3_6_s_1}  The Regge poles $\lambda_n(\omega)$ for the scalar field (empty markers) and for the axial gravitational waves (filled markers). %We assume $2M =1$.
 }
@@
  \subsection{The WKB approximation}
- \tom{Tom to review this section}
-
-To investigate the relationship between the qualitative features of the effective potential (Fig.~\ref{fig:Veff}) and the three branches of Regge poles revealed in Sec.~\ref{subsec:results}, we now employ the WKB method, with a view of obtain an approximation that is valid at high frequencies ($M\omega \rightarrow \infty$).
+
+To investigate the relationship between the qualitative features of the effective potential (Fig.~\ref{fig:Veff}) and the three branches of Regge poles revealed in Sec.~\ref{subsec:results1}, we now employ the WKB method, with a view to obtaining an approximation that is valid at high frequencies ($M\omega \rightarrow \infty$).
 
 Here we follow the approach of Zhang, Wu and Leung~\cite{Zhang:2011pq}, who applied the WKB method to determine the axial \textit{w}-modes of a variety of stellar models.
-Here, we adapt the method to obtain analytical approximations for the ``broad resonances'' for waves on a stellar background.
+We adapt their method to obtain analytical approximations for the ``broad resonances'' for massless waves on a stellar background.
 The starting point is with the radial equation (\ref{H_Radial_equation}) with either the effective potential for the scalar field (\ref{Inside_Potentiel}), or for axial gravitational perturbations (\ref{RW_Potentiel_axialGW}).
@@
 It has been shown \cite{Zhang:2011pq} that the asymptotic expressions of $\phireg$ and $\phiout$ can be derived in asymptotic regions, by using the standard WKB approximation.
-In the high-frequency limit, the interior solution of Eq.~(\ref{H_Radial_equation}) is (see Refs \ldots \sam{Please fill this in})
+In the high-frequency limit, the interior solution of Eq.~(\ref{H_Radial_equation}) is (see Ref.~\cite{Zhang:2011pq})
 \begin{equation}\label{Approx_origin}
@@
 \end{equation}
-where $j_{\lambda-1/2}(\cdot)$ is the spherical Bessel function of the first kind and
+where $j_{\lambda-1/2}(\cdot)$ is the spherical Bessel function of the first kind. In addition
 \begin{equation}
@@
 and $\mathcal{R}$ is a reflection coefficient with the definition given in Ref.~\cite{Berry_1982}.
-Because the potential has a direct discontinuity at the surface of the compact body (see.
-Refs \cite{Zhang:2011pq,Berry_1982} for more details), we have for our model (\textit{i.e.}, a compact body with a constant density)
+Because the potential has a direct discontinuity at the surface of the compact body (see. Refs \cite{Zhang:2011pq,Berry_1982} for more details), we have for our model
+%
 \begin{equation}\label{R_reflection_1}
@@
 \end{eqnarray}
-where $\Delta V$ is the discontinuity in the effective potential at the surface, defined in Eq.~(\ref{def:DeltaV}), and the $+$ ($-$) sign is chosen for scalar field (axial gravitational wave) cases.
+where $\Delta V$ is the discontinuity in the effective potential at the surface, defined in Eq.~(\ref{def:DeltaV}), and the $+$ ($-$) sign denotes the scalar (axial gravitational wave) case.
 
@@
 %\end{equation}
-Now, by inserting the high frequency approximation for $j_{\lambda-1/2} (\omega r_*)$ into Eq.~\eqref{Approx_origin} \cite{nist},
+Inserting the high frequency approximation for $j_{\lambda-1/2} (\omega r_*)$ into Eq.~\eqref{Approx_origin} we obtain \cite{nist},
 \begin{equation}\label{Approx_origin_bis}
-  \phi^{}_{\omega,\lambda-1/2} \underset{\omega \to \infty}{\approx} - \sin\left(\frac{\left(\lambda-1/2\right)\pi}{2}-\omega r_*\right)\quad\quad 0\leq r_*\leq R_*
-\end{equation}
-and Eq. \eqref{Approx_infinity} into the condition  \eqref{Wronskian}, we obtain
+  \phi^{}_{\omega,\lambda-1/2} \underset{\omega \to \infty}{\approx} - \sin\left(\frac{\left(\lambda-1/2\right)\pi}{2}-\omega r_*\right)\quad\quad 0\leq r_*\leq R_*.
+\end{equation}
+Substituting Eq. \eqref{Approx_infinity} into condition \eqref{Wronskian} we obtain
 \begin{equation}\label{WKB_1}
@@
 %
-We then solve Eq.~\eqref{WKB_1} to obtain
+We then solve Eq.~\eqref{WKB_1} to obtain the approximate Regge pole solution
 \begin{equation}\label{lambda_Approx}
@@
 %
-This corresponds to a series of Regge poles with spacing $|\Delta \lambda_n|\approx 2$ with the almost-constant imaginary part; these are the broad resonances shown in Figs.~\ref{fig:rp1} and \ref{fig:rp2}.
+This corresponds to a series of Regge poles with spacing $|\Delta \lambda_n|\approx 2$ and an almost-constant imaginary part; these are the broad resonances shown in Figs.~\ref{fig:rp1} and \ref{fig:rp2}.
 The formula also correctly accounts for the alternating sequence of the scalar-field and axial-GW modes.

### 2019-12-11 rainbowCAM.tex
Some typos are coorected, the captions of the plots (5-6-7) are modified, the location of plots are rearranged and my email sheffield restored (i find it class)

@@
-\documentclass[aps,prd,longbibliography,reprint,twocolumn,amsmath,amssymb,amsfonts,showpacs,superscriptaddress]{revtex4-1}%reprint
+%\documentclass[aps,prd,longbibliography,reprint,twocolumn,amsmath,amssymb,amsfonts,showpacs,superscriptaddress]{revtex4-1}%reprint
+\documentclass[aps,prd,longbibliography,reprint,twocolumn,amsmath,amssymb,amsfonts,showpacs,footnote,superscriptaddress]{revtex4-1}%reprint
 
@@
 \renewcommand{\arraystretch}{1.3} % espace entre les lignes de la table
-%\setlength{\tabcolsep}{.3cm} % espace entre les colonnes de la table
+%\setlength{\tabcolsep}{0.3pt} % espace entre les colonnes de la table
 
@@
 
-\author{Mohamed \surname{Ould~El~Hadj}}
-\email{med.ouldelhadj@gmail.com}
+\author{Mohamed \surname{Ould~El~Hadj}}\email{m.ouldelhadj@sheffield.ac.uk}
 
@@
 \section{Introduction}
-
-Change !
 
@@
 % \nonumber % Remove numbering (before each equation)
- \phi_{\omega_\ell}(r)&=&\left(\frac{r}{2M}-1\right)^{i 2M\omega} \,e^{i\omega r} \sum_{n,=0}^{+\infty}a_n\left(1-\frac{b}{r}\right)^n \nonumber \\
-                      &=& e^{i\omega r_*(r)}\sum_{n,=0}^{+\infty}a_n\left(1-\frac{b}{r}\right)^n
+ \phi_{\omega_\ell}(r)&=&\left(\frac{r}{2M}-1\right)^{i 2M\omega} \,e^{i\omega r} \sum_{n=0}^{+\infty}a_n\left(1-\frac{b}{r}\right)^n \nonumber \\
+                      &=& e^{i\omega r_*(r)}\sum_{n=0}^{+\infty}a_n\left(1-\frac{b}{r}\right)^n
 \end{eqnarray}
@@
  \includegraphics[scale=0.50]{RP_R_6_2Mw_3_16_s_0_s_2}
-\caption{\label{RP_R6_approx_2Mw_3_6_s_1} The Regge poles $\lambda_n(\omega)$ for the scalar field (empty markers) and for the axial gravitational waves (filled markers). %We assume $2M =1$.
+\caption{\label{RP_R6_approx_2Mw_3_6_s_1} The Regge poles $\lambda_n(\omega)$ for the scalar field (unfilled markers) and for the axial gravitational waves (filled markers). %We assume $2M =1$.
 }
@@
  \includegraphics[scale=0.50]{RP_R_2_dot_26_2Mw_3_6_s_0_s_2}
-\caption{\label{RP_R226_approx_2Mw_3_6_s_1}  The Regge poles $\lambda_n(\omega)$ for the scalar field (empty markers) and for the axial gravitational waves (filled markers). %We assume $2M =1$.
+\caption{\label{RP_R226_approx_2Mw_3_6_s_1}  The Regge poles $\lambda_n(\omega)$ for the scalar field (unfilled markers) and for the axial gravitational waves (filled markers). %We assume $2M =1$.
 }
@@
 \begin{table}[htp]
+\fontsize{5.}{10}
 \begin{threeparttable}[htp]
-%\captionsetup{font=small}
+\captionsetup{font=small}
 \caption{\label{tab:table4} The lowest Regge poles $\lambda_{n}(\omega)$ for the axial gravitational waves. The radius of the compact bodies is $R = 2.26M$.}
@@
 \section{Scattering and CAM theory}
-In this section we calculate the scattering cross section $d\sigma / d\Omega$ by means of the Complex Angular Momentum (CAM) method, and we compare with results obtained in the standard way from a partial-wave series \cite{Dolan:2017rtj}.
+In this section we calculate the scattering cross section $d\sigma / d\Omega$ by means of the CAM method, and we compare with results obtained in the standard way from a partial-wave series \cite{Dolan:2017rtj}.
 
@@
 
-Figures \ref{S_0_R_6_2Mw_3_Exact_vs_CAM}, \ref{S_0_R_6_2Mw_16_Exact_vs_CAM}, \ref{S_0_R_2-dot-26_2Mw_3_Exact_vs_CAM}, \ref{S_0_R_2-dot-26_2Mw_6_Exact_vs_CAM}, \ref{Rainbow_Cross_Section_R_6_2Mw_16}, and \ref{Diff_Contribution_Cross_Section_R_2-dot-26_2Mw_6} show a selection of results for the scattering cross section $d\sigma / d\Omega$ computed with the CAM method, and compared with results from the standard partial-wave method.
-As in Sec.~\ref{subsec:results1}, we focus on two cases: a neutron-star-like object with $R/M = 6$, and an Ultra-Compact Object with $R/M = 2.26$.
-
-Figure \ref{S_0_R_6_2Mw_3_Exact_vs_CAM} demonstrates that the CAM cross section approaches the partial-wave cross section as (i) successively more Regge poles are included in the sum (\ref{CAM_Scalar_Scattering_amp_decomp_RP}), and (ii) the background-integral contributions (\ref{CAM_Scalar_Scattering_amp_decomp_Background}) are included.
-The first plot shows that, at a `low' frequency of $M \omega = 3/2$ for the neutron star model ($R/M = 6$), taking a sum over just \emph{two} Regge poles in Eq.~(\ref{CAM_Scalar_Scattering_amp_decomp_RP}) captures the crude features of the cross section.
-The final plot shows that a cross section calculated from a sum of $15$ Regge poles and the background integral is indistinguishable (on the plot) from the partial-wave sum.
-
-\begin{figure*}%[h!]
+\begin{figure*}[htp!]
  \includegraphics[scale=0.50]{Scattering_Cross_Section_R_6_2Mw_3}
+  \vspace*{-0.3cm}
 \caption{\label{S_0_R_6_2Mw_3_Exact_vs_CAM} The scalar cross section of a compact bodies for $2M\omega=3$ and $R=6M$, its Regge pole approximation and the background integral contribution.
@@
 \end{figure*}
+
+\begin{figure*}[htp!]
+ \includegraphics[scale=0.50]{Scattering_Cross_Section_R_6_2Mw_16}
+ \vspace*{-0.3cm}
+\caption{\label{S_0_R_6_2Mw_16_Exact_vs_CAM} The scalar cross section of a compact bodies for $2M\omega=16$ and $R=6M$, its Regge pole approximation and the background integral contribution.
+The plots show the effect of including successively more Regge poles (plots 1--3).
+In the final plot, the background integral is added, giving a cross section which agrees well with the (regularized) partial-wave sum.}
+\end{figure*}
+
+\begin{figure*}[htp]
+\centering
+ \includegraphics[scale=0.50]{Scattering_Cross_Section_R_2-dot-26_2Mw_3}
+  \vspace*{-0.3cm}
+\caption{\label{S_0_R_2-dot-26_2Mw_3_Exact_vs_CAM} The scalar cross section of a very compact bodies for $2M\omega=3$ and $R=2.26M$ and its Regge pole approximation.
+The plots show the effect of including successively more Regge poles (plots 1--3).
+In the final plot, The sum over Regge poles gives a cross section which agrees well with the (regularized) partial-wave sum for intermediate and large values of the scattering
+angle.}
+\end{figure*}
+
+\begin{figure*}[htp]
+\centering
+ \includegraphics[scale=0.50]{Scattering_Cross_Section_R_2-dot-26_2Mw_6}
+  \vspace*{-0.3cm}
+\caption{\label{S_0_R_2-dot-26_2Mw_6_Exact_vs_CAM} The scalar cross section of a very compact bodies for $2M\omega=6$ and $R=2.26M$ and its Regge pole approximation.
+The plots show the effect of including successively more Regge poles (plots 1--3).
+In the final plot, The sum over Regge poles gives a cross section which agrees well with the (regularized) partial-wave sum for intermediate and large values of the scattering
+angle.}
+\end{figure*}
+
+\begin{figure}[htp]
+\centering
+ \includegraphics[scale=0.50]{Rainbow_Cross_Section_R_6_2Mw_16}
+  \vspace*{-0.3cm}
+\caption{\label{Rainbow_Cross_Section_R_6_2Mw_16} Rainbow scattering for compact bodies for $2M\omega=16$ and $R=6M$, its Regge pole approximation and different contributions of the sum over Regge poles.}
+\end{figure}
+
+\begin{figure}[htp]
+\centering
+ \includegraphics[scale=0.50]{Diff_Contribution_Cross_Section_R_2-dot-26_2Mw_6}
+  \vspace*{-0.3cm}
+\caption{\label{Diff_Contribution_Cross_Section_R_2-dot-26_2Mw_6} Rainbow scattering for compact bodies for $2M\omega=16$ and $R=2.26M$, its Regge pole approximation and different contributions of the sum over Regge poles.}
+\end{figure}
+
+Figures \ref{S_0_R_6_2Mw_3_Exact_vs_CAM}, \ref{S_0_R_6_2Mw_16_Exact_vs_CAM}, \ref{S_0_R_2-dot-26_2Mw_3_Exact_vs_CAM}, \ref{S_0_R_2-dot-26_2Mw_6_Exact_vs_CAM}, \ref{Rainbow_Cross_Section_R_6_2Mw_16}, and \ref{Diff_Contribution_Cross_Section_R_2-dot-26_2Mw_6} show a selection of results for the scattering cross section $d\sigma / d\Omega$ computed with the CAM method, and compared with results from the standard partial-wave method.
+As in Sec.~\ref{subsec:results1}, we focus on two cases: a neutron-star-like object with $R/M = 6$, and an Ultra-Compact Object with $R/M = 2.26$.
+
+Figure \ref{S_0_R_6_2Mw_3_Exact_vs_CAM} demonstrates that the CAM cross section approaches the partial-wave cross section as (i) successively more Regge poles are included in the sum (\ref{CAM_Scalar_Scattering_amp_decomp_RP}), and (ii) the background-integral contributions (\ref{CAM_Scalar_Scattering_amp_decomp_Background}) are included.
+The first plot shows that, at a `low' frequency of $M \omega = 3/2$ for the neutron star model ($R/M = 6$), taking a sum over just \emph{two} Regge poles in Eq.~(\ref{CAM_Scalar_Scattering_amp_decomp_RP}) captures the crude features of the cross section.
+The final plot shows that a cross section calculated from a sum of $15$ Regge poles and the background integral is indistinguishable (on the plot) from the partial-wave sum.
 
@@
 Finally, with 81 Regge poles and the background integral included, the CAM result is again indistinguishable from the partial-wave result on the plot.
-
-\begin{figure*}%[h!]
- \includegraphics[scale=0.50]{Scattering_Cross_Section_R_6_2Mw_16}
-\caption{\label{S_0_R_6_2Mw_16_Exact_vs_CAM} The scalar cross section of a compact bodies for $2M\omega=16$ and $R=6M$, its Regge pole approximation and the background integral contribution.}
-\end{figure*}
 
@@
 
-\begin{figure*}%[h!]
-\centering
- \includegraphics[scale=0.50]{Scattering_Cross_Section_R_2-dot-26_2Mw_3}
-\caption{\label{S_0_R_2-dot-26_2Mw_3_Exact_vs_CAM} The scalar cross section of a very compact bodies for $2M\omega=3$ and $R=2.26M$ and its Regge pole approximation.}
-\end{figure*}
-
 Figure \ref{S_0_R_2-dot-26_2Mw_6_Exact_vs_CAM} shows the cross section for an UCO at the higher frequency of $M \omega = 8$.
@@
 
-\begin{figure*}%[h!]
-\centering
- \includegraphics[scale=0.50]{Scattering_Cross_Section_R_2-dot-26_2Mw_6}
-\caption{\label{S_0_R_2-dot-26_2Mw_6_Exact_vs_CAM} The scalar cross section of a very compact bodies for $2M\omega=6$ and $R=2.26M$ and its Regge pole approximation.}
-\end{figure*}
-
 Figures \ref{Rainbow_Cross_Section_R_6_2Mw_16} and \ref{Diff_Contribution_Cross_Section_R_2-dot-26_2Mw_6} show the relative magnitudes of the contributions from the different branches of Regge poles.
@@
 
-\begin{figure}%[h!]
-\centering
- \includegraphics[scale=0.50]{Rainbow_Cross_Section_R_6_2Mw_16}
-\caption{\label{Rainbow_Cross_Section_R_6_2Mw_16} Rainbow scattering for compact bodies for $2M\omega=16$ and $R=6M$, its Regge pole approximation and different contributions of the sum over Regge poles.}
-\end{figure}
-
 For $R/M = 2.26$ (Fig.~\ref{Diff_Contribution_Cross_Section_R_2-dot-26_2Mw_6}), however, the amplitudes  from the three branches are comparable in magnitude, but their sum is several orders-of-magnitude smaller.
 In other words, there is some delicate cancellation occurring between the contributions from the branches, suggesting that the CAM approach used here is not an efficient method for computing the cross section in this case.
-
-\begin{figure}%[h!]
-\centering
- \includegraphics[scale=0.50]{Diff_Contribution_Cross_Section_R_2-dot-26_2Mw_6}
-\caption{\label{Diff_Contribution_Cross_Section_R_2-dot-26_2Mw_6} Rainbow scattering for compact bodies for $2M\omega=16$ and $R=2.26M$, its Regge pole approximation and different contributions of the sum over Regge poles.}
-\end{figure}
 
@@
 \acknowledgments
-M.
-O.
-E.
-H.
-wish to thank Antoine Folacci for various discussions concerning this work.
+M. O. E. H. wishes to thank Antoine Folacci for various discussions concerning this work and thanks Sam R. Dolan for his kind
+invitation to the University of Sheffield.
 T.S.~acknowledges financial support from EPSRC.

### 2019-12-12 rainbowCAM.tex
Tinkering.

--- 2019-12-09 rainbowCAM.tex
@@
 
-Change !
-
 The time-independent scattering of planar waves in the gravitational field of a compact body has been studied in some detail since the 1960s \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970}.
@@
 The radial function $h(r)$ is $C^0$ at the surface of the star $r=R$ (i.e.~continuous but not differentiable), and the radial function $f(r)$ is $C^1$ there (i.e.~once-differentiable).
-%In the polytropic cases $n > 0$, the functions are more regular \sam{can we make a precise statement?}\tom{I will write something here} at the surface, but not $C^\infty$ (i.e.~not smooth).
-As we shall see, the breakdown of smoothness leads to consequences for the Regge pole spectrum.
-For a general polytrope with $n>0$ and $m$ the smallest integer such that $m \geq n$, $h(r)$ is $C^m$ and $f(r)$ is $C^{m+1}$ at the surface. 
-%\tom{This can be seen from equations relating $(m,\rho,p,f,h)$ and by noting $\rho \sim a(R-r)^n$ at the surface \cite{Lindblom:1983ps} but we don't mention these.}
+In the polytropic cases $n > 0$, the functions are more regular \sam{can we make a precise statement?}\tom{I will write something here} at the surface, but not $C^\infty$ (i.e.~not smooth).
 As we shall see, the breakdown of smoothness leads to consequences for the Regge pole spectrum.
@@
 \begin{equation}\label{lambda_Approx}
-  \lambda_n \approx \frac{2 \omega R_*}{\pi}-\left(2n \pm \frac{1}{2}\right)+\frac{2 i}{\pi} \ln\left(\frac{2 R^2 \omega}{\sqrt{3M (R-2M)}}\right) .
-\end{equation}
-%
+  \lambda_n \approx \frac{2 \omega R_*}{\pi}-\left(2n \pm \frac{1}{2}\right)+\frac{i}{\pi} \ln\left(\frac{2 R^2 \omega}{\sqrt{3M (R-2M)}}\right) .
+\end{equation}
+\sam{Please double-check this formula is correct for both scalar (+) and axial GW (-) cases.}
 This corresponds to a series of Regge poles with spacing $|\Delta \lambda_n|\approx 2$ with the almost-constant imaginary part; these are the broad resonances shown in Figs.~\ref{fig:rp1} and \ref{fig:rp2}.

### 2019-12-12 rainbowCAM.tex
I worked on the Introduction.

--- 2019-12-11 rainbowCAM.tex
@@
 A substantial literature has developed on \emph{black hole scattering}, focussing on the canonical scenario of a planar wave of circular frequency $\omega$ and spin $s$ \cite{Chrzanowski:1976jb} impinging upon a black hole of mass $M$ in vacuum \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970, Mashhoon:1973zz,Fabbri:1975,Sanchez:1977vz,MatznerRyan1978,Handler:1980un,Matzner:1985rjn,Futterman:1988ni,Andersson:1995vi,Glampedakis:2001cx,Dolan:2006vj,Dolan:2007ut,Dolan:2008kf,Crispino:2009xt,Cotaescu:2014jca,Gussmann:2016mkp}.
-A dimensionless parameter
+The dimensionless parameter
 $
@@
 $
-encapsulates the ratio of the gravitational radius $r_g = 2GM/c^2$ to the wavelength $\lambda$ (we adopt geometric units such that $G=c=1$).
-The long wavelength ($M \omega \ll 1$), short wavelength ($M \omega \gg 1$) and intermediate regimes have been studied with a combination of perturbative \cite{DeLogi:1977dp,Dolan:2007ut,Guadagnini:2008ha,Sorge:2015yoa}, semi-classical \cite{Matzner:1985rjn, Anninos:1992ih} and numerical methods.
+encapsulates the ratio of the gravitational radius $r_g = 2GM/c^2$ to the wavelength $\lambda$ (herein we adopt geometric units such that $G=c=1$).
+The long-wavelength ($M \omega \ll 1$), short-wavelength ($M \omega \gg 1$) and intermediate regimes have been studied with a combination of perturbative \cite{DeLogi:1977dp,Dolan:2007ut,Guadagnini:2008ha,Sorge:2015yoa}, semi-classical \cite{Matzner:1985rjn, Anninos:1992ih} and numerical methods.
 The $s = 0$ (scalar) \cite{Matzner:1968,Sanchez:1977vz,Andersson:1995vi,Glampedakis:2001cx,Leite:2019eis}, $s=1/2$ (fermion) \cite{Dolan:2006vj,Cotaescu:2014jca}, $s=1$ (electromagnetic) \cite{Fabbri:1975, Crispino:2009xt, Crispino:2015gua} and $s=2$ (gravitational) cases \cite{MatznerRyan1978,Handler:1980un,Dolan:2008kf} have all been addressed.
@@
 Time-independent scattering by a compact body of radius $R$ with a regular centre, such as a neutron star or white dwarf, has received comparatively less attention.
-In such a scenario, an electromagnetic wave will not penetrate inside the compact body; but on the other hand, a gravitational wave will pass through the body without impediment from the matter distribution.
+In such a scenario, an electromagnetic wave will not penetrate far inside the compact body; but on the other hand, a gravitational wave will pass through the body without much impediment from the matter distribution.
 Similarly, a neutron star is expected to be substantially transparent to neutrinos.
-However, even in these cases where the coupling to matter is negligible, the incident wave is still scattered by the influence of the spacetime curvature.
-Recent work \cite{Dolan:2017rtj, Stratton:2019deq} explored the \emph{rainbow scattering} phenomenon that arises at short wavelengths, due to a stationary point in the geodesic deflection function associated with a ray that passes somewhat inside the body.
-In principle, the rainbow angle is a diagnostic of the matter distribution of the body, and thus its nuclear equation of state.
-Indeed, in the 1970s, experimental data on rainbows in nucleon-nucleon scattering experiments was used to constrain models of the nuclear potential.
-
-Other recent works have examined scattering from a compact object with an absorbing surface \cite{Nambu:2019sqn}; and scattering simulations using finite-element-method codes \cite{He:2019orl}.
-
-The tenuity (inverse compactness) .
+Even in cases where the coupling to matter is negligible, the incident wave will nevertheless be scattered by the influence of the spacetime curvature.
+Thus, the resulting scattering pattern depends on $M\omega$, on the internal structure of the body, and on its inverse compactness or \emph{tenuity} $R/M$.
+Typical values of the tenuity are: $R/M \sim 6$ for neutron stars, $\sim 1.4-9.4 \times 10^3$ for white dwarfs, $4.7 \times 10^5$ for the Sun, and $1.4 \times 10^9$ for Earth.
+More speculatively, we shall also consider the case of (hypothetical) Ultra Compact Objects (UCO), whose tenuity is bounded from below by the Buchdahl bound of $R / M = 9/4$.
+
+Studies of black hole scattering typically involve the calculation of scattering amplitude(s) via partial-wave expansions.
+A powerful approach for resumming these partial-wave expansions is provided by so-called Complex Angular Momentum (CAM) techniques.
+In the CAM approach, the sum over partial waves is replaced by an integral, and the contour of integration is deformed into  the complex-angular-momentum plane such that one collects a sum over the residues of simple poles: these are the so-called \emph{Regge poles}.
+
+CAM theory, originally developed for high-energy physics applications, has been successfully applied to black hole scattering scenarios.
+In 1994, Andersson and Thylwe \cite{Andersson:1994rk} described the scattering of scalar waves by a Schwarzschild BH by utilising CAM techniques, and they showed that, in this case, Regge poles are associated with ``surface waves'' localised near the unstable light ring at $r=3M$ (later it was shown that the corresponding quasinormal modes are Breit-Wigner type resonances generated by these surface waves \cite{Decanini:2002ha}).
+Recently, Folacci and Ould Elhadj have shown that CAM methods can be used for precise numerical calculations of scattering cross sections of scalar fields, electromagnetic fields \cite{Folacci:2019cmc} and gravitational waves  \cite{Folacci:2019vtt} on the Schwarzschild spacetime.
+Moreover, they have obtained an approximate  formula (see Sec.~IV in Ref.~\cite{Folacci:2019vtt}) that accurately describes both the `orbiting' and `glory' oscillations in black hole scattering cross sections in the short-wavelength regime.
+This approximation arises from applying WKB theory to characterise the Regge pole with the smallest imaginary part, and its residue.
+\sam{Mohamed, please correct this if wrong.}
+
+CAM techniques have not yet been applied to compact-body scattering, it appears, with one notable exception: in 1991, Chandrasekhar and Ferrari \cite{ChandrasekharIV:1992ey} examined the Regge pole spectra for relativistic stellar models.
+Their study focussed on resonant modes: poles with small imaginary parts corresponding to trapped $w$-modes or fluid modes, and it employed Complex Angular Momentum (CAM) theory to calculate the flow of gravitational energy through a star.
+
+ It seems reasonable to expect that CAM may also aid in our understanding of other compact objects such as UCOs and neutron stars.
+With this in mind, we now turn our attention to calculating the Regge pole spectrum for compact bodies.
+
+It was recently shown \cite{Dolan:2017rtj, Stratton:2019deq} that time-independent scattering by compact bodies generates (in principle) the \emph{rainbow scattering} phenomenon in the short wavelength regime ($M \omega \gg 1$).
+The rainbow scattering phenomenon is linked to the formation of a cusp caustic in the incident wavefront (see Fig.~1 in Ref.~\cite{Stratton:2019deq}), and to the stationary point in the geodesic deflection function associated with a ray (that is, a null geodesic) that passes somewhat inside the body.
+For dilute bodies, such as stars and white dwarfs, the cusp caustic forms at a distance $d \sim R^2 / (4M)$ downstream of the body, and the rainbow angle is $\theta_r \approx 4M/R$ (e.g.~for the Sun, $d \approx 550 \, \text{a.u.}$ and $\theta_r \approx 1.8 \, \text{arcsec}$).
+For compact bodies such as neutron stars, however, the cusp caustic forms near the surface of the body, and the rainbow angle is sizable ($\theta_r \gtrsim 59.6^\circ$ for $R/M = 6$; see Table I in Ref.~\cite{Stratton:2019deq}).
+In this case, the rainbow angle is -- in principle at least -- a diagnostic of the matter distribution within the body and thus its nuclear equation of state.
+
+Other recent works on the theme of scattering by a compact body include studies of: scattering by compact objects with an absorbing surface \cite{Nambu:2019sqn}; time-domain simulations with finite-element-method methods \cite{He:2019orl}; gravitationally-induced interference patterns in flavour oscillations in neutrino astronomy \cite{Alexandre:2018crg}; and the use of continuous sources of gravitational waves to probe stellar structure \cite{Marchant:2019swq}.
+
+ \cite{Folacci:2018sef} \cite{Decanini:2011xi, Decanini:2011xw}
+
+to study time-independent scattering by a compact body.
+
+More literature exists on Regge pole theory applied to black hole scattering, for example They .
+Later,  We see here that CAM theory is a powerful approach to BH physics, that provides a clear and robust physical picture.
 
@@
 \cite{Leite:2017zyb,Nambu:2019sqn, Folacci:2019vtt,}.
-
-As far as we know, the only published study into Regge pole spectra for relativistic stellar models was that of Chandrasekhar and Ferrari in 1991 \cite{ChandrasekharIV:1992ey}.
-%They used Regge pole theory to calculate the flow of gravitational energy through a star.
-They restricted their attention to resonant modes, i.e.
-poles with small imaginary parts.
-For the axial sector these are only present for UCOs.
-For the polar sector the situation is more complicated, as there are long lived fluid pulsation modes.
-They considered resonant modes (poles with small imaginary parts corresponding to trapped $w$-modes or fluid modes), and used CAM theory to calculate the flow of gravitational energy through a star.
-More literature exists on Regge pole theory applied to black hole scattering, for example Andersson and Thylwe have described scattering of scalar waves by a Schwarzschild BH utilising CAM techniques \cite{Andersson:1994rk}.
-They associate the BH Regge poles with ``surface waves'' localised near the unstable light ring at $r=3M$.
-Later, Decanini, Folacci and Jensen showed that the Schwarzschild BH QNMs are in fact Breit-Wigner type resonances generated by said surface waves \cite{Decanini:2002ha}.
-We see here that CAM theory is a powerful approach to BH physics, that provides a clear and robust physical picture.
-It seems reasonable to expect that CAM may also aid in our understanding of other compact objects such as UCOs and neutron stars.
-With this in mind, we now turn our attention to calculating the Regge pole spectrum for compact bodies.
 
@@
 
+Remarkably, in the 1970s, experimental data on rainbows in nucleon-nucleon scattering experiments was used to constrain models of the nuclear potential.
+
 \acknowledgments

### 2019-12-12 rainbowCAM.tex
Further work on the Intro.

@@
 The time-independent scattering of planar waves in the gravitational field of a compact body has been studied in some detail since the 1960s \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970}.
-A substantial literature has developed on \emph{black hole scattering}, focussing on the canonical scenario of a planar wave of circular frequency $\omega$ and spin $s$ \cite{Chrzanowski:1976jb} impinging upon a black hole of mass $M$ in vacuum \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970, Mashhoon:1973zz,Fabbri:1975,Sanchez:1977vz,MatznerRyan1978,Handler:1980un,Matzner:1985rjn,Futterman:1988ni,Andersson:1995vi,Glampedakis:2001cx,Dolan:2006vj,Dolan:2007ut,Dolan:2008kf,Crispino:2009xt,Cotaescu:2014jca,Gussmann:2016mkp}.
-The dimensionless parameter
+A substantial literature has accumulated on \emph{black hole scattering}, focussing on the canonical scenario of a planar wave of circular frequency $\omega$ and spin $s$ \cite{Chrzanowski:1976jb} impinging upon a black hole of mass $M$ in vacuum \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970, Mashhoon:1973zz,Fabbri:1975,Sanchez:1977vz,MatznerRyan1978,Handler:1980un,Matzner:1985rjn,Futterman:1988ni,Andersson:1995vi,Glampedakis:2001cx,Dolan:2006vj,Dolan:2007ut,Dolan:2008kf,Crispino:2009xt,Cotaescu:2014jca,Gussmann:2016mkp}.
+A dimensionless parameter
 $
@@
 $
-encapsulates the ratio of the gravitational radius $r_g = 2GM/c^2$ to the wavelength $\lambda$ (herein we adopt geometric units such that $G=c=1$).
+encapsulates the ratio of the gravitational radius $r_g = 2GM/c^2$ to the wavelength $\lambda$; herein we adopt geometric units such that $G=c=1$.
 The long-wavelength ($M \omega \ll 1$), short-wavelength ($M \omega \gg 1$) and intermediate regimes have been studied with a combination of perturbative \cite{DeLogi:1977dp,Dolan:2007ut,Guadagnini:2008ha,Sorge:2015yoa}, semi-classical \cite{Matzner:1985rjn, Anninos:1992ih} and numerical methods.
@@
 
-Time-independent scattering by a compact body of radius $R$ with a regular centre, such as a neutron star or white dwarf, has received comparatively less attention.
+Time-independent scattering by a compact body of radius $R$ with a regular centre, such as a neutron star or white dwarf, has received less attention, by comparison.
 In such a scenario, an electromagnetic wave will not penetrate far inside the compact body; but on the other hand, a gravitational wave will pass through the body without much impediment from the matter distribution.
@@
 Even in cases where the coupling to matter is negligible, the incident wave will nevertheless be scattered by the influence of the spacetime curvature.
-Thus, the resulting scattering pattern depends on $M\omega$, on the internal structure of the body, and on its inverse compactness or \emph{tenuity} $R/M$.
+Thus, the resulting scattering pattern depends not just on $M\omega$, but also on the internal structure of the body, and on its inverse compactness or \emph{tenuity}, $R/M$.
 Typical values of the tenuity are: $R/M \sim 6$ for neutron stars, $\sim 1.4-9.4 \times 10^3$ for white dwarfs, $4.7 \times 10^5$ for the Sun, and $1.4 \times 10^9$ for Earth.
-More speculatively, we shall also consider the case of (hypothetical) Ultra Compact Objects (UCO), whose tenuity is bounded from below by the Buchdahl bound of $R / M = 9/4$.
+More speculatively, we shall also consider here the case of (hypothetical) \emph{ultra-compact objects} (UCOs), whose tenuity is bounded from below by the Buchdahl bound of $R / M = 9/4$.
 
@@
 Moreover, they have obtained an approximate  formula (see Sec.~IV in Ref.~\cite{Folacci:2019vtt}) that accurately describes both the `orbiting' and `glory' oscillations in black hole scattering cross sections in the short-wavelength regime.
-This approximation arises from applying WKB theory to characterise the Regge pole with the smallest imaginary part, and its residue.
-\sam{Mohamed, please correct this if wrong.}
-
-CAM techniques have not yet been applied to compact-body scattering, it appears, with one notable exception: in 1991, Chandrasekhar and Ferrari \cite{ChandrasekharIV:1992ey} examined the Regge pole spectra for relativistic stellar models.
-Their study focussed on resonant modes: poles with small imaginary parts corresponding to trapped $w$-modes or fluid modes, and it employed Complex Angular Momentum (CAM) theory to calculate the flow of gravitational energy through a star.
-
- It seems reasonable to expect that CAM may also aid in our understanding of other compact objects such as UCOs and neutron stars.
-With this in mind, we now turn our attention to calculating the Regge pole spectrum for compact bodies.
-
-It was recently shown \cite{Dolan:2017rtj, Stratton:2019deq} that time-independent scattering by compact bodies generates (in principle) the \emph{rainbow scattering} phenomenon in the short wavelength regime ($M \omega \gg 1$).
+This approximation arises from applying WKB theory to characterise the Regge pole with the smallest imaginary part, and its residue \sam{Mohamed, please correct this if wrong.}.
+An accurate approximation for the black hole absorption cross section has also been derived via an analysis of Regge poles \cite{Decanini:2011xi, Decanini:2011xw}.
+
+CAM techniques are yet to be applied to compact-body scattering, it appears, with one notable exception: in 1991, Chandrasekhar and Ferrari \cite{ChandrasekharIV:1992ey} examined the Regge pole spectra for relativistic stellar models.
+Their study focussed on resonant modes (poles with small imaginary parts corresponding to trapped $w$-modes or fluid modes), and it employed CAM theory to calculate the flow of gravitational energy through a star.
+It seems reasonable to expect that CAM can aid our understanding of other compact objects such as and neutron stars and UCOs, and this is our purpose below.
+
+There is a close relationship between Regge poles and quasi-normal modes (QNMs); both are sets of poles of the scattering matrix, with the latter lying in the complex-frequency plane.
+The excitation of black hole QNMs leads to distinctive signatures in time-dependent scattering scenarios.
+For example, in the immediate aftermath of a black hole merger, the perturbed black hole returns to a quiescent state via a `ringdown phase' in which its gravitational-wave signal is well described as a sum of quasinormal modes \cite{Giesler:2019uxc}.
+The QNM spectrum of compact bodies have been well-studied by several authors  \cite{Detweiler:1985zz, Kokkotas:1986gd, Chandrasekhar449, Kokkotas:1992ka, Leins:1993zz, Andersson:1995ez, Andersson1996}, and are reviewed in Ref.~\cite{Kokkotas:1999bd}.
+
+It was recently shown \cite{Dolan:2017rtj, Stratton:2019deq} that time-independent scattering by compact bodies generates (in principle) a \emph{rainbow scattering} phenomenon in the short wavelength regime ($M \omega \gg 1$).
 The rainbow scattering phenomenon is linked to the formation of a cusp caustic in the incident wavefront (see Fig.~1 in Ref.~\cite{Stratton:2019deq}), and to the stationary point in the geodesic deflection function associated with a ray (that is, a null geodesic) that passes somewhat inside the body.
-For dilute bodies, such as stars and white dwarfs, the cusp caustic forms at a distance $d \sim R^2 / (4M)$ downstream of the body, and the rainbow angle is $\theta_r \approx 4M/R$ (e.g.~for the Sun, $d \approx 550 \, \text{a.u.}$ and $\theta_r \approx 1.8 \, \text{arcsec}$).
-For compact bodies such as neutron stars, however, the cusp caustic forms near the surface of the body, and the rainbow angle is sizable ($\theta_r \gtrsim 59.6^\circ$ for $R/M = 6$; see Table I in Ref.~\cite{Stratton:2019deq}).
-In this case, the rainbow angle is -- in principle at least -- a diagnostic of the matter distribution within the body and thus its nuclear equation of state.
+For dilute bodies, such as stars and white dwarfs, the cusp caustic forms at a distance $d \sim R^2 / (4M)$ downstream of the body, and the rainbow angle is $\theta_r \approx 4M/R$ (e.g.~for the Sun, $d \approx 550 \, \text{a.u.}$ and $\theta_r \approx 1.8 \, \text{arcsec}$) \footnote{The rainbow angle $\theta_r \approx 4M/R$ is distinct from the Einstein ring angle of $\theta_E \approx \sqrt{4M/r}$}.
+For compact bodies such as neutron stars, however, the cusp caustic forms near the surface of the body, and the rainbow angle is large ($\theta_r \gtrsim 59.6^\circ$ for $R/M = 6$; see Table I in Ref.~\cite{Stratton:2019deq}).
+In this case, the rainbow angle is -- in principle at least -- a useful diagnostic of the matter distribution within the body and thus its nuclear equation of state.
 
@@
 
- \cite{Folacci:2018sef} \cite{Decanini:2011xi, Decanini:2011xw}
-
-to study time-independent scattering by a compact body.
-
-More literature exists on Regge pole theory applied to black hole scattering, for example They .
-Later,  We see here that CAM theory is a powerful approach to BH physics, that provides a clear and robust physical picture.
-
-Now describe the application of CAM methods to black holes, and its successes ... The aim of this work is to extend the methods to compact bodies.
-
-Describe QNMs - resonances in the time domain: \cite{Detweiler:1985zz, Kokkotas:1986gd, Chandrasekhar449, Kokkotas:1992ka, Leins:1993zz, Andersson:1995ez, Andersson1996} Review of QNMs: \cite{Kokkotas:1999bd}.
-Now describe how these are connected to Regge poles.
-
-Finally a paragraph on the connections to Mie scattering by a transparent sphere.
-
-\cite{Leite:2017zyb,Nambu:2019sqn, Folacci:2019vtt,}.
+Finally a paragraph on the connections to Mie scattering by a transparent sphere?
+
+\cite{Leite:2017zyb}
 

### 2019-12-12 rainbowCAM.tex
Some typos are corredcted, update plots 6-7 (legend), Paragraph before Eq 41 modified (please, find remark in the pdf)

--- 2019-12-12 rainbowCAM.tex
@@
 $
-encapsulates the ratio of the gravitational radius $r_g = 2GM/c^2$ to the wavelength $\lambda$ (herein we adopt geometric units such that $G=c=1$).
-The long-wavelength ($M \omega \ll 1$), short-wavelength ($M \omega \gg 1$) and intermediate regimes have been studied with a combination of perturbative \cite{DeLogi:1977dp,Dolan:2007ut,Guadagnini:2008ha,Sorge:2015yoa}, semi-classical \cite{Matzner:1985rjn, Anninos:1992ih} and numerical methods.
+encapsulates the ratio of the gravitational radius $r_g = 2GM/c^2$ to the wavelength $\lambda$ (we adopt geometric units such that $G=c=1$).
+The long wavelength ($M \omega \ll 1$), short wavelength ($M \omega \gg 1$) and intermediate regimes have been studied with a combination of perturbative \cite{DeLogi:1977dp,Dolan:2007ut,Guadagnini:2008ha,Sorge:2015yoa}, semi-classical \cite{Matzner:1985rjn, Anninos:1992ih} and numerical methods.
 The $s = 0$ (scalar) \cite{Matzner:1968,Sanchez:1977vz,Andersson:1995vi,Glampedakis:2001cx,Leite:2019eis}, $s=1/2$ (fermion) \cite{Dolan:2006vj,Cotaescu:2014jca}, $s=1$ (electromagnetic) \cite{Fabbri:1975, Crispino:2009xt, Crispino:2015gua} and $s=2$ (gravitational) cases \cite{MatznerRyan1978,Handler:1980un,Dolan:2008kf} have all been addressed.
@@
 Time-independent scattering by a compact body of radius $R$ with a regular centre, such as a neutron star or white dwarf, has received comparatively less attention.
-In such a scenario, an electromagnetic wave will not penetrate far inside the compact body; but on the other hand, a gravitational wave will pass through the body without much impediment from the matter distribution.
+In such a scenario, an electromagnetic wave will not penetrate inside the compact body; but on the other hand, a gravitational wave will pass through the body without impediment from the matter distribution.
 Similarly, a neutron star is expected to be substantially transparent to neutrinos.
-Even in cases where the coupling to matter is negligible, the incident wave will nevertheless be scattered by the influence of the spacetime curvature.
-Thus, the resulting scattering pattern depends on $M\omega$, on the internal structure of the body, and on its inverse compactness or \emph{tenuity} $R/M$.
-Typical values of the tenuity are: $R/M \sim 6$ for neutron stars, $\sim 1.4-9.4 \times 10^3$ for white dwarfs, $4.7 \times 10^5$ for the Sun, and $1.4 \times 10^9$ for Earth.
-More speculatively, we shall also consider the case of (hypothetical) Ultra Compact Objects (UCO), whose tenuity is bounded from below by the Buchdahl bound of $R / M = 9/4$.
-
-Studies of black hole scattering typically involve the calculation of scattering amplitude(s) via partial-wave expansions.
-A powerful approach for resumming these partial-wave expansions is provided by so-called Complex Angular Momentum (CAM) techniques.
-In the CAM approach, the sum over partial waves is replaced by an integral, and the contour of integration is deformed into  the complex-angular-momentum plane such that one collects a sum over the residues of simple poles: these are the so-called \emph{Regge poles}.
-
-CAM theory, originally developed for high-energy physics applications, has been successfully applied to black hole scattering scenarios.
-In 1994, Andersson and Thylwe \cite{Andersson:1994rk} described the scattering of scalar waves by a Schwarzschild BH by utilising CAM techniques, and they showed that, in this case, Regge poles are associated with ``surface waves'' localised near the unstable light ring at $r=3M$ (later it was shown that the corresponding quasinormal modes are Breit-Wigner type resonances generated by these surface waves \cite{Decanini:2002ha}).
-Recently, Folacci and Ould Elhadj have shown that CAM methods can be used for precise numerical calculations of scattering cross sections of scalar fields, electromagnetic fields \cite{Folacci:2019cmc} and gravitational waves  \cite{Folacci:2019vtt} on the Schwarzschild spacetime.
-Moreover, they have obtained an approximate  formula (see Sec.~IV in Ref.~\cite{Folacci:2019vtt}) that accurately describes both the `orbiting' and `glory' oscillations in black hole scattering cross sections in the short-wavelength regime.
-This approximation arises from applying WKB theory to characterise the Regge pole with the smallest imaginary part, and its residue.
-\sam{Mohamed, please correct this if wrong.}
-
-CAM techniques have not yet been applied to compact-body scattering, it appears, with one notable exception: in 1991, Chandrasekhar and Ferrari \cite{ChandrasekharIV:1992ey} examined the Regge pole spectra for relativistic stellar models.
-Their study focussed on resonant modes: poles with small imaginary parts corresponding to trapped $w$-modes or fluid modes, and it employed Complex Angular Momentum (CAM) theory to calculate the flow of gravitational energy through a star.
-
+However, even in these cases where the coupling to matter is negligible, the incident wave is still scattered by the influence of the spacetime curvature.
+Recent work \cite{Dolan:2017rtj, Stratton:2019deq} explored the \emph{rainbow scattering} phenomenon that arises at short wavelengths, due to a stationary point in the geodesic deflection function associated with a ray that passes somewhat inside the body.
+In principle, the rainbow angle is a diagnostic of the matter distribution of the body, and thus its nuclear equation of state.
+Indeed, in the 1970s, experimental data on rainbows in nucleon-nucleon scattering experiments was used to constrain models of the nuclear potential.
+
+Other recent works have examined scattering from a compact object with an absorbing surface \cite{Nambu:2019sqn}; and scattering simulations using finite-element-method codes \cite{He:2019orl}.
+
+The tenuity (inverse compactness) .
+
+Now describe the application of CAM methods to black holes, and its successes ... The aim of this work is to extend the methods to compact bodies.
+
+Describe QNMs - resonances in the time domain: \cite{Detweiler:1985zz, Kokkotas:1986gd, Chandrasekhar449, Kokkotas:1992ka, Leins:1993zz, Andersson:1995ez, Andersson1996} Review of QNMs: \cite{Kokkotas:1999bd}.
+Now describe how these are connected to Regge poles.
+
+Finally a paragraph on the connections to Mie scattering by a transparent sphere.
+
+\cite{Leite:2017zyb,Nambu:2019sqn, Folacci:2019vtt,}.
+
+As far as we know, the only published study into Regge pole spectra for relativistic stellar models was that of Chandrasekhar and Ferrari in 1991 \cite{ChandrasekharIV:1992ey}.
+%They used Regge pole theory to calculate the flow of gravitational energy through a star.
+They restricted their attention to resonant modes, i.e.
+poles with small imaginary parts.
+For the axial sector these are only present for UCOs.
+For the polar sector the situation is more complicated, as there are long lived fluid pulsation modes.
+They considered resonant modes (poles with small imaginary parts corresponding to trapped $w$-modes or fluid modes), and used CAM theory to calculate the flow of gravitational energy through a star.
+More literature exists on Regge pole theory applied to black hole scattering, for example Andersson and Thylwe have described scattering of scalar waves by a Schwarzschild BH utilising CAM techniques \cite{Andersson:1994rk}.
+They associate the BH Regge poles with ``surface waves'' localised near the unstable light ring at $r=3M$.
+Later, Decanini, Folacci and Jensen showed that the Schwarzschild BH QNMs are in fact Breit-Wigner type resonances generated by said surface waves \cite{Decanini:2002ha}.
+We see here that CAM theory is a powerful approach to BH physics, that provides a clear and robust physical picture.
 It seems reasonable to expect that CAM may also aid in our understanding of other compact objects such as UCOs and neutron stars.
 With this in mind, we now turn our attention to calculating the Regge pole spectrum for compact bodies.
-
-It was recently shown \cite{Dolan:2017rtj, Stratton:2019deq} that time-independent scattering by compact bodies generates (in principle) the \emph{rainbow scattering} phenomenon in the short wavelength regime ($M \omega \gg 1$).
-The rainbow scattering phenomenon is linked to the formation of a cusp caustic in the incident wavefront (see Fig.~1 in Ref.~\cite{Stratton:2019deq}), and to the stationary point in the geodesic deflection function associated with a ray (that is, a null geodesic) that passes somewhat inside the body.
-For dilute bodies, such as stars and white dwarfs, the cusp caustic forms at a distance $d \sim R^2 / (4M)$ downstream of the body, and the rainbow angle is $\theta_r \approx 4M/R$ (e.g.~for the Sun, $d \approx 550 \, \text{a.u.}$ and $\theta_r \approx 1.8 \, \text{arcsec}$).
-For compact bodies such as neutron stars, however, the cusp caustic forms near the surface of the body, and the rainbow angle is sizable ($\theta_r \gtrsim 59.6^\circ$ for $R/M = 6$; see Table I in Ref.~\cite{Stratton:2019deq}).
-In this case, the rainbow angle is -- in principle at least -- a diagnostic of the matter distribution within the body and thus its nuclear equation of state.
-
-Other recent works on the theme of scattering by a compact body include studies of: scattering by compact objects with an absorbing surface \cite{Nambu:2019sqn}; time-domain simulations with finite-element-method methods \cite{He:2019orl}; gravitationally-induced interference patterns in flavour oscillations in neutrino astronomy \cite{Alexandre:2018crg}; and the use of continuous sources of gravitational waves to probe stellar structure \cite{Marchant:2019swq}.
-
- \cite{Folacci:2018sef} \cite{Decanini:2011xi, Decanini:2011xw}
-
-to study time-independent scattering by a compact body.
-
-More literature exists on Regge pole theory applied to black hole scattering, for example They .
-Later,  We see here that CAM theory is a powerful approach to BH physics, that provides a clear and robust physical picture.
-
-Now describe the application of CAM methods to black holes, and its successes ... The aim of this work is to extend the methods to compact bodies.
-
-Describe QNMs - resonances in the time domain: \cite{Detweiler:1985zz, Kokkotas:1986gd, Chandrasekhar449, Kokkotas:1992ka, Leins:1993zz, Andersson:1995ez, Andersson1996} Review of QNMs: \cite{Kokkotas:1999bd}.
-Now describe how these are connected to Regge poles.
-
-Finally a paragraph on the connections to Mie scattering by a transparent sphere.
-
-\cite{Leite:2017zyb,Nambu:2019sqn, Folacci:2019vtt,}.
 
@@
 
+%\subsubsection{Sommerfield-Watson representation of the scattering amplitude}
+%\label{SecIIc_1}
+
 To construct the CAM representation of $\hat{f}(\theta)$, we follow the steps in section~II of Ref.~\cite{Folacci:2019cmc} and recall the main results below.
@@
 
-It is important to note that the poles of  $S_{\lambda -1/2} (\omega)$ in the complex $\lambda$ plan (i.e., the Regge poles) are defined  as  the zeros of the coefficient  $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~(\ref{Matrix_S_CAM})], i.e., the values $\lambda_n(\omega)$ such that
+%\subsubsection{Regge poles and associated residues}
+%\label{SecIIc_2}
+
+%It is important to note that the poles of  $S_{\lambda -1/2} (\omega)$ in the complex $\lambda$ plan (i.e., the Regge poles) are defined  as  the zeros of the coefficient  $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~(\ref{Matrix_S_CAM})], i.e., the values $\lambda_n(\omega)$ such that
+%\begin{equation}\label{PR_def_Am}
+%A^{(-)}_{\lambda_n(\omega)-1/2} (\omega)=0,
+%\end{equation}
+%with $n=1,2,3,\ldots$
+%The residue of the matrix $S_{\lambda-1/2}(\omega)$ at the pole $\lambda=\lambda_n(\omega)$ is defined by [see Eq.~(\ref{Matrix_S_CAM})]
+%\begin{equation}\label{residues_RP}
+%r_n(\omega)=e^{i\pi [\lambda_n(\omega)+1/2]} \left[ \frac{A_{\lambda -1/2}^{(+)}(\omega)}{\frac{d}{d \lambda}A_{\lambda -1/2}^{(-)}(\omega)}\right]_{\lambda=\lambda_n(\omega)}.
+%\end{equation}
+%These residues play a central role in the complex angular momentum paradigm.
+%
+\moh{Remark for Tom and Sam : In the next paragraph, I modified it to include the Regge poles of the third quadrant by symmetry to the origin $O$ , in the others words by changing $\ell \rightarrow -\ell-1$ } \\
+
+It is also important to recall that the poles of  $S_{\lambda-1/2}(\omega)$ in the complex $\lambda$ plan (i.e., the Regge poles) and which are lying in the first and third quadrants, symmetrically distributed with respect to the origin $O$, are defined  as  the zeros of the coefficient  $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~(\ref{Matrix_S_CAM})], i.e., the values $\lambda_n(\omega)$ such that
 \begin{equation}\label{PR_def_Am}
@@
 \end{equation}
-with $n=1,2,3,\ldots$
+with $n=1,2,3,\ldots$.
+
 The residue of the matrix $S_{\lambda-1/2}(\omega)$ at the pole $\lambda=\lambda_n(\omega)$ is defined by [see Eq.~(\ref{Matrix_S_CAM})]
@@
 
-Figure \ref{S_0_R_6_2Mw_16_Exact_vs_CAM} shows the cross section for an Ultra Compact Object with $R/M = 2.26$ at the `low' frequency of $M \omega = 3/2$.
+Figure \ref{S_0_R_2-dot-26_2Mw_3_Exact_vs_CAM} shows the cross section for an Ultra Compact Object with $R/M = 2.26$ at the `low' frequency of $M \omega = 3/2$.
 In this case, the rainbow angle exceeds $180^\circ$, and there is both a light-ring and a trapping region (see Fig.~\ref{fig:Veff}).
@@
 
-Remarkably, in the 1970s, experimental data on rainbows in nucleon-nucleon scattering experiments was used to constrain models of the nuclear potential.
-
 \acknowledgments

### 2019-12-12 rainbowCAM.tex
Finished the first draft of the Introduction.

--- 2019-12-12 rainbowCAM.tex
@@
 Time-independent scattering by a compact body of radius $R$ with a regular centre, such as a neutron star or white dwarf, has received less attention, by comparison.
-In such a scenario, an electromagnetic wave will not penetrate far inside the compact body; but on the other hand, a gravitational wave will pass through the body without much impediment from the matter distribution.
+In such a scenario, an electromagnetic wave will not penetrate far inside the compact body; but on the other hand, a gravitational wave will pass through the body without impediment from the matter distribution.
 Similarly, a neutron star is expected to be substantially transparent to neutrinos.
-Even in cases where the coupling to matter is negligible, the incident wave will nevertheless be scattered by the influence of the spacetime curvature.
+Even in such cases where the coupling to matter is negligible, the incident wave will nevertheless be scattered by the influence of the spacetime curvature.
 Thus, the resulting scattering pattern depends not just on $M\omega$, but also on the internal structure of the body, and on its inverse compactness or \emph{tenuity}, $R/M$.
@@
 A powerful approach for resumming these partial-wave expansions is provided by so-called Complex Angular Momentum (CAM) techniques.
-In the CAM approach, the sum over partial waves is replaced by an integral, and the contour of integration is deformed into  the complex-angular-momentum plane such that one collects a sum over the residues of simple poles: these are the so-called \emph{Regge poles}.
+In the CAM approach, the sum over partial waves is replaced by an integral, and the contour of integration is deformed into  the complex-angular-momentum plane such that one collects a sum of residues of simple poles: these are the so-called \emph{Regge poles}.
 
@@
 
-CAM techniques are yet to be applied to compact-body scattering, it appears, with one notable exception: in 1991, Chandrasekhar and Ferrari \cite{ChandrasekharIV:1992ey} examined the Regge pole spectra for relativistic stellar models.
+CAM techniques are yet to be fully applied to compact-body scattering, it appears, with one notable exception: in 1991, Chandrasekhar and Ferrari \cite{ChandrasekharIV:1992ey} examined the Regge pole spectra for relativistic stellar models.
 Their study focussed on resonant modes (poles with small imaginary parts corresponding to trapped $w$-modes or fluid modes), and it employed CAM theory to calculate the flow of gravitational energy through a star.
-It seems reasonable to expect that CAM can aid our understanding of other compact objects such as and neutron stars and UCOs, and this is our purpose below.
+It seems reasonable to assume that CAM theory can aid a deeper understanding of scattering by other compact objects, such as neutron stars and UCOs, and this is our purpose herein.
 
 There is a close relationship between Regge poles and quasi-normal modes (QNMs); both are sets of poles of the scattering matrix, with the latter lying in the complex-frequency plane.
-The excitation of black hole QNMs leads to distinctive signatures in time-dependent scattering scenarios.
+The excitation of black hole QNMs leads to distinctive signatures in \emph{time-dependent} scattering scenarios.
 For example, in the immediate aftermath of a black hole merger, the perturbed black hole returns to a quiescent state via a `ringdown phase' in which its gravitational-wave signal is well described as a sum of quasinormal modes \cite{Giesler:2019uxc}.
@@
 The rainbow scattering phenomenon is linked to the formation of a cusp caustic in the incident wavefront (see Fig.~1 in Ref.~\cite{Stratton:2019deq}), and to the stationary point in the geodesic deflection function associated with a ray (that is, a null geodesic) that passes somewhat inside the body.
-For dilute bodies, such as stars and white dwarfs, the cusp caustic forms at a distance $d \sim R^2 / (4M)$ downstream of the body, and the rainbow angle is $\theta_r \approx 4M/R$ (e.g.~for the Sun, $d \approx 550 \, \text{a.u.}$ and $\theta_r \approx 1.8 \, \text{arcsec}$) \footnote{The rainbow angle $\theta_r \approx 4M/R$ is distinct from the Einstein ring angle of $\theta_E \approx \sqrt{4M/r}$}.
+For less-dense bodies, such as stars and white dwarfs, the cusp caustic forms at a distance $d \sim R^2 / (4M)$ downstream of the body, and the rainbow angle is $\theta_r \sim 4M/R$ (e.g.~for the Sun, $d \approx 550 \, \text{a.u.}$ and $\theta_r \approx 1.8 \, \text{arcsec}$) \footnote{The rainbow angle $\theta_r \approx 4M/R$ is distinct from the Einstein ring angle of $\theta_E \approx \sqrt{4M/r}$}.
 For compact bodies such as neutron stars, however, the cusp caustic forms near the surface of the body, and the rainbow angle is large ($\theta_r \gtrsim 59.6^\circ$ for $R/M = 6$; see Table I in Ref.~\cite{Stratton:2019deq}).
@@
 
-Finally a paragraph on the connections to Mie scattering by a transparent sphere?
-
-\cite{Leite:2017zyb}
-
-\sam{Sam to finish}
+The remainder of this paper is organised as follows.
+Sec.~\ref{SecII} reviews the theory of scalar waves on a spherically-symmetric spacetime of a compact object.
+Here we describe our model spacetime (\ref{SecIIa}), the effective potentials for wave scattering (\ref{subsec:Potentials}) and the physical boundary conditions that define the S-matrix (\ref{subsec:bc}).
+Sec.~\ref{sec:RP} focusses on the Regge pole spectrum.
+Here we outline the link between Regge poles and QNMs (\ref{subsec:QNMs_RPs}), we describe the numerical method (\ref{subsec:method}), and we present new numerical results for the spectrum (\ref{subsec:results1}) which exhibits three distinct branches of Regge poles (see e.g.~Fig.~\ref{RP_R226_approx_2Mw_3_6_s_1}); in Sec.~\ref{subsec:WKB} we apply the WKB method to obtain an approximate formula for the `broad resonance' branch.
+Sec.~\ref{sec:CAM} concerns the application of CAM techniques to the calculation of the scattering cross section.
+Here we review the standard partial-wave expansion of the scattering amplitude (\ref{subsec:partial}), we apply CAM techniques to write this as the sum of a residue series and a background integral (\ref{SecIIc}), and we present a selection of numerical results for $d\sigma/d\Omega$ (\ref{subsec:results2}).
+We conclude with a discussion in Sec.~\ref{sec:conclusions}.
 
 %\section{Differential scattering cross sections for scalar waves, their CAM representation and their Regge pole approximations}
-\section{Waves on a compact-body spacetime}
-\label{SecII}
+\section{Waves on a compact-body spacetime} \label{SecII}
 
@@
 
-\section{The Regge pole spectrum}
+\section{The Regge pole spectrum}\label{sec:RP}
 
@@
 
- \subsection{The WKB approximation}
+ \subsection{The WKB approximation}\label{subsec:WKB}
 
@@
 
-\section{Scattering and CAM theory}
+\section{Scattering and CAM theory} \label{sec:CAM}
 In this section we calculate the scattering cross section $d\sigma / d\Omega$ by means of the CAM method, and we compare with results obtained in the standard way from a partial-wave series \cite{Dolan:2017rtj}.
 
-\subsection{The partial wave expansion}
+\subsection{The partial wave expansion} \label{subsec:partial}
 
@@
 
+Finally a paragraph on the connections to Mie scattering by a transparent sphere.
+
 \acknowledgments

### 2019-12-12 rainbowCAM.tex
Going home now.

@@
 
-We have calculated the full spectrum of Regge poles for a compact body spacetime for the first time.
-
-We find 2 distinct branches - - in the case $R > 3M$, and a third branch of narrow resonances appears for UCO.
-
-Confident that there are no additional poles in the first quadrant with imaginary parts less than (blah), for two reasons.
-First, we have scanned across the domain using the scanning method.
-Second, we obtain an excellent agreement, which would not be the case if poles in this domain had been missed.
+In this work, we have calculated the full spectrum of Regge poles for a compact body spacetime for the first time; we have applied CAM theory to obtain a complementary expression for the scattering amplitude (); and we have used this expression to calculate scattering cross sections numerically, showing precise agreement with the numerical results of the partial-wave expansion first obtained in Ref.~\cite{Dolan:2017rtj}.
+
+The spectrum of Regge poles for the neutron star case ($R/M = 6$) exhibits two distinct branches of poles (see ), which we have labelled `broad resonances' and `surface waves' \cite{}.
+Ultra-compact objects have, in addition, a third branch of `narrow resonances' corresponding to modes inside a cavity between the light-ring and their surface.
 
@@
 
-Through a WKB method, we have obtained qualitative understanding of the broad resonances, finding that the imaginary part is predicted, with a certain degree of accuracy, from the discontinuity in the potential at the surface of the body.
-Further work is need on modelling the surface-wave branch, the narrow resonances.
-Taking the WKB method to higher orders will presumably improve the accuracy.
+By applying a WKB method at lowest order, we have obtained a better understanding of the spectrum of the broad resonances, finding that the magnitude of the imaginary part is linked to the magnitude of the discontinuity in the effective potential at the surface of the body (see Eq.~).
+Taking the WKB method to higher orders will presumably improve the accuracy of approximation.
+Further work is need to model the surface-wave branch, and the narrow-resonance branch.
+
+We can be confident that there are no additional branches Regge poles in the first quadrant, for two reasons.
+First, we have searched across the complex-$\lambda$ domain using the scanning method detailed in Sec.~.
+Second, in our calculation of $d\sigma/d\Omega$, we find a precise numerical agreement between our CAM calculation and our partial-wave calculation; this would not be the case if poles in this domain had been missed.
 

### 2019-12-13 rainbowCAM.tex
First draft of conclusions, although there may be more to add.

--- 2019-12-12 rainbowCAM.tex
@@
 
-The Regge pole spectrum for a compact body is qualitatively similar to the Regge pole spectrum found in Mie scattering of electromagnetic waves by a transparent droplet of refractive index $\tilde{n}$.
+The Regge pole spectrum for a compact body is qualitatively similar to the Regge pole spectrum found in Mie scattering of electromagnetic waves by a transparent sphere of refractive index $\tilde{n}$.
 This has been studied since the 1960s; see for example Fig.~9.2 in Ref.~\cite{Nussenzveig:2006}.
@@
 with
-\begin{eqnarray}
+\begin{eqnarray} \label{eq:alpha}
 % \nonumber % Remove numbering (before each equation)
@@
 
-\sam{Sam to write this}
-
-In this work, we have calculated the full spectrum of Regge poles for a compact body spacetime for the first time; we have applied CAM theory to obtain a complementary expression for the scattering amplitude (); and we have used this expression to calculate scattering cross sections numerically, showing precise agreement with the numerical results of the partial-wave expansion first obtained in Ref.~\cite{Dolan:2017rtj}.
-
-The spectrum of Regge poles for the neutron star case ($R/M = 6$) exhibits two distinct branches of poles (see ), which we have labelled `broad resonances' and `surface waves' \cite{}.
-Ultra-compact objects have, in addition, a third branch of `narrow resonances' corresponding to modes inside a cavity between the light-ring and their surface.
-
-Links between QNMs and Regge poles. Further examination.
-
-By applying a WKB method at lowest order, we have obtained a better understanding of the spectrum of the broad resonances, finding that the magnitude of the imaginary part is linked to the magnitude of the discontinuity in the effective potential at the surface of the body (see Eq.~).
-Taking the WKB method to higher orders will presumably improve the accuracy of approximation.
-Further work is need to model the surface-wave branch, and the narrow-resonance branch.
+In this work, we have: (1) calculated the full spectrum of Regge poles for a compact body spacetime for the first time; (2) applied CAM theory to obtain an expression for the scattering amplitude as a residue series accompanied by a background integral, Eqs.~(\ref{CAM_Scalar_Scattering_amp_tot})--(\ref{CAM_Scalar_Scattering_amp_decomp_RP}); and (3) utilised the CAM formulae to calculated scattering cross sections numerically, demonstrating precise agreement with the numerical results of the partial-wave expansion first computed in Ref.~\cite{Dolan:2017rtj}.
+
+The spectrum of Regge poles exhibits two distinct branches of poles in the neutron star case $R/M = 6$ (see Fig.~\ref{RP_R6_approx_2Mw_3_6_s_1}), which we have labelled `broad resonances' and `surface waves'.
+Ultra-compact objects have, in addition, a third branch of `narrow resonances' (see Fig.~\ref{RP_R226_approx_2Mw_3_6_s_1}), linked to the existence of an effective cavity between the light-ring and the object's surface.
+Similar branches of poles arise in scattering by a transparent sphere, and so it is natural to adopt the terminology used to describe these branches in Mie scattering \cite{Nussenzveig:2006}.
+
+By applying a WKB method at lowest order, we have obtained a better understanding of the spectrum of the broad resonances, finding that the magnitude of the imaginary part is linked to the magnitude of the discontinuity in the effective potential at the surface of the body (see Eq.~(\ref{eq:alpha}), Eq.~(\ref{lambda_Approx}) and Fig.~\ref{fig:Veff}).
+Taking the WKB method to higher orders would improve the accuracy of approximation.
+Further work is need to obtain asymptotic approximations for the surface-wave branch, and the narrow-resonance branch.
 
 We can be confident that there are no additional branches Regge poles in the first quadrant, for two reasons.
-First, we have searched across the complex-$\lambda$ domain using the scanning method detailed in Sec.~.
-Second, in our calculation of $d\sigma/d\Omega$, we find a precise numerical agreement between our CAM calculation and our partial-wave calculation; this would not be the case if poles in this domain had been missed.
-
-Complementary method.
-Not efficient method at present.
-Convergence of the sum is not as rapid as in the BH case, due to the branch of broad resonances close to the real axis.
-Neither have we obtained an approximation has powerful as that of Ould Elhadj and Folacci for describing the orbiting phenomenon.
-In the case of Mie scattering, a powerful resummation approach is that of Regge-Debye poles, reducing to one branch of poles of higher order.
-This is a possible direction for future work.
-
-We have examined the case of $R=2.26M$, which is above the Buchdahl bound but nevertheless below ... blah blah, work in Tom's text.
-
-Remarkably, in the 1970s, experimental data on rainbows in nucleon-nucleon scattering experiments was used to constrain models of the nuclear potential.
-
-Finally a paragraph on the connections to Mie scattering by a transparent sphere.
+First, we have scanned across the complex-$\lambda$ domains shown in Figs.~\ref{RP_R6_approx_2Mw_3_6_s_1} and \ref{RP_R226_approx_2Mw_3_6_s_1}, as detailed in Sec.~\ref{subsec:method}.
+Second, in our calculation of $d\sigma/d\Omega$, we find a precise numerical agreement between the CAM calculation and the partial-wave calculation; this would not be the case if poles in this domain had been missed.
+
+The CAM toolkit was applied here to gain a complementary practical method for calculating scattering amplitudes.
+However, in its current form, the method is not particularly efficient, for two reasons; first, it requires the computation of a background integral in addition to residue sum; and second, the poles on the `broad resonance' branch have an approximately uniform spacing $\Delta \lambda \sim 2$, and thus a large number of poles must be found.
+In the black-hole case, by contrast, there is only a single branch of surface-wave-type modes (see Fig.~\ref{RP_R6_approx_2Mw_3_6_s_1}), and in the high-frequency limit, a single pole captures both the orbiting and glory phenomena \cite{Folacci:2019cmc, Folacci:2019vtt}.
+In the case of Mie scattering, a powerful extension of the CAM approach is to define the so-called Regge-Debye poles \cite{Nussenzveig:2006}, thereby eliminating the surface-wave branch entirely.
+This is a possible direction for future investigation.
+
+%In this work, we have  $R=2.26M$, which is above the Buchdahl bound but nevertheless below ... blah blah, work in Tom's text.
+
+%Remarkably, in the 1970s, experimental data on rainbows in nucleon-nucleon scattering experiments was used to constrain models of the nuclear potential.
+
+%Finally a paragraph on the connections to Mie scattering by a transparent sphere.
 
 \acknowledgments
-M. O. E. H. wishes to thank Antoine Folacci for various discussions concerning this work and thanks Sam R. Dolan for his kind
+M.O.E.H. wishes to thank Antoine Folacci for various discussions concerning this work and thanks Sam R. Dolan for his kind
 invitation to the University of Sheffield.

### 2019-12-13 rainbowCAM.tex
Started on the abstract.

@@
 \begin{abstract}
-To be written
+We calculate the Regge poles of the scattering matrix for a compact gravitating body, showing that the spectrum has three branches, which we classify as surface waves, broad resonances and narrow resonances.
+We examine the spectrum for neutron-star-like body, and compare with the spectrum for an ultra-compact body.
+for the massless scalar field and the odd-parity gravitational-wave sector.
 \end{abstract}

### 2019-12-13 rainbowCAM.tex
Wrote an abstract.

--- 2019-12-13 rainbowCAM.tex
@@
 \begin{abstract}
-To be written
+First, we calculate the Regge poles of the scattering matrix for a gravitating compact body, for both scalar fields and gravitational waves in the axial sector.
+For a neutron-star-like body, the spectrum exhibits two distinct branches of poles, which we label as surface waves and broad resonances; for ultra-compact objects, the spectrum also includes by a finite set of narrow resonances.
+We show, via a WKB analysis, that the discontinuity of the effective potential at the body's surface determines the imaginary component of the broad-resonance branch of poles.
+
+Next, we examine the role of Regge poles in the time-independent scattering of monochromatic planar waves.
+We apply Complex Angular Momentum techniques to re-sum the partial wave series for the scattering amplitude, expressing it as a residue series evaluated at poles in the first quadrant, accompanied by a background integral.
+We compute the scattering cross section at several frequencies, and show precise agreement with the partial-wave calculations.
+Finally, we show that compact bodies naturally give rise to orbiting, glory, and rainbow-scattering interference effects.
 \end{abstract}

### 2019-12-13 rainbowCAM.tex
First complete draft for a read-through.

@@
 \begin{abstract}
-We calculate the Regge poles of the scattering matrix for a compact gravitating body, showing that the spectrum has three branches, which we classify as surface waves, broad resonances and narrow resonances.
-We examine the spectrum for neutron-star-like body, and compare with the spectrum for an ultra-compact body.
-for the massless scalar field and the odd-parity gravitational-wave sector.
+We calculate the Regge poles of the scattering matrix for a gravitating compact body, for scalar fields and for gravitational waves in the axial sector.
+For a neutron-star-like body, the spectrum exhibits two distinct branches of poles, labelled surface waves and broad resonances; for ultra-compact objects, the spectrum also includes a finite number of narrow resonances.
+We show, via a WKB analysis, that the discontinuity of the effective potential at the body's surface determines the imaginary component of the broad-resonance poles.
+
+Next, we examine the role of Regge poles in the time-independent scattering of monochromatic planar waves.
+We apply Complex Angular Momentum techniques to re-sum the partial wave series for the scattering amplitude, expressing it as a residue series evaluated at poles in the first quadrant, accompanied by a background integral.
+We compute the scattering cross section at several frequencies, and show precise agreement with the partial-wave calculations.
+Finally, we show that compact bodies naturally give rise to orbiting, glory, and rainbow-scattering interference effects.
 \end{abstract}
@@
 
-CAM theory, originally developed for high-energy physics applications, has been successfully applied to black hole scattering scenarios.
+%CAM theory, originally developed for high-energy physics applications, has been successfully applied to black hole scattering scenarios.
 In 1994, Andersson and Thylwe \cite{Andersson:1994rk} described the scattering of scalar waves by a Schwarzschild BH by utilising CAM techniques, and they showed that, in this case, Regge poles are associated with ``surface waves'' localised near the unstable light ring at $r=3M$ (later it was shown that the corresponding quasinormal modes are Breit-Wigner type resonances generated by these surface waves \cite{Decanini:2002ha}).
@@
 An accurate approximation for the black hole absorption cross section has also been derived via an analysis of Regge poles \cite{Decanini:2011xi, Decanini:2011xw}.
+
+The CAM theory was originally developed to deal theoretically with the propagation and diffraction of radio waves around the Earth, by Watson~\cite{Watson18} (see also the work of Sommerfeld~\cite{Sommerfeld49}).
+It has since been extensively used in several domains of physics involving resonant scattering theory (see, \textit{e.g.}, Refs.~\cite{deAlfaro:1965zz,Newton:1982qc,Watson18,Sommerfeld49,Nus92,Grandy2000,Uberall1992,AkiRichards2002,AkiRichards2002,Gribov69,
+Collins77,BaronePredazzi2002,DonnachieETAL2005} as well as references therein for various applications in quantum mechanics, nuclear physics, electromagnetism, optics, seismology and high energy physics).
+Since the pioneering work in 1994 by Andersson and Thylwe~\cite{Andersson:1994rk,Andersson:1994rm} the CAM theory has been successfully applied to black hole scattering scenarios.
+They described the scattering of scalar waves by a Schwarzschild black hole using CAM techniques, and showed that, in this case, the Regge poles are associated with ``surface waves'' localised near the unstable light ring at $ r = 3M $ (\textit{i.e.}, the so-called photon sphere).
+Later, Decanini, Folacci and Jensen have shown that the complex frequencies of weakly damped QNMs are Breit-Wigner resonances generated by surface waves previously mentioned and, using the concept of Regge trajectories, they were able to construct semiclassically the spectrum of the QNM complex frequencies~\cite{Decanini:2002ha}.
+Recently, Folacci and Ould~El~Hadj have shown that CAM machinery can be used for precise numerical calculations of scattering cross sections of scalar fields, electromagnetic fields~\cite{Folacci:2019cmc} and gravitational waves~\cite{Folacci:2019vtt} on Schwarzschild space-time.
+Moreover, using the third WKB approximation to obtain the asymptotic expressions for the lowest Regge poles~\cite{Decanini:2009mu} and associated residues, they have able to provide an analytical approximation describing accurately both ``glory'' and large part of the ``orbiting'' oscillations in black hole scattering cross sections in the short-wavelength regime.
+An accurate approximation for the black hole absorption cross section has also been derived via an analysis of Regge poles~\cite{Decanini:2011xi,Decanini:2011xw}.
+In addition, an alternative description of gravitational radiation from black holes based on CAM theory was developed in Ref.~\cite{Folacci:2018sef}.
 
@@
 The radial function $h(r)$ is $C^0$ at the surface of the star $r=R$ (i.e.~continuous but not differentiable), and the radial function $f(r)$ is $C^1$ there (i.e.~once-differentiable).
-%In the polytropic cases $n > 0$, the functions are more regular \sam{can we make a precise statement?}\tom{I will write something here} at the surface, but not $C^\infty$ (i.e.~not smooth).
-As we shall see, the breakdown of smoothness leads to consequences for the Regge pole spectrum.
 For a general polytrope with $n>0$ and $m$ the smallest integer such that $m \geq n$, $h(r)$ is $C^m$ and $f(r)$ is $C^{m+1}$ at the surface. 
-%\tom{This can be seen from equations relating $(m,\rho,p,f,h)$ and by noting $\rho \sim a(R-r)^n$ at the surface \cite{Lindblom:1983ps} but we don't mention these.}
 As we shall see, the breakdown of smoothness leads to consequences for the Regge pole spectrum.
@@
 %
-\moh{Remark for Tom and Sam : In the next paragraph, I modified it to include the Regge poles of the third quadrant by symmetry to the origin $O$ , in the others words by changing $\ell \rightarrow -\ell-1$ } \\
 
@@
   \vspace*{-0.3cm}
-\caption{\label{S_0_R_2-dot-26_2Mw_3_Exact_vs_CAM} The scalar cross section of a very compact bodies for $2M\omega=3$ and $R=2.26M$ and its Regge pole approximation.
+\caption{\label{S_0_R_2-dot-26_2Mw_3_Exact_vs_CAM} The scalar cross section of an ultra-compact body for $2M\omega=3$ and $R=2.26M$ and its Regge pole approximation.
 The plots show the effect of including successively more Regge poles (plots 1--3).
-In the final plot, The sum over Regge poles gives a cross section which agrees well with the (regularized) partial-wave sum for intermediate and large values of the scattering
-angle.}
+In the final plot, the sum over Regge poles gives a cross section which agrees well with the (regularized) partial-wave sum for intermediate and large values of the scattering angle.}
 \end{figure*}
@@
   \vspace*{-0.3cm}
-\caption{\label{S_0_R_2-dot-26_2Mw_6_Exact_vs_CAM} The scalar cross section of a very compact bodies for $2M\omega=6$ and $R=2.26M$ and its Regge pole approximation.
+\caption{\label{S_0_R_2-dot-26_2Mw_6_Exact_vs_CAM} The scalar cross section of an ultra-compact body for $2M\omega=6$ and $R=2.26M$ and its Regge pole approximation.
 The plots show the effect of including successively more Regge poles (plots 1--3).
-In the final plot, The sum over Regge poles gives a cross section which agrees well with the (regularized) partial-wave sum for intermediate and large values of the scattering
-angle.}
+In the final plot, the sum over Regge poles gives a cross section which agrees well with the (regularized) partial-wave sum for intermediate and large values of the scattering angle.}
 \end{figure*}
@@
 Figures \ref{Rainbow_Cross_Section_R_6_2Mw_16} and \ref{Diff_Contribution_Cross_Section_R_2-dot-26_2Mw_6} show the relative magnitudes of the contributions from the different branches of Regge poles.
-For $R/M = 6$ (Fig.~ \ref{Rainbow_Cross_Section_R_6_2Mw_16}) the surface-wave and broad-resonance amplitudes are similar in magnitude, and similar in magnitude to their sum.
+For $R/M = 6$ (Fig.~\ref{Rainbow_Cross_Section_R_6_2Mw_16}) the surface-wave and broad-resonance amplitudes are similar in magnitude, and similar in magnitude to their sum.
 There is a difference in phase between these amplitudes which generates the peaks and troughs of the rainbow-scattering pattern.
@@
 
-In this work, we have: (1) calculated the full spectrum of Regge poles for a compact body spacetime for the first time; (2) applied CAM theory to obtain an expression for the scattering amplitude as a residue series accompanied by a background integral, Eqs.~(\ref{CAM_Scalar_Scattering_amp_tot})--(\ref{CAM_Scalar_Scattering_amp_decomp_RP}); and (3) utilised the CAM formulae to calculated scattering cross sections numerically, demonstrating precise agreement with the numerical results of the partial-wave expansion first computed in Ref.~\cite{Dolan:2017rtj}.
+In this work, we have: (1) calculated the full spectrum of Regge poles for a compact body spacetime for the first time; (2) applied CAM theory to obtain an expression for the scattering amplitude as a residue series accompanied by a background integral, Eqs.~(\ref{CAM_Scalar_Scattering_amp_tot})--(\ref{CAM_Scalar_Scattering_amp_decomp_RP}); and (3) utilised the CAM formulae to calculated scattering cross sections numerically, demonstrating precise agreement with the numerical results of the partial-wave expansion, first computed in Ref.~\cite{Dolan:2017rtj}.
 
@@
 By applying a WKB method at lowest order, we have obtained a better understanding of the spectrum of the broad resonances, finding that the magnitude of the imaginary part is linked to the magnitude of the discontinuity in the effective potential at the surface of the body (see Eq.~(\ref{eq:alpha}), Eq.~(\ref{lambda_Approx}) and Fig.~\ref{fig:Veff}).
-Taking the WKB method to higher orders would improve the accuracy of approximation.
-Further work is need to obtain asymptotic approximations for the surface-wave branch, and the narrow-resonance branch.
-
-We can be confident that there are no additional branches Regge poles in the first quadrant, for two reasons.
+Extending the WKB method to higher orders would improve the accuracy of this approximation, and further work is need to obtain asymptotic approximations for the surface-wave branch, and the narrow-resonance branch.
+
+We can be confident that there are no additional branches of Regge poles in the first quadrant, for two reasons.
 First, we have scanned across the complex-$\lambda$ domains shown in Figs.~\ref{RP_R6_approx_2Mw_3_6_s_1} and \ref{RP_R226_approx_2Mw_3_6_s_1}, as detailed in Sec.~\ref{subsec:method}.
@@
 The CAM toolkit was applied here to gain a complementary practical method for calculating scattering amplitudes.
-However, in its current form, the method is not particularly efficient, for two reasons; first, it requires the computation of a background integral in addition to residue sum; and second, the poles on the `broad resonance' branch have an approximately uniform spacing $\Delta \lambda \sim 2$, and thus a large number of poles must be found.
+However, in its current form, the method is not particularly efficient, for two reasons; first, it requires the computation of a background integral in addition to residue sum; and second, the poles on the broad-resonance branch have an approximately uniform spacing, $\Delta \lambda \sim 2$, and thus a large number of poles must be calculated.
 In the black-hole case, by contrast, there is only a single branch of surface-wave-type modes (see Fig.~\ref{RP_R6_approx_2Mw_3_6_s_1}), and in the high-frequency limit, a single pole captures both the orbiting and glory phenomena \cite{Folacci:2019cmc, Folacci:2019vtt}.
@@
 %In this work, we have  $R=2.26M$, which is above the Buchdahl bound but nevertheless below ... blah blah, work in Tom's text.
-
 %Remarkably, in the 1970s, experimental data on rainbows in nucleon-nucleon scattering experiments was used to constrain models of the nuclear potential.
-
 %Finally a paragraph on the connections to Mie scattering by a transparent sphere.
@@
 \acknowledgments
-M.O.E.H. wishes to thank Antoine Folacci for various discussions concerning this work and thanks Sam R. Dolan for his kind
+M.O.E.H. wishes to thank Antoine Folacci for various discussions concerning this work and thanks S.R.D.~for his kind
 invitation to the University of Sheffield.

### 2019-12-13 rainbowCAM.tex
some typos are corrected, update of legende in plots 6-7 and some reformulated paragraphs, please find remarks in pdf

--- 2019-12-13 rainbowCAM.tex
@@
 An accurate approximation for the black hole absorption cross section has also been derived via an analysis of Regge poles \cite{Decanini:2011xi, Decanini:2011xw}.
+
+ \moh{Remark to Tom and Sam : I reformulated the following paragraph! What do you think}\\
+
+The CAM theory originally developed to deal  theoretically with the propagation and diffraction of radio waves around the Earth, by Watson~\cite{Watson18} (see also the work of Sommerfeld ~\cite{Sommerfeld49}) has since been  extensively used in several domains of physics involving resonant scattering theory (see,\textit{e.g.}, Refs.~\cite{deAlfaro:1965zz,Newton:1982qc,Watson18,Sommerfeld49,Nus92,Grandy2000,Uberall1992,AkiRichards2002,AkiRichards2002,Gribov69,
+Collins77,BaronePredazzi2002,DonnachieETAL2005} as well as references therein for various applications in quantum mechanics, nuclear physics, electromagnetism, optics, seismology and high energy physics).
+And since the pioneering work in 1994 by Andersson and Thylwe~\cite{Andersson:1994rk,Andersson:1994rm} the CAM theory has been successfully applied to black hole scattering scenarios.
+They, in particular, described the scattering of scalar waves by a Schwarzschild black hole using CAM techniques, also showed that, in this case, the Regge poles are associated with ``surface waves'' localised near the unstable light ring at $ r = 3M $ (\textit{i.e.}, the so-called photon sphere).
+Later, Decanini, Folacci and Jensen have shown that the complex frequencies of weakly damped QNMs are Breit-Wigner resonances generated by surface waves previously mentioned and using the concept of Regge trajectories, they have been able to construct semiclassically the spectrum of the QNM complex frequencies~\cite{Decanini:2002ha}.
+Recently, Folacci and Ould~El~Hadj have shown that CAM machinery can be used for precise numerical calculations of scattering cross sections of scalar fields, electromagnetic fields~\cite{Folacci:2019cmc} and gravitational waves~\cite{Folacci:2019vtt} on Schwarzschild space-time.
+Moreover, using the third WKB approximation to obtain the asymptotic expressions for the lowest Regge poles~\cite{Decanini:2009mu} and associated residues, they have able to provide an analytical approximation describing accurately both ``glory'' and large part of the ``orbiting'' oscillations in black hole scattering cross sections in the short-wavelength regime.
+An accurate approximation for the black hole absorption cross section has also been derived via an analysis of Regge poles~\cite{Decanini:2011xi,Decanini:2011xw}.
+Also, was obtained an alternative description of gravitational radiation from black holes based on CAM theory~\cite{Folacci:2018sef}.
 

### 2019-12-13 rainbowCAM.tex

@@
 \begin{abstract}
-We calculate the Regge poles of the scattering matrix for a compact gravitating body, showing that the spectrum has three branches, which we classify as surface waves, broad resonances and narrow resonances.
-We examine the spectrum for neutron-star-like body, and compare with the spectrum for an ultra-compact body.
-for the massless scalar field and the odd-parity gravitational-wave sector.
+First, we calculate the Regge poles of the scattering matrix for a gravitating compact body, for both scalar fields and gravitational waves in the axial sector.
+For a neutron-star-like body, the spectrum exhibits two distinct branches of poles, which we label as surface waves and broad resonances; for ultra-compact objects, the spectrum also includes by a finite set of narrow resonances.
+We show, via a WKB analysis, that the discontinuity of the effective potential at the body's surface determines the imaginary component of the broad-resonance branch of poles.
+
+Next, we examine the role of Regge poles in the time-independent scattering of monochromatic planar waves.
+We apply Complex Angular Momentum techniques to re-sum the partial wave series for the scattering amplitude, expressing it as a residue series evaluated at poles in the first quadrant, accompanied by a background integral.
+We compute the scattering cross section at several frequencies, and show precise agreement with the partial-wave calculations.
+Finally, we show that compact bodies naturally give rise to orbiting, glory, and rainbow-scattering interference effects.
 \end{abstract}

### 2019-12-16 rainbowCAM.tex
The remarks in PDF

--- 2019-12-13 rainbowCAM.tex
@@
 \usepackage{xcolor}
+\usepackage{soul}
 
@@
 The CAM theory was originally developed to deal theoretically with the propagation and diffraction of radio waves around the Earth, by Watson~\cite{Watson18} (see also the work of Sommerfeld~\cite{Sommerfeld49}).
-It has since been extensively used in several domains of physics involving resonant scattering theory (see, \textit{e.g.}, Refs.~\cite{deAlfaro:1965zz,Newton:1982qc,Watson18,Sommerfeld49,Nus92,Grandy2000,Uberall1992,AkiRichards2002,AkiRichards2002,Gribov69,
+It has since been extensively used in several domains of physics involving resonant scattering theory (see, e.g., Refs.~\cite{deAlfaro:1965zz,Newton:1982qc,Watson18,Sommerfeld49,Nussenzveig:2006,Grandy2000,Uberall1992,AkiRichards2002,AkiRichards2002,Gribov69,
 Collins77,BaronePredazzi2002,DonnachieETAL2005} as well as references therein for various applications in quantum mechanics, nuclear physics, electromagnetism, optics, seismology and high energy physics).
@@
 The excitation of black hole QNMs leads to distinctive signatures in \emph{time-dependent} scattering scenarios.
-For example, in the immediate aftermath of a black hole merger, the perturbed black hole returns to a quiescent state via a `ringdown phase' in which its gravitational-wave signal is well described as a sum of quasinormal modes \cite{Giesler:2019uxc}.
+For example, in the immediate aftermath of a black hole merger, the perturbed black hole returns to a quiescent state via a ``ringdown phase'' in which its gravitational-wave signal is well described as a sum of quasinormal modes \cite{Giesler:2019uxc}.
 The QNM spectrum of compact bodies have been well-studied by several authors  \cite{Detweiler:1985zz, Kokkotas:1986gd, Chandrasekhar449, Kokkotas:1992ka, Leins:1993zz, Andersson:1995ez, Andersson1996}, and are reviewed in Ref.~\cite{Kokkotas:1999bd}.
 
-It was recently shown \cite{Dolan:2017rtj, Stratton:2019deq} that time-independent scattering by compact bodies generates (in principle) a \emph{rainbow scattering} phenomenon in the short wavelength regime ($M \omega \gg 1$).
+%It was recently shown \cite{Dolan:2017rtj, Stratton:2019deq} that time-independent scattering by compact bodies generates (in principle) a \emph{rainbow scattering} phenomenon in the short wavelength regime ($M \omega \gg 1$).
 The rainbow scattering phenomenon is linked to the formation of a cusp caustic in the incident wavefront (see Fig.~1 in Ref.~\cite{Stratton:2019deq}), and to the stationary point in the geodesic deflection function associated with a ray (that is, a null geodesic) that passes somewhat inside the body.
@@
 
+\moh{Remark for Tom and Sam : In the following paragraph : Render unto Caesar the things that are Caesar's}\\
+
+Stratton and Dolan have recently shown that time-independent scattering by compact bodies generates (in principle) a \emph{rainbow scattering} phenomenon in the short wavelength regime ($M \omega \gg 1$)~\cite{Dolan:2017rtj, Stratton:2019deq}.
+The rainbow scattering phenomenon is linked to the formation of a cusp caustic in the incident wavefront (see Fig.~1 in Ref.~\cite{Stratton:2019deq}), and to the stationary point in the geodesic deflection function associated with a ray (that is, a null geodesic) that passes somewhat inside the body.
+For less-dense bodies, such as stars and white dwarfs, the cusp caustic forms at a distance $d \sim R^2 / (4M)$ downstream of the body, and the rainbow angle is $\theta_r \sim 4M/R$ (e.g.~for the Sun, $d \approx 550 \, \text{a.u.}$ and $\theta_r \approx 1.8 \, \text{arcsec}$) \footnote{The rainbow angle $\theta_r \approx 4M/R$ is distinct from the Einstein ring angle of $\theta_E \approx \sqrt{4M/r}$}.
+For compact bodies such as neutron stars, however, the cusp caustic forms near the surface of the body, and the rainbow angle is large ($\theta_r \gtrsim 59.6^\circ$ for $R/M = 6$; see Table I in Ref.~\cite{Stratton:2019deq}).
+In this case, the rainbow angle is -- in principle at least -- a useful diagnostic of the matter distribution within the body and thus its nuclear equation of state.
+
 Other recent works on the theme of scattering by a compact body include studies of: scattering by compact objects with an absorbing surface \cite{Nambu:2019sqn}; time-domain simulations with finite-element-method methods \cite{He:2019orl}; gravitationally-induced interference patterns in flavour oscillations in neutrino astronomy \cite{Alexandre:2018crg}; and the use of continuous sources of gravitational waves to probe stellar structure \cite{Marchant:2019swq}.
@@
 Sec.~\ref{sec:RP} focusses on the Regge pole spectrum.
-Here we outline the link between Regge poles and QNMs (\ref{subsec:QNMs_RPs}), we describe the numerical method (\ref{subsec:method}), and we present new numerical results for the spectrum (\ref{subsec:results1}) which exhibits three distinct branches of Regge poles (see e.g.~Fig.~\ref{RP_R226_approx_2Mw_3_6_s_1}); in Sec.~\ref{subsec:WKB} we apply the WKB method to obtain an approximate formula for the `broad resonance' branch.
+Here we outline the link between Regge poles and QNMs (\ref{subsec:QNMs_RPs}), we describe the numerical method (\ref{subsec:method}), and we present new numerical results for the spectrum (\ref{subsec:results1}) which exhibits three distinct branches of Regge poles (see e.g.~Fig.~\ref{RP_R226_approx_2Mw_3_6_s_1}); in Sec.~\ref{subsec:WKB} we apply the WKB method to obtain an approximate formula for the ``broad resonance'' branch.
 Sec.~\ref{sec:CAM} concerns the application of CAM techniques to the calculation of the scattering cross section.
@@
 %
+Or equivalently \moh{we can also use this forme}
+\begin{align}
+\label{recurrence_Hill_RN_4_termes}
+D_n    & =\left(\prod_{k=1}^{n+1} k^2\right) P_{n+1} \nonumber\\
+       &  = 1\times 2^2 \ldots (n-2)^2(n-1)^2n^2(n+1)^2 P_{n+1},
+\end{align}
+where
+\begin{eqnarray}
+\label{recurrence_Hill_RN_4_termes_bis}
+% \nonumber % Remove numbering (before each equation)
+P_n = & & \left(\frac{\beta_{n-1}}{n^2}\right)P_{n-1}-\left(\frac{\gamma_{n-1}}{n^2}\right)\left(\frac{\alpha_{n-2}}{(n-1)^2}\right)P_{n-2} \nonumber \\
+  &+& \left(\frac{\delta_{n-1}}{n^2}\right) \left(\frac{\alpha_{n-2}}{(n-1)^2}\right) \left(\frac{\alpha_{n-3}}{(n-2)^2}\right) P_{n-3}
+\end{eqnarray}
+with the initial conditions
+ \begin{equation}
+ \begin{split}
+    P_1&=\beta_0\\
+    P_2&=\frac{\beta_0\beta_1-\gamma_1\alpha_0}{4} \\
+    P_3&=\frac{\beta_0(\beta_1 \beta_2 - \alpha_1 \gamma_2)- \alpha_0(\alpha_1 \delta_2 -\gamma_1 \beta_2)}{36}
+ \end{split}
+ \end{equation}
+
 Regge poles (QNM frequencies) are found by fixing $\omega$ ($\lambda$) and numerically finding roots $\lambda_n$ ($\omega_n$) of $D_n$, i.e.~ $D_n(\lambda_n,\omega)=0$ ($D_n(\lambda,\omega_n)=0$).
@@
 Due to the long rang nature of the field propagating on the Schwarzschild BH (outside the compact body), the scattering amplitude~\eqref{Scalar_Scattering_amp} and the background integral~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} both suffer a lack of convergence.
-To overcome this problem, i.e., to accelerate the convergence of this sum and integral, we have used the method described in the Appendix of Ref~\cite{Folacci:2019cmc}.
+To overcome this problem, \textit{i.e.}, to accelerate the convergence of this sum and integral, we have used the method described in the Appendix of Ref~\cite{Folacci:2019cmc}.
 We have performed all the numerical calculations by using {\it Mathematica}.
@@
  \includegraphics[scale=0.50]{Scattering_Cross_Section_R_6_2Mw_3}
-  \vspace*{-0.3cm}
+  \vspace*{-0.35cm}
 \caption{\label{S_0_R_6_2Mw_3_Exact_vs_CAM} The scalar cross section of a compact bodies for $2M\omega=3$ and $R=6M$, its Regge pole approximation and the background integral contribution.
@@
  \includegraphics[scale=0.50]{Scattering_Cross_Section_R_6_2Mw_16}
- \vspace*{-0.3cm}
+ \vspace*{-0.35cm}
 \caption{\label{S_0_R_6_2Mw_16_Exact_vs_CAM} The scalar cross section of a compact bodies for $2M\omega=16$ and $R=6M$, its Regge pole approximation and the background integral contribution.
@@
 
-\begin{figure*}[htp]
+\begin{figure*}[htp!]
 \centering
  \includegraphics[scale=0.50]{Scattering_Cross_Section_R_2-dot-26_2Mw_3}
-  \vspace*{-0.3cm}
-\caption{\label{S_0_R_2-dot-26_2Mw_3_Exact_vs_CAM} The scalar cross section of an ultra-compact body for $2M\omega=3$ and $R=2.26M$ and its Regge pole approximation.
+  \vspace*{-0.45cm}
+\caption{\label{S_0_R_2-dot-26_2Mw_3_Exact_vs_CAM} The scalar cross section of an UCOs for $2M\omega=3$ and $R=2.26M$ and its Regge pole approximation.
 The plots show the effect of including successively more Regge poles (plots 1--3).
@@
 
-\begin{figure*}[htp]
+\begin{figure*}[htp!]
 \centering
  \includegraphics[scale=0.50]{Scattering_Cross_Section_R_2-dot-26_2Mw_6}
-  \vspace*{-0.3cm}
-\caption{\label{S_0_R_2-dot-26_2Mw_6_Exact_vs_CAM} The scalar cross section of an ultra-compact body for $2M\omega=6$ and $R=2.26M$ and its Regge pole approximation.
+  \vspace*{-0.45cm}
+\caption{\label{S_0_R_2-dot-26_2Mw_6_Exact_vs_CAM} The scalar cross section of an UCOs for $2M\omega=6$ and $R=2.26M$ and its Regge pole approximation.
 The plots show the effect of including successively more Regge poles (plots 1--3).
@@
 
-\begin{figure}[htp]
+\begin{figure}[htp!]
 \centering
  \includegraphics[scale=0.50]{Rainbow_Cross_Section_R_6_2Mw_16}
-  \vspace*{-0.3cm}
+  \vspace*{-0.45cm}
 \caption{\label{Rainbow_Cross_Section_R_6_2Mw_16} Rainbow scattering for compact bodies for $2M\omega=16$ and $R=6M$, its Regge pole approximation and different contributions of the sum over Regge poles.}
@@
 
-\begin{figure}[htp]
+\begin{figure}[htp!]
 \centering
  \includegraphics[scale=0.50]{Diff_Contribution_Cross_Section_R_2-dot-26_2Mw_6}
-  \vspace*{-0.3cm}
-\caption{\label{Diff_Contribution_Cross_Section_R_2-dot-26_2Mw_6} Rainbow scattering for compact bodies for $2M\omega=16$ and $R=2.26M$, its Regge pole approximation and different contributions of the sum over Regge poles.}
+  \vspace*{-0.45cm}
+\caption{\label{Diff_Contribution_Cross_Section_R_2-dot-26_2Mw_6} Rainbow scattering for UCOs for $2M\omega=16$ and $R=2.26M$, its Regge pole approximation and different contributions of the sum over Regge poles.}
 \end{figure}
@@
 Figure \ref{S_0_R_6_2Mw_3_Exact_vs_CAM} demonstrates that the CAM cross section approaches the partial-wave cross section as (i) successively more Regge poles are included in the sum (\ref{CAM_Scalar_Scattering_amp_decomp_RP}), and (ii) the background-integral contributions (\ref{CAM_Scalar_Scattering_amp_decomp_Background}) are included.
-The first plot shows that, at a `low' frequency of $M \omega = 3/2$ for the neutron star model ($R/M = 6$), taking a sum over just \emph{two} Regge poles in Eq.~(\ref{CAM_Scalar_Scattering_amp_decomp_RP}) captures the crude features of the cross section.
+The first plot shows that, at a ``low'' frequency of $M \omega = 3/2$ for the neutron star model ($R/M = 6$), taking a sum over just \emph{two} Regge poles in Eq.~(\ref{CAM_Scalar_Scattering_amp_decomp_RP}) captures the crude features of the cross section.
 The final plot shows that a cross section calculated from a sum of $15$ Regge poles and the background integral is indistinguishable (on the plot) from the partial-wave sum.
@@
 
-Figure \ref{S_0_R_2-dot-26_2Mw_3_Exact_vs_CAM} shows the cross section for an Ultra Compact Object with $R/M = 2.26$ at the `low' frequency of $M \omega = 3/2$.
+Figure \ref{S_0_R_2-dot-26_2Mw_3_Exact_vs_CAM} shows the cross section for an Ultra Compact Object with $R/M = 2.26$ at the ``low'' frequency of $M \omega = 3/2$.
 In this case, the rainbow angle exceeds $180^\circ$, and there is both a light-ring and a trapping region (see Fig.~\ref{fig:Veff}).
@@
 
-The spectrum of Regge poles exhibits two distinct branches of poles in the neutron star case $R/M = 6$ (see Fig.~\ref{RP_R6_approx_2Mw_3_6_s_1}), which we have labelled `broad resonances' and `surface waves'.
-Ultra-compact objects have, in addition, a third branch of `narrow resonances' (see Fig.~\ref{RP_R226_approx_2Mw_3_6_s_1}), linked to the existence of an effective cavity between the light-ring and the object's surface.
+The spectrum of Regge poles exhibits two distinct branches of poles in the neutron star case $R/M = 6$ (see Fig.~\ref{RP_R6_approx_2Mw_3_6_s_1}), which we have labelled ``broad resonances'' and ``surface waves''.
+Ultra-compact objects have, in addition, a third branch of ``narrow resonances'' (see Fig.~\ref{RP_R226_approx_2Mw_3_6_s_1}), linked to the existence of an effective cavity between the light-ring and the object's surface.
 Similar branches of poles arise in scattering by a transparent sphere, and so it is natural to adopt the terminology used to describe these branches in Mie scattering \cite{Nussenzveig:2006}.
@@
 
-The CAM toolkit was applied here to gain a complementary practical method for calculating scattering amplitudes.
+\moh{I propose this following paragraph in summary}\\
+
+%The CAM toolkit was applied here to gain a complementary practical method for calculating scattering amplitudes.
 However, in its current form, the method is not particularly efficient, for two reasons; first, it requires the computation of a background integral in addition to residue sum; and second, the poles on the broad-resonance branch have an approximately uniform spacing, $\Delta \lambda \sim 2$, and thus a large number of poles must be calculated.
@@
 This is a possible direction for future investigation.
+
+The CAM toolkit was applied here to gain a complementary practical method for calculating scattering amplitudes.
+In summary, we have shown that, for the intermediate and high angles, these scattering amplitudes can be reconstructed in terms of Regge poles with great precision in the regime of intermediate and high frequencies.
+It is important to note that for compact objects (\textit{i.e.}, $R/M=6$), we observed that it is necessary to take into account the background integral contributions to describe the glory and this regardless of the frequency.
+Which does not the case for UCOs since only the sum over the Regge poles is enough.
+Moreover, the sum over the Regge poles permitted us to overcome the difficulties linked to the lack of convergence from which the scattering amplitude suffers (\textit{i.e.} partial wave expansions) due to the long-range of the field propagating on the Schwarzschild black hole (outside the compact body).
+However, the existence of the broad resonance branch (see also narrow resonance branch for the UCOs) close to the real axis with an approximately uniform spacing, $\Delta\lambda\sim 2 $, requires the calculation of a large number of poles.
+In the black-hole case, by contrast, there is only a single branch of surface-wave-type modes  (see Fig.~\ref{RP_R6_approx_2Mw_3_6_s_1}), and in the high-frequency limit, a few poles ($<5$) capture both the orbiting and glory phenomena \cite{Folacci:2019cmc, Folacci:2019vtt}.
+Also, in the case of the Mie scattering, a powerful extension of the CAM approach is to define the so-called Regge-Debye poles using the Debye expansion (see the chapter 9 of the monograph of Nussenzveig \cite{Nussenzveig:2006}), thereby eliminating the broad resonance branch entirely and accelerating the convergence.
+This is a possible direction for a future investigation
 

### 2019-12-16 rainbowCAM.tex

@@
 The CAM toolkit was applied here to gain a complementary practical method for calculating scattering amplitudes.
-In summary, we have shown that, for the intermediate and high angles, these scattering amplitudes can be reconstructed in terms of Regge poles with great precision in the regime of intermediate and high frequencies.
+In summary, we have shown that, for the intermediate and high angles, these scattering amplitudes can be reconstructed in terms of Regge poles with great precision in the intermediate and high frequencies regime.
 It is important to note that for compact objects (\textit{i.e.}, $R/M=6$), we observed that it is necessary to take into account the background integral contributions to describe the glory and this regardless of the frequency.
@@
 Moreover, the sum over the Regge poles permitted us to overcome the difficulties linked to the lack of convergence from which the scattering amplitude suffers (\textit{i.e.} partial wave expansions) due to the long-range of the field propagating on the Schwarzschild black hole (outside the compact body).
-However, the existence of the broad resonance branch (see also narrow resonance branch for the UCOs) close to the real axis with an approximately uniform spacing, $\Delta\lambda\sim 2 $, requires the calculation of a large number of poles.
+However, the existence of the broad resonance branch (see also narrow resonance branch for the UCOs) close to the real axis with an approximately uniform spacing, $\Delta\lambda\sim 2$, requires the calculation of a large number of poles.
 In the black-hole case, by contrast, there is only a single branch of surface-wave-type modes (see Fig.~\ref{RP_R6_approx_2Mw_3_6_s_1}), and in the high-frequency limit, a few poles ($<5$) capture both the orbiting and glory phenomena \cite{Folacci:2019cmc, Folacci:2019vtt}.

### 2019-12-16 rainbowCAM.tex

@@
 Next, we examine the role of Regge poles in the time-independent scattering of monochromatic planar waves.
-We apply Complex Angular Momentum techniques to re-sum the partial wave series for the scattering amplitude, expressing it as a residue series evaluated at poles in the first quadrant, accompanied by a background integral.
+We apply Complex Angular Momentum techniques to re-sum the partial wave series for the scattering amplitude, expressing it as a residue series evaluated at poles in the first and fourth quadrants, accompanied by a background integral.
 We compute the scattering cross section at several frequencies, and show precise agreement with the partial-wave calculations.
@@
 They described the scattering of scalar waves by a Schwarzschild black hole using CAM techniques, and showed that, in this case, the Regge poles are associated with ``surface waves'' localised near the unstable light ring at $ r = 3M $ (\textit{i.e.}, the so-called photon sphere).
-Later, Decanini, Folacci and Jensen have shown that the complex frequencies of weakly damped QNMs are Breit-Wigner resonances generated by surface waves previously mentioned and, using the concept of Regge trajectories, they were able to construct semiclassically the spectrum of the QNM complex frequencies~\cite{Decanini:2002ha}.
-Recently, Folacci and Ould~El~Hadj have shown that CAM machinery can be used for precise numerical calculations of scattering cross sections of scalar fields, electromagnetic fields~\cite{Folacci:2019cmc} and gravitational waves~\cite{Folacci:2019vtt} on Schwarzschild space-time.
-Moreover, using the third WKB approximation to obtain the asymptotic expressions for the lowest Regge poles~\cite{Decanini:2009mu} and associated residues, they have able to provide an analytical approximation describing accurately both ``glory'' and large part of the ``orbiting'' oscillations in black hole scattering cross sections in the short-wavelength regime.
+Later, Decanini, Folacci and Jensen showed that the complex frequencies of weakly damped QNMs are Breit-Wigner resonances generated by the surface waves previously mentioned and, using the concept of Regge trajectories, they were able to construct semiclassically the spectrum of the QNM complex frequencies~\cite{Decanini:2002ha}.
+Recently, Folacci and Ould~El~Hadj have shown that CAM machinery can be used for precise numerical calculations of scattering cross sections of scalar fields, electromagnetic fields~\cite{Folacci:2019cmc} and gravitational waves~\cite{Folacci:2019vtt} on a Schwarzschild space-time.
+Moreover, using the third WKB approximation to obtain the asymptotic expressions for the lowest Regge poles~\cite{Decanini:2009mu} and associated residues, they have been able to provide an analytical approximation describing accurately both the ``glory'' and a large part of the ``orbiting'' oscillations in black hole scattering cross sections in the short-wavelength regime.
 An accurate approximation for the black hole absorption cross section has also been derived via an analysis of Regge poles~\cite{Decanini:2011xi,Decanini:2011xw}.
@@
 Their study focussed on resonant modes (poles with small imaginary parts corresponding to trapped $w$-modes or fluid modes), and it employed CAM theory to calculate the flow of gravitational energy through a star.
-It seems reasonable to assume that CAM theory can aid a deeper understanding of scattering by other compact objects, such as neutron stars and UCOs, and this is our purpose herein.
-
-There is a close relationship between Regge poles and quasi-normal modes (QNMs); both are sets of poles of the scattering matrix, with the latter lying in the complex-frequency plane.
+It seems reasonable to assume that CAM theory could lead to a deeper understanding of scattering by other compact objects, such as neutron stars and UCOs, and this is our purpose herein.
+
+There is a close relationship between Regge poles and quasi-normal mode (QNM) frequencies; both are sets of poles of the scattering matrix, with the latter lying in the complex-frequency plane.
 The excitation of black hole QNMs leads to distinctive signatures in \emph{time-dependent} scattering scenarios.
@@
 p &= \rho \frac{\beta(R) - \beta(r)}{ \beta(r) - 3 \beta(R)} , \\
-\beta(x) &= \sqrt{3 - 8 \pi \rho x^2}
+\beta(x) &= \sqrt{3 - 8 \pi \rho x^2},
 \end{align}
@@
 The radial function $h(r)$ is $C^0$ at the surface of the star $r=R$ (i.e.~continuous but not differentiable), and the radial function $f(r)$ is $C^1$ there (i.e.~once-differentiable).
-For a general polytrope with $n>0$ and $m$ the smallest integer such that $m \geq n$, $h(r)$ is $C^m$ and $f(r)$ is $C^{m+1}$ at the surface.
+For a general polytrope with $\hat{n}>0$ and $m$ the smallest integer such that $m \geq \hat{n}$, $h(r)$ is $C^m$ and $f(r)$ is $C^{m+1}$ at the surface.
 As we shall see, the breakdown of smoothness leads to consequences for the Regge pole spectrum.
@@
 with $s=0$ in the scalar-field case, and $s=2$ in the axial gravitational-wave case.
-In the exterior, the tortoise coordinates $r_\ast$ reduces to $r_\ast = r+ 2M \ln [r/(2M) -1]+k$, where $k$ is a constant that is chosen such that $r_\ast(r=0) = 0$ and $r_\ast(r)$ is a continuous function.
+In the exterior, the tortoise coordinate $r_\ast$ reduces to $r_\ast = r+ 2M \ln [r/(2M) -1]+k$, where $k$ is a constant that is chosen such that $r_\ast(r=0) = 0$ and $r_\ast(r)$ is a continuous function.
 
@@
 % (i.e.~close to the Buchdahl bound of $R/M = 9/4$).
-In both cases we observe a discontinuity in $V_{\ell}(r)$ across the star's surface, due to the $C^0$ property of $h(r)$.
+In both cases we observe a discontinuity in $V_{\ell}(r)$ across the star's surface, due to the discontinuity in the density $\rho$ (which implies the $C^0$ property of $h(r)$).
 The jump in the potential takes opposite signs in the scalar-field and gravitational-wave cases, with
@@
 \centering
- \includegraphics[scale=0.50]{potentials_s02_CD_R6L2_v3} \\ \vspace{0.2cm}
- \includegraphics[scale=0.50]{potentials_s02_CD_R2p26L2_v3}
+ \includegraphics[scale=0.50]{potentials_s02_CD_R6L2_v4} \\ \vspace{0.2cm}
+ \includegraphics[scale=0.50]{potentials_s02_CD_R2p26L2_v4}
 \caption{\label{RP_approx_2Mw_3_6_s_1} The effective potential $V_\ell$ for a quadrupole ($\ell =2$) perturbation of a compact body of constant density and tenuity $R/M = 6$ (upper) and $R /M = 2.26$ (lower).
-The scalar field potential (\ref{Inside_Potentiel}) and axial gravitational-wave potential (\ref{RW_Potentiel_axialGW}) are indicated as solid/black lines and dotted/red lines, respectively.
+The scalar field potential - Eq.~(\ref{Inside_Potentiel}) - and axial gravitational-wave potential - Eq.~(\ref{RW_Potentiel_axialGW}) - are indicated as solid/black lines and dotted/red lines, respectively.
 The horizontal axis is the tortoise coordinate $r_\ast/(2M)$ defined in Eq.~(\ref{eq:tortoise}).}
@@
 
-The \emph{quasinormal mode spectrum} is the set of frequencies $\{ \omega_{\ell n} \}$ in the complex-$\omega$ plane at which the scattering matrix $ S_{\ell}(\omega)$ has a simple pole for a integer value of $\ell$ (so $\ell \in \mathbb{N}$ and $\omega_{\ell n} \in \mathbb{C}$).
+The \emph{quasinormal mode spectrum} is the set of frequencies $\{ \omega_{\ell n} \}$ in the complex-$\omega$ plane at which the scattering matrix $ S_{\ell}(\omega)$ has a simple pole for an integer value of $\ell$ (so $\ell \in \mathbb{N}$ and $\omega_{\ell n} \in \mathbb{C}$).
 
@@
 This branch of modes is somewhat similar to modes for acoustic waves scattered of a hard sphere.
-   \item Trapped modes \cite{Chandrasekhar449}: These modes exist for UCOs with $R/M < 3$, because the effective radial potential has a local minimum inside the star, and local maximum near the photon sphere $r=3M$.
+   \item Trapped modes \cite{Chandrasekhar449}: These modes may exist when the effective radial potential has a cavity region, which is the case for UCOs ($R/M < 3$).
 %The trapped modes are essentially the first few curvature modes with energy less than the potential barrier.
@@
 Benhar, Berti and Ferarri (BBF) have extended this method to the axial sector.
-Here we shall present a generalisation the BBF method for axial \emph{and} scalar QNM frequencies ($s=2$ and $s=0$ respectively).
+Here we shall present a generalisation of the BBF method for axial \emph{and} scalar QNM frequencies ($s=2$ and $s=0$ respectively).
 The method is equally valid, \textit{mutatis mutandis}, for finding Regge poles $\{\lambda_n(\omega)= \ell_n +1/2\}$ of $ S_{\ell}(\omega)$.
@@
 
-It is important to note that, the \textit{continued fraction method} is applied to the three-term recurrence relation. To do this, Leins~\emph{et al.} and BBF use the method introduced by Leaver in
-the case of Reissner-Nordst\"om black holes \cite{Leaver:1990zz}, \textit{i.e.}, reducing the four-term recurrence relations \eqref{Recurrence_4_terms} to a three-term recurrence relation by using the gaussian elimination step.
+It is important to note that, the \textit{continued fraction method} applies to three-term recurrence relations. Leins~\emph{et al.} and BBF use the method introduced by Leaver in
+the case of Reissner-Nordst\"om black holes \cite{Leaver:1990zz} to reduce four-term recurrence relations (as in \eqref{Recurrence_4_terms}) to three-term recurrence relations by using the gaussian elimination step.
 
@@
 The axial GW $s=2$ modes (filled markers) are typically close to their scalar-field $s=0$ counterparts (unfilled markers), as might be anticipated from the similarities in the effective potentials for the two cases (see Fig.~\ref{fig:Veff}).
+\tom{We find no evidence of Regge poles in the fourth quadrant when $\omega>0$.
+For $\omega<0$ we find that $\lambda_n(-\omega) = \lambda_n(\omega)$.
+The contour integral deformation means we do not consider poles in the second and third quadrants (for Mohamed: I propose we do not go into more detail about this and the choice of boundary condition...but I am happy to be over ruled!)}
 
@@
 \end{equation}
-It has been shown \cite{Zhang:2011pq} that the asymptotic expressions of $\phireg$ and $\phiout$ can be derived in asymptotic regions, by using the standard WKB approximation.
-In the high-frequency limit, the interior solution of Eq.~(\ref{H_Radial_equation}) is (see Ref.~\cite{Zhang:2011pq})
+It has been shown \cite{Zhang:2011pq} that asymptotic expressions of $\phireg$ and $\phiout$ can be derived in asymptotic regions, by using a WKB approximation. 
+They claim that in the high-frequency limit, the interior solution of Eq.~(\ref{H_Radial_equation}) is (see Ref.~\cite{Zhang:2011pq})
+%
 \begin{equation}\label{Approx_origin}
@@
 \end{equation}
-where $j_{\lambda-1/2}(\cdot)$ is the spherical Bessel function of the first kind. In addition
+where $j_{\lambda-1/2}(\cdot)$ is the spherical Bessel function of the first kind.
+This is in fact the regular solution of a comparison equation to Eq.~(\ref{H_Radial_equation}) obtained by keeping only the angular momentum term of the potential, by replacing $r\rightarrow r_*$ in the denominator of this term, and setting $f(r) =1$.
+Keeping only the angular momentum term is justified if $l>>1$,.
+The other two steps seem justified when we consider expansions in the tenuity $R/M$, and reject terms of $O\l( \frac{M}{R}\r)$.
+We have
+\begin{eqnarray}\label{r_star}
+  r_*(r) &=& \int_{0}^{r}\, dr'\,\frac{1}{\sqrt{f(r')h(r')}} \\
+  &\approx&  r - \frac{3}{2}\frac{M}{R}r + O\l( \frac{M}{R}\r)^2,
+\end{eqnarray}
+and 
+\begin{equation}
+f(r) \approx 1 - 3 \frac{M}{R} + O\l( \frac{M}{R}\r)^2. 
+\end{equation}
+%
+Thus, this approach is only justified for objects with a \emph{large} tenuity. We will see that this yields reasonably good qualitative results even for a modest $R/M \approx 6$. 
+Secondly
 \begin{equation}
@@
 \end{equation}
-Substituting Eq. \eqref{Approx_infinity} into condition \eqref{Wronskian} we obtain
+Substituting Eqs. \eqref{Approx_infinity} and \eqref{Approx_origin_bis} into condition \eqref{Wronskian} we obtain
 \begin{equation}\label{WKB_1}
@@
 \end{eqnarray}
-is a sum over the Regge poles lying in the first quadrant of the CAM plane.
+is a sum over the Regge poles lying in the first and fourth quadrants of the CAM plane.
 Of course, Eqs.~(\ref{CAM_Scalar_Scattering_amp_tot}), (\ref{CAM_Scalar_Scattering_amp_decomp}) and (\ref{CAM_Scalar_Scattering_amp_decomp_RP}) provide an exact representation of the scattering amplitude $\hat{f} (\omega, \theta)$ for the scalar field, equivalent to the initial partial wave expansion (\ref{Scalar_Scattering_amp}).
@@
 
-We can be confident that there are no additional branches of Regge poles in the first quadrant, for two reasons.
+We can be confident that there are no additional branches of Regge poles in the first or fourth quadrants, for two reasons.
 First, we have scanned across the complex-$\lambda$ domains shown in Figs.~\ref{RP_R6_approx_2Mw_3_6_s_1} and \ref{RP_R226_approx_2Mw_3_6_s_1}, as detailed in Sec.~\ref{subsec:method}.

### 2019-12-17 rainbowCAM.tex
Tom, please add the new versions of the plots in Fig 1 to the repository.
made some comments on poles in the other quadrants

@@
 Next, we examine the role of Regge poles in the time-independent scattering of monochromatic planar waves.
-We apply Complex Angular Momentum techniques to re-sum the partial wave series for the scattering amplitude, expressing it as a residue series evaluated at poles in the first and fourth quadrants, accompanied by a background integral.
+We apply Complex Angular Momentum techniques to re-sum the partial wave series for the scattering amplitude, expressing it as a residue series evaluated at poles in the first quadrant, accompanied by a background integral.
 We compute the scattering cross section at several frequencies, and show precise agreement with the partial-wave calculations.
@@
 \centering
- \includegraphics[scale=0.50]{potentials_s02_CD_R6L2_v4} \\ \vspace{0.2cm}
- \includegraphics[scale=0.50]{potentials_s02_CD_R2p26L2_v4}
+ \includegraphics[scale=0.50]{potentials_s02_CD_R6L2_v3} \\ \vspace{0.2cm}
+ \includegraphics[scale=0.50]{potentials_s02_CD_R2p26L2_v3}
 \caption{\label{RP_approx_2Mw_3_6_s_1} The effective potential $V_\ell$ for a quadrupole ($\ell =2$) perturbation of a compact body of constant density and tenuity $R/M = 6$ (upper) and $R /M = 2.26$ (lower).
@@
 The axial GW $s=2$ modes (filled markers) are typically close to their scalar-field $s=0$ counterparts (unfilled markers), as might be anticipated from the similarities in the effective potentials for the two cases (see Fig.~\ref{fig:Veff}).
-\tom{We find no evidence of Regge poles in the fourth quadrant when $\omega>0$.
-For $\omega<0$ we find that $\lambda_n(-\omega) = \lambda_n(\omega)$.
-The contour integral deformation means we do not consider poles in the second and third quadrants (for Mohamed: I propose we do not go into more detail about this and the choice of boundary condition...but I am happy to be over ruled!)}
+
+\tom{I have added two comments here about the rest of the complex $\lambda$ plane. Feel free to edit.}
+
+We find no evidence of Regge poles in the fourth quadrant when $\omega>0$.
+In addition, we find that $\lambda_n(-\omega) = \lambda_n(\omega)^*$ so that there are Regge poles in the fourth quadrant when $\omega<0$.
+Here we will only consider $\omega>0$.
+
+We propose that the good analytical extension of modes into the second and third quadrants is to enforce the regular boundary condition for Re$[\lambda]<0$, i.e.
+$\phi_{\omega\ell} \sim r^{-\lambda+1/2}$ as $r\rightarrow 0$.
+Since the wave equation is invariant under the transformation $\lambda \rightarrow -\lambda$, it can be seen that the distribution of poles in the left half complex plane - Re$[\lambda]<0$ - follows from the poles in the right half complex plane by reflection through the origin.
 
@@
 \end{eqnarray}
-is a sum over the Regge poles lying in the first and fourth quadrants of the CAM plane.
+is a sum over the Regge poles lying in the first quadrant of the CAM plane.
 Of course, Eqs.~(\ref{CAM_Scalar_Scattering_amp_tot}), (\ref{CAM_Scalar_Scattering_amp_decomp}) and (\ref{CAM_Scalar_Scattering_amp_decomp_RP}) provide an exact representation of the scattering amplitude $\hat{f} (\omega, \theta)$ for the scalar field, equivalent to the initial partial wave expansion (\ref{Scalar_Scattering_amp}).
@@
 
-We can be confident that there are no additional branches of Regge poles in the first or fourth quadrants, for two reasons.
+We can be confident that there are no additional branches of Regge poles in the first quadrant, for two reasons.
 First, we have scanned across the complex-$\lambda$ domains shown in Figs.~\ref{RP_R6_approx_2Mw_3_6_s_1} and \ref{RP_R226_approx_2Mw_3_6_s_1}, as detailed in Sec.~\ref{subsec:method}.

### 2019-12-18 rainbowCAM.tex
Minor changes on a read through up to Tom's WKB section. Also edited Moh's para slightly in the conclusions, and changed the bibliography style.

@@
 In such a scenario, an electromagnetic wave will not penetrate far inside the compact body; but on the other hand, a gravitational wave will pass through the body without impediment from the matter distribution.
-Similarly, a neutron star is expected to be substantially transparent to neutrinos.
-Even in such cases where the coupling to matter is negligible, the incident wave will nevertheless be scattered by the influence of the spacetime curvature.
+A neutron star is also expected to be effectively transparent to neutrinos.
+Even in such cases where the coupling to matter is negligible, the incident wave will nevertheless be scattered by the spacetime curvature.
 Thus, the resulting scattering pattern depends not just on $M\omega$, but also on the internal structure of the body, and on its inverse compactness or \emph{tenuity}, $R/M$.
@@
 Their study focussed on resonant modes (poles with small imaginary parts corresponding to trapped $w$-modes or fluid modes), and it employed CAM theory to calculate the flow of gravitational energy through a star.
-It seems reasonable to assume that CAM theory could lead to a deeper understanding of scattering by other compact objects, such as neutron stars and UCOs, and this is our purpose herein.
+% It seems reasonable to assume that CAM theory could lead to a deeper understanding of scattering by other compact objects, such as neutron stars and UCOs, and this is our purpose herein.
 
@@
 
-\moh{Remark for Tom and Sam : In the following paragraph : Render unto Caesar the things that are Caesar's}\\
-
-Stratton and Dolan have recently shown that time-independent scattering by compact bodies generates (in principle) a \emph{rainbow scattering} phenomenon in the short wavelength regime ($M \omega \gg 1$)~\cite{Dolan:2017rtj, Stratton:2019deq}.
+Time-independent scattering by compact bodies generates (in principle) a \emph{rainbow scattering} phenomenon in the short wavelength regime ($M \omega \gg 1$)~\cite{Dolan:2017rtj, Stratton:2019deq}.
 The rainbow scattering phenomenon is linked to the formation of a cusp caustic in the incident wavefront (see Fig.~1 in Ref.~\cite{Stratton:2019deq}), and to the stationary point in the geodesic deflection function associated with a ray (that is, a null geodesic) that passes somewhat inside the body.
@@
 For compact bodies such as neutron stars, however, the cusp caustic forms near the surface of the body, and the rainbow angle is large ($\theta_r \gtrsim 59.6^\circ$ for $R/M = 6$; see Table I in Ref.~\cite{Stratton:2019deq}).
-In this case, the rainbow angle is -- in principle at least -- a useful diagnostic of the matter distribution within the body and thus its nuclear equation of state.
+In this case, the rainbow angle is -- in principle at least -- a diagnostic of the matter distribution within the body and thus its nuclear equation of state.
 
@@
 Sec.~\ref{sec:RP} focusses on the Regge pole spectrum.
-Here we outline the link between Regge poles and QNMs (\ref{subsec:QNMs_RPs}), we describe the numerical method (\ref{subsec:method}), and we present new numerical results for the spectrum (\ref{subsec:results1}) which exhibits three distinct branches of Regge poles (see e.g.~Fig.~\ref{RP_R226_approx_2Mw_3_6_s_1}); in Sec.~\ref{subsec:WKB} we apply the WKB method to obtain an approximate formula for the ``broad resonance'' branch.
+Here we outline the link between Regge poles and QNMs (\ref{subsec:QNMs_RPs}), we describe the numerical method (\ref{subsec:method}), and we present new numerical results for the spectrum (\ref{subsec:results1}) which exhibits three distinct branches of Regge poles (see e.g.~Fig.~\ref{RP_R226_approx_2Mw_3_6_s_1}).
+In Sec.~\ref{subsec:WKB} we apply the WKB method to obtain an approximate formula for the ``broad resonance'' branch.
 Sec.~\ref{sec:CAM} concerns the application of CAM techniques to the calculation of the scattering cross section.
@@
 
-In this section we describe the model for the compact object (\ref{SecIIa}); we introduce the effective potentials for scalar field and axial gravitational waves (\ref{subsec:Potentials}); and we define the physical boundary conditions and the S-matrix (\ref{subsec:bc}).
+%In this section we describe the model for the compact object (\ref{SecIIa}); we introduce the effective potentials for scalar field and axial gravitational waves (\ref{subsec:Potentials}); and we define the physical boundary conditions and the S-matrix (\ref{subsec:bc}).
 
@@
 
-The \emph{Regge pole spectrum} is the set of angular momenta $\lambda_{n}(\omega) = \ell_{n}(\omega) + 1/2$ in the complex-$\lambda$ plane at which the scattering matrix has a simple pole for a real value of $\omega$ (so $\omega \in \mathbb{R}$ and $\lambda_{n}(\omega) \in \mathbb{C}$).
+The \emph{Regge pole spectrum} is the set of angular momenta $\lambda_{n}(\omega) \equiv \ell_{n}(\omega) + 1/2$ in the complex-$\lambda$ plane at which the scattering matrix has a simple pole for a real value of $\omega$ (so $\omega \in \mathbb{R}$ and $\lambda_{n}(\omega) \in \mathbb{C}$).
 Here $n$ is an index for enumerating the discrete spectrum of poles.
@@
 They are highly damped and correspond to excitations of the dynamical perturbed space-time.
-For a review of (gravitational) quasinormal modes in relativistic stars and black holes see Ref.~\cite{Kokkotas:1999bd}.
+For a review of (gravitational) quasinormal modes in relativistic stars and black holes, see Ref.~\cite{Kokkotas:1999bd}.
 
@@
    \item Interface modes ($\omega_{\text{II}}$-modes \cite{Leins:1993zz}), characterised by very rapid damping (i.e.~large negative imaginary part of $\omega_{\ell n}$).
-This branch of modes is somewhat similar to modes for acoustic waves scattered of a hard sphere.
+This branch of modes is somewhat similar to modes for acoustic waves scattered by a hard sphere.
    \item Trapped modes \cite{Chandrasekhar449}: These modes may exist when the effective radial potential has a cavity region, which is the case for UCOs ($R/M < 3$).
@@
 % \nonumber % Remove numbering (before each equation)
- \phi_{\omega_\ell}(r)&=&\left(\frac{r}{2M}-1\right)^{i 2M\omega} \,e^{i\omega r} \sum_{n=0}^{+\infty}a_n\left(1-\frac{b}{r}\right)^n \nonumber \\
-                      &=& e^{i\omega r_*(r)}\sum_{n=0}^{+\infty}a_n\left(1-\frac{b}{r}\right)^n
+ \phi_{\omega_\ell}(r)&=&\left(\frac{r}{2M}-1\right)^{i 2M\omega} \,e^{i\omega r} \sum_{n=0}^{+\infty}a_n\left(1-\frac{b}{r}\right)^n , \nonumber \\
+                      &=& e^{i\omega r_*(r)}\sum_{n=0}^{+\infty}a_n\left(1-\frac{b}{r}\right)^n .
 \end{eqnarray}
@@
 \begin{equation}\label{Recurrence_4_terms}
-\alpha_n a_{n+1} + \beta_n a_{n} +\gamma_{n} a_{n-1} +\delta_{n} a_{n-2}  = 0, \quad \forall n\geq 2
+\alpha_n a_{n+1} + \beta_n a_{n} +\gamma_{n} a_{n-1} +\delta_{n} a_{n-2}  = 0, \quad \forall n\geq 2 ,
 \end{equation}
@@
 \begin{eqnarray}\label{Coeffs_3_termes}
- && \alpha_n = n (n+1)\left(1-\frac{2M}{b}\right)   \\
- && \beta_n  = 2i\omega b n + 3\left(\frac{2M}{b}\right)n^2-2n^2  \\
- && \gamma_n = \left(1-\frac{6M}{b}\right)n(n-1)-\frac{2M\beta_s}{b}-\ell(\ell+1)  \\
- && \delta_n = \left(\frac{2M}{b}\right)\left(n(n-2)+\beta_s\right)
+ && \alpha_n = n (n+1)\left(1-\frac{2M}{b}\right),    \\
+ && \beta_n  = 2i\omega b n + 3\left(\frac{2M}{b}\right)n^2-2n^2 ,  \\
+ && \gamma_n = \left(1-\frac{6M}{b}\right)n(n-1)-\frac{2M\beta_s}{b}-\ell(\ell+1) ,  \\
+ && \delta_n = \left(\frac{2M}{b}\right)\left(n(n-2)+\beta_s\right) .
 \end{eqnarray}
 \end{subequations}
-To determine the initial conditions $a_0$ and $a_1$, we impose the continuity of $\phi_{\omega_\ell}(r)$ and its derivative in $r = b$, according to Eq~\eqref{Power_series}, we obtain:
+To determine the initial conditions $a_0$ and $a_1$, we impose the continuity of $\phi_{\omega_\ell}(r)$ and its derivative in $r = b$, according to Eq~\eqref{Power_series}, to obtain:
 \begin{eqnarray}\label{Initial_Conds}
- && a_0 = e^{i\omega r_*(b)\phi_{\omega_\ell}(b)}  \\
- && a_1 = b e^{-i\omega r_*(b)}\left(\frac{-i\omega b}{b-2M}\phi_{\omega_\ell}(b)+ \frac{d}{dr}\phi_{\omega_\ell}(r)\Big{|}_{r=b}\right)
+ && a_0 = e^{i\omega r_*(b)\phi_{\omega_\ell}(b)} ,  \\
+ && a_1 = b e^{-i\omega r_*(b)}\left(\frac{-i\omega b}{b-2M}\phi_{\omega_\ell}(b)+ \frac{d}{dr}\phi_{\omega_\ell}(r)\Big{|}_{r=b}\right) .
 \end{eqnarray}
-Here, to obtain $\phi_{\omega_\ell}(b)$ and its derivative in $r=b$, we need to solve numerically the Eq.~\eqref{H_Radial_equation} inside the star and to continue the solution outside, up to $r=b$, by solving the Regge-wheeler equation.
+Here, to obtain $\phi_{\omega_\ell}(b)$ and its derivative in $r=b$, we need to solve Eq.~\eqref{H_Radial_equation} numerically inside the star, and then to extend the solution outside, up to $r=b$, by solving the Regge-Wheeler equation numerically.
 
 It is important to note that, the \textit{continued fraction method} applies to three-term recurrence relations. Leins~\emph{et al.} and BBF use the method introduced by Leaver in
-the case of Reissner-Nordst\"om black holes \cite{Leaver:1990zz} to reduce four-term recurrence relations (as in \eqref{Recurrence_4_terms}) to three-term recurrence relations by using the gaussian elimination step.
-
-We do not use the gaussian elimination step.
+the case of Reissner-Nordst\"om black holes \cite{Leaver:1990zz} to reduce four-term recurrence relations (as in \eqref{Recurrence_4_terms}) to three-term recurrence relations by using a Gaussian elimination step.
+
+We do not use the Gaussian elimination step.
 Instead we find solutions of \eqref{Recurrence_4_terms} by adapting the \textit{Hill determinant approach} employed by Majumdar and Panchapakesan~\cite{mp} to solve the black hole recurrence formula of Leaver \cite{Leaver:1985ax}.
@@
 %
-Letting $D_n$ be the determinant of the $n \times n$ sub matrix of $D$ (with diagonal $\{\beta_0,\beta_1,....\beta_n\}$), by \eqref{Recurrence_4_terms}
+Letting $D_n$ be the determinant of the $n \times n$ sub-matrix of $D$ (with diagonal $\{\beta_0,\beta_1,....\beta_n\}$), by \eqref{Recurrence_4_terms}
 %
@@
 \label{derecurrence_4_termes}
-D_n=\beta_n D_{n-1} - \gamma_{n}\alpha_{n-1}D_{n-2} + \delta_n \alpha_{n-1} \alpha_{n-2} D_{n-3}
+D_n=\beta_n D_{n-1} - \gamma_{n}\alpha_{n-1}D_{n-2} + \delta_n \alpha_{n-1} \alpha_{n-2} D_{n-3} ,
 \end{equation}
@@
     D_0 &=\beta_0, \\
-    D_1 &=\beta_1\beta_0-\gamma_1\alpha_0  \\
-    D_2 &=\beta_0(\beta_1 \beta_2 - \alpha_1 \gamma_2)- \alpha_0(\alpha_1 \delta_2 -\gamma_1 \beta_2)
+    D_1 &=\beta_1\beta_0-\gamma_1\alpha_0 , \\
+    D_2 &=\beta_0(\beta_1 \beta_2 - \alpha_1 \gamma_2)- \alpha_0(\alpha_1 \delta_2 -\gamma_1 \beta_2) .
  \end{split}
@@
 %
-Or equivalently \moh{we can also use this forme}
+Equivalently, % \moh{we can also use this forme}
 \begin{align}
 \label{recurrence_Hill_RN_4_termes}
-D_n    & =\left(\prod_{k=1}^{n+1} k^2\right) P_{n+1} \nonumber\\
+D_n    & =\left(\prod_{k=1}^{n+1} k^2\right) P_{n+1} , \nonumber\\
        &  = 1\times 2^2 \ldots (n-2)^2(n-1)^2n^2(n+1)^2 P_{n+1},
@@
   &+& \left(\frac{\delta_{n-1}}{n^2}\right) \left(\frac{\alpha_{n-2}}{(n-1)^2}\right) \left(\frac{\alpha_{n-3}}{(n-2)^2}\right) P_{n-3}
+,
 \end{eqnarray}
@@
  \begin{split}
-    P_1&=\beta_0\\
-    P_2&=\frac{\beta_0\beta_1-\gamma_1\alpha_0}{4} \\
-    P_3&=\frac{\beta_0(\beta_1 \beta_2 - \alpha_1 \gamma_2)- \alpha_0(\alpha_1 \delta_2 -\gamma_1 \beta_2)}{36}
+    P_1&=\beta_0 , \\
+    P_2&=\frac{\beta_0\beta_1-\gamma_1\alpha_0}{4} ,\\
+    P_3&=\frac{\beta_0(\beta_1 \beta_2 - \alpha_1 \gamma_2)- \alpha_0(\alpha_1 \delta_2 -\gamma_1 \beta_2)}{36} .
  \end{split}
@@
 
-Regge poles (QNM frequencies) are found by fixing $\omega$ ($\lambda$) and numerically finding roots $\lambda_n$ ($\omega_n$) of $D_n$, i.e.~ $D_n(\lambda_n,\omega)=0$ ($D_n(\lambda,\omega_n)=0$).
+Regge poles (QNM frequencies) are found by fixing $\omega$ ($\lambda$) and numerically finding roots $\lambda_n$ ($\omega_n$) of $D_n$, i.e.,~$D_n(\lambda_n,\omega)=0$ ($D_n(\lambda,\omega_n)=0$).
 %Regge poles $\lambda_n$ (QNM frequencies $\omega_n$) are roots of $D_n$
@@
  \subsection{Numerical results: the spectrum}\label{subsec:results1}
-In this section we show numerical results for the Regge pole spectrum of a compact body, in two particular cases: (i) a neutron-star-like body with tenuity $R / M = 6$, and (ii) a UCO with tenuity $R / M = 2.26$ close to the Buchdahl bound.
+In this section we show numerical results for the Regge pole spectrum of a compact body, in two particular cases: (i) a neutron-star-like body with tenuity $R / M = 6$, and (ii) a UCO with tenuity $R / M = 2.26$, close to the Buchdahl bound.
 Results for the frequencies $M \omega = 3/2$ and $M \omega = 8$ are compared, for the scalar-field ($s=0$) and axial GW ($s=2$) cases.
@@
 Figure \ref{fig:rp1} shows the Regge pole spectrum for a neutron-star-like body ($R/M = 6$).
-We see that there are two branches of Regge poles in the first quadrant, which meet at $\text{Re}( \lambda_n(\omega) ) \sim \omega b_0$, where $b_0$ is the impact parameter for the null ray which grazes the surface of the compact body.
+We see that there are two branches of Regge poles in the first quadrant, which meet near $\text{Re}( \lambda_n(\omega) ) \sim \omega b_0$, where $b_0$ is the impact parameter for the null ray which grazes the surface of the compact body.
 The axial GW $s=2$ modes (filled markers) are typically close to their scalar-field $s=0$ counterparts (unfilled markers), as might be anticipated from the similarities in the effective potentials for the two cases (see Fig.~\ref{fig:Veff}).
@@
 \tom{I have added two comments here about the rest of the complex $\lambda$ plane. Feel free to edit.}
+\sam{Let's discuss this on Skype - below are my naive questions.}
 
@@
 Here we will only consider $\omega>0$.
+\sam{Are there poles in the second quadrant}
 
@@
 Since the wave equation is invariant under the transformation $\lambda \rightarrow -\lambda$, it can be seen that the distribution of poles in the left half complex plane - Re$[\lambda]<0$ - follows from the poles in the right half complex plane by reflection through the origin.
+\sam{reflection through the origin would generate poles in the 3rd quadrant; and if there were originally poles in the 2nd quadrant, poles in the 4th quadrant. Can we clarify this?}
 
@@
 We adapt their method to obtain analytical approximations for the ``broad resonances'' for massless waves on a stellar background.
-The starting point is with the radial equation (\ref{H_Radial_equation}) with either the effective potential for the scalar field (\ref{Inside_Potentiel}), or for axial gravitational perturbations (\ref{RW_Potentiel_axialGW}).
-
-Regge poles and quasinormal modes for relativistic stellar models (of which \textit{w}-modes are a sub-category for gravitational perturbations) both satisfy the same wave equation and the same boundary conditions but with different interpretations for the angular momentum index and the frequency.
+The starting point is the radial equation (\ref{H_Radial_equation}) with either the effective potential for the scalar field (\ref{Inside_Potentiel}), or for axial gravitational perturbations (\ref{RW_Potentiel_axialGW}).
+
+Regge poles and quasinormal modes for relativistic stellar models (of which \textit{w}-modes are a sub-category for gravitational perturbations) both satisfy the same wave equation and the same boundary conditions, but with different interpretations for the angular momentum index and the frequency.
 Both types of pole satisfy the regularity condition at the origin~\eqref{bc_1_in} and the condition of a purely outgoing wave in the far field
@@
 It has been shown \cite{Zhang:2011pq} that asymptotic expressions of $\phireg$ and $\phiout$ can be derived in asymptotic regions, by using a WKB approximation. 
-They claim that in the high-frequency limit, the interior solution of Eq.~(\ref{H_Radial_equation}) is (see Ref.~\cite{Zhang:2011pq})
+They claim that in the high-frequency limit, the interior solution of Eq.~(\ref{H_Radial_equation}) is (see Ref.~\cite{Zhang:2011pq}). \sam{hmm `they claim' - do we agree?}
 %
@@
 
-The CAM toolkit was applied here to gain a complementary practical method for calculating scattering amplitudes.
-In summary, we have shown that, for the intermediate and high angles, these scattering amplitudes can be reconstructed in terms of Regge poles with great precision in the intermediate and high frequencies regime.
-It is important to note that for compact objects (\textit{i.e.}, $R/M=6$), we observed that it is necessary to take into account the background integral contributions to describe the glory and this regardless of the frequency.
-Which does not the case for UCOs since only the sum over the Regge poles is enough.
-Moreover, the sum over the Regge poles permitted us to overcome the difficulties linked to the lack of convergence from which the scattering amplitude suffers (\textit{i.e.} partial wave expansions) due to the long-range of the field propagating on the Schwarzschild black hole (outside the compact body).
-However, the existence of the broad resonance branch (see also narrow resonance branch for the UCOs) close to the real axis with an approximately uniform spacing, $\Delta\lambda\sim 2$, requires the calculation of a large number of poles.
+\sam{I have made v minor edits. It looks good to me, and I propose we remove both these comments during the Skype.}
+
+The CAM toolkit was applied here to gain a complementary method for calculating scattering amplitudes.
+In summary, we have shown that, for the intermediate and high angles, these scattering amplitudes can be reconstructed in terms of Regge poles with great precision in the intermediate and high frequency regimes.
+For compact objects ($R/M\sim6$), we observed that it is necessary to take into account the background integral contributions to describe the glory, and this is true regardless of the frequency.
+Conversely, this is not the case for UCOs ($R/M < 3$), where the sum over the Regge poles is sufficient to accurately describe the glory.
+Moreover, the sum over the Regge poles permitted us to overcome the difficulties linked to the lack of convergence from which the scattering amplitude suffers (\textit{i.e.} partial wave expansions) due to the long-range of the field propagating on the Schwarzschild spacetime outside the compact body.
+However, the existence of the broad resonance branch %(see also narrow resonance branch for the UCOs)
+close to the real axis with an approximately uniform spacing, $\Delta\lambda\sim 2$, requires the calculation of a large number of poles.
 In the black-hole case, by contrast, there is only a single branch of surface-wave-type modes (see Fig.~\ref{RP_R6_approx_2Mw_3_6_s_1}), and in the high-frequency limit, a few poles ($<5$) capture both the orbiting and glory phenomena \cite{Folacci:2019cmc, Folacci:2019vtt}.
-Also, in the case of the Mie scattering, a powerful extension of the CAM approach is to define the so-called Regge-Debye poles using the Debye expansion (see the chapter 9 of the monograph of Nussenzveig \cite{Nussenzveig:2006}), thereby eliminating the broad resonance branch entirely and accelerating the convergence.
-This is a possible direction for a future investigation
+
+In the case of Mie scattering, a powerful extension of the CAM approach is to define the so-called Regge-Debye poles using the Debye expansion (see the chapter 9 of the monograph of Nussenzveig \cite{Nussenzveig:2006}), thereby eliminating the broad resonance branch entirely, and accelerating the convergence.
+This is a possible direction for a future investigation.
 

### 2019-12-18 rainbowCAM.tex
Edited two parts of the document, following Skype discussion. Over to Mohamed for final review.

@@
 \centering
- \includegraphics[scale=0.50]{potentials_s02_CD_R6L2_v3} \\ \vspace{0.2cm}
- \includegraphics[scale=0.50]{potentials_s02_CD_R2p26L2_v3}
+ \includegraphics[scale=0.50]{potentials_s02_CD_R6L2_v4} \\ \vspace{0.2cm}
+ \includegraphics[scale=0.50]{potentials_s02_CD_R2p26L2_v4}
 \caption{\label{RP_approx_2Mw_3_6_s_1} The effective potential $V_\ell$ for a quadrupole ($\ell =2$) perturbation of a compact body of constant density and tenuity $R/M = 6$ (upper) and $R /M = 2.26$ (lower).
@@
 
-\tom{I have added two comments here about the rest of the complex $\lambda$ plane. Feel free to edit.}
-\sam{Let's discuss this on Skype - below are my naive questions.}
-
-We find no evidence of Regge poles in the fourth quadrant when $\omega>0$.
-In addition, we find that $\lambda_n(-\omega) = \lambda_n(\omega)^*$ so that there are Regge poles in the fourth quadrant when $\omega<0$.
-Here we will only consider $\omega>0$.
-\sam{Are there poles in the second quadrant}
-
-We propose that the good analytical extension of modes into the second and third quadrants is to enforce the regular boundary condition for Re$[\lambda]<0$, i.e.
-$\phi_{\omega\ell} \sim r^{-\lambda+1/2}$ as $r\rightarrow 0$.
-Since the wave equation is invariant under the transformation $\lambda \rightarrow -\lambda$, it can be seen that the distribution of poles in the left half complex plane - Re$[\lambda]<0$ - follows from the poles in the right half complex plane by reflection through the origin.
-\sam{reflection through the origin would generate poles in the 3rd quadrant; and if there were originally poles in the 2nd quadrant, poles in the 4th quadrant. Can we clarify this?}
+\sam{Mohamed: please edit these two paragraphs for final version, then delete this comment.}
+
+After scanning across the domain, we find no evidence of Regge poles in the fourth quadrant of the complex-$\lambda$ plane for $\omega>0$.
+Exploring the second and third quadrants, where $\text{Re}[{\lambda}] < 0$, requires a choice to be made on the form of the boundary condition imposed at $r=0$.
+A natural choice is to impose regularity, i.e.,~$\phi_{\omega\ell} \sim r^{-\lambda+1/2}$ as $r \rightarrow 0$ for $\text{Re} [\lambda] < 0$.
+An advantage of this choice is that it leads to the same symmetry as in the black hole case for the S-matrix elements, viz.,
+\begin{equation}
+S_{\lambda - 1/2} (\omega) =. .
+\end{equation}
+\sam{Mohamed: please complete the equation above, then delete this comment.} 
+Furthermore, since the wave equation is invariant under the transformation $\lambda \rightarrow -\lambda$, it follows that the distribution of poles in the left-half of the complex plane follows by reflection through the origin.
+Thus, for $\omega > 0$, the 4th and 2nd quadrants are devoid of poles, and the 3rd quadrant has the same structure as shown in Fig.~\ref{fig:rp1}.
+Conversely, for $\omega < 0$, we may use the symmetry $\lambda_n(-\omega) = \lambda_n(\omega)^*$ to establish that there are poles in the 2nd and 4th quadrants only.
 
@@
 It has been shown \cite{Zhang:2011pq} that asymptotic expressions of $\phireg$ and $\phiout$ can be derived in asymptotic regions, by using a WKB approximation.
-They claim that in the high-frequency limit, the interior solution of Eq.~(\ref{H_Radial_equation}) is (see Ref.~\cite{Zhang:2011pq}). \sam{hmm `they claim' - do we agree?}
-%
+
+In the interior of the star, the radial function $f(r)$ is 
+\begin{equation}
+f(r) = f_0 \left(1 + O\left(\frac{M r^2}{R^3} \right) \right),
+\end{equation}
+where $f_0$ is a constant, and $h(r) = 1 - 2Mr^2/R^3$. In the vicinity of $r=0$, we may solve Eq.~(\ref{eq:tortoise}) to obtain the tortoise coordinate $r_\ast(r)$, or inversely,
+\begin{equation}
+r = \sqrt{f_0} \, r_\ast \left(1 + O\left(\frac{M r_\ast^2}{R^3} \right) \right) . \label{eq:rrstar}
+\end{equation}
+Now let us consider the radial equation (\ref{H_Radial_equation}) in the high-frequency regime with $\ell \gg 1$, such that we may neglect all but the angular momentum terms in the effective potential (\ref{Inside_Potentiel}).
+Inserting (\ref{eq:rrstar}) and neglecting the quadratic corrections leads to a comparison equation
+\begin{equation}
+\left[\frac{d^{2}}{dr_{\ast}^{2}}+\omega^{2} - \frac{\ell (\ell+1)}{r_\ast^2} \right] \phi_{\omega\ell}= 0,
+\end{equation}
+with the regular interior solution
 \begin{equation}\label{Approx_origin}
-  \phireg \underset{\omega \to \infty}{=} \omega r_* j_{\lambda-1/2} (\omega r_*),  \quad\quad 0\leq r_*\leq R_* ,
+  \phireg \underset{\omega \to \infty}{=} \omega r_* j_{\lambda-1/2} (\omega r_*),  
 \end{equation}
 where $j_{\lambda-1/2}(\cdot)$ is the spherical Bessel function of the first kind.
-This is in fact the regular solution of a comparison equation to Eq.~(\ref{H_Radial_equation}) obtained by keeping only the angular momentum term of the potential, by replacing $r\rightarrow r_*$ in the denominator of this term, and setting $f(r) =1$.
-Keeping only the angular momentum term is justified if $l>>1$,.
-The other two steps seem justified when we consider expansions in the tenuity $R/M$, and reject terms of $O\l( \frac{M}{R}\r)$.
-We have
-\begin{eqnarray}\label{r_star}
-  r_*(r) &=& \int_{0}^{r}\, dr'\,\frac{1}{\sqrt{f(r')h(r')}} \\
-  &\approx&  r - \frac{3}{2}\frac{M}{R}r + O\l( \frac{M}{R}\r)^2,
-\end{eqnarray}
-and 
-\begin{equation}
-f(r) \approx 1 - 3 \frac{M}{R} + O\l( \frac{M}{R}\r)^2. 
-\end{equation}
-%
-Thus, this approach is only justified for objects with a \emph{large} tenuity. We will see that this yields reasonably good qualitative results even for a modest $R/M \approx 6$. 
-Secondly
+
+Near the surface of the body, and in the exterior region, we use the asymptotic forms \cite{Zhang:2011pq}
 \begin{equation}
@@
 Here $R_*$ is the tortoise coordinate at the surface of the body,
-\begin{equation}\label{R_star}
-  R_*=\int_{0}^{R}\, dr\,\frac{1}{\sqrt{f(r)h(r)}}
-\end{equation}
+%\begin{equation}\label{R_star}
+%  R_*=\int_{0}^{R}\, dr\,\frac{1}{\sqrt{f(r)h(r)}}
+%\end{equation}
 and $\mathcal{R}$ is a reflection coefficient with the definition given in Ref.~\cite{Berry_1982}.
@@
 %\end{equation}
-Inserting the high frequency approximation for $j_{\lambda-1/2} (\omega r_*)$ into Eq.~\eqref{Approx_origin} we obtain \cite{nist},
+Inserting the high-frequency approximation for $j_{\lambda-1/2} (\omega r_*)$ into Eq.~\eqref{Approx_origin} we obtain \cite{nist},
 \begin{equation}\label{Approx_origin_bis}
-  \phi^{}_{\omega,\lambda-1/2} \underset{\omega \to \infty}{\approx} - \sin\left(\frac{\left(\lambda-1/2\right)\pi}{2}-\omega r_*\right)\quad\quad 0\leq r_*\leq R_*.
-\end{equation}
-Substituting Eqs. \eqref{Approx_infinity} and \eqref{Approx_origin_bis} into condition \eqref{Wronskian} we obtain
+  \phi^{}_{\omega,\lambda-1/2} \underset{\omega \to \infty}{\approx} - \sin\left(\frac{\left(\lambda-1/2\right)\pi}{2}-\omega r_*\right).
+\end{equation}
+Substituting Eqs.~\eqref{Approx_infinity} and \eqref{Approx_origin_bis} into condition \eqref{Wronskian} leads to
 \begin{equation}\label{WKB_1}
@@
 The data shows that, while the leading-order WKB approximation captures the essential features of the broad resonance branch, it is not particularly accurate.
-Higher-order extensions are possible, but not pursued here.
+Higher-order extensions are possible in principle, but not pursued here.
 
@@
 
-\moh{I propose this following paragraph in summary}\\
-
-%The CAM toolkit was applied here to gain a complementary practical method for calculating scattering amplitudes.
-However, in its current form, the method is not particularly efficient, for two reasons; first, it requires the computation of a background integral in addition to residue sum; and second, the poles on the broad-resonance branch have an approximately uniform spacing, $\Delta \lambda \sim 2$, and thus a large number of poles must be calculated.
-In the black-hole case, by contrast, there is only a single branch of surface-wave-type modes (see Fig.~\ref{RP_R6_approx_2Mw_3_6_s_1}), and in the high-frequency limit, a single pole captures both the orbiting and glory phenomena \cite{Folacci:2019cmc, Folacci:2019vtt}.
-In the case of Mie scattering, a powerful extension of the CAM approach is to define the so-called Regge-Debye poles \cite{Nussenzveig:2006}, thereby eliminating the surface-wave branch entirely.
-This is a possible direction for future investigation.
-
-\sam{I have made v minor edits. It looks good to me, and I propose we remove both these comments during the Skype.}
-
 The CAM toolkit was applied here to gain a complementary method for calculating scattering amplitudes.

### 2019-12-18 rainbowCAM.tex
Adding the symmetry property of S-matrix, and made comment for 2 paragraphs

@@
 Sec.~\ref{SecII} reviews the theory of scalar waves on a spherically-symmetric spacetime of a compact object.
-Here we describe our model spacetime (\ref{SecIIa}), the effective potentials for wave scattering (\ref{subsec:Potentials}) and the physical boundary conditions that define the S-matrix (\ref{subsec:bc}).
+Here we describe our model spacetime (\ref{SecIIa}), the effective potentials for wave scattering (\ref{subsec:Potentials}) and the physical boundary conditions that define the $S$-matrix (\ref{subsec:bc}).
 Sec.~\ref{sec:RP} focusses on the Regge pole spectrum.
@@
 \end{equation}
-With the complex coefficients $A^{(\pm)}_\ell (\omega)$ we then define the \emph{S-matrix elements},
+With the complex coefficients $A^{(\pm)}_\ell (\omega)$ we then define the \emph{$S$-matrix elements},
 \begin{equation}\label{Matrix_S}
@@
 
-\sam{Mohamed: please edit these two paragraphs for final version, then delete this comment.}
+\moh{Sam \& Tom: I find the two paragraphs are perfect!
+A small suggestion: the remarks in these two paragraphs also concern UCOs, so I added in the 2nd paragraph \ldots ``as shown in Fig.
+2 and 3.
+''.
+If you agree, please, delete the comment}
 
@@
 A natural choice is to impose regularity, i.e.,~$\phi_{\omega\ell} \sim r^{-\lambda+1/2}$ as $r \rightarrow 0$ for $\text{Re} [\lambda] < 0$.
-An advantage of this choice is that it leads to the same symmetry as in the black hole case for the S-matrix elements, viz.,
-\begin{equation}
-S_{\lambda - 1/2} (\omega) =. .
-\end{equation}
-\sam{Mohamed: please complete the equation above, then delete this comment.} 
+An advantage of this choice is that it leads to the same symmetry as in the black hole case for the $S$-matrix elements (see Ref.~\cite{Andersson:1994rk,Folacci:2019cmc}), viz.,
+\begin{equation}\label{Matrix_S_CAM_symm}
+S_{-\lambda -1/2}(\omega) =  e^{-2i \pi \lambda} \, S_{\lambda -1/2}(\omega)
+\end{equation}
+
 Furthermore, since the wave equation is invariant under the transformation $\lambda \rightarrow -\lambda$, it follows that the distribution of poles in the left-half of the complex plane follows by reflection through the origin.
-Thus, for $\omega > 0$, the 4th and 2nd quadrants are devoid of poles, and the 3rd quadrant has the same structure as shown in Fig.~\ref{fig:rp1}.
+Thus, for $\omega > 0$, the 4th and 2nd quadrants are devoid of poles, and the 3rd quadrant has the same structure as shown in Fig.~\ref{fig:rp1} and~\ref{fig:rp2}.
 Conversely, for $\omega < 0$, we may use the symmetry $\lambda_n(-\omega) = \lambda_n(\omega)^*$ to establish that there are poles in the 2nd and 4th quadrants only.

### 2019-12-21 rainbowCAM.tex
I agreed with Mohamed's minor change, and I have deleted the comment as suggested.
Adding appendix and one reference to biblio

@@
 
-\moh{Sam \& Tom: I find the two paragraphs are perfect!
-A small suggestion: the remarks in these two paragraphs also concern UCOs, so I added in the 2nd paragraph \ldots ``as shown in Fig.
-2 and 3.
-''.
-If you agree, please, delete the comment}
-
 After scanning across the domain, we find no evidence of Regge poles in the fourth quadrant of the complex-$\lambda$ plane for $\omega>0$.
@@
 
+\appendix
+
+\section{Location of the Regge poles in complex $\lambda$-plan}
+\label{appen}
+
+\moh{I have established some proprieties (symmetry relations) to connect different quadrants and I moved part of the paragraph from section III-c to the appendix.
+Sam \& Tom : Please be critical and It is free to change.}
+
+In this appendix, we will show that, for $\omega$ real, the zeros of the $S$-matrix (\textit{i.e.}, the Regge poles), or in other words 
+the zeros of the coefficient $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~\eqref{Matrix_S_CAM}]
+\begin{equation}\label{zeros_Am}
+   A^{(-)}_{\lambda-1/2} (\omega)\Big{|}_{\lambda =\lambda_n} = 0
+\end{equation}
+are lying in the right-half of the complex $\lambda$-plan. To do this, it is convenient to write the boundary conditions \eqref{bc_1_in} and \eqref{bc_2_in} in the following form:
+\begin{equation}
+\label{bc_CAM}
+\phi_{\lambda-\frac{1}{2}}(\omega) \sim
+\left\{
+\begin{aligned}
+&r^{\lambda+\frac{1}{2}}\hspace{8em} \scriptstyle{r \rightarrow 0,} \quad \text{(regular solution)}\\
+&A_{\lambda-1/2}^{(-)}(\omega) e^{-i\omega r_*} + A_{\lambda-1/2}^{(+)}(\omega) e^{+i\omega r_*}  \hspace{0.2em}\scriptstyle{r_* \rightarrow +\infty.}
+\end{aligned}
+\right.
+\end{equation}
+
+Let us consider the radial equation~\eqref{H_Radial_equation}, written for the regular solution
+\begin{equation}\label{Wave_equation_reg}
+   \frac{d^2}{dr_*^2}\phi_{\omega,\lambda-1/2}(r)+\left(\omega^2 -V_{\lambda-1/2}\right) \phi_{\omega,\lambda-1/2}(r) =0
+ \end{equation}
+and its complex conjugate
+ \begin{equation}\label{Wave_equation_reg_conjugate}
+   \frac{d^2}{dr_*^2}\overline{\phi}_{\omega,\lambda-1/2}(r)+ \left(\omega^2 -V_{\overline{\lambda}-1/2}\right)\overline{\phi}_{\omega,{\lambda-1/2}}(r) =0
+ \end{equation}
+Multiplying \eqref{Wave_equation_reg} by $\overline{\phi}_{\omega,\lambda-1/2}(r)$ and \eqref{Wave_equation_reg_conjugate} by $\phi_{\omega,\lambda-1/2}(r)$ and subtracting, it follows,
+\begin{widetext}
+\begin{equation}\label{Derivative_Wronskian}
+\begin{aligned}
+ \overline{\phi}_{\omega,\lambda-1/2}(r) \frac{d^2}{dr_*^2}\phi_{\omega,\lambda-1/2}(r) - \phi_{\omega,\lambda-1/2}(r) \frac{d^2}{dr_*^2} \overline{\phi}_{\omega,\lambda-1/2}(r) &= 2 i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{2\text{Re}[\lambda]\text{Im}[\lambda]}{r^2} \\
+                           &= 2 i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{\text{Im}[\lambda^2]}{r^2} 
+ \end{aligned}
+\end{equation}
+\end{widetext}
+In Eq.~\eqref{Derivative_Wronskian}, the l.h.s is the derivative of the Wronskian, $W$, of the two solutions respect to $r_*$ and it is a constant (\textit{i.e.}, $d/dr_* W[\overline{\phi},\phi] = 0$) if $\lambda$ either real or purely imaginary.
+According to Eq.~\eqref{Derivative_Wronskian}, we can write
+\begin{equation}\label{Derivative_Wronskian_bis}
+\frac{d}{dr_*}W[\overline{\phi},\phi]= 2i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{2\text{Re}[\lambda]\text{Im}[\lambda]}{r^2}
+\end{equation}
+
+Integration of \eqref{Derivative_Wronskian_bis} gives
+\begin{equation}\label{Evaluation_W}
+\lim_{r_*\rightarrow \infty}  W[\overline{\phi},\phi] = 4i\, \text{Im}[\lambda]\, \text{Re}[\lambda] \int_{0}^{+\infty} \frac{|\phi_{\lambda-1/2}(\omega)|^2}{r^2}\,dr
+\end{equation}
+where we have used $\frac{dr}{dr_*}=f(r)$ to transform the integration variable. In other hand,  By evaluating the  Wronskian from the boundary condition~\eqref{bc_CAM}, we obtain
+\begin{equation}\label{Evaluation_W_bis}
+\lim_{r_*\rightarrow \infty}  W[\overline{\phi},\phi] =-2i\, \omega\left(|A^{(-)}_{\lambda-1/2}|^2-|A^{(+)}_{\lambda-1/2}|^2\right)
+\end{equation}
+hence we get (\textit{c.f.} \eqref{Evaluation_W} and  \eqref{Evaluation_W_bis})
+\begin{equation}\label{Evaluation_W_bis_1}
+  |A^{(-)}_{\lambda-1/2}|^2-|A^{(+)}_{\lambda-1/2}|^2 = -\frac{2}{\omega}\text{Re}[\lambda]\text{Im}[\lambda]\int_{0}^{+\infty} \frac{ |\phi_{\lambda-1/2}(\omega)|^2}{r^2}\,dr
+\end{equation}
+
+Since the integral is positive and $\omega$ is real, $A^{(-)}_{\lambda-1/2}$ can  vanish in the right-half complex $\lambda$-plan (\text{i.e.} $\text{Re}[\lambda] >0 $) only for
+\begin{equation}
+    \begin{dcases}
+        \omega>0 \\
+        \text{Im}[\lambda]>0 
+     \end{dcases}
+\quad\text{or}\quad
+    \begin{dcases}
+      \omega<0 \\
+        \text{Im}[\lambda]<0
+    \end{dcases}
+\end{equation}\
+
+Thus, in the right-half complex $\lambda$-plan, the Regge poles lie only in the first quadrant for $\omega > 0$, and only in the fourth quadrant for $\omega < 0$.
+
+It is important to note that we have, under transformation $\omega \rightarrow -\omega$, the coefficient $A^{(-)}_{\lambda-1/2}(\omega)$ defined by the problem  \eqref{H_Radial_equation}--\eqref{bc_1_in}--\eqref{bc_2_in}, satisfy
+\begin{equation}\label{symmetry_relation}
+ A^{(-)}_{\lambda-1/2}(-\omega) = \left[A^{(-)}_{\lambda^*-1/2}(\omega)\right]^*
+\end{equation}
+hence, due to this symmetry relation, we get 
+\begin{equation}\label{Relation_1st_4th}
+\lambda_n(-\omega) = \lambda_n(\omega)^*  
+\end{equation}
+
+Exploring the second and third quadrants, where $\text{Re}[{\lambda}] < 0$, requires a choice to be made on the form of the boundary condition imposed at $r=0$.
+A natural choice is to impose regularity, i.e.,~$\phi_{\omega\ell} \sim r^{-\lambda+1/2}$ as $r \rightarrow 0$ for $\text{Re} [\lambda] < 0$.
+An advantage of this choice is that it leads to the same symmetry as in the black hole case for the $S$-matrix elements (see Ref.~\cite{Andersson:1994rk,Folacci:2019cmc}), viz.,
+\begin{equation}\label{Matrix_S_CAM_symm}
+S_{-\lambda -1/2}(\omega) =  e^{-2i \pi \lambda} \, S_{\lambda -1/2}(\omega)
+\end{equation}
+Furthermore, since the wave equation is invariant under the transformation $\lambda \rightarrow -\lambda$ and according to \eqref{Evaluation_W_bis_1} and \eqref{Relation_1st_4th}, it follows that the distribution of poles in the left-half of the complex plane follows by reflection through the origin.
+In the other words, in the left-half complex $\lambda$-plan (\text{i.e.} $\text{Re}[\lambda] < 0 $), the Regge poles occur for
+\begin{equation}
+    \begin{dcases}
+        \omega>0 \\
+        \text{Im}[\lambda]<0
+     \end{dcases}
+\quad\text{or}\quad
+    \begin{dcases}
+      \omega<0 \\
+        \text{Im}[\lambda]>0
+    \end{dcases}
+\end{equation}\
+
+The results established here agree with the situation in non-relativistic wave and atom/particle scattering (see \textit{e.g.} \cite{Newton:1982qc,Bottino1962} and references therein), also with the Schwarzschild black hole scattering \cite{Andersson:1994rk}.
+
 \bibliography{rainbowCAM}

### 2019-12-21 rainbowCAM.tex
change the overilne (conjugate) to asterik in appendix

@@
  \begin{equation}\label{Wave_equation_reg_conjugate}
-   \frac{d^2}{dr_*^2}\overline{\phi}_{\omega,\lambda-1/2}(r)+ \left(\omega^2 -V_{\overline{\lambda}-1/2}\right)\overline{\phi}_{\omega,{\lambda-1/2}}(r) =0
- \end{equation}
-Multiplying \eqref{Wave_equation_reg} by $\overline{\phi}_{\omega,\lambda-1/2}(r)$ and \eqref{Wave_equation_reg_conjugate} by $\phi_{\omega,\lambda-1/2}(r)$ and subtracting, it follows,
+   \frac{d^2}{dr_*^2}\phi^*_{\omega,\lambda-1/2}(r)+ \left(\omega^2 -V_{\lambda^*-1/2}\right)\phi^*_{\omega,{\lambda-1/2}}(r) =0
+ \end{equation}
+Multiplying \eqref{Wave_equation_reg} by $\phi^*_{\omega,\lambda-1/2}(r)$ and \eqref{Wave_equation_reg_conjugate} by $\phi_{\omega,\lambda-1/2}(r)$ and subtracting, it follows,
 \begin{widetext}
@@
 \begin{aligned}
- \overline{\phi}_{\omega,\lambda-1/2}(r) \frac{d^2}{dr_*^2}\phi_{\omega,\lambda-1/2}(r) - \phi_{\omega,\lambda-1/2}(r) \frac{d^2}{dr_*^2} \overline{\phi}_{\omega,\lambda-1/2}(r) &= 2 i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{2\text{Re}[\lambda]\text{Im}[\lambda]}{r^2} \\
+ \phi^*_{\omega,\lambda-1/2}(r) \frac{d^2}{dr_*^2}\phi_{\omega,\lambda-1/2}(r) - \phi_{\omega,\lambda-1/2}(r) \frac{d^2}{dr_*^2} \phi^*_{\omega,\lambda-1/2}(r) &= 2 i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{2\text{Re}[\lambda]\text{Im}[\lambda]}{r^2} \\
                            &= 2 i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{\text{Im}[\lambda^2]}{r^2}
@@
 \end{widetext}
-In Eq.~\eqref{Derivative_Wronskian}, the l.h.s is the derivative of the Wronskian, $W$, of the two solutions respect to $r_*$ and it is a constant (\textit{i.e.}, $d/dr_* W[\overline{\phi},\phi] = 0$) if $\lambda$ either real or purely imaginary.
+In Eq.~\eqref{Derivative_Wronskian}, the l.h.s is the derivative of the Wronskian, $W$, of the two solutions respect to $r_*$ and it is a constant (\textit{i.e.}, $d/dr_* W[\phi^*,\phi] = 0$) if $\lambda$ either real or purely imaginary.
 According to Eq.~\eqref{Derivative_Wronskian}, we can write
 \begin{equation}\label{Derivative_Wronskian_bis}
-\frac{d}{dr_*}W[\overline{\phi},\phi]= 2i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{2\text{Re}[\lambda]\text{Im}[\lambda]}{r^2}
+\frac{d}{dr_*}W[\phi^*,\phi]= 2i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{2\text{Re}[\lambda]\text{Im}[\lambda]}{r^2}
 \end{equation}
@@
 \begin{equation}\label{Evaluation_W}
-\lim_{r_*\rightarrow \infty}  W[\overline{\phi},\phi] = 4i\, \text{Im}[\lambda]\, \text{Re}[\lambda] \int_{0}^{+\infty} \frac{|\phi_{\lambda-1/2}(\omega)|^2}{r^2}\,dr
+\lim_{r_*\rightarrow \infty}  W[\phi^*,\phi] = 4i\, \text{Im}[\lambda]\, \text{Re}[\lambda] \int_{0}^{+\infty} \frac{|\phi_{\lambda-1/2}(\omega)|^2}{r^2}\,dr
 \end{equation}
@@
 \begin{equation}\label{Evaluation_W_bis}
-\lim_{r_*\rightarrow \infty}  W[\overline{\phi},\phi] =-2i\, \omega\left(|A^{(-)}_{\lambda-1/2}|^2-|A^{(+)}_{\lambda-1/2}|^2\right)
+\lim_{r_*\rightarrow \infty}  W[\phi^*,\phi] =-2i\, \omega\left(|A^{(-)}_{\lambda-1/2}|^2-|A^{(+)}_{\lambda-1/2}|^2\right)
 \end{equation}
@@
 
-It is important to note that we have, under transformation $\omega \rightarrow -\omega$, the coefficient $A^{(-)}_{\lambda-1/2}(\omega)$ defined by the problem  \eqref{H_Radial_equation}--\eqref{bc_1_in}--\eqref{bc_2_in}, satisfy
+It is important to note that we have, under transformation $\omega \rightarrow -\omega$, the coefficient $A^{(-)}_{\lambda-1/2}(\omega)$ defined by the problem  \eqref{H_Radial_equation}--\eqref{bc_1_in}--\eqref{bc_2_in}, satisfy the symmetry relation
 \begin{equation}\label{symmetry_relation}
@@
 \end{equation}
-hence, due to this symmetry relation, we get 
+where, we have
 \begin{equation}\label{Relation_1st_4th}
@@
 
-Exploring the second and third quadrants, where $\text{Re}[{\lambda}] < 0$, requires a choice to be made on the form of the boundary condition imposed at $r=0$.
+Exploring the second and third quadrants, where $\text{Re}[{\lambda}] < 0$, requires a choice to be made on the form of the boundary condition imposed at $r=0$~\eqref{bc_CAM}.
 A natural choice is to impose regularity, i.e.,~$\phi_{\omega\ell} \sim r^{-\lambda+1/2}$ as $r \rightarrow 0$ for $\text{Re} [\lambda] < 0$.
@@
 
-The results established here agree with the situation in non-relativistic wave and atom/particle scattering (see \textit{e.g.} \cite{Newton:1982qc,Bottino1962} and references therein), also with the Schwarzschild black hole scattering \cite{Andersson:1994rk}.
+The results established here agree with the situation in non-relativistic wave and atom/particle scattering (see \textit{e.g.} \cite{Newton:1982qc,Bottino1962} and references therein), also with the Schwarzschild black hole scattering \cite{Andersson:1994rk,Decanini:2009mu}.
 

### 2019-12-21 rainbowCAM.tex
some minor changes to appendix

@@
 Sam \& Tom : Please be critical and It is free to change.}
+\tom{I have made a few minor rewordings. Agree with moving III C para to here.}.
 
@@
 \end{equation}
-are lying in the right-half of the complex $\lambda$-plan. To do this, it is convenient to write the boundary conditions \eqref{bc_1_in} and \eqref{bc_2_in} in the following form:
+are lying in the right-half of the complex $\lambda$-plan.
+
+\tom{ rewording: In this appendix we will show which quadrants of the complex $\lambda$-plane may contain the Regge poles for scalar and axial metric perturbations on a stellar background.
+In other words, we will constrain the possible locations of the zeros of the coefficient $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~\eqref{Matrix_S_CAM}],
+\begin{equation}\label{zeros_Am}
+   A^{(-)}_{\lambda-1/2} (\omega)\Big{|}_{\lambda =\lambda_n} = 0,
+\end{equation}
+for $\omega$ real.
+}
+
+To do this, it is convenient to write the boundary conditions \eqref{bc_1_in} and \eqref{bc_2_in} in the following form:
 \begin{equation}
@@
  \end{equation}
-Multiplying \eqref{Wave_equation_reg} by $\phi^*_{\omega,\lambda-1/2}(r)$ and \eqref{Wave_equation_reg_conjugate} by $\phi_{\omega,\lambda-1/2}(r)$ and subtracting, it follows,
+Multiplying \eqref{Wave_equation_reg} by $\phi^*_{\omega,\lambda-1/2}(r)$ and \eqref{Wave_equation_reg_conjugate} by $\phi_{\omega,\lambda-1/2}(r)$ and subtracting, it follows that
 \begin{widetext}
@@
 \end{widetext}
-In Eq.~\eqref{Derivative_Wronskian}, the l.h.s is the derivative of the Wronskian, $W$, of the two solutions respect to $r_*$ and it is a constant (\textit{i.e.}, $d/dr_* W[\phi^*,\phi] = 0$) if $\lambda$ either real or purely imaginary.
+The LHS of Eq.~\eqref{Derivative_Wronskian} is the derivative of the Wronskian, $W$, of the two solutions with respect to $r_*$ and it is a constant (\textit{i.e.}, $d/dr_* W[\phi^*,\phi] = 0$) if $\lambda$ either real or purely imaginary.
 According to Eq.~\eqref{Derivative_Wronskian}, we can write
 \begin{equation}\label{Derivative_Wronskian_bis}
-\frac{d}{dr_*}W[\phi^*,\phi]= 2i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{2\text{Re}[\lambda]\text{Im}[\lambda]}{r^2}
+\frac{d}{dr_*}W[\phi^*,\phi]= 2i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{2\text{Re}[\lambda]\text{Im}[\lambda]}{r^2}.
 \end{equation}
@@
 \end{equation}
-where we have used $\frac{dr}{dr_*}=f(r)$ to transform the integration variable. In other hand,  By evaluating the  Wronskian from the boundary condition~\eqref{bc_CAM}, we obtain
+where we have used $\frac{dr}{dr_*}=f(r)$ to transform the integration variable. On the other hand,  by evaluating the  Wronskian from the boundary condition~\eqref{bc_CAM}, we obtain
 \begin{equation}\label{Evaluation_W_bis}
-\lim_{r_*\rightarrow \infty}  W[\phi^*,\phi] =-2i\, \omega\left(|A^{(-)}_{\lambda-1/2}|^2-|A^{(+)}_{\lambda-1/2}|^2\right)
+\lim_{r_*\rightarrow \infty}  W[\phi^*,\phi] =-2i\, \omega\left(|A^{(-)}_{\lambda-1/2}|^2-|A^{(+)}_{\lambda-1/2}|^2\right),
 \end{equation}
@@
 \begin{equation}\label{Evaluation_W_bis_1}
-  |A^{(-)}_{\lambda-1/2}|^2-|A^{(+)}_{\lambda-1/2}|^2 = -\frac{2}{\omega}\text{Re}[\lambda]\text{Im}[\lambda]\int_{0}^{+\infty} \frac{ |\phi_{\lambda-1/2}(\omega)|^2}{r^2}\,dr
+  |A^{(-)}_{\lambda-1/2}|^2-|A^{(+)}_{\lambda-1/2}|^2 = -\frac{2}{\omega}\text{Re}[\lambda]\text{Im}[\lambda]\int_{0}^{+\infty} \frac{ |\phi_{\lambda-1/2}(\omega)|^2}{r^2}\,dr.
 \end{equation}
@@
 
-It is important to note that we have, under transformation $\omega \rightarrow -\omega$, the coefficient $A^{(-)}_{\lambda-1/2}(\omega)$ defined by the problem  \eqref{H_Radial_equation}--\eqref{bc_1_in}--\eqref{bc_2_in}, satisfy the symmetry relation
+It is important to note that under the transformation $\omega \rightarrow -\omega$, the coefficient $A^{(-)}_{\lambda-1/2}(\omega)$ defined by \eqref{H_Radial_equation}--\eqref{bc_1_in}--\eqref{bc_2_in} satisfies the symmetry relation
 \begin{equation}\label{symmetry_relation}
- A^{(-)}_{\lambda-1/2}(-\omega) = \left[A^{(-)}_{\lambda^*-1/2}(\omega)\right]^*
-\end{equation}
-where, we have
+ A^{(-)}_{\lambda-1/2}(-\omega) = \left[A^{(-)}_{\lambda^*-1/2}(\omega)\right]^*,
+\end{equation}
+and thus
 \begin{equation}\label{Relation_1st_4th}
-\lambda_n(-\omega) = \lambda_n(\omega)^*
+\lambda_n(-\omega) = \lambda_n(\omega)^*.
 \end{equation}

### 2019-12-21 rainbowCAM.tex
Minor changes to Appendix A, and the text in the main body that refers to this.y

@@
 
-After scanning across the domain, we find no evidence of Regge poles in the fourth quadrant of the complex-$\lambda$ plane for $\omega>0$.
+In Appendix \ref{appen} we present an argument for why no Regge poles are expected to be located in the fourth quadrant of the complex-$\lambda$ plane for $\omega>0$. As a consistency check, 
+we have scanned the fourth quadrant with the numerical method above, and have found no evidence for Regge poles.
+
 Exploring the second and third quadrants, where $\text{Re}[{\lambda}] < 0$, requires a choice to be made on the form of the boundary condition imposed at $r=0$.
@@
 
-\moh{I have established some proprieties (symmetry relations) to connect different quadrants and I moved part of the paragraph from section III-c to the appendix.
+%\moh{I have established some proprieties (symmetry relations) to connect different quadrants and I moved part of the paragraph from section III-c to the appendix.
 Sam \& Tom : Please be critical and It is free to change.}
-\tom{I have made a few minor rewordings. Agree with moving III C para to here.}.
-
-In this appendix, we will show that, for $\omega$ real, the zeros of the $S$-matrix (\textit{i.e.}, the Regge poles), or in other words
-the zeros of the coefficient $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~\eqref{Matrix_S_CAM}]
-\begin{equation}\label{zeros_Am}
-   A^{(-)}_{\lambda-1/2} (\omega)\Big{|}_{\lambda =\lambda_n} = 0
-\end{equation}
-are lying in the right-half of the complex $\lambda$-plan.
-
-\tom{ rewording: In this appendix we will show which quadrants of the complex $\lambda$-plane may contain the Regge poles for scalar and axial metric perturbations on a stellar background.
+%\tom{I have made a few minor rewordings. Agree with moving III C para to here.}.
+
+%In this appendix, we will show that, for $\omega$ real, the zeros of the $S$-matrix (\textit{i.e.}, the Regge poles), or in other words
+%the zeros of the coefficient $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~\eqref{Matrix_S_CAM}]
+%\begin{equation}\label{zeros_Am}
+%   A^{(-)}_{\lambda-1/2} (\omega)\Big{|}_{\lambda =\lambda_n} = 0
+%\end{equation}
+%are lying in the right-half of the complex $\lambda$-plan.
+
+In this appendix, we establish which quadrants of the complex $\lambda$-plane may contain Regge poles, for scalar and axial metric perturbations on a stellar background.
 In other words, we will constrain the possible locations of the zeros of the coefficient $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~\eqref{Matrix_S_CAM}],
@@
 for $\omega$ real.
-}
-
-To do this, it is convenient to write the boundary conditions \eqref{bc_1_in} and \eqref{bc_2_in} in the following form:
+
+To do this, it is convenient to write the boundary conditions \eqref{bc_1_in} and \eqref{bc_2_in} defining a solution that is regular at the origin in the following form:
 \begin{equation}
@@
 \phi_{\lambda-\frac{1}{2}}(\omega) \sim
-\left\{
-\begin{aligned}
-&r^{\lambda+\frac{1}{2}}\hspace{8em} \scriptstyle{r \rightarrow 0,} \quad \text{(regular solution)}\\
-&A_{\lambda-1/2}^{(-)}(\omega) e^{-i\omega r_*} + A_{\lambda-1/2}^{(+)}(\omega) e^{+i\omega r_*}  \hspace{0.2em}\scriptstyle{r_* \rightarrow +\infty.}
-\end{aligned}
-\right.
-\end{equation}
-
-Let us consider the radial equation~\eqref{H_Radial_equation}, written for the regular solution
+\begin{cases}
+r^{\lambda+\frac{1}{2}}, &
+r \rightarrow 0, \\
+\phantom{+} A_{\lambda-1/2}^{(-)}(\omega) e^{-i\omega r_*} & \\ 
+ + A_{\lambda-1/2}^{(+)}(\omega) e^{+i\omega r_*} , &r_* \rightarrow +\infty.
+\end{cases}
+\end{equation}
+%
+We next consider the radial equation~\eqref{H_Radial_equation} for the regular solution
 \begin{equation}\label{Wave_equation_reg}
-   \frac{d^2}{dr_*^2}\phi_{\omega,\lambda-1/2}(r)+\left(\omega^2 -V_{\lambda-1/2}\right) \phi_{\omega,\lambda-1/2}(r) =0
- \end{equation}
-and its complex conjugate
+   \frac{d^2}{dr_*^2}\phi_{\omega,\lambda-1/2}(r)+\left(\omega^2 -V_{\lambda-1/2}\right) \phi_{\omega,\lambda-1/2}(r) =0,
+ \end{equation}
+and its complex conjugate, 
  \begin{equation}\label{Wave_equation_reg_conjugate}
-   \frac{d^2}{dr_*^2}\phi^*_{\omega,\lambda-1/2}(r)+ \left(\omega^2 -V_{\lambda^*-1/2}\right)\phi^*_{\omega,{\lambda-1/2}}(r) =0
- \end{equation}
-Multiplying \eqref{Wave_equation_reg} by $\phi^*_{\omega,\lambda-1/2}(r)$ and \eqref{Wave_equation_reg_conjugate} by $\phi_{\omega,\lambda-1/2}(r)$ and subtracting, it follows that
+   \frac{d^2}{dr_*^2}\phi^*_{\omega,\lambda-1/2}(r)+ \left(\omega^2 -V_{\lambda^*-1/2}\right)\phi^*_{\omega,{\lambda-1/2}}(r) = 0 .
+ \end{equation}
+Multiplying \eqref{Wave_equation_reg} by $\phi^*_{\omega,\lambda-1/2}(r)$ and \eqref{Wave_equation_reg_conjugate} by $\phi_{\omega,\lambda-1/2}(r)$ and taking the difference, it follows that
 \begin{widetext}
@@
 \begin{aligned}
- \phi^*_{\omega,\lambda-1/2}(r) \frac{d^2}{dr_*^2}\phi_{\omega,\lambda-1/2}(r) - \phi_{\omega,\lambda-1/2}(r) \frac{d^2}{dr_*^2} \phi^*_{\omega,\lambda-1/2}(r) &= 2 i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{2\text{Re}[\lambda]\text{Im}[\lambda]}{r^2} \\
-                           &= 2 i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{\text{Im}[\lambda^2]}{r^2}
+ \phi^*_{\omega,\lambda-1/2}(r) \frac{d^2}{dr_*^2}\phi_{\omega,\lambda-1/2}(r) - \phi_{\omega,\lambda-1/2}(r) \frac{d^2}{dr_*^2} \phi^*_{\omega,\lambda-1/2}(r) %&= 2 i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{2\text{Re}[\lambda]\text{Im}[\lambda]}{r^2} \\
+                           &= 2 i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{\text{Im}[\lambda^2]}{r^2} .
  \end{aligned}
@@
 \end{widetext}
-The LHS of Eq.~\eqref{Derivative_Wronskian} is the derivative of the Wronskian, $W$, of the two solutions with respect to $r_*$ and it is a constant (\textit{i.e.}, $d/dr_* W[\phi^*,\phi] = 0$) if $\lambda$ either real or purely imaginary.
+The LHS of Eq.~\eqref{Derivative_Wronskian} is the derivative of $W$, the Wronskian of the two solutions with respect to $r_*$.
+The Wronskian is a constant (\textit{i.e.}, $d/dr_* W[\phi^*,\phi] = 0$) if $\lambda$ either real or purely imaginary.
 According to Eq.~\eqref{Derivative_Wronskian}, we can write
@@
 \begin{equation}\label{Evaluation_W}
-\lim_{r_*\rightarrow \infty}  W[\phi^*,\phi] = 4i\, \text{Im}[\lambda]\, \text{Re}[\lambda] \int_{0}^{+\infty} \frac{|\phi_{\lambda-1/2}(\omega)|^2}{r^2}\,dr
+\lim_{r_*\rightarrow \infty}  W[\phi^*,\phi] = 4i\, \text{Im}[\lambda]\, \text{Re}[\lambda] \int_{0}^{+\infty} \frac{|\phi_{\lambda-1/2}(\omega)|^2}{r^2}\,dr ,
 \end{equation}
@@
 \end{equation}
-hence we get (\textit{c.f.} \eqref{Evaluation_W} and  \eqref{Evaluation_W_bis})
+hence we get (\textit{c.f.}~\eqref{Evaluation_W} and  \eqref{Evaluation_W_bis})
 \begin{equation}\label{Evaluation_W_bis_1}
@@
 
-The results established here agree with the situation in non-relativistic wave and atom/particle scattering (see \textit{e.g.} \cite{Newton:1982qc,Bottino1962} and references therein), also with the Schwarzschild black hole scattering \cite{Andersson:1994rk,Decanini:2009mu}.
+The results established here agree with the situation in non-relativistic wave and atom/particle scattering (see \textit{e.g.}~\cite{Newton:1982qc,Bottino1962} and references therein), and also with the results of Schwarzschild black hole scattering \cite{Andersson:1994rk,Decanini:2009mu}.
 

### 2019-12-22 rainbowCAM.tex
typo corrected in Eq.A2
removed some material from appendix as it is discussed in 3 c

@@
 We conclude with a discussion in Sec.~\ref{sec:conclusions}.
+In an appendix, we show which quadrants of the complex $\lambda$-plan contain Regge poles of the $S$-matrix.
 
@@
 \label{bc_CAM}
-\phi_{\lambda-\frac{1}{2}}(\omega) \sim
+\phi_{\omega,\lambda-\frac{1}{2}}(r) \sim
 \begin{cases}
@@
 
-Exploring the second and third quadrants, where $\text{Re}[{\lambda}] < 0$, requires a choice to be made on the form of the boundary condition imposed at $r=0$~\eqref{bc_CAM}.
+%Exploring the second and third quadrants, where $\text{Re}[{\lambda}] < 0$, requires a choice to be made on the form of the boundary condition imposed at $r=0$~\eqref{bc_CAM}.
 A natural choice is to impose regularity, i.e.,~$\phi_{\omega\ell} \sim r^{-\lambda+1/2}$ as $r \rightarrow 0$ for $\text{Re} [\lambda] < 0$.
 An advantage of this choice is that it leads to the same symmetry as in the black hole case for the $S$-matrix elements (see Ref.~\cite{Andersson:1994rk,Folacci:2019cmc}), viz.,
-\begin{equation}\label{Matrix_S_CAM_symm}
-S_{-\lambda -1/2}(\omega) =  e^{-2i \pi \lambda} \, S_{\lambda -1/2}(\omega)
-\end{equation}
-Furthermore, since the wave equation is invariant under the transformation $\lambda \rightarrow -\lambda$ and according to \eqref{Evaluation_W_bis_1} and \eqref{Relation_1st_4th}, it follows that the distribution of poles in the left-half of the complex plane follows by reflection through the origin.
-In the other words, in the left-half complex $\lambda$-plan (\text{i.e.} $\text{Re}[\lambda] < 0 $), the Regge poles occur for
+%\begin{equation}\label{Matrix_S_CAM_symm}
+%S_{-\lambda -1/2}(\omega) =  e^{-2i \pi \lambda} \, S_{\lambda -1/2}(\omega)
+%\end{equation}
+%Furthermore, since the wave equation is invariant under the transformation $\lambda \rightarrow -\lambda$ and according to \eqref{Evaluation_W_bis_1} and \eqref{Relation_1st_4th}, it follows that the distribution of poles in the left-half of the complex plane follows by reflection through the origin.
+%In the other words, in the left-half complex $\lambda$-plan (\text{i.e.} $\text{Re}[\lambda] < 0 $), the Regge poles occur for
+
+As discussed in Sec.~\ref{subsec:results1}, a good analytic extension of the S-matrix into the left-half complex $\lambda$-plane leads to the symmetry \eqref{Matrix_S_CAM_symm}.
+Then, it follows that the Regge poles with $\text{Re}[\lambda] < 0 $ may be found for
+%
 \begin{equation}
@@
         \text{Im}[\lambda]>0
-    \end{dcases}
+    \end{dcases}.
 \end{equation}\

### 2019-12-22 rainbowCAM.tex
Small changes in appendix and Sec III.C

@@
 They described the scattering of scalar waves by a Schwarzschild black hole using CAM techniques, and showed that, in this case, the Regge poles are associated with ``surface waves'' localised near the unstable light ring at $ r = 3M $ (\textit{i.e.}, the so-called photon sphere).
-Later, Decanini, Folacci and Jensen showed that the complex frequencies of weakly damped QNMs are Breit-Wigner resonances generated by the surface waves previously mentioned and, using the concept of Regge trajectories, they were able to construct semiclassically the spectrum of the QNM complex frequencies~\cite{Decanini:2002ha}.
+Later, Decanini, Folacci and Jensen showed that the complex frequencies of weakly damped quasinormal modes (QNMs) are Breit-Wigner resonances generated by the surface waves previously mentioned and, using the concept of Regge trajectories, they were able to construct semiclassically the spectrum of the QNM complex frequencies~\cite{Decanini:2002ha}.
 Recently, Folacci and Ould~El~Hadj have shown that CAM machinery can be used for precise numerical calculations of scattering cross sections of scalar fields, electromagnetic fields~\cite{Folacci:2019cmc} and gravitational waves~\cite{Folacci:2019vtt} on a Schwarzschild space-time.
@@
 
-There is a close relationship between Regge poles and quasi-normal mode (QNM) frequencies; both are sets of poles of the scattering matrix, with the latter lying in the complex-frequency plane.
+There is a close relationship between Regge poles and QNM frequencies; both are sets of poles of the scattering matrix, with the latter lying in the complex-frequency plane.
 The excitation of black hole QNMs leads to distinctive signatures in \emph{time-dependent} scattering scenarios.
@@
 
-%Finally we apply the CAM-approach developed for black-hole scattering in \cite{Folacci:2019cmc} and \cite{Folacci:2019vtt}.
+%Finally we apply the CAM-approach developed for black hole scattering in \cite{Folacci:2019cmc} and \cite{Folacci:2019vtt}.
 
@@
 
-In Appendix \ref{appen} we present an argument for why no Regge poles are expected to be located in the fourth quadrant of the complex-$\lambda$ plane for $\omega>0$. As a consistency check,
-we have scanned the fourth quadrant with the numerical method above, and have found no evidence for Regge poles.
+In Appendix \ref{appen} we present an argument for why no Regge poles are expected to be located in the fourth quadrant of the complex-$\lambda$ plane for $\omega>0$.
+As a consistency check, we have scanned the fourth quadrant with the numerical method above, and have found no evidence for Regge poles.
 
@@
 Thus, for $\omega > 0$, the 4th and 2nd quadrants are devoid of poles, and the 3rd quadrant has the same structure as shown in Fig.~\ref{fig:rp1} and~\ref{fig:rp2}.
-Conversely, for $\omega < 0$, we may use the symmetry $\lambda_n(-\omega) = \lambda_n(\omega)^*$ to establish that there are poles in the 2nd and 4th quadrants only.
+Conversely, for $\omega < 0$, and due to the symmetry relation~\eqref{symmetry_relation}, we may use $\lambda_n(-\omega) = \lambda_n(\omega)^*$ to establish that there are poles in the 2nd and 4th quadrants only.
 
@@
 \end{enumerate}
-In Figs.~\ref{fig:rp1} and \ref{fig:rp2} the broad resonances, surface waves and narrow resonances are indicated by red squares, blue circles and purple triangles, respectively; and black diamonds indicate the black hole RPs.
+In Figs.~\ref{fig:rp1} and \ref{fig:rp2} the broad resonances, surface waves and narrow resonances are indicated by red squares, blue circles and purple triangles, respectively; and black diamonds indicate the black hole Regge poles.
 Whereas there exists an infinite number of poles of the surface-wave branch, in principle, there are no narrow-resonance poles at all in the $R/M = 6$ case, and just $\le 4$ narrow-resonance poles in the $R/M = 2.26$ case.
-The narrow-resonance branch is observed to end close to the start of the black-hole branch.
+The narrow-resonance branch is observed to end close to the start of the black hole branch.
 
@@
 
-%\subsubsection{Regge poles and associated residues}
-%\label{SecIIc_2}
-
-%It is important to note that the poles of  $S_{\lambda -1/2} (\omega)$ in the complex $\lambda$ plan (i.e., the Regge poles) are defined  as  the zeros of the coefficient  $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~(\ref{Matrix_S_CAM})], i.e., the values $\lambda_n(\omega)$ such that
-%\begin{equation}\label{PR_def_Am}
-%A^{(-)}_{\lambda_n(\omega)-1/2} (\omega)=0,
-%\end{equation}
-%with $n=1,2,3,\ldots$
-%The residue of the matrix $S_{\lambda-1/2}(\omega)$ at the pole $\lambda=\lambda_n(\omega)$ is defined by [see Eq.~(\ref{Matrix_S_CAM})]
-%\begin{equation}\label{residues_RP}
-%r_n(\omega)=e^{i\pi [\lambda_n(\omega)+1/2]} \left[ \frac{A_{\lambda -1/2}^{(+)}(\omega)}{\frac{d}{d \lambda}A_{\lambda -1/2}^{(-)}(\omega)}\right]_{\lambda=\lambda_n(\omega)}.
-%\end{equation}
-%These residues play a central role in the complex angular momentum paradigm.
-%
-
 It is also important to recall that the poles of  $S_{\lambda-1/2}(\omega)$ in the complex $\lambda$ plan (i.e., the Regge poles) and which are lying in the first and third quadrants, symmetrically distributed with respect to the origin $O$, are defined  as  the zeros of the coefficient  $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~(\ref{Matrix_S_CAM})], i.e., the values $\lambda_n(\omega)$ such that
@@
 To construct the scattering amplitude \eqref{Scalar_Scattering_amp}, the background integrals~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} and~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_b}, and the Regge pole amplitude~\eqref{CAM_Scalar_Scattering_amp_decomp_RP}, we use, \textit{mutatis mutandis}, the computational methods of Refs~\cite{Folacci:2019cmc,Folacci:2019vtt}.
-In these works the authors calculated the CAM representation of scattering amplitudes for scalar, electromagnetic and gravitational waves by Schwarzschild BH (see also Ref~\cite{Dolan:2017rtj}).
-
-Due to the long rang nature of the field propagating on the Schwarzschild BH (outside the compact body), the scattering amplitude~\eqref{Scalar_Scattering_amp} and the background integral~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} both suffer a lack of convergence.
+In these works the authors calculated the CAM representation of scattering amplitudes for scalar, electromagnetic and gravitational waves by Schwarzschild black hole (see also Ref~\cite{Dolan:2017rtj}).
+
+Due to the long rang nature of the field propagating on the Schwarzschild black hole (outside the compact body), the scattering amplitude~\eqref{Scalar_Scattering_amp} and the background integral~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} both suffer a lack of convergence.
 To overcome this problem, \textit{i.e.}, to accelerate the convergence of this sum and integral, we have used the method described in the Appendix of Ref~\cite{Folacci:2019cmc}.
@@
 close to the real axis with an approximately uniform spacing, $\Delta\lambda\sim 2$, requires the calculation of a large number of poles.
-In the black-hole case, by contrast, there is only a single branch of surface-wave-type modes (see Fig.~\ref{RP_R6_approx_2Mw_3_6_s_1}), and in the high-frequency limit, a few poles ($<5$) capture both the orbiting and glory phenomena \cite{Folacci:2019cmc, Folacci:2019vtt}.
+In the black hole case, by contrast, there is only a single branch of surface-wave-type modes (see Fig.~\ref{RP_R6_approx_2Mw_3_6_s_1}), and in the high-frequency limit, a few poles ($<5$) capture both the orbiting and glory phenomena \cite{Folacci:2019cmc, Folacci:2019vtt}.
 
@@
 As discussed in Sec.~\ref{subsec:results1}, a good analytic extension of the S-matrix into the left-half complex $\lambda$-plane leads to the symmetry \eqref{Matrix_S_CAM_symm}.
-Then, it follows that the Regge poles with $\text{Re}[\lambda] < 0 $ may be found for
+Then, it follows that the Regge poles with $\text{Re}[\lambda] < 0 $ may be found for (\textit{c.f.} \eqref{Evaluation_W_bis_1} and \eqref{Relation_1st_4th})
 %

### 2020-04-14 rainbowCAM.tex
Version submited to arXiv
corrected typo in eq 50 (a) - imaginary background integral
tom: reformatted eq 50 (c) after correcting + added files pertaining to the referees comments and our response. Now need to collate comments for a reply and to implement any changes
made some changes for referee comments - see summary of changes

@@
-%\documentclass[aps,prd,longbibliography,reprint,twocolumn,amsmath,amssymb,amsfonts,showpacs,superscriptaddress]{revtex4-1}%reprint
 \documentclass[aps,prd,longbibliography,reprint,twocolumn,amsmath,amssymb,amsfonts,showpacs,footnote,superscriptaddress]{revtex4-1}%reprint
@@
 The starting point is the radial equation (\ref{H_Radial_equation}) with either the effective potential for the scalar field (\ref{Inside_Potentiel}), or for axial gravitational perturbations (\ref{RW_Potentiel_axialGW}).
+It is valid only for models with $R/M>3$.
 
@@
 In the interior of the star, the radial function $f(r)$ is
-\begin{equation}
+\begin{equation}\label{eq:f_exp}
 f(r) = f_0 \left(1 + O\left(\frac{M r^2}{R^3} \right) \right),
@@
 In other words, there are a finite number of the broad resonances in the first quadrant.
+
+As $M/R \rightarrow 0$ (a large dilute star), the poles move closer to the real axis. When $M/R=0$ (i.e. no star), the potential is $C^{\infty}$ and the branch does not exist.
+
+For any stellar model (such as a polytropic fluid sphere), the potential may in general be $C^{N}$ at the surface (and $C^{\infty}$ elsewhere).
+In this case, $\mathcal{R}$ and thus the broad resonance branch depends on the discontinuity in the $N$-th derivative of the potential at $r=R$.
+We do not go into detail here, but see Eq.~4.5 of Ref.
+\cite{Zhang:2011pq}.
 
@@
 \begin{eqnarray}\label{CAM_Scalar_Scattering_amp_decomp_Background_b}
-\hat{f}^\text{\tiny{B},\tiny{Im}} && (\omega, \theta) = \frac{1}{2 \omega}\left(\int_{+i\infty}^{0} d\lambda \, \left[S_{\lambda -1/2}(\omega) P_{\lambda-1/2} (-\cos \theta) \right.
+\hat{f} && ^\text{\tiny{B},\tiny{Im}}  (\omega, \theta) = \frac{1}{2 \omega}\left(\int_{+i\infty}^{0} d\lambda \, \left[S_{\lambda -1/2}(\omega) P_{\lambda-1/2} (-\cos \theta) \right.
 \right.\nonumber \\
-&& -\left. \left. S_{-\lambda -1/2}(\omega) e^{i \pi \left(\lambda+1/2\right)}P_{\lambda-1/2} (\cos \theta) \right]\lambda\right).
+ - && \left.  \left. S_{-\lambda -1/2}(\omega) e^{i \pi \left(\lambda+1/2\right)}P_{\lambda-1/2} (\cos \theta) \right] \frac{\lambda}{\cos (\pi \lambda) } \right).
 \end{eqnarray}

### 2020-04-15 referee PRD/RefereeResponse_DN12236.tex
made final changes for referee response

\magnification=1050 \baselineskip=12pt plus 1pt minus 2pt
\nopagenumbers

\noindent {\bf Manuscript Code Number: DN12236}

\smallskip
\noindent {\bf Title: Scattering from compact objects: Regge poles and the Complex Angular Momentum method}

\smallskip
\noindent {\bf Authors: Mohamed Ould El Hadj, Tom Stratton and Sam R. Dolan}

\bigskip
\bigskip

We thank the referee for her/his careful reading of our manuscript and her/his useful remarks that have been taken into account and that have permitted us to improve our article:

\bigskip

\noindent $\underline{\hbox{Comments:}} $
\medskip

\bigskip
\qquad - In the case where $α \rightarrow0$, the effective potential becomes continuous and the branch of Regge poles associated with the discontinuity, i.e. the broad resonances ``disappears''. However, this does not mean that the black hole does not have a pole. Because the effective potential of the black hole is not only continuous, it has a maximum and the poles of the $\cal{S}$--matrix (QNFs and/or RPs) are associated with this maximum (see for example Folacci, Decanin and Jensen: Complex angular momentum in black hole physics and quasinormal modes and reference therein. Ref[40] in our article).

\bigskip
\qquad - Perhaps one can refer to the use of the approximation Eq.(30) and (31) of the function f(r). The WKB approximation  in this case is valid just for $R > 3M$ i.e. in case the potential has no well.

\bigskip
\qquad -  Usually we stop when the sum over the Regge poles converges. For the background integral, its evaluation allows us to see whether it is negligible or not. For example, in the case of the black hole and ultra-compact objects, in the high frequency regime, the background integral is negligible. This is surprising since this is not the case in other areas of physics (acoustics, optics, electromagnetics, quantum mechanics,...), where the CAM method finds its origins, and this independently of the frequency.

\bigskip\bigskip

\noindent $\underline{\hbox{Other changes:}}  $
\medskip

\smallskip
\qquad - Do not forget to add the Ref[Sebastian H. Völkel and Kostas D. Kokkotas] :  On the Inverse Spectrum Problem of Neutron Stars.

%@article{Volkel:2019gpq,
%      author         = "Völkel, Sebastian H. and Kokkotas, Kostas D.",
%      title          = "{On the Inverse Spectrum Problem of Neutron Stars}",
%      journal        = "Class. Quant. Grav.",
%      volume         = "36",
%      year           = "2019",
%      number         = "11",
%      pages          = "115002",
%      doi            = "10.1088/1361-6382/ab186e",
%      eprint         = "1901.11262",
%      archivePrefix  = "arXiv",
%      primaryClass   = "gr-qc",
%      SLACcitation   = "%%CITATION = ARXIV:1901.11262;%%"
%}

\vfill \eject \bye

### 2020-04-15 rainbowCAM.tex
made final changes for referee response

@@
 
-Here we follow the approach of Zhang, Wu and Leung~\cite{Zhang:2011pq}, who applied the WKB method to determine the axial \textit{w}-modes of a variety of stellar models.
+Here we follow the approach of Zhang, Wu and Leung~\cite{Zhang:2011pq}, who applied the WKB method to determine the axial \textit{w}-modes of a variety of stellar models (see also \cite{Volkel:2019gpq}).
 We adapt their method to obtain analytical approximations for the ``broad resonances'' for massless waves on a stellar background.
@@
 \cite{Zhang:2011pq}.
+Recall that the above analysis is not appropriate for compact bodies with $R/M<3$ and black holes (since the effective potential has a qualitatively different structure, and the ansatz Eq.~(\ref{Approx_infinity}) is not valid ).
 
@@
 By applying a WKB method at lowest order, we have obtained a better understanding of the spectrum of the broad resonances, finding that the magnitude of the imaginary part is linked to the magnitude of the discontinuity in the effective potential at the surface of the body (see Eq.~(\ref{eq:alpha}), Eq.~(\ref{lambda_Approx}) and Fig.~\ref{fig:Veff}).
-Extending the WKB method to higher orders would improve the accuracy of this approximation, and further work is need to obtain asymptotic approximations for the surface-wave branch, and the narrow-resonance branch.
+Extending the WKB method to higher orders would improve the accuracy of this approximation, and further work is needed to obtain asymptotic approximations for the surface-wave branch, and the narrow-resonance branch.
 
@@
 
+Here we have numerically determined if a background integral, and how many Regge-poles and residues, need to be calculated to accurately reproduce a scattering cross section in an angular region.
+Loosely speaking, for scattering at higher frequencies, more poles must be included since there are more broad resonances.
+Also the background integral is negligible except for weak glory scattering.
+This is an interesting result in itself (as noted in \cite{Folacci:2019cmc,Folacci:2019vtt}) since in most CAM scattering studies the background integral is significant in geometrically illuminated regions \cite{Nussenzveig:2006}.
+\tom{Speculatively, this could be related to the long range nature of gravitational scattering by compact bodies (it is not just the body that is scattering, but the bodies extended gravitational field).
+By contrast, in acoustics, quantum mechanics, and optics [\emph{find citations}] the scatterer generally has a short range influence.}
+An asymptotic analysis is an important next step towards understanding the role of the background integral and higher Regge-pole overtones, both computationally and, in a semiclassical interpretation, physically.
+
 In the case of Mie scattering, a powerful extension of the CAM approach is to define the so-called Regge-Debye poles using the Debye expansion (see the chapter 9 of the monograph of Nussenzveig \cite{Nussenzveig:2006}), thereby eliminating the broad resonance branch entirely, and accelerating the convergence.
-This is a possible direction for a future investigation.
+This is another possible direction for a future investigation.
 

### 2020-04-15 referee PRD/RefereeResponse_DN12236.tex
final response?

@@
 \bigskip
-\qquad - In the case where $α \rightarrow0$, the effective potential becomes continuous and the branch of Regge poles associated with the discontinuity, i.e.
+(i) In the case where $\alpha \rightarrow0$, the effective potential becomes continuous and the branch of Regge poles associated with the discontinuity, i.e.
 the broad resonances ``disappears''.
@@
 \bigskip
-\qquad - Perhaps one can refer to the use of the approximation Eq.(30) and (31) of the function f(r).
-The WKB approximation  in this case is valid just for $R > 3M$ i.e.
-in case the potential has no well.
+(ii) The referee is correct that the radius of the body does enter the approximation scheme in eqs 30 and 31.
+However, the Wronskain (eq.
+29) is evalutated at  $r_{*} \approx 1/\omega$, and thus terms of  $O(M r_{*}^2 / R^3  )$ are of  $ O \left(  (M \omega)^{-2} (M/R)^3 \right) $ and we have $M/R< 1/2$.
+Hence, the  scale $M \omega$ is really the controlling factor in the expansion scheme.
+On the other hand, we must have $R/M>3$ for the WKB approximation to be valid, and we have made this clearer in the text.
+
+%Perhaps one can refer to the use of the approximation Eq.(30) and (31) of the function f(r). The WKB approximation  in this case is valid just for $R > 3M$ i.e. in case the potential has no well.
 
 \bigskip
-\qquad -  Usually we stop when the sum over the Regge poles converges.
+(iii)  Usually we stop when the sum over the Regge poles converges.
 For the background integral, its evaluation allows us to see whether it is negligible or not.
@@
 This is surprising since this is not the case in other areas of physics (acoustics, optics, electromagnetics, quantum mechanics,...), where the CAM method finds its origins, and this independently of the frequency.
+To obtain a qualitative argument and deeper understanding of the Regge pole sum convergence, and significance of the background integral is desirable as the referee points out.
+Our article is focused on a proof of concept, and we have deferred this to futher work.
+
+\bigskip\bigskip
+
+\noindent $\underline{\hbox{Summary of changes made in response to referee's comments:}}  $
+\medskip
+
+\smallskip
+(i) - Added two paragraphs in section III D (after equation 40) to discuss the limit $\alpha \rightarrow0$,  stellar models with continuous potentials at the surface, and clarifying that the analysis of this section is not applicable to black holes.
+
+\bigskip
+(ii)  At the end of paragraph 2 in section III D we have clarified that the analysis is for models with $R/M>3$, and recalled this at the end of the section.
+
+\bigskip
+(iii) Added a (penultimate) paragraph in section V expanding on comment (iii) above.
 
@@
 \smallskip
-\qquad - Do not forget to add the Ref[Sebastian H. Völkel and Kostas D. Kokkotas] :  On the Inverse Spectrum Problem of Neutron Stars.
-
-%@article{Volkel:2019gpq,
-%      author         = "Völkel, Sebastian H. and Kokkotas, Kostas D.",
-%      title          = "{On the Inverse Spectrum Problem of Neutron Stars}",
-%      journal        = "Class. Quant. Grav.",
-%      volume         = "36",
-%      year           = "2019",
-%      number         = "11",
-%      pages          = "115002",
-%      doi            = "10.1088/1361-6382/ab186e",
-%      eprint         = "1901.11262",
-%      archivePrefix  = "arXiv",
-%      primaryClass   = "gr-qc",
-%      SLACcitation   = "%%CITATION = ARXIV:1901.11262;%%"
-%}
+-Added a reference: Sebastian H. V{\"o}lkel and Kostas D. Kokkotas, `On the Inverse Spectrum Problem of Neutron Stars'.
+\bigskip
+-Corrected a couple of minor typos.
 

### 2020-04-15 referee PRD/RefereeResponse_DN12236.tex
some final edits

@@
 \bigskip 
+For the issue of continuity it is worth distinguishing between two cases: \bigskip
+
+\qquad  (a)  in our model, $\alpha \rightarrow 0$ iff $M/R \rightarrow 0$, e.g. a large dilute star. In this case the modes move close to the real axis.
+In the case $\alpha = 0$, $M/R = 0$, there is no star at all and no modes at all. (cf. singular perturbation theory).
+
+\bigskip
+
+ \qquad (b) In different stellar models (such as a polytrope) in which the potential is $C^n$ at the surface ($n \geq 0$), the imaginary part of the broad resonance branch is proportional to $(n+1)$ and in the large-$n$ limit the associated modes have large imaginary parts and little physical consequence.
+
+\bigskip
+\bigskip
 (ii) The referee is correct that the radius of the body does enter the approximation scheme in eqs 30 and 31.
-However, the Wronskain (eq.
+However, the Wronskian (eq.
 29) is evalutated at  $r_{*} \approx 1/\omega$, and thus terms of  $O(M r_{*}^2 / R^3  )$ are of  $ O \left(  (M \omega)^{-2} (M/R)^3 \right) $ and we have $M/R< 1/2$.
@@
 
+\bigskip
 \bigskip
@@
 \smallskip
-(i) - Added two paragraphs in section III D (after equation 40) to discuss the limit $\alpha \rightarrow0$,  stellar models with continuous potentials at the surface, and clarifying that the analysis of this section is not applicable to black holes.
+(i) Added two paragraphs in section III D (after eq.
+40) to discuss the limit $\alpha \rightarrow0$, different stellar models with continuous potentials at the surface, and clarifying that the analysis of this section is not applicable to black holes.
 

### 2020-04-20 rainbowCAM.tex
some final edits
correcting mistakes spotted by Sam on 17 april ready for responce

@@
 In this case, $\mathcal{R}$ and thus the broad resonance branch depends on the discontinuity in the $N$-th derivative of the potential at $r=R$.
-We do not go into detail here, but see Eq.~4.5 of Ref.
-\cite{Zhang:2011pq}.
-Recall that the above analysis is not appropriate for compact bodies with $R/M<3$ and black holes (since the effective potential has a qualitatively different structure, and the ansatz Eq.~(\ref{Approx_infinity}) is not valid ).
+It can be shown that the imaginary part of the poles is proportional to $(N+1)$ (see Eq.~4.5 of Ref.
+\cite{Zhang:2011pq}), so in the large-$N$ limit the associated modes have large imaginary parts and little physical consequence.
+
+Recall that the above analysis is not appropriate for compact bodies with $R/M<3$ and black holes (since the effective potential has a qualitatively different structure, and the ansatz Eq.~(\ref{Approx_infinity}) is not valid).
 
@@
 This is an interesting result in itself (as noted in \cite{Folacci:2019cmc,Folacci:2019vtt}) since in most CAM scattering studies the background integral is significant in geometrically illuminated regions \cite{Nussenzveig:2006}.
-\tom{Speculatively, this could be related to the long range nature of gravitational scattering by compact bodies (it is not just the body that is scattering, but the bodies extended gravitational field).
-By contrast, in acoustics, quantum mechanics, and optics [\emph{find citations}] the scatterer generally has a short range influence.}
 An asymptotic analysis is an important next step towards understanding the role of the background integral and higher Regge-pole overtones, both computationally and, in a semiclassical interpretation, physically.

### 2020-04-29 PRD proofs/ProofCorrections_DN12236(PRD).tex
added proofs and response files

\documentclass[10pt,a4paper]{report}

%\usepackage{kpfonts}
\usepackage{lmodern}
\usepackage[utf8]{inputenc}
\usepackage[french,english]{babel}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amsfonts,amssymb}

\usepackage{xcolor}

\usepackage[left=1cm,right=1cm,top=1cm,bottom=1.5cm]{geometry}

\usepackage{indentfirst}

\usepackage{academicons}
\definecolor{orcidlogocol}{HTML}{A6CE39}
\definecolor{darkbue}{rgb}{0.1,0,0.65}
\usepackage[pdftex,hidelinks]{hyperref}

%\usepackage{tikz}
%\usetikzlibrary{scopes}

\begin{document}

% \thispagestyle{empty}

\noindent {\bf MANUSCRIPT DN12236.hadj (PRD)}

\bigskip

\noindent {\bf Title: Scattering from compact objects: Regge poles and the complex angular momentum method}

\medskip
\noindent {\bf Authors: }\\
Mohamed Ould El Hadj \hspace{10pt} \href{https://orcid.org/0000-0002-8558-7992}{\textcolor{orcidlogocol}{ORCID :    }\textcolor{darkbue}{https://orcid.org/0000-0002-8558-7992}}\\
Tom Stratton \hspace{55pt}  \href{https://orcid.org/0000-0002-2936-5404}{\textcolor{orcidlogocol}{ORCID :    }\textcolor{darkbue}{https://orcid.org/0000-0002-2936-5404}}\\
Sam R. Dolan \hspace{53pt} \href{https://orcid.org/0000-0002-4672-6523}{\textcolor{orcidlogocol}{ORCID :    }\textcolor{darkbue}{https://orcid.org/0000-0002-4672-6523}}

\bigskip

\bigskip
\bigskip

\bigskip
\noindent {\bf Corrections corresponding to ``Specific Questions and
Comments to Address for This Paper''}

\bigskip
\noindent [A] - Item Q: All references include complete titles.

\bigskip
\noindent [B] - Item 1: WKB is an abbreviation in common use for more than half a century and accepted by PRD.

\bigskip
\noindent [C] - Item 2: Ok.

\bigskip
\noindent [D] - Item 3: Ok.

\bigskip
\noindent [E] - Item 4: Ok.

\bigskip
\bigskip

\bigskip
\noindent {\bf Other corrections in the text}

\bigskip
\noindent [I] - Line 725: ``\ldots CAM formulas to calculated scattering\ldots'' has to be changed into ``\ldots CAM formulas to calculate scattering \ldots''.

\bigskip\bigskip\bigskip\bigskip\bigskip

%\bigskip
%\noindent {\bf Important remark: We would like to check the new version before publication in PRD.}
%\bigskip

\noindent We thank you for your careful editing of our manuscript.

\noindent  M.O.E.H., T.S and S.R.D

\end{document}

### 2020-05-19 rainbowCAM.tex
v2: Typos corrected and minor changes in the text to match the published version

@@
 
-\title{Scattering from compact objects: \\ Regge poles and the Complex Angular Momentum method}
+\title{Scattering from compact objects: \\ Regge poles and the complex angular momentum method}
 
@@
 We calculate the Regge poles of the scattering matrix for a gravitating compact body, for scalar fields and for gravitational waves in the axial sector.
-For a neutron-star-like body, the spectrum exhibits two distinct branches of poles, labelled surface waves and broad resonances; for ultra-compact objects, the spectrum also includes a finite number of narrow resonances.
+For a neutron-starlike body, the spectrum exhibits two distinct branches of poles, labeled surface waves and broad resonances; for ultracompact objects, the spectrum also includes a finite number of narrow resonances.
 We show, via a WKB analysis, that the discontinuity of the effective potential at the body's surface determines the imaginary component of the broad-resonance poles.
@@
 Next, we examine the role of Regge poles in the time-independent scattering of monochromatic planar waves.
-We apply Complex Angular Momentum techniques to re-sum the partial wave series for the scattering amplitude, expressing it as a residue series evaluated at poles in the first quadrant, accompanied by a background integral.
+We apply complex angular momentum techniques to re-sum the partial wave series for the scattering amplitude, expressing it as a residue series evaluated at poles in the first quadrant, accompanied by a background integral.
 We compute the scattering cross section at several frequencies, and show precise agreement with the partial-wave calculations.
@@
 The time-independent scattering of planar waves in the gravitational field of a compact body has been studied in some detail since the 1960s \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970}.
-A substantial literature has accumulated on \emph{black hole scattering}, focussing on the canonical scenario of a planar wave of circular frequency $\omega$ and spin $s$ \cite{Chrzanowski:1976jb} impinging upon a black hole of mass $M$ in vacuum \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970, Mashhoon:1973zz,Fabbri:1975,Sanchez:1977vz,MatznerRyan1978,Handler:1980un,Matzner:1985rjn,Futterman:1988ni,Andersson:1995vi,Glampedakis:2001cx,Dolan:2006vj,Dolan:2007ut,Dolan:2008kf,Crispino:2009xt,Cotaescu:2014jca,Gussmann:2016mkp}.
+A substantial literature has accumulated on \emph{black hole scattering}, focusing on the canonical scenario of a planar wave of circular frequency $\omega$ and spin $s$ \cite{Chrzanowski:1976jb} impinging upon a black hole of mass $M$ in vacuum \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970, Mashhoon:1973zz,Fabbri:1975,Sanchez:1977vz,MatznerRyan1978,Handler:1980un,Matzner:1985rjn,Futterman:1988ni,Andersson:1995vi,Glampedakis:2001cx,Dolan:2006vj,Dolan:2007ut,Dolan:2008kf,Crispino:2009xt,Cotaescu:2014jca,Gussmann:2016mkp}.
 A dimensionless parameter
@@
 encapsulates the ratio of the gravitational radius $r_g = 2GM/c^2$ to the wavelength $\lambda$; herein we adopt geometric units such that $G=c=1$.
-The long-wavelength ($M \omega \ll 1$), short-wavelength ($M \omega \gg 1$) and intermediate regimes have been studied with a combination of perturbative \cite{DeLogi:1977dp,Dolan:2007ut,Guadagnini:2008ha,Sorge:2015yoa}, semi-classical \cite{Matzner:1985rjn, Anninos:1992ih} and numerical methods.
+The long-wavelength ($M \omega \ll 1$), short-wavelength ($M \omega \gg 1$) and intermediate regimes have been studied with a combination of perturbative \cite{DeLogi:1977dp,Dolan:2007ut,Guadagnini:2008ha,Sorge:2015yoa}, semiclassical \cite{Matzner:1985rjn, Anninos:1992ih} and numerical methods.
 The $s = 0$ (scalar) \cite{Matzner:1968,Sanchez:1977vz,Andersson:1995vi,Glampedakis:2001cx,Leite:2019eis}, $s=1/2$ (fermion) \cite{Dolan:2006vj,Cotaescu:2014jca}, $s=1$ (electromagnetic) \cite{Fabbri:1975, Crispino:2009xt, Crispino:2015gua} and $s=2$ (gravitational) cases \cite{MatznerRyan1978,Handler:1980un,Dolan:2008kf} have all been addressed.
 
-Time-independent scattering by a compact body of radius $R$ with a regular centre, such as a neutron star or white dwarf, has received less attention, by comparison.
+Time-independent scattering by a compact body of radius $R$ with a regular center, such as a neutron star or white dwarf, has received less attention, by comparison.
 In such a scenario, an electromagnetic wave will not penetrate far inside the compact body; but on the other hand, a gravitational wave will pass through the body without impediment from the matter distribution.
@@
 Typical values of the tenuity are: $R/M \sim 6$ for neutron stars, $\sim 1.4-9.4 \times 10^3$ for white dwarfs, $4.7 \times 10^5$ for the Sun, and $1.4 \times 10^9$ for Earth.
-More speculatively, we shall also consider here the case of (hypothetical) \emph{ultra-compact objects} (UCOs), whose tenuity is bounded from below by the Buchdahl bound of $R / M = 9/4$.
+More speculatively, we shall also consider here the case of (hypothetical) \emph{ultracompact objects} (UCOs), whose tenuity is bounded from below by the Buchdahl bound of $R / M = 9/4$.
 
 Studies of black hole scattering typically involve the calculation of scattering amplitude(s) via partial-wave expansions.
-A powerful approach for resumming these partial-wave expansions is provided by so-called Complex Angular Momentum (CAM) techniques.
+A powerful approach for resumming these partial-wave expansions is provided by so-called complex angular momentum (CAM) techniques.
 In the CAM approach, the sum over partial waves is replaced by an integral, and the contour of integration is deformed into the complex-angular-momentum plane such that one collects a sum of residues of simple poles: these are the so-called \emph{Regge poles}.
@@
 For example, in the immediate aftermath of a black hole merger, the perturbed black hole returns to a quiescent state via a ``ringdown phase'' in which its gravitational-wave signal is well described as a sum of quasinormal modes \cite{Giesler:2019uxc}.
-The QNM spectrum of compact bodies have been well-studied by several authors  \cite{Detweiler:1985zz, Kokkotas:1986gd, Chandrasekhar449, Kokkotas:1992ka, Leins:1993zz, Andersson:1995ez, Andersson1996}, and are reviewed in Ref.~\cite{Kokkotas:1999bd}.
+The QNM spectrum of compact bodies have been well studied by several authors  \cite{Detweiler:1985zz, Kokkotas:1986gd, Chandrasekhar449, Kokkotas:1992ka, Leins:1993zz, Andersson:1995ez, Andersson1996}, and are reviewed in Ref.~\cite{Kokkotas:1999bd}.
 
@@
 The remainder of this paper is organised as follows.
-Sec.~\ref{SecII} reviews the theory of scalar waves on a spherically-symmetric spacetime of a compact object.
+Sec.~\ref{SecII} reviews the theory of scalar waves on a spherically symmetric spacetime of a compact object.
 Here we describe our model spacetime (\ref{SecIIa}), the effective potentials for wave scattering (\ref{subsec:Potentials}) and the physical boundary conditions that define the $S$-matrix (\ref{subsec:bc}).
@@
 
-Effective potentials for the incompressible model are shown in Fig.~\ref{fig:Veff}, for two cases: (i) a neutron-star model with $R = 6M$, and (ii) a ultra-compact object (UCO \cite{Macedo:2018yoi}) with $R = 2.26M$.
+Effective potentials for the incompressible model are shown in Fig.~\ref{fig:Veff}, for two cases: (i) a neutron-star model with $R = 6M$, and (ii) a ultracompact object (UCO \cite{Macedo:2018yoi}) with $R = 2.26M$.
 % (i.e.~close to the Buchdahl bound of $R/M = 9/4$).
@@
 \subsection{Boundary conditions and scattering}\label{subsec:bc}
-The modes $\phi_{\omega \ell}$ in Eq.~(\ref{eq:sepvariables}) should have a regular behaviour at the centre of the object ($r = 0$), and inspection of the radial equation (\ref{H_Radial_equation}) shows that
+The modes $\phi_{\omega \ell}$ in Eq.~(\ref{eq:sepvariables}) should have a regular behaviour at the center of the object ($r = 0$), and inspection of the radial equation (\ref{H_Radial_equation}) shows that
 \begin{equation}\label{bc_1_in}
@@
 
-The quasinormal mode spectrum of spherically-symmetric compact objects has been studied in some detail in Refs.~\cite{Kokkotas:1986gd,Kokkotas:1992ka,Andersson:1997eq,Kokkotas:1999bd,Leins:1993zz}.
-Newly-formed neutron stars, the remnants of supernovae collapse, are predicted to pulsate with a large initial energy, and fluid pulsations will generate gravitational waves.
+The quasinormal mode spectrum of spherically symmetric compact objects has been studied in some detail in Refs.~\cite{Kokkotas:1986gd,Kokkotas:1992ka,Andersson:1997eq,Kokkotas:1999bd,Leins:1993zz}.
+Newly formed neutron stars, the remnants of supernovae collapse, are predicted to pulsate with a large initial energy, and fluid pulsations will generate gravitational waves.
 In 1967, Thorne and Campolattaro \cite{thorne1967non} classified the fluid modes of a relativistic compact body by analogy with the fluid modes of a Newtonian body, with the addition of a damping time due to the emission of GWs.
@@
 It is important to note that, the \textit{continued fraction method} applies to three-term recurrence relations. Leins~\emph{et al.} and BBF use the method introduced by Leaver in
-the case of Reissner-Nordst\"om black holes \cite{Leaver:1990zz} to reduce four-term recurrence relations (as in \eqref{Recurrence_4_terms}) to three-term recurrence relations by using a Gaussian elimination step.
+the case of Reissner-Nordst\"om black holes \cite{Leaver:1990zz} to reduce four-term recurrence relations [as in \eqref{Recurrence_4_terms}] to three-term recurrence relations by using a Gaussian elimination step.
 
@@
 %
-Letting $D_n$ be the determinant of the $n \times n$ sub-matrix of $D$ (with diagonal $\{\beta_0,\beta_1,....\beta_n\}$), by \eqref{Recurrence_4_terms}
+Letting $D_n$ be the determinant of the $n \times n$ submatrix of $D$ (with diagonal $\{\beta_0,\beta_1,....\beta_n\}$), by \eqref{Recurrence_4_terms}
 %
@@
 
- \subsection{Numerical results: the spectrum}\label{subsec:results1}
-In this section we show numerical results for the Regge pole spectrum of a compact body, in two particular cases: (i) a neutron-star-like body with tenuity $R / M = 6$, and (ii) a UCO with tenuity $R / M = 2.26$, close to the Buchdahl bound.
+ \subsection{Numerical results: The spectrum}\label{subsec:results1}
+In this section we show numerical results for the Regge pole spectrum of a compact body, in two particular cases: (i) a neutron-starlike body with tenuity $R / M = 6$, and (ii) a UCO with tenuity $R / M = 2.26$, close to the Buchdahl bound.
 Results for the frequencies $M \omega = 3/2$ and $M \omega = 8$ are compared, for the scalar-field ($s=0$) and axial GW ($s=2$) cases.
 
-Figure \ref{fig:rp1} shows the Regge pole spectrum for a neutron-star-like body ($R/M = 6$).
+Figure \ref{fig:rp1} shows the Regge pole spectrum for a neutron-starlike body ($R/M = 6$).
 We see that there are two branches of Regge poles in the first quadrant, which meet near $\text{Re}( \lambda_n(\omega) ) \sim \omega b_0$, where $b_0$ is the impact parameter for the null ray which grazes the surface of the compact body.
@@
 A natural choice is to impose regularity, i.e.,~$\phi_{\omega\ell} \sim r^{-\lambda+1/2}$ as $r \rightarrow 0$ for $\text{Re} [\lambda] < 0$.
-An advantage of this choice is that it leads to the same symmetry as in the black hole case for the $S$-matrix elements (see Ref.~\cite{Andersson:1994rk,Folacci:2019cmc}), viz.,
+An advantage of this choice is that it leads to the same symmetry as in the black hole case for the $S$-matrix elements (see Refs.~\cite{Andersson:1994rk,Folacci:2019cmc}), viz.,
 \begin{equation}\label{Matrix_S_CAM_symm}
@@
 % In the latter case, the poles are given by the zeros of a combination of special functions.
-Henceforth we shall adopt the terminology of Nussenzveig \cite{Nussenzveig:2006}, in which the three branches are labelled as:
+Henceforth we shall adopt the terminology of Nussenzveig \cite{Nussenzveig:2006}, in which the three branches are labeled as:
 \begin{enumerate}
- \item \emph{Broad resonances}: approximately uniformly-spaced poles above the real axis with approximately constant imaginary part; somewhat sensitive to internal structure ($r < R$);
- \item \emph{Surface waves}: highly-damped modes that are relatively insensitive to the internal structure and which depend chiefly on the surface geometry.
+ \item \emph{Broad resonances}: approximately uniformly spaced poles above the real axis with approximately constant imaginary part; somewhat sensitive to internal structure ($r < R$);
+ \item \emph{Surface waves}: highly damped modes that are relatively insensitive to the internal structure and which depend chiefly on the surface geometry.
  \item \emph{Narrow resonances}: modes approaching the real axis corresponding to trapped modes which only appear in the UCO case ($R < 3M$).
@@
 
-Regge poles and quasinormal modes for relativistic stellar models (of which \textit{w}-modes are a sub-category for gravitational perturbations) both satisfy the same wave equation and the same boundary conditions, but with different interpretations for the angular momentum index and the frequency.
+Regge poles and quasinormal modes for relativistic stellar models (of which \textit{w}-modes are a subcategory for gravitational perturbations) both satisfy the same wave equation and the same boundary conditions, but with different interpretations for the angular momentum index and the frequency.
 Both types of pole satisfy the regularity condition at the origin~\eqref{bc_1_in} and the condition of a purely outgoing wave in the far field
@@
 
-The overtones are labelled by $n =1,2,\ldots$ and the condition $\text{Re} \, \lambda_n > 0$ leads to an upper limit for $n$ of %
+The overtones are labeled by $n =1,2,\ldots$ and the condition $\text{Re} \, \lambda_n > 0$ leads to an upper limit for $n$ of %
 \begin{equation}\label{Limit_Broad_RP}
@@
 In this case, $\mathcal{R}$ and thus the broad resonance branch depends on the discontinuity in the $N$-th derivative of the potential at $r=R$.
-It can be shown that the imaginary part of the poles is proportional to $(N+1)$ (see Eq.~4.5 of Ref.
+It can be shown that the imaginary part of the poles is proportional to $(N+1)$ (see Eq.~(4.5) of Ref.
 \cite{Zhang:2011pq}), so in the large-$N$ limit the associated modes have large imaginary parts and little physical consequence.
@@
 
-\subsection{Numerical results: scattering cross sections}
+\subsection{Numerical results: Scattering cross sections}
 \label{subsec:results2}
@@
 Figures \ref{S_0_R_6_2Mw_3_Exact_vs_CAM}, \ref{S_0_R_6_2Mw_16_Exact_vs_CAM}, \ref{S_0_R_2-dot-26_2Mw_3_Exact_vs_CAM}, \ref{S_0_R_2-dot-26_2Mw_6_Exact_vs_CAM}, \ref{Rainbow_Cross_Section_R_6_2Mw_16}, and \ref{Diff_Contribution_Cross_Section_R_2-dot-26_2Mw_6} show a selection of results for the scattering cross section $d\sigma / d\Omega$ computed with the CAM method, and compared with results from the standard partial-wave method.
-As in Sec.~\ref{subsec:results1}, we focus on two cases: a neutron-star-like object with $R/M = 6$, and an Ultra-Compact Object with $R/M = 2.26$.
+As in Sec.~\ref{subsec:results1}, we focus on two cases: a neutron-starlike object with $R/M = 6$, and an ultracompact object with $R/M = 2.26$.
 
@@
 
-Figure \ref{S_0_R_2-dot-26_2Mw_3_Exact_vs_CAM} shows the cross section for an Ultra Compact Object with $R/M = 2.26$ at the ``low'' frequency of $M \omega = 3/2$.
+Figure \ref{S_0_R_2-dot-26_2Mw_3_Exact_vs_CAM} shows the cross section for an ultracompact object with $R/M = 2.26$ at the ``low'' frequency of $M \omega = 3/2$.
 In this case, the rainbow angle exceeds $180^\circ$, and there is both a light-ring and a trapping region (see Fig.~\ref{fig:Veff}).
@@
 
-In this work, we have: (1) calculated the full spectrum of Regge poles for a compact body spacetime for the first time; (2) applied CAM theory to obtain an expression for the scattering amplitude as a residue series accompanied by a background integral, Eqs.~(\ref{CAM_Scalar_Scattering_amp_tot})--(\ref{CAM_Scalar_Scattering_amp_decomp_RP}); and (3) utilised the CAM formulae to calculated scattering cross sections numerically, demonstrating precise agreement with the numerical results of the partial-wave expansion, first computed in Ref.~\cite{Dolan:2017rtj}.
-
-The spectrum of Regge poles exhibits two distinct branches of poles in the neutron star case $R/M = 6$ (see Fig.~\ref{RP_R6_approx_2Mw_3_6_s_1}), which we have labelled ``broad resonances'' and ``surface waves''.
-Ultra-compact objects have, in addition, a third branch of ``narrow resonances'' (see Fig.~\ref{RP_R226_approx_2Mw_3_6_s_1}), linked to the existence of an effective cavity between the light-ring and the object's surface.
+In this work, we have: (1) calculated the full spectrum of Regge poles for a compact body spacetime for the first time; (2) applied CAM theory to obtain an expression for the scattering amplitude as a residue series accompanied by a background integral, Eqs.~(\ref{CAM_Scalar_Scattering_amp_tot})--(\ref{CAM_Scalar_Scattering_amp_decomp_RP}); and (3) utilised the CAM formulas to calculate scattering cross sections numerically, demonstrating precise agreement with the numerical results of the partial-wave expansion, first computed in Ref.~\cite{Dolan:2017rtj}.
+
+The spectrum of Regge poles exhibits two distinct branches of poles in the neutron star case $R/M = 6$ (see Fig.~\ref{RP_R6_approx_2Mw_3_6_s_1}), which we have labeled ``broad resonances'' and ``surface waves''.
+Ultracompact objects have, in addition, a third branch of ``narrow resonances'' (see Fig.~\ref{RP_R226_approx_2Mw_3_6_s_1}), linked to the existence of an effective cavity between the light-ring and the object's surface.
 Similar branches of poles arise in scattering by a transparent sphere, and so it is natural to adopt the terminology used to describe these branches in Mie scattering \cite{Nussenzveig:2006}.
@@
 This is an interesting result in itself (as noted in \cite{Folacci:2019cmc,Folacci:2019vtt}) since in most CAM scattering studies the background integral is significant in geometrically illuminated regions \cite{Nussenzveig:2006}.
-An asymptotic analysis is an important next step towards understanding the role of the background integral and higher Regge-pole overtones, both computationally and, in a semiclassical interpretation, physically.
+An asymptotic analysis is an important next step toward understanding the role of the background integral and higher Regge-pole overtones, both computationally and, in a semiclassical interpretation, physically.
 
